### 2018-01-09 paper.tex
Initial commit:
Started work transforming thesis into a paper

 On branch master

 Initial commit

 Changes to be committed:
	new file:   bib.bib
	new file:   paper.tex

%\documentclass[a4paper,11pt]{article}
\documentclass[fleqn,usenatbib,useAMS]{mnras}
\usepackage{amssymb}
\usepackage{natbib} % references in text to look like MNRAS/ApJ/A&A
% \usepackage{hyperref} % references become hyperlinks to bibliography
% \hypersetup{
% 	colorlinks,
% 	citecolor=black,
% 	filecolor=black,
% 	linkcolor=black,
% 	urlcolor=black
% }
\usepackage{amsmath} % align enviroment 
% \usepackage{gensymb} % degree symbol in math enviroments
\usepackage{mhchem} % typeset chemistry symbols
% \usepackage{ccaption} % for contcaption to continue figure onto multiple pages
\usepackage[flushleft, referable]{threeparttablex} % Adding notes under tables
\usepackage{multirow} % for multirow command
\usepackage{url}
\urlstyle{same}

\usepackage{array} % For wrapping text in cell in tables
% \newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}} % centered wrapped text in tables
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} %

\title{An IFS study of Low-powered Radio Galaxies}
\author[J. Warren et al.]{
Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:joshua.warren@physics.ox.ac.uk}{joshua.warren@physics.ox.ac.uk}}
Martin Bureau,$^{1}$
Bernd Hasemann,$^{2}$
Isabella Prandoni,$^{3}$ \newauthor
Francesco Santoro,$^{3}$
Robert Laing,$^{3}$
Paola Parma,$^{3}$
Hans de Ruiter$^{3}$
and Arturo Mignano$^{3}$
\\
$^{1}$Sub-department of Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, UK\\
$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. München, Germany\\
$^{3}$INAF - Istituto di Radioastronomia, Via P. Gobetti 101, 40129 Bologna, Italy}

\begin{document}
\maketitle

%\date{Oxford, \today} % date is given automatically at top of page in mnras formatting

\begin{abstract}

\end{abstract}

\section{Introduction}
	\label{sec:intro}
	% There are known to be strong scaling relations between the mass of the central supermassive black-hole (SMBH) and the global properties in a given galaxy, such as velocity dispersion, the $M-\sigma$ relation \citep{Ferrarese2000, Gebhardt2000, Graham2011}; Sersic index \citep{Graham2007, Savorgnan2013}; luminosity \citep{Laor2001, McLure2001, Lauer2007, Graham2012}; etc. AGN feedback is understood to be the mechanism by which the SMBH can expand its sphere of influence to galactic scales to affect these relationship.

	% This is generally understood to be a feedback process, where large amounts of gas within the galaxy cools, falls on the SMBH. Here the black-hole imparts energy to the gas, causing outflows (or jets) and/or thermal emission. We observe this as an Active Galactic Nuclei (AGN) which can have distinctive emission across the electromagnetic spectrum. The exact mechanisms of imparting energy still remains an open question, with much theoretical and observational work ongoing. The outflows can then effect the outer parts of the galaxy, by methods such as fountain effects \citep{}, thermal heating \citep{DeYoung2010} and shocks created by the outflows \citep{}.

	% One identifier of AGNs is a radio signature consistent with Synchrotron emission from the outflow i.e a radio galaxy (RG). These are typically categorized into one of two classes: Fanaroff-Riley (FR) I or FR II \citep{Fanaroff1974}. Of these we focus on the former since these are by far the most common mode in the local universe (possibly as far as $z \sim 1$ \citep{Rigby2008}), and so to discuss radio AGN feedback is to consider feedback from FR I sources \citep{DeYoung2010}. Indeed, while there is broad consensus \citep{Heckman1986, Baum1992} that the brightest RGs (mostly FR IIs) are caused when a massive galaxy merges with a gas rich galaxy (a wet merger) giving a plentiful fuel reservoir to the AGN \citep{Baum1992}, there is much more debate when it comes to low-powered ($P_\mathrm{1.4 GHz} \lesssim 10^{24.5} \, \mathrm{W Hz^{-1}}$) RGs (mostly FR I). Suggestions fall into two categories: an extrapolation of radio-loud galaxies (i.e. a merger with either small gas reservoirs or low efficiency accretion onto the SMBH) or a highly efficient accretion of gas from secular origins (such as Bondi accretion of the hot X-ray component of the Inter-Stellar Medium (ISM) \citep{Allen2006} or from existing cold gas reservoirs \citep{Prandoni2010}). This project aims to add to this discussion using Integral Field Unit (IFU) observations in the visible band of nearby radio galaxies and comparing this with Atlas-3D sample \citep{Cappellari2011} as a control sample.

% More to add to intro - e.g. summery of paper

\section{Sample Description}
	\label{sec:samp}

	% 	\begin{table}
	% 	\centering
	% 	\caption{Key sample selection criteria.}
	% 	\label{tab:selection}
	% 	\begin{tabular}{l c}
	% 		\hline
	% 		\hline
	% 		Declination				& $-17\degree < \delta < -40\degree$ \\
	% 		2.7\,GHz flux density 		& $S_\text{2.7GHz} \ge 0.25 \, \text{Jy} $ \\
	% 		$V$-band apparent magnitude 	& $m_V \le 17.0 $ \\
	% 		Redshift 					& $z < 0.03$ \\			
	% 		\hline
	% 		\hline
	% 	\end{tabular}
	% \end{table}

	% To study RGs in better detail, a sample of 11 galaxies in the southern hemisphere was constructed by \citet{Prandoni2010}. This sample is similar to the B2 sample of northern hemisphere RGs \citep{Prandoni2007}.

	The Parkes 2.7 GHz survey \citep{Ekers1989} was used as a parent sample, as it contains radio sources (down to a flux density limit of 250\,mJy at 2.7\,GHz) with an optical counterpart (with an $V$-band apparent magnitude of $m_V \le 17.0$). Host galaxies with a redshift greater than 0.03 were discarded. %The selection criteria are summarised in Table \ref{tab:selection}. 
	It is worth noting that both the radio and optical limits are apparent measurements, and as such this is not a volume-limited sample.

	\begin{table*}
		\centering
	\begin{threeparttable}
		\caption{Key sample characteristics of the Southern Sample galaxies.}
		\label{tab:sample}
		\begin{tabular}{l l r r r l}
			\hline
			\hline
			Host galaxy	& Radio source 	& Redshift	& $S_\text{1.4\,GHz}$	& $m_K$ & Dust morphology\\
						& (PKS) 		& 			& (mJy) 			& (mag)	&\\
			\hline 
			ESO 443-G024 & 1258-321 	& 0.01703	& $1387 \pm 45$		& 8.51 & no dust\tnote{a}	\\ 
			IC 1459 	& 2254-367 		& 0.00565 	& $1280 \pm 45$		& 6.81 & dust lane\tnote{b}	\\
			IC 1531 	& 0007-325 		& 0.02553 	& $388 \pm 12$		& 9.55 & --					\\
			IC 4296		& 1333-\leavevmode\phantom{0}33 		& 0.01248 	& $1342 \pm 41$		& 7.50 & edge-on disc\tnote{b} \\
			NGC 612 	& 0131-\leavevmode\phantom{0}36 		& 0.02954 	& $585 \pm 18$		& 9.58 & dust lane\tnote{c}	\\
			NGC 1316 	& 0320-\leavevmode\phantom{0}37 & 0.00591 	& $255 \pm 10$		& 5.59 & dust patches\tnote{b} \\
			NGC 1399 	& 0336-\leavevmode\phantom{0}35 & 0.00472 	& $209 \pm \leavevmode\phantom{0}7$	& 6.31 & no dust\tnote{b}	\\
			NGC 3100 	& 0958-314 		& 0.00879 	& $530 \pm 16$		& 8.08 & dust lane\tnote{d}	\\
			NGC 3557 	& 1107-372 		& 0.01016 	& $484 \pm 16$		& 7.203 & face-on disc\tnote{b}\\
			NGC 7075 	& 2128-388 		& 0.01819 	& $837 \pm 28$		& 9.56 & --					\\
			--			& 0718-\leavevmode\phantom{0}34 		& 0.02897 	& $1119 \pm 41$		& 9.97 & dust patches\tnote{e} \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
		\footnotesize
		\note Col.\,1: host galaxy name. Col.\,2: radio source name from Parkes Southern Radio Source Catalogue. Col.\,3: redshift. Col.\,4: National Radio Astronomy Observatory (NRAO) Very Large Array (VLA) Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}. Col.\,5: Two Micron All Sky Survey (2MASS) $K$-band apparent magnitude (with errors of $\pm 0.025$ mag; \citealt{Skrutskie2006}). Col.\,6: dust morphologies from (a) \citet{Govoni2000}, (b) \citet{Lauer2005}, (c) \citet{Bettoni2001}, (d) \citet{Sandage1979}, (e) \citet{Colbert2001}. 
		\item We hereafter refer to the last galaxy by its PKS name only.
		\end{tablenotes}
	\end{threeparttable}
	\end{table*}

	These criteria lead to a sample of 11 galaxies hereafter referred to as the Southern Sample. The key observed characteristics are summarised in Table \ref{tab:sample}.
	%, while the derived characteristics are listed in Table \ref{tab:sampleDerived}. 
	All galaxies have a FR I radio morphology according to the \citet{Fanaroff1974} scheme; the bulk of the radio emission is centrally-concentrated, as opposed to the FR II morphology where the brightest points are at the ends of the radio lobes.

	The sample was initially observed with the Atacama Pathfinder Experiment \citep[APEX; ][]{Gusten2006}, with detections claimed for the \ce{^{12}CO(2-1)} transition for all galaxies. Some galaxies had extremely large line widths (up to a full-width half-maximum of $904 \, \mathrm{km \, s^{-1}}$ for IC 4296), but most showed a flat or double-horn spectrum indicative of ordered rotation \citep{Prandoni2012}.

	% \begin{table}
	% 	\centering
	% \begin{threeparttable}[b]
	% 	\caption{Derived characteristics of the Southern Sample galaxies.}
	% 	\label{tab:sampleDerived}
	% 	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l l l l}

	% 		\hline
	% 		\hline
	% 		Host galaxy	& $M_K$ & $\log P_\text{1.4\,GHz}$ & Spectral index 	\\
	% 					& (mag)	& ([W Hz$^{-1}$])		& ([Jy][GHz]$^{-1}$) 	\\
	% 		\hline 
	% 		ESO 443-G024 & -25.86 & 24.0 				& $-0.56 \pm 0.08$	\\
	% 		IC 1459 	& -25.27 & 23.0 				& $\leavevmode\phantom{-}0.25 \pm 0.06$\tnote{a} 	\\
	% 		IC 1531 	& -25.70 & 23.9 				& $-0.33 \pm 0.03$ 	\\
	% 		IC 4296		& -26.18 & 25.4 				& $-1.52 \pm 0.27$ 	\\
	% 		NGC 612 	& -26.01 & 25.0 				& $-1.05 \pm 0.24$ 	\\
	% 		NGC 1316 	& -26.44 & 22.4 				& $-4.7\leavevmode\phantom{0} \pm 2.1\leavevmode\phantom{0}$ 	\\
	% 		NGC 1399 	& -25.25 & 22.5 				& $-0.65 \pm 0.66$ 	\\
	% 		NGC 3100 	& -24.85 & 23.0 				& $-0.40 \pm 0.03$ 	\\
	% 		NGC 3557 	& -26.08 & 23.3 				& $-0.72 \pm 0.13$ 	\\
	% 		NGC 7075 	& -24.98 & 23.9 				& $-0.90 \pm 0.06$ 	\\
	% 		PKS 0718-34 & -25.59 & 24.6 				& $-0.63 \pm 0.06$ 	\\
	% 		\hline
	% 		\hline
	% 		% Also need to correct P_1.4 values are I have changed the S_1.4 values to NVSS in tab:sample
	% 	\end{tabular*}
	% 	\begin{tablenotes}
	% 	\footnotesize
	% 	\note Col.\,1: galaxy name. Col.\,2: $K$-band absolute magnitude. Col.\,3: 1.4 GHz radio power. Col.\,4: radio spectral index (from a straight line fitted to the logarithm of all data points below 10 GHz taken from the Photometric Points tool in the Strasbourg astronomical Data Center (CDS) Portal \citealt{Wenger2000}).
	% 	\item [a] IC 1459 shows a turn over in its spectral energy distribution at $\approx 1 \, \text{GHz}$ (see Fig.\,\ref{fig:ic1459radio}) i.e.\ it is a gigahertz-peaked spectrum (GPS) galaxy. This means the spectral index is very sensitive to the frequency range over which is measured.
	% 	\end{tablenotes}
	% \end{threeparttable}
	% \end{table}

	% The sample was first set out in \citet{Prandoni2010}. The Parkes 2.7 GHz survey was used as the parent sample. This had the selection criteria of a declination range of $-14\deg < \delta < -40\deg$, flux density limit of $S_\mathrm{2.7 GHz} > 0.25 \mathrm{Jy}$ and an associated early type galaxy (ETG) host with a V-band magnitude of $m_V < 17 \mathrm{mag}$. From this parent sample, all source with the host at a redshift of $z<0.03$ were selected. This left 11 sources, which hereafter will be referred to as the Southern Sample. All display an FRI morphology with low to intermediate radio power.

	% Of this sample, 10 were observed with the APEX single dish telescope for CO, with the remaining host (NGC 1316) already observed in \citet{Horellou2001}. All were detected and results are given in \citet{Prandoni2010}. These detections (except NGC1316 and NGC1399) have since been followed up with ALMA (not yet released).

\section{Observing strategy and Data Reduction}
	\label{sec:obs}
	% \subsection{The Visible Multi-Object Spectrograph (VIMOS)}
	% 	\label{subsec:VIMOS}
	The sample was observed with the Visible Multi-Object Spectrograph (VIMOS), mounted on UT3 on the VLT in Paranal \citep{LeFevre2003}. All observations were taken with a spatial sampling of $0\farcs67$, using the high-resolution blue grism yielding a wavelength range of 3700-5520\,\AA\ with a spectral resolution of 1440 and sampling of 0.71\,\AA\,$\mathrm{pix^{-1}}$. Each object was observed with a total integration time of $\approx 100$\,min on-source, equally spread over three observing blocks (OBs). Each OB also contained all the necessary observation for standard IFS data reduction. 
		%Each OB contained 2 science exposures followed by 3 continuum lamp exposures for flatfielding and finally 1 He-Ne arc lamp exposure for wavelength calibration. In addition, the standard VIMOS calibration programme provided 5 bias exposures per night. The flux calibration was calculated using publicly available observations of the spectro-photometric standard star Feige 110 provided by ESO.

		% VIMOS has several well known, though not well understood technical issues. These include several low transmission (bad) fibers, strong flexure and large differences in sensitivity across its 4 separate detectors, known as quadrants. These are addressed by a specialist data reduction pipeline as described in Section \ref{subsec:reduct}.

		% VIMOS has several well-known though poorly-understood technical issues. These include several low transmission (bad) fibres, strong flexure and large differences in sensitivity across its 4 quadrants. These are partially dealt with using a specialist data-reduction pipeline described in Section \ref{subsec:VIMOSreduction}, with a discussion of the resulting data quality presented in Section \ref{subsec:VIMOSartefacts} (for more details see the instrument manual, Section 2.8 in the version for Observing Period 100\footnote{\url{http://www.eso.org/sci/facilities/paranal/instruments/vimos/doc.html}}).

		% Four of the sample (IC1459, IC1531, NGC1316 and NGC1399) where found to be in the archive for the Multi-Unit Spectroscoptic Explorer (MUSE). NGC1316 and NGC1399 where both observed as mosaics, while IC1459 and IC4296 where observed in single pointing. All were observed in the wide-field mode without adaptive optics. The phase 3 (pre-reduced) data products from ESO were used.

	% \subsection{VIMOS Data Reduction}
	% 	\label{subsec:reduct}
		% The data reduction pipeline was produced using \textsc{Py3D}, a suite of programs based on those developed for Califa DR1 \citep{Sanchez2011, Husemann2013} and later updated for VIMOS by \citet{Husemann2014}. This pipeline accounts for many of the known issues with VIMOS such as bad fibers and strong flexure. A brief outline is the additional steps to accounts for these is given below, while detailed descriptions can be found in \citet{Sanchez2011} for the standard reduction steps (bias subtraction, flat-fielding and wavelength and flux calibrations) and \citep{Husemann2014} for the VIMOS specific modifications. 
		% \begin{itemize}
		% \item The known bad pixels and flexure offsets are included when completing the wavelength calibration. In testing, this was found to be robust except for the blue end of the spectrum ($\lambda < 4300 \AA$) when using the blue HR grism \citep{Husemann2014}. Indeed, we found that the spectrum below the 4000\AA break was not robust and was therefore discarded.
		% \item Flexure also gives an offset to flat-fielding and while this known to be only up to $\pm0.5$pixels, this is also taken into account.
		% \item The dense packing of the fibers onto the CCD means that cross-talk is occurs and is extracted using \citep{Horne1986}. 
		% \end{itemize}
		% All of the above steps are detailed in Section 2.3 in \citet{Husemann2014}.

		% Following on from this, it was noted that the cubes where still not fully corrected. A fringe-like pattern was still observable in the spectral direction and quadrants were not calibrated to each other. These were improved by implementing a \textsc{python} version of the ad-hoc corrections given in \citet{Lagerholm2012}. This involves re-normalizing the quadrants by minimizing the difference of the integrated spectra in neighboring fibers (Q2 was held constant) followed by the removal of a fringe-like pattern, by dividing out a smoothed median spectrum from the eight surrounding fibers of any given fiber, over a scale of 150 pixels. These steps mean that the data-cubes will not be flux-calibrated, however the effect is multiplicative and thus will not effect equivalent width measurements.

		% The variance spectra is propagated throughout the data reduction pipeline to be used a noise input in the analysis (\S \ref{sec:analysis})

	VIMOS has several well-known though poorly-understood technical issues. These include several low transmission (bad) fibres, strong flexure, contamination from adjacent spectra on the CCD (cross-talk) and large differences in sensitivity across its 4 quadrants. To address these issues, we adopted a data-reduction pipeline produced using \textsc{Py3D}, a suite of programs based on the \textsc{python} versions of those developed for the Calar Alto Legacy Integral Field spectroscopy Area survey \citep[CALIFA;][]{Sanchez2012, Husemann2013} but later updated for VIMOS by \citet{Husemann2014}. \textsc{Py3D} applies all standard IFS data-reductions steps: bias subtraction, spectrum identification, flatfielding and wavelength calibration. In addition, the data was flux calibrated using publicly available observations of the spectro-photometric standard star Feige 110 provided by ESO. All steps include methods to account for the bad fibres, flexure and cross-talk within VIMOS.

	Following this, we noted that the cubes where still not properly calibrated. Three main issues remain: the quadrants have different intensities, clearly showing uncorrected throughput differences; diagonal intensity stripes are present in the reconstructed images at all wavelengths; and spectral features are observed \citep{Jullo2008} that are visually similar to fringe patterns caused by interference within the CCD between incident light and light reflected from the interfaces between layers of the CCD materials. \citet{Lagerholm2012} present ad-hoc methods to correct for these issues, which we here adopt. These additional steps mean that the datacubes are not perfectly flux-calibrated, but all the corrections are multiplicative and thus will not effect equivalent width or line ratio measurements. From comparisons to the MUSE data (see Section \ref{sec:MUSE}), we then estimate the flux calibration of the resulting datacubes.

	The variance spectra are propagated throughout the data-reduction pipeline (including these ad-hoc corrections) and are square-rooted at this point, to be used as noise inputs in the following analyses (see Section \ref{sec:analysis}).

	\subsection{MUSE Archival Data}
		\label{subsec:MUSE}
		Four of the sample galaxies are in the Multi-unit Spectroscopic Explorer (MUSE) archive: IC 1459, IC 4296, NGC 1316 and NGC 1399. We include these in our analysis as they have better (spatial and spectral) resolution and sampling, a larger field-of-view and larger wavelength range than the VIMOS data.

		We used the pre-reduced (Phase 3) datacubes from ESO. These were generally of sufficient quality for our purpose, except in both IC 1459 and IC 4296 the sky appears to have been over-subtracted. To remove this over-subtraction, we developed our own pseudo-sky subtraction routine. A median spectrum was taken from four $20 \times 20$\,spaxel regions, one in from each spatial corner of the ESO reduced cube. After checking that no stellar continuum could be fit to the medium sky spectrum (i.e.\ that very little light from the galaxy is contaminating the pseudo-sky regions), this median sky spectrum was subtracted from each spaxel in the cube.

		Finally, we trimmed all the MUSE cubes to the central $30\arcsec \times 30\arcsec$ ($150 \times 150$\,spaxels) only, to (a) avoid the regions used for the pseudo-sky spectrum and (b) reduce the computing resources required for spatial binning (see Section \ref{sec:analysis}). In any case, the bins would be so large in the outer parts as to be effectively useless (see Fig\,\ref{fig:egSNR}).

		% As stated in section \ref{subsec:MUSE}, we used the supplied, reduced data product, however it was noted that the sky for both IC1459 and IC426 had been over subtracted leading to large apparent absorption features (often with negative fluxes). To remove this over-subtraction, our own pseudo-sky subtraction routine was developed. The median spectrum was taken from four 20x20 spaxel boxes taken from each corner of the observation. After checking that no stellar continuum could be fitted to the spectrum (i.e. there was very little light from the galaxy contaminating our pseudo-sky spectrum), this spectrum was subtracted from each spaxel in the cube. The data-cubes were then trimmed to the central 30"x30" (150x150 spaxels).

\section{Data Analysis}
	\label{sec:analysis}
% 	The analysis was nearly identical for data from the two instruments. The only differences being that the MUSE cubes were binned to a high Signal to Noise ratio (S/N) and the emission lines kinematics were allowed to vary up to the fourth moment (i.e. $h_3$ and $h_4$ were allowed to vary), whilst emission line within the VIMOS data was only allow to vary to the second moment (i.e. $h_3 \, h_4 = 0$).

% 	The cube was then spatially binned using Voronoi Binning technique \citep{Cappellari2003} to a uniform Signal to Noise ratio (S/N), defined to be the ratio of the medians of the spatially integrated cube and the spatially integrated noise spectrum, of 30 for VIMOS data and 60 for MUSE data. %Below about the calcium doublet, Ca4227, the observed spectrum tended to become unresponsive and so a hard cut lower cut was applied at 4200 \AA. 
% 	When calculating total flux or any parameter dependent on total flux, only the wavelength range common to all bins was used (the quadrants have slightly different wavelength ranges), otherwise this was computed individually for each bin in order to preserve as much as information as possible.

% 	Following this the cubes were analyzed using the \textsc{pPXF} package \citep{Cappellari2004} to find a best fit spectrum by stacking the Miles empirical stellar spectra \citep{Sanchez-Blazquez2006} convolved with a line-of-sight velocity distribution (LOSVD) given by a Gaussian-like distribution, allowed to vary up to the 4th Gauss-Hermite moment (i.e. the LOSVD could be characterized by 4 parameters: recessional velocity, $v$; line-of-sight velocity dispersion, $\sigma$ and the 3rd and 4th Gauss-Hermite moments, $h_3$ and $h_4$). To allow accurate estimation of the uncertainties in these values, a simple Monty Carlo (MC) method with 1000 repeats was used. In each iteration, random noise, with an amplitude comparable to the noise propagated through the data reduction pipeline, was added to the original bestfit spectrum.

% 	In an attempt to combat template mismatch in the fitting of emission lines, we follow the recipe set out in \citet{Sarzi2005}. This is a three step process:
% 	\begin{enumerate}
% 		\item the region encompassing $\pm 300 \mathrm{km s^{-1}}$ around each emission line's rest frame wavelength is masked, and the stellar spectrum is fitted.
% 		\item The kinematics of the stellar spectrum is then fixed to the kinematics found in Step 1. The region around the [OIII] line is unmasked and fitted. In VIMOS data, the line is given just 2 free kinematic moments ($h_3 \, h_4 = 0$), whereas in MUSE data [OIII] is given 4 free moments ($h_3$ and $h_4$ are free to vary). 
% 		\item All emission lines are unmasked, but have their kinematics fixed to that found for [OIII] in Step 2. The emission lines are therefore being fitted for their amplitudes only. 
% 	\end{enumerate}

% 	All steps are repeated with the MC method described above to propagate uncertainties and include a tenth order multiplicative Lagrange polynomial to account for continuum emission. An emission line measurement is only considered a detection using the Amplitude to Noise (A/N, defined as the median noise in the region $\pm 300 \mathrm{km s^{-1}}$). For [OIII], a measurement was considered a detection if $(\mathrm{A/N})_\mathrm{[OIII]} \ge 4$; for all other lines, i, except [NI], a detection was recorded if [OIII] was detected in the same bin and if $(\mathrm{A/N})_\mathrm{i} \ge 3$; while a detection of [NI] required a detection of H$_\beta$ and $(\mathrm{A/N})_\mathrm{[N.I]} \ge 4$. This is in keeping with \citet{Sarzi2005}. In the VIMOS data, H$_\mathrm{\delta}$ is detected in 3/10 galaxies and [NI] is redshifted out of the spectral range is 3/10 galaxies.

% 	A short MCMC code was used to establish initial guesses for each galaxy of recessional velocity (redshift) and $\sigma$ (this routine uses course measurements of redshift taken from SIMBAD \citep{Wenger2000} for its own initial guess and $\sigma = 200 \mathrm{km s^{-1}}$).

% 	%In this way the [OIII] doublet, H$_\mathrm{\beta}$, H$_\mathrm{\gamma}$, H$_\mathrm{\delta}$ and [NI] emission lines are included in the fit. A fourth order additive Legendre polynomial was allowed as a free parameter to correct for the continuum shape. A short MCMC code was used to establish initial guesses for each galaxy of recessional velocity (redshift) and $\sigma$ (this routine uses course measurements of redshift taken from SIMBAD \citep{Wenger2000} for its own initial guess and $\sigma = 200 \mathrm{km s^{-1}}$).

% 	%Ionized gas detection was treated in a similar way to \citet{Sarzi2005}: only if an amplitude to noise ratio of greater than 4 was observed for the given bin would the detection be included. H$_\mathrm{\delta}$ is detected in 3/10 galaxies and [NI] is redshifted out of the spectral range is 3/10 galaxies.

% 	% To make use of the extended wavelength range of MUSE over VIMOS, the emission lines, [NII], [OI], [SII] and H$_\mathrm{\alpha}$, were also fitted alongside [OIII], H$_\mathrm{\beta}$, H$_\mathrm{\gamma}$, H$_\mathrm{\delta}$ and [NI], as in the VIMOS cubes. This allows the use the Baldwin, Phillips and Terlevich (BPT) diagrams to map the dominant source of ionization (see section \ref{subsec:BPT}).

\section{Kinematics}
	\label{sec:kine}
	% The kinematics of the sample are classified according to the Regular-Rotator/Non Regular-Rotator (RR/NRR) regime given in \citet{Krajnovic2011}, Fast/Slow Rotator (FR/SR) regime given in \citet{Cappellari2016} (originally defined by \citet{Emsellem2011}, but later refined by \citet{Cappellari2016}). Beyond this attempts have been made to use the kinematic features as defined in \citet{Krajnovic2011}, however the quality of the data has meant that many have had to be classified by eye as the artifacts from the VIMOS quadrants confuse any ellipse fitting methods.

	% The following briefly describe the observations and results of each of the sample. %It is also worth noting that many maps have been clipped in the color axis, to allow the more detailed structures to not be overwhelmed by the extremes.

	% \textbf{IC 1459} is known to contain a KDC. This is clearly seen in both the VIMOS and MUSE velocity maps (Fig. \ref{fig:stellar_vel}, \ref{fig:MUSEstellar_vel}). It is also known to have ionized gas counter rotating to the decoupled core. This is again seen by comparing Fig. \ref{fig:stellar_vel} with \ref{fig:gas_vel} and \ref{fig:MUSEstellar_vel} with \ref{fig:MUSEgas_vel}. From the MUSE velocity maps it can be seen that the gas is not coupled to the outer parts of the galaxy either. The KDC appears to be embedded in a slow rotator, though the KDC contaminates the $\lambda_{Re}$ measurement such that it is classified as a Fast Rotator. This is consistent with Section \ref{subsec:KDCsize}.

	% \textbf{IC 1531} seems to contain a KT. This galaxy has a very limited detection of ionized gas concentrated in the center (with the exception of [NI] (Fig. \ref{fig:NI_eqW}), which is more dispersed).

	% \textbf{IC 4296} appears to have KT, though this may be a quadrant feature. There is potentially 2 peaks in all of the gas intensity maps, one at the center of the galaxy and one to the south-east which is not seen in the image (total flux/collapsed cube).

	% \textbf{NGC 0612} has a large dust lane to the east of the apparent center of the galaxy perpendicular to the axis of rotation. The dust lane is also seen as a lower velocity dispersion (Fig \ref{fig:stellar_sigma}). Dust lanes generally imply a disky galaxy: indeed this seems to be the case here as the dust lane is aligned with the plane of the disk. The kinematic maps show NF. The dust lane also contains large amounts of gas.

	% \textbf{NGC1316} (Fornax A) was not observed with VIMOS, however the MUSE maps show it to have a clear rotation signature (Fig. \ref{fig:MUSEstellar_vel}), though disturbed kinematics (e.g. Fig. \ref{fig:MUSEstellar_sigma}). The ionized gas is very clumpy and has no rotation (Fig. \ref{fig:MUSEgas_vel}).

	% \textbf{NGC 1399}, the central galaxy of the Fornax Cluster \citep{Jordan2007}, is known to have kinematic twist (see MUSE map in \citet{Zieleniewski2017}) on the scale of our MUSE field of view (reduced to 30"). Very little ionized gas was detected.

	% \textbf{NGC 3100} is has NF in the stellar kinematics, however there is significant amount of ionized gas, which seems to be split into two clouds. This is most obviously seen in Fig. \ref{fig:Hbeta_eqW}. The gas also seems to have a non-standard rotation, possibly linked to its spacial distribution.

	% \textbf{NGC 3557} is known to be FR with very high velocities, especially considering it's size, with NF. In our maps, there some significant quadrant effects. NGC 3557 also has a very dispersed, non-centrally concentrated H$_\mathrm{\beta}$ distribution.

	% \textbf{NGC 7075} appears to have NF, though with quite slow velocities. There is some H$_\mathrm{\beta}$ detected at the very center of the galaxy.

	% \textbf{PKS 0718-34} is a KDC, though S/N issues mean that as in IC 1459, the galaxy cannot be seen beyond the core. It has very little gas detected, though the often faint $H_\mathrm{\delta}$ line is detected. [NI] is redshifted out of the VIMOS spectral range.

	% \textbf{ESO 443-G024} is consistent with a NR. It has a very dispersed H$_\mathrm{\beta}$ (similar to NGC 3557 (Fig. \ref{fig:Hbeta_eqW})).

	% \subsection{In/Out-flows}
	% 	\label{subsec:inflows}

\section{Absorption Line Strengths and Stellar Populations}
	\label{sec:stellarPop}
	% Absorption line strengths were measured using \textsc{python} code developed by \_\_\_\_\_\_. We use the bandpasses defined in \_\_\_\_\_\_.

	% We measure the line strengths in several steps:
	% \begin{enumerate}
	% 	\item Firstly we subtracted any fitted emission lines from the spectra and de-redshift to the rest frame. This included removing emission lines that we did not consider a detection. The spectrum is then convolved to a FWHM of 8.4\AA in order to match the LIS system \citep{Vazdekis2010}. The absorption line strengths of this stellar-only spectra was measured. This is the principle observation, $EW_{i,obs}$.
	% 	\item From the reported weightings of the stellar templates (and multiplicative polynomials) we built a spectra that is unconvolved with the LOSVD, which we measure the line strength for. This is the unconvolved bestfit and the measured line strengths are $EW_{i,unc}$.
	% 	\item We measure the line strengths for the best-fitting spectrum (with emission lines subtracted and de-redshifted). This is the convolved bestfit with line strengths being $EW_{i,con}$.
	% 	\item Finally, we use the ratio of the line strengths of the unconvolved and convolved bestfits as a correction factor for velocity dispersion. 
	% \end{enumerate}
	% The final value is therefore:
	% \begin{equation}
	% EW_i = \frac{EW_{i, unc}}{EW_{i, con}} EW_{i, obs}
	% \end{equation}

	% To test the routine we measured the absorption line strength for the SAURON project \citep{Kuntschner2006} galaxies within a radius of $R_e/8$ and compare to the measurements found by \citet{Vazdekis2010}. We found a mean difference of 0.29 \AA and a spread of 0.61 \AA between our measurements and \citet{Vazdekis2010}.

	% \begin{table}
	% 	\caption{Comparisons to the literature}
	% 	\label{tab:litAbsorption}
	% 	\begin{tabular}{c c c c}
	% 		\hline
	% 		\hline
	% 		Index 		& N$_{gals}	& Offset 	& Dispersion \\
	% 					& 			& $\AA$		& $\AA$ \\
	% 		\hline
	% 		\multicolumn{4}{c}{\citet{Vazdekis2010}} \\
	% 		\hline
	% 		H$_\beta$ 	& 46		& -0.02		& 0.25	\\
	% 		Fe5015		& 46		& 0.66		& 0.34	\\
	% 		Mg$_b$ 		& 46		& 0.06		& 0.33	\\
	% 		\hline
	% 		\multicolumn{4}{c}{\citet{Rampazzo2005} (VIMOS)}
	% 		\hline
	% 		G4300 		& 3 		& 			& \\
	% 		Fe4383 		& 3 		& 			& \\
	% 		Ca4455 		& 3 		& 			& \\
	% 		Fe4531 		& 3 		& 			& \\
	% 		H$_\beta$ 	& 3 		& 			& \\
	% 		Fe5015 		& 3 		& 			& \\
	% 		Mg$_b$ 		& 3 		& 			& \\
	% 		\hline
	% 		\multicolumn{4}{c}{\citet{Rampazzo2005} (MUSE)}
	% 		\hline

	% 		\hline
	% 	\end{tabular}
	% \end{table}

% \section{Discussion}
% 	\label{sec:discuss}
% 	\subsection{Selection Bias}
% 	\label{subsec:bias}
% 	It was originally intended that this sample should be volume limited, however the selection criteria for the parent sample \citep{Ekers1989} are based on apparent qualities rather than absolute (radio flux density and apparent V-band apparent magnitude). The effect is shown as redshift bias in figure \ref{fig:redshift_bias}. This shows a clear redshift dependence in $P_\mathrm{2.7 GHz}$ as well as (with the exception of NGC 612, a known radio galaxy anomaly) a bias towards low redshift for higher $\lambda_{Re}$. Interestingly, though $M_k$ is well spread in redshift.

% 	\subsection{BPT}
% 	\label{subsec:BPT}
% 	The BPT diagrams can be useful diagnostics for the dominant source of ionization. In the age of the IFU, the diagrams can be used in a spatially resolved manner to produce maps of ionizing source.

% 	It is worth taking a moment to

% 	Much of the current literature use the BPT diagram as an absolute diagnostic tool, were everything below the \_\_\_\_\_\_\_\_\_\_ line is assumed to be entirely due to star formation, while everything above both the \_\_\_\_\_\_ and the \_\_\_\_\_ lines is due to a Seyfert 2 type AGN, and the remaining region is due to a LINER type AGN. This is not how it was originally intended to be used. In fact the \_\_\_\_\_\_\_\_ line marks the upper limit of where star formation \textit{could} be the sole source of ionization. Above the \_\_\_\_\_ line is where an AGN \textit{could} be the sole source of ionization. The region between is where is were either \textit{could} be the sole source of ionization.

% 	\subsection{KDC stellar populations}
% 	\label{subsec:KDCsize}
% 	The relationship between the size of a KDC, it's age and the properties of the host galaxy was first set out in \citet{McDermid2006}. Here is was found that two populations of KDCs existed: the first was very small, but could be any age, and was typically embedded in a fast rotator host. The second was any size, but old, and was embedded in a slow rotator.

% 	Figure \ref{fig:KDCsize} shows all KDCs in our sample fit the relationship found by the SAURON group: they are all large and old. This adds weight to the suggestion that they are embedded in intrinsically slow rotators. Given the distance of our objects, we lack the resolution to properly resolve the small KDCs with in the fast rotators, despite the fast rotators being biased to be observed at a lower redshift.

% \section{Conclusion}
% 	\label{sec:conc}
% 	We have presented the VIMOS and MUSE observations of our sample of low-powered radio galaxies. We find a diverse range of kinematic features and classifications as well as varying detection rates in both brightness and extent.

\section*{Acknowledgments}
% \addcontentsline{toc}{section}{Acknowledgments} % add to contents - not sure if MNRAS want this...

%\FloatBarrier
\bibliographystyle{mnras}

\bibliography{bib}{}

\appendix

% \input{appendix.tex}

\end{document}

### 2018-01-10 paper.tex
Continued with work on paper
 On branch master
 Changes to be committed:
	modified:   paper.tex

@@
 \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} % 
+\newcommand{\bracket}[1]{[#1]} % to be able to use [] in arguments
 
@@
 
-		% As stated in section \ref{subsec:MUSE}, we used the supplied, reduced data product, however it was noted that the sky for both IC1459 and IC426 had been over subtracted leading to large apparent absorption features (often with negative fluxes).
-To remove this over-subtraction, our own pseudo-sky subtraction routine was developed.
-The median spectrum was taken from four 20x20 spaxel boxes taken from each corner of the observation.
-After checking that no stellar continuum could be fitted to the spectrum (i.e.
-there was very little light from the galaxy contaminating our pseudo-sky spectrum), this spectrum was subtracted from each spaxel in the cube.
-The data-cubes were then trimmed to the central 30"x30" (150x150 spaxels).
-
 \section{Data Analysis}
 	\label{sec:analysis}
-% 	The analysis was nearly identical for data from the two instruments.
-The only differences being that the MUSE cubes were binned to a high Signal to Noise ratio (S/N) and the emission lines kinematics were allowed to vary up to the fourth moment (i.e.
-$h_3$ and $h_4$ were allowed to vary), whilst emission line within the VIMOS data was only allow to vary to the second moment (i.e.
-$h_3 \, h_4 = 0$).
+	From this point on, the VIMOS and MUSE datasets are treated almost identically, the only difference (other than the different spectral ranges and resolutions) being that the MUSE datacubes are spatially binned to a higher signal-to-noise ratio (S/N) using Voronoi binning\footnote{\url{http://www-astro.physics.ox.ac.uk/~mxc/software/}} \citep{Cappellari2003}.
+For our purposes, we define the `signal' and `noise' of each spaxel as the median value of its spectrum and noise spectrum, respectively.
+We require a S/N of 30 for all VIMOS datacubes and 50 for the IC 1459 and IC 4296 MUSE datacubes.
+The NGC 1316 and NGC 1399 MUSE datacubes were binned to a S/N of 50 for the analysis of the stellar kinematics and 100 for the analysis of the emission line kinematics and stellar populations.
+
+	% Identify the relevant stellar templates, by fitting the entire galaxy spectrum (obtained by summing all galaxy spectra) with all the templates from the Medium-resolution Issac Newton Telescope (INT) Library of Empirical Spectra (MILES) library, and hereafter using only the non-zero weight templates.
+
+	Next we implement a routine to find optimal initial guesses of the redshift and velocity dispersion for each galaxy, to be used when fitting individual bins, by means of iterative fits to the spatially collapsed (i.e.
+summed across both spatial dimensions of the datacube) spectrum.
+We use the penalized-fitting (\textsc{pPXF}) routine\footnote{\url{http://www-astro.physics.ox.ac.uk/~mxc/software/}} of \citet{Cappellari2004} and \citet{Cappellari2016a} with the Medium-resolution Issac Newton Telescope (INT) Library of Empirical Spectra (MILES) library \citep{Sanchez-Blazquez2006, Falcon-Barroso2011a} to find the best-fitting line-of-sight velocity distribution (LOSVD; as parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion).
+The final mean velocity of a given galaxy, is used as its precise spectroscopic redshift and is given in Table \ref{tab:sample}.
+Beyond this point, each bin is analysed independently.
+
+	\subsection{Stellar Kinematics}
+		\label{subsec:starKin}
+		% Find the best-fitting line-of-sight velocity distribution (LOSVD; as parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion) of the stellar and ionized gas components in each bin, using a Monte--Carlo method to estimate the uncertainties on the measurements.
+
+		% Each one is processed through \textsc{pPXF} using only the MILES templates with non-zero weights identified above, using the redshift and velocity dispersion estimates from the last step as initial guesses.
+Again, r
+
+		Each bin is fit independently again using \textsc{pPXF} with the MILES library.
+For the fit regions around potential emission lines are masked, and a fourth order polynomial additive continuum correction is used.
+A Monte--Carlo (MC) estimate of the uncertainties is used.
+
+		%, with 1000 repetitions is used, whereby in each iteration (after the first), random noise is added to the best-fitting model from the first run, distributed with a Gaussian profile of width equal to the noise in the spectrum (as propagated through the data reduction pipeline).
+The standard deviation of the best-fitting parameters from these 1000 iterations are then adopted as the best-fitting uncertainties.
+
+	\subsection{Ionized Gas Distribution and Kinematics}
+		We fit the ionized gas fluxes and kinematics from the emission lines listed in Table \ref{tab:EmissionLine}, using Gaussian templates are used to independently fit emission lines from the interstellar medium (ISM), with a single LOSVDs, independently of the stellar kinematics.
+However, to minimize template mismatch, whereby emission lines are erroneously fitted to the edges of badly modeled and thus subtracted absorption features, we follow the method set out in \citet{Sarzi2005}, whereby the stellar component is first fitted as above with masked potential emission line regions, followed by the unmasking and fitting of the [\ion{O}{iii}] doublet which sets the kinematics for all the emission lines and finally the amplitude of the remaining emission lines.
+Some of the forbidden emission lines have the ratio of their amplitudes fixed (see Table \ref{tab:EmissionLine}, Col.\,4).
+
+		\begin{table}
+	 		\centering
+	 	\begin{threeparttable}
+	 		\caption{Emission lines considered in the \textsc{pPXF} fits.}
+	 		\label{tab:EmissionLine}
+	 		\begin{tabular}{l c c c}
+	 		\hline
+	 		\hline
+	 		Emission & Rest-frame & Doublet rest-frame & Amplitude  \\
+	 		Line & wavelength & wavelength & ratio \\
+	 		 & (\AA) & (\AA) \\
+	 		\hline
+	 		\bracket{\ion{O}{ii}} 	& 3726.03 & 3728.82 & Free \\
+	 		H\,$\delta$ 	& 4101.76 & -- & -- \\
+	 		H\,$\gamma$ 	& 4340.47 & -- & -- \\
+	 		H\,$\beta$ 		& 4861.33 & -- & -- \\
+	 		\bracket{\ion{O}{iii}}	& 4958.92 & 5006.84 & 0.35 \\
+	 		\bracket{\ion{N}{i}} 	& 5199.36 & 5201.86 & 0.65 \\
+	 		\bracket{\ion{O}{i}} 	& 6300.30 & 6363.67 & 0.33 \\
+	 		\bracket{\ion{N}{ii}} 	& 6548.03 & 6583.41 & 0.34 \\
+	 		H\,$\alpha$ 	& 6562.30 & -- & -- \\
+	 		\bracket{\ion{S}{ii}} 	& 6716.47 & 6730.85 & Free \\
+	 		\hline
+	 		\hline
+	 		\end{tabular}
+	 		\begin{tablenotes}
+	 		\note Col\,1: Emission line name.
+Col\,2: Emission line rest-frame wavelength.
+Col\,3: Doublet rest-frame wavelength for forbidden lines.
+Col\,4: The fixed ratio of the amplitudes of the lines within a doublet.
+`Free' indicates the amplitudes of both doublet constituents are fit independently of each other.
+	 		\end{tablenotes}
+	 	\end{threeparttable}
+	 	\end{table}
+
+	\subsection{Absorption Line Strengths and Stellar Populations}
+		\label{subsec:absorption}
+		Remove the fitted emission lines and measure the absorption line strengths in each bin. % include corrections
+
+		\subsubsection{Best-fitting Stellar Populations}
+			\label{subsubsec:stellarPop}
+			Identify the best-fitting stellar population model in each bin using the measured absorption line strengths.
+
+	For each galaxy (i.e.\ each combined cube), the data analysis process can summed up as follows, each step being detailed below.
 

### 2018-01-11 paper.tex
EoDC: Futher work to methods sections of paper
Have finished methods (data reduction and analysis).

 On branch master
 Changes to be committed:
	modified:   paper.tex
	renamed:    bib.bib -> refs.bib#

@@
 \newcommand{\bracket}[1]{[#1]} % to be able to use [] in arguments
+
+\defcitealias{Thomas2010}{TMJ} % TMJ alias
 
@@
 	\label{sec:samp}
-
-	% 	\begin{table}
-	% 	\centering
-	% 	\caption{Key sample selection criteria.}
-	% 	\label{tab:selection}
-	% 	\begin{tabular}{l c}
-	% 		\hline
-	% 		\hline
-	% 		Declination				& $-17\degree < \delta < -40\degree$ \\
-	% 		2.7\,GHz flux density 		& $S_\text{2.7GHz} \ge 0.25 \, \text{Jy} $ \\
-	% 		$V$-band apparent magnitude 	& $m_V \le 17.0 $ \\
-	% 		Redshift 					& $z < 0.03$ \\			
-	% 		\hline
-	% 		\hline
-	% 	\end{tabular}
-	% \end{table}
-
-	% To study RGs in better detail, a sample of 11 galaxies in the southern hemisphere was constructed by \citet{Prandoni2010}.
-This sample is similar to the B2 sample of northern hemisphere RGs \citep{Prandoni2007}.
-
 	The Parkes 2.7 GHz survey \citep{Ekers1989} was used as a parent sample, as it contains radio sources (down to a flux density limit of 250\,mJy at 2.7\,GHz) with an optical counterpart (with an $V$-band apparent magnitude of $m_V \le 17.0$).
 Host galaxies with a redshift greater than 0.03 were discarded.
-%The selection criteria are summarised in Table \ref{tab:selection}.
 It is worth noting that both the radio and optical limits are apparent measurements, and as such this is not a volume-limited sample.
@@
 
-	% \begin{table}
-	% 	\centering
-	% \begin{threeparttable}[b]
-	% 	\caption{Derived characteristics of the Southern Sample galaxies.}
-	% 	\label{tab:sampleDerived}
-	% 	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l l l l}
-
-	% 		\hline
-	% 		\hline
-	% 		Host galaxy	& $M_K$ & $\log P_\text{1.4\,GHz}$ & Spectral index 	\\
-	% 					& (mag)	& ([W Hz$^{-1}$])		& ([Jy][GHz]$^{-1}$) 	\\
-	% 		\hline 
-	% 		ESO 443-G024 & -25.86 & 24.0 				& $-0.56 \pm 0.08$	\\
-	% 		IC 1459 	& -25.27 & 23.0 				& $\leavevmode\phantom{-}0.25 \pm 0.06$\tnote{a} 	\\
-	% 		IC 1531 	& -25.70 & 23.9 				& $-0.33 \pm 0.03$ 	\\
-	% 		IC 4296		& -26.18 & 25.4 				& $-1.52 \pm 0.27$ 	\\
-	% 		NGC 612 	& -26.01 & 25.0 				& $-1.05 \pm 0.24$ 	\\
-	% 		NGC 1316 	& -26.44 & 22.4 				& $-4.7\leavevmode\phantom{0} \pm 2.1\leavevmode\phantom{0}$ 	\\
-	% 		NGC 1399 	& -25.25 & 22.5 				& $-0.65 \pm 0.66$ 	\\
-	% 		NGC 3100 	& -24.85 & 23.0 				& $-0.40 \pm 0.03$ 	\\
-	% 		NGC 3557 	& -26.08 & 23.3 				& $-0.72 \pm 0.13$ 	\\
-	% 		NGC 7075 	& -24.98 & 23.9 				& $-0.90 \pm 0.06$ 	\\
-	% 		PKS 0718-34 & -25.59 & 24.6 				& $-0.63 \pm 0.06$ 	\\
-	% 		\hline
-	% 		\hline
-	% 		% Also need to correct P_1.4 values are I have changed the S_1.4 values to NVSS in tab:sample
-	% 	\end{tabular*}
-	% 	\begin{tablenotes}
-	% 	\footnotesize
-	% 	\note Col.\,1: galaxy name.
-Col.\,2: $K$-band absolute magnitude.
-Col.\,3: 1.4 GHz radio power.
-Col.\,4: radio spectral index (from a straight line fitted to the logarithm of all data points below 10 GHz taken from the Photometric Points tool in the Strasbourg astronomical Data Center (CDS) Portal \citealt{Wenger2000}).
-	% 	\item [a] IC 1459 shows a turn over in its spectral energy distribution at $\approx 1 \, \text{GHz}$ (see Fig.\,\ref{fig:ic1459radio}) i.e.\ it is a gigahertz-peaked spectrum (GPS) galaxy.
-This means the spectral index is very sensitive to the frequency range over which is measured.
-	% 	\end{tablenotes}
-	% \end{threeparttable}
-	% \end{table}
-
-	% The sample was first set out in \citet{Prandoni2010}.
-The Parkes 2.7 GHz survey was used as the parent sample.
-This had the selection criteria of a declination range of $-14\deg < \delta < -40\deg$, flux density limit of $S_\mathrm{2.7 GHz} > 0.25 \mathrm{Jy}$ and an associated early type galaxy (ETG) host with a V-band magnitude of $m_V < 17 \mathrm{mag}$.
-From this parent sample, all source with the host at a redshift of $z<0.03$ were selected.
-This left 11 sources, which hereafter will be referred to as the Southern Sample.
-All display an FRI morphology with low to intermediate radio power.
-
-	% Of this sample, 10 were observed with the APEX single dish telescope for CO, with the remaining host (NGC 1316) already observed in \citet{Horellou2001}.
-All were detected and results are given in \citet{Prandoni2010}.
-These detections (except NGC1316 and NGC1399) have since been followed up with ALMA (not yet released).
-
 \section{Observing strategy and Data Reduction}
 	\label{sec:obs}
-	% \subsection{The Visible Multi-Object Spectrograph (VIMOS)}
-	% 	\label{subsec:VIMOS}
 	The sample was observed with the Visible Multi-Object Spectrograph (VIMOS), mounted on UT3 on the VLT in Paranal \citep{LeFevre2003}.
@@
 Each OB also contained all the necessary observation for standard IFS data reduction.
-		%Each OB contained 2 science exposures followed by 3 continuum lamp exposures for flatfielding and finally 1 He-Ne arc lamp exposure for wavelength calibration.
-In addition, the standard VIMOS calibration programme provided 5 bias exposures per night.
-The flux calibration was calculated using publicly available observations of the spectro-photometric standard star Feige 110 provided by ESO.
-
-		% VIMOS has several well known, though not well understood technical issues.
-These include several low transmission (bad) fibers, strong flexure and large differences in sensitivity across its 4 separate detectors, known as quadrants.
-These are addressed by a specialist data reduction pipeline as described in Section \ref{subsec:reduct}.
-
-		% VIMOS has several well-known though poorly-understood technical issues.
-These include several low transmission (bad) fibres, strong flexure and large differences in sensitivity across its 4 quadrants.
-These are partially dealt with using a specialist data-reduction pipeline described in Section \ref{subsec:VIMOSreduction}, with a discussion of the resulting data quality presented in Section \ref{subsec:VIMOSartefacts} (for more details see the instrument manual, Section 2.8 in the version for Observing Period 100\footnote{\url{http://www.eso.org/sci/facilities/paranal/instruments/vimos/doc.html}}).
-
-		% Four of the sample (IC1459, IC1531, NGC1316 and NGC1399) where found to be in the archive for the Multi-Unit Spectroscoptic Explorer (MUSE).
-NGC1316 and NGC1399 where both observed as mosaics, while IC1459 and IC4296 where observed in single pointing.
-All were observed in the wide-field mode without adaptive optics.
-The phase 3 (pre-reduced) data products from ESO were used.
-
-	% \subsection{VIMOS Data Reduction}
-	% 	\label{subsec:reduct}
-		% The data reduction pipeline was produced using \textsc{Py3D}, a suite of programs based on those developed for Califa DR1 \citep{Sanchez2011, Husemann2013} and later updated for VIMOS by \citet{Husemann2014}.
-This pipeline accounts for many of the known issues with VIMOS such as bad fibers and strong flexure.
-A brief outline is the additional steps to accounts for these is given below, while detailed descriptions can be found in \citet{Sanchez2011} for the standard reduction steps (bias subtraction, flat-fielding and wavelength and flux calibrations) and \citep{Husemann2014} for the VIMOS specific modifications.
-		% \begin{itemize}
-		% \item The known bad pixels and flexure offsets are included when completing the wavelength calibration.
-In testing, this was found to be robust except for the blue end of the spectrum ($\lambda < 4300 \AA$) when using the blue HR grism \citep{Husemann2014}.
-Indeed, we found that the spectrum below the 4000\AA break was not robust and was therefore discarded.
-		% \item Flexure also gives an offset to flat-fielding and while this known to be only up to $\pm0.5$pixels, this is also taken into account.
-		% \item The dense packing of the fibers onto the CCD means that cross-talk is occurs and is extracted using \citep{Horne1986}. 
-		% \end{itemize}
-		% All of the above steps are detailed in Section 2.3 in \citet{Husemann2014}.
-
-		% Following on from this, it was noted that the cubes where still not fully corrected.
-A fringe-like pattern was still observable in the spectral direction and quadrants were not calibrated to each other.
-These were improved by implementing a \textsc{python} version of the ad-hoc corrections given in \citet{Lagerholm2012}.
-This involves re-normalizing the quadrants by minimizing the difference of the integrated spectra in neighboring fibers (Q2 was held constant) followed by the removal of a fringe-like pattern, by dividing out a smoothed median spectrum from the eight surrounding fibers of any given fiber, over a scale of 150 pixels.
-These steps mean that the data-cubes will not be flux-calibrated, however the effect is multiplicative and thus will not effect equivalent width measurements.
-
-		% The variance spectra is propagated throughout the data reduction pipeline to be used a noise input in the analysis (\S \ref{sec:analysis})
 
@@
 
-	% Identify the relevant stellar templates, by fitting the entire galaxy spectrum (obtained by summing all galaxy spectra) with all the templates from the Medium-resolution Issac Newton Telescope (INT) Library of Empirical Spectra (MILES) library, and hereafter using only the non-zero weight templates.
-
 	Next we implement a routine to find optimal initial guesses of the redshift and velocity dispersion for each galaxy, to be used when fitting individual bins, by means of iterative fits to the spatially collapsed (i.e.
@@
 		\label{subsec:starKin}
-		% Find the best-fitting line-of-sight velocity distribution (LOSVD; as parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion) of the stellar and ionized gas components in each bin, using a Monte--Carlo method to estimate the uncertainties on the measurements.
-
-		% Each one is processed through \textsc{pPXF} using only the MILES templates with non-zero weights identified above, using the redshift and velocity dispersion estimates from the last step as initial guesses.
-Again, r
-
 		Each bin is fit independently again using \textsc{pPXF} with the MILES library.
@@
 
-		%, with 1000 repetitions is used, whereby in each iteration (after the first), random noise is added to the best-fitting model from the first run, distributed with a Gaussian profile of width equal to the noise in the spectrum (as propagated through the data reduction pipeline).
-The standard deviation of the best-fitting parameters from these 1000 iterations are then adopted as the best-fitting uncertainties.
-
 	\subsection{Ionized Gas Distribution and Kinematics}
+		\label{subsec:EmissionLines}
 		We fit the ionized gas fluxes and kinematics from the emission lines listed in Table \ref{tab:EmissionLine}, using Gaussian templates are used to independently fit emission lines from the interstellar medium (ISM), with a single LOSVDs, independently of the stellar kinematics.
@@
 		\label{subsec:absorption}
-		Remove the fitted emission lines and measure the absorption line strengths in each bin. % include corrections
+		Due to the lack of calibration observations of Lick/Cassegrain Image Dissector Scanner spectrograph system (hereafter Lick/IDS system; \citealt{Faber1985, Worthey1994}) we use the line index system (LIS) of \citet{Vazdekis2010} instead.
+This relies on flux calibrations instead of correcting to the continuum shape and wavelength dependent resolution of the Lick/IDS system.
+We use the index definitions of \citet{Trager1998}, measuring the following indices: G4300, Fe4383, Ca4455, Fe4531, H\,$\beta$, Fe5015, Mg\,b, Fe5270, Fe5335, Fe5406, Fe5709, Fe5782, NaD, TiO1 and TiO2.
+TiO1 and TiO2 are considered molecular absorption lines and are measured in magnitude units, while all others are atomic and measured in angstroms.
+
+		Quoted line strengths are corrected for both emission line and the effect of the velocity dispersion of the stars. These corrections are detailed below.
+
+		\subsubsection{Removing Emission Lines}
+			Emission lines are removed from the spectra by subtracting the best-fitting emission lines from Section \ref{subsec:EmissionLines} from the data and using only the stellar templates (and continuum correction) for reconstructing the best-fit for use in the velocity dispersion correction (see below).
+
+		\subsubection{Correcting for Stellar Velocity Dispersion}
+			We correct for the effect of the different velocity dispersions of the stars which varyingly spread absorption features such that differing fractions of the absorption is outside of the central bandpasses.
+To do this, we create a best-fitting spectrum (as in the previous step) which is \textit{not} convolved with the best-fitting LOSVD.
+A given index, $I$, is then measured for both this `unconvolved' spectrum ($I^\text{unc}$) and the convolved best-fitting spectrum ($I^\text{conv}$), and the ratio of these two indices is used as a multiplicative correction factor for the index measured ($I^\text{obs}$), such that the corrected index ($I^\text{corr}$) is given by
+			\begin{equation}
+				I^\text{corr} \equiv \frac{I^\text{unc}}{I^\text{conv}} I^\text{obs} \, .
+			\end{equation}
+			These corrected indices are those reported and discussed in the sections below.
 
@@
 			\label{subsubsec:stellarPop}
-			Identify the best-fitting stellar population model in each bin using the measured absorption line strengths.
-
-	For each galaxy (i.e.\ each combined cube), the data analysis process can summed up as follows, each step being detailed below.
-
-% 	The cube was then spatially binned using Voronoi Binning technique \citep{Cappellari2003} to a uniform Signal to Noise ratio (S/N), defined to be the ratio of the medians of the spatially integrated cube and the spatially integrated noise spectrum, of 30 for VIMOS data and 60 for MUSE data.
-%Below about the calcium doublet, Ca4227, the observed spectrum tended to become unresponsive and so a hard cut lower cut was applied at 4200 \AA.
-% 	When calculating total flux or any parameter dependent on total flux, only the wavelength range common to all bins was used (the quadrants have slightly different wavelength ranges), otherwise this was computed individually for each bin in order to preserve as much as information as possible.
-
-% 	Following this the cubes were analyzed using the \textsc{pPXF} package \citep{Cappellari2004} to find a best fit spectrum by stacking the Miles empirical stellar spectra \citep{Sanchez-Blazquez2006} convolved with a line-of-sight velocity distribution (LOSVD) given by a Gaussian-like distribution, allowed to vary up to the 4th Gauss-Hermite moment (i.e.
-the LOSVD could be characterized by 4 parameters: recessional velocity, $v$; line-of-sight velocity dispersion, $\sigma$ and the 3rd and 4th Gauss-Hermite moments, $h_3$ and $h_4$).
-To allow accurate estimation of the uncertainties in these values, a simple Monty Carlo (MC) method with 1000 repeats was used.
-In each iteration, random noise, with an amplitude comparable to the noise propagated through the data reduction pipeline, was added to the original bestfit spectrum.
-
-% 	In an attempt to combat template mismatch in the fitting of emission lines, we follow the recipe set out in \citet{Sarzi2005}. This is a three step process:
-% 	\begin{enumerate}
-% 		\item the region encompassing $\pm 300 \mathrm{km s^{-1}}$ around each emission line's rest frame wavelength is masked, and the stellar spectrum is fitted.
-% 		\item The kinematics of the stellar spectrum is then fixed to the kinematics found in Step 1.
-The region around the [OIII] line is unmasked and fitted.
-In VIMOS data, the line is given just 2 free kinematic moments ($h_3 \, h_4 = 0$), whereas in MUSE data [OIII] is given 4 free moments ($h_3$ and $h_4$ are free to vary).
-% 		\item All emission lines are unmasked, but have their kinematics fixed to that found for [OIII] in Step 2. The emission lines are therefore being fitted for their amplitudes only. 
-% 	\end{enumerate}
-
-% 	All steps are repeated with the MC method described above to propagate uncertainties and include a tenth order multiplicative Lagrange polynomial to account for continuum emission.
-An emission line measurement is only considered a detection using the Amplitude to Noise (A/N, defined as the median noise in the region $\pm 300 \mathrm{km s^{-1}}$).
-For [OIII], a measurement was considered a detection if $(\mathrm{A/N})_\mathrm{[OIII]} \ge 4$; for all other lines, i, except [NI], a detection was recorded if [OIII] was detected in the same bin and if $(\mathrm{A/N})_\mathrm{i} \ge 3$; while a detection of [NI] required a detection of H$_\beta$ and $(\mathrm{A/N})_\mathrm{[N.I]} \ge 4$.
-This is in keeping with \citet{Sarzi2005}.
-In the VIMOS data, H$_\mathrm{\delta}$ is detected in 3/10 galaxies and [NI] is redshifted out of the spectral range is 3/10 galaxies.
-
-% 	A short MCMC code was used to establish initial guesses for each galaxy of recessional velocity (redshift) and $\sigma$ (this routine uses course measurements of redshift taken from SIMBAD \citep{Wenger2000} for its own initial guess and $\sigma = 200 \mathrm{km s^{-1}}$).
-
-% 	%In this way the [OIII] doublet, H$_\mathrm{\beta}$, H$_\mathrm{\gamma}$, H$_\mathrm{\delta}$ and [NI] emission lines are included in the fit.
-A fourth order additive Legendre polynomial was allowed as a free parameter to correct for the continuum shape.
-A short MCMC code was used to establish initial guesses for each galaxy of recessional velocity (redshift) and $\sigma$ (this routine uses course measurements of redshift taken from SIMBAD \citep{Wenger2000} for its own initial guess and $\sigma = 200 \mathrm{km s^{-1}}$).
-
-% 	%Ionized gas detection was treated in a similar way to \citet{Sarzi2005}: only if an amplitude to noise ratio of greater than 4 was observed for the given bin would the detection be included.
-H$_\mathrm{\delta}$ is detected in 3/10 galaxies and [NI] is redshifted out of the spectral range is 3/10 galaxies.
-
-% 	% To make use of the extended wavelength range of MUSE over VIMOS, the emission lines, [NII], [OI], [SII] and H$_\mathrm{\alpha}$, were also fitted alongside [OIII], H$_\mathrm{\beta}$, H$_\mathrm{\gamma}$, H$_\mathrm{\delta}$ and [NI], as in the VIMOS cubes.
-This allows the use the Baldwin, Phillips and Terlevich (BPT) diagrams to map the dominant source of ionization (see section \ref{subsec:BPT}).
+			In each bin, using the measured absorption line strengths, we identify the best-fitting single stellar population (SSP) model from the models of \citeauthor{Thomas2010} (\citeyear{Thomas2010}; hereafter \citetalias{Thomas2010}) using \textsc{emcee}, a \textsc{python}, affine-invariant Markov chain Monte--Carlo (MCMC) fitting package \citep{Foreman-Mackey2013}.
+The \citetalias{Thomas2010} models are chosen because they are based on high-resolution, flux-calibrated spectra and therefore not requiring absorption line strength measurement to be in the Lick/IDS system.
 
@@
 
-\bibliography{bib}{}
+\bibliography{refs}{}
 

### 2018-01-12 paper.tex
EoDC1
Work on stellar kinematics section

 On branch master
 Changes to be committed:
	modified:   paper.tex

@@
 		\label{tab:sample}
-		\begin{tabular}{l l r r r l}
+		\begin{tabular}{l c c c c l}
 			\hline
@@
 			IC 1459 	& 2254-367 		& 0.00565 	& $1280 \pm 45$		& 6.81 & dust lane\tnote{b}	\\
-			IC 1531 	& 0007-325 		& 0.02553 	& $388 \pm 12$		& 9.55 & --					\\
+			IC 1531 	& 0007-325 		& 0.02553 	& \leavevmode\phantom{0}$388 \pm 12$		& 9.55 & --					\\
 			IC 4296		& 1333-\leavevmode\phantom{0}33 		& 0.01248 	& $1342 \pm 41$		& 7.50 & edge-on disc\tnote{b} \\
-			NGC 612 	& 0131-\leavevmode\phantom{0}36 		& 0.02954 	& $585 \pm 18$		& 9.58 & dust lane\tnote{c}	\\
-			NGC 1316 	& 0320-\leavevmode\phantom{0}37 & 0.00591 	& $255 \pm 10$		& 5.59 & dust patches\tnote{b} \\
-			NGC 1399 	& 0336-\leavevmode\phantom{0}35 & 0.00472 	& $209 \pm \leavevmode\phantom{0}7$	& 6.31 & no dust\tnote{b}	\\
-			NGC 3100 	& 0958-314 		& 0.00879 	& $530 \pm 16$		& 8.08 & dust lane\tnote{d}	\\
-			NGC 3557 	& 1107-372 		& 0.01016 	& $484 \pm 16$		& 7.203 & face-on disc\tnote{b}\\
-			NGC 7075 	& 2128-388 		& 0.01819 	& $837 \pm 28$		& 9.56 & --					\\
+			NGC 612 	& 0131-\leavevmode\phantom{0}36 		& 0.02954 	& \leavevmode\phantom{0}$585 \pm 18$		& 9.58 & dust lane\tnote{c}	\\
+			NGC 1316 	& 0320-\leavevmode\phantom{0}37 & 0.00591 	& \leavevmode\phantom{0}$255 \pm 10$		& 5.59 & dust patches\tnote{b} \\
+			NGC 1399 	& 0336-\leavevmode\phantom{0}35 & 0.00472 	& \leavevmode\phantom{0}$209 \pm \leavevmode\phantom{0}7$	& 6.31 & no dust\tnote{b}	\\
+			NGC 3100 	& 0958-314 		& 0.00879 	& \leavevmode\phantom{0}$530 \pm 16$		& 8.08 & dust lane\tnote{d}	\\
+			NGC 3557 	& 1107-372 		& 0.01016 	& \leavevmode\phantom{0}$484 \pm 16$		& 7.20 & face-on disc\tnote{b}\\
+			NGC 7075 	& 2128-388 		& 0.01819 	& \leavevmode\phantom{0}$837 \pm 28$		& 9.56 & --					\\
 			--			& 0718-\leavevmode\phantom{0}34 		& 0.02897 	& $1119 \pm 41$		& 9.97 & dust patches\tnote{e} \\
@@
 
-\section{Kinematics}
-	\label{sec:kine}
-	% The kinematics of the sample are classified according to the Regular-Rotator/Non Regular-Rotator (RR/NRR) regime given in \citet{Krajnovic2011}, Fast/Slow Rotator (FR/SR) regime given in \citet{Cappellari2016} (originally defined by \citet{Emsellem2011}, but later refined by \citet{Cappellari2016}).
-Beyond this attempts have been made to use the kinematic features as defined in \citet{Krajnovic2011}, however the quality of the data has meant that many have had to be classified by eye as the artifacts from the VIMOS quadrants confuse any ellipse fitting methods.
+\section{Stellar Kinematics}
+	\label{sec:StarKine}
+	Using the methods above, we produce stellar kinematic maps for all datacubes (shown in Section \ref{sec:Maps}).
+Here we use these maps to classify each galaxy according to the Atlas$^\text{3D}$ regular/non-regular rotator and fast/slow rotator classification schemes of \citet{Krajnovic2006} and \citet{Cappellari2016}, respectively, as well as the qualitative kinematic classes of \citet{Krajnovic2011}.
 
-	% The following briefly describe the observations and results of each of the sample.
-%It is also worth noting that many maps have been clipped in the color axis, to allow the more detailed structures to not be overwhelmed by the extremes.
+	% Ellipticity is measured as the ellipticity of the best-fitting ellipse to the surface-brightness map with an mean radius $R_\mathrm{m}$, of 1 effective radius $R_\mathrm{e}$.
+Firstly the centre of the galaxy is found as the luminosity weighted centre using the \textsc{python} routine \textsc{find\_galaxy}, which is part of the \textsc{mge} package\footnote{\url{http://www-astro.physics.ox.ac.uk/\~mxc/software/}} by \citet{Cappellari2002}.
+This is then used as an input for the \textsc{idl} routine \textsc{kinemetry}\footnote{\url{http://davor.krajnovic.org/idl/}} by \citet{Krajnovic2006} which finds the best-fitting ellipses at a range of evenly spaced semi-major axes.
+This is achieved by performing harmonic expansion of maps along ellipses with a given semi-major axis and, when used for even moments (e.g.\ surface brightness, velocity dispersion, h$_4$ etc.), minimizing the amplitude of the first and second harmonics.
+The results include the ellipticity, $\epsilon$ and position angle $PA_\text{phot}$ of the best-fitting ellipse for each semi-major axis.
+The fit is repeated for increasing semi-major axis until $<$75\% of the ellipse is not contained within the field of view.
 
-	% \textbf{IC 1459} is known to contain a KDC.
-This is clearly seen in both the VIMOS and MUSE velocity maps (Fig.
-\ref{fig:stellar_vel}, \ref{fig:MUSEstellar_vel}).
-It is also known to have ionized gas counter rotating to the decoupled core.
-This is again seen by comparing Fig.
-\ref{fig:stellar_vel} with \ref{fig:gas_vel} and \ref{fig:MUSEstellar_vel} with \ref{fig:MUSEgas_vel}.
-From the MUSE velocity maps it can be seen that the gas is not coupled to the outer parts of the galaxy either.
-The KDC appears to be embedded in a slow rotator, though the KDC contaminates the $\lambda_{Re}$ measurement such that it is classified as a Fast Rotator.
-This is consistent with Section \ref{subsec:KDCsize}.
+	% In reality, the field of view does not always contain 1 $R_\mathrm{e}$.
+Where this is the case, we follow the method by \citet{Emsellem2007}, were $R_\mathrm{m}$ is redefined as $R_\mathrm{m} \equiv \sqrt{A_\mathrm{s}/\pi}$, where $A_\mathrm{s}$ is the area of the ellipse contained within the field of view.
+For a given galaxy, we fit ellipses as described above, up to $R_\mathrm{m} = R_\mathrm{max}$, where $A_\mathrm{s}$ reaches a maximum difference if 15\% to the area of the fitted ellipse, $A_\text{ellipse}$.
+The value $\epsilon_\mathrm{e}$, the ellipticity at 1 $R_\mathrm{e}$ or $R_\text{max}$, whichever is smallest, is given in Table \ref{tab:classify}.
 
-	% \textbf{IC 1531} seems to contain a KT.
-This galaxy has a very limited detection of ionized gas concentrated in the center (with the exception of [NI] (Fig.
-\ref{fig:NI_eqW}), which is more dispersed).
+	% Misalignment
 
-	% \textbf{IC 4296} appears to have KT, though this may be a quadrant feature.
-There is potentially 2 peaks in all of the gas intensity maps, one at the center of the galaxy and one to the south-east which is not seen in the image (total flux/collapsed cube).
+	All other measurements (e.g.
+the specific angular momentum parapmeter $\lambda_\mathrm{R_e}$) and the classifications are made using the methods and critia described in the referenced literature above, with the results shown in Table \ref{tab:classify}.
 
-	% \textbf{NGC 0612} has a large dust lane to the east of the apparent center of the galaxy perpendicular to the axis of rotation.
-The dust lane is also seen as a lower velocity dispersion (Fig \ref{fig:stellar_sigma}).
-Dust lanes generally imply a disky galaxy: indeed this seems to be the case here as the dust lane is aligned with the plane of the disk.
-The kinematic maps show NF.
-The dust lane also contains large amounts of gas.
-
-	% \textbf{NGC1316} (Fornax A) was not observed with VIMOS, however the MUSE maps show it to have a clear rotation signature (Fig.
-\ref{fig:MUSEstellar_vel}), though disturbed kinematics (e.g.
-Fig.
-\ref{fig:MUSEstellar_sigma}).
-The ionized gas is very clumpy and has no rotation (Fig.
-\ref{fig:MUSEgas_vel}).
-
-	% \textbf{NGC 1399}, the central galaxy of the Fornax Cluster \citep{Jordan2007}, is known to have kinematic twist (see MUSE map in \citet{Zieleniewski2017}) on the scale of our MUSE field of view (reduced to 30").
-Very little ionized gas was detected.
-
-	% \textbf{NGC 3100} is has NF in the stellar kinematics, however there is significant amount of ionized gas, which seems to be split into two clouds.
-This is most obviously seen in Fig.
-\ref{fig:Hbeta_eqW}.
-The gas also seems to have a non-standard rotation, possibly linked to its spacial distribution.
-
-	% \textbf{NGC 3557} is known to be FR with very high velocities, especially considering it's size, with NF.
-In our maps, there some significant quadrant effects.
-NGC 3557 also has a very dispersed, non-centrally concentrated H$_\mathrm{\beta}$ distribution.
-
-	% \textbf{NGC 7075} appears to have NF, though with quite slow velocities. There is some H$_\mathrm{\beta}$ detected at the very center of the galaxy.
-
-	% \textbf{PKS 0718-34} is a KDC, though S/N issues mean that as in IC 1459, the galaxy cannot be seen beyond the core.
-It has very little gas detected, though the often faint $H_\mathrm{\delta}$ line is detected.
-[NI] is redshifted out of the VIMOS spectral range.
-
-	% \textbf{ESO 443-G024} is consistent with a NR. It has a very dispersed H$_\mathrm{\beta}$ (similar to NGC 3557 (Fig. \ref{fig:Hbeta_eqW})).
-
-	% \subsection{In/Out-flows}
-	% 	\label{subsec:inflows}
+	\begin{table*}
+		\centering
+	\begin{threeparttable}
+		\caption{Kinematic classifications}
+		\label{tab:classify}
+		\begin{tabular}{l c c c c c c c}
+			\hline
+			\hline
+			Galaxy		& $\lambda_\mathrm{R_e}$ & $\epsilon_\mathrm{e}$  & $\Gamma_\text{kin}$ & FR/SR 	& RR/NRR 	& Feature & Group 	\\
+			 & & & (deg) \\
+			\hline 
+			ESO 443-G024 & 0.048 & 0.35 & $-18\pm\leavevmode\phantom{0}2$	& SR & NRR & KDC & c \\
+			IC 1459 	& 0.125 & 0.24 & \leavevmode\phantom{0}$-3\pm\leavevmode\phantom{0}1$ & SR & NRR & KDC & c \\
+			IC 1531 	& 0.101 & 0.08 & $-54\pm25$	& FR & NRR & LV & a \\
+			IC 4296		& 0.034 & 0.03 & \leavevmode\phantom{$-0$}$8\pm12$ & SR &\leavevmode\phantom{N}RR & -- & e \\
+			NGC 612 	& 0.655 & 0.36 & \leavevmode\phantom{$-$}$12\pm\leavevmode\phantom{0}6$	& FR &\leavevmode\phantom{N}RR & -- & e \\
+			NGC 1316 	& 0.100 & 0.39 & \leavevmode\phantom{$-0$}$6\pm\leavevmode\phantom{0}2$ & FR & NRR & -- & f \\
+			NGC 1399 	& 0.090 & 0.12 & $-74\pm\leavevmode\phantom{0}5$ & SR & NRR & LV & a \\
+			NGC 3100 	& 0.354 & 0.24 & \leavevmode\phantom{0}$-8\pm\leavevmode\phantom{0}2$ & FR &\leavevmode\phantom{N}RR & -- & e \\
+			NGC 3557 	& 0.312 & 0.20 & \leavevmode\phantom{$-$}$16\pm\leavevmode\phantom{0}5$ & FR &\leavevmode\phantom{N}RR & -- & e\\
+			NGC 7075 	& 0.068 & 0.04 & \leavevmode\phantom{$-$}$36\pm50$ & SR & NRR & -- & b \\
+			PKS 718-34  & 0.159 & 0.17 & \leavevmode\phantom{$-$}$15\pm25$ & FR & NRR & KDC\tnote{a} & b\\
+			\hline
+			\hline
+		\end{tabular}
+		\begin{tablenotes}
+		\footnotesize
+		\note Col.\,1: Galaxy name.
+Col.\,2: $\lambda_\mathrm{R}$ evaluated at $R_\mathrm{e}$.
+Col.\,3: Ellipticity at $R_\mathrm{e}$.
+Col.\,4: Misalignment angle between the kinematic and photometric position angles.
+Col.\,5: Fast-/slow-rotator (FR/SR) classification.
+Col.\,6: Regular-rotator (RR) or non-regular-rotator (NRR).
+Col.\,7: Kinematic features.
+Col.\,8: Kinematic group.
+		\item [a] Tentative classification. A higher signal-to-noise ratio (S/N) in the outer regions of the field of view is required for confirmation.
+		\end{tablenotes}
+	\end{threeparttable}
+	\end{table*}
 
@@
 	\label{sec:stellarPop}
-	% Absorption line strengths were measured using \textsc{python} code developed by \_\_\_\_\_\_. We use the bandpasses defined in \_\_\_\_\_\_.
-
-	% We measure the line strengths in several steps:
-	% \begin{enumerate}
-	% 	\item Firstly we subtracted any fitted emission lines from the spectra and de-redshift to the rest frame.
-This included removing emission lines that we did not consider a detection.
-The spectrum is then convolved to a FWHM of 8.4\AA in order to match the LIS system \citep{Vazdekis2010}.
-The absorption line strengths of this stellar-only spectra was measured.
-This is the principle observation, $EW_{i,obs}$.
-	% 	\item From the reported weightings of the stellar templates (and multiplicative polynomials) we built a spectra that is unconvolved with the LOSVD, which we measure the line strength for.
-This is the unconvolved bestfit and the measured line strengths are $EW_{i,unc}$.
-	% 	\item We measure the line strengths for the best-fitting spectrum (with emission lines subtracted and de-redshifted). This is the convolved bestfit with line strengths being $EW_{i,con}$.
-	% 	\item Finally, we use the ratio of the line strengths of the unconvolved and convolved bestfits as a correction factor for velocity dispersion. 
-	% \end{enumerate}
-	% The final value is therefore:
-	% \begin{equation}
-	% EW_i = \frac{EW_{i, unc}}{EW_{i, con}} EW_{i, obs}
-	% \end{equation}
-
-	% To test the routine we measured the absorption line strength for the SAURON project \citep{Kuntschner2006} galaxies within a radius of $R_e/8$ and compare to the measurements found by \citet{Vazdekis2010}.
-We found a mean difference of 0.29 \AA and a spread of 0.61 \AA between our measurements and \citet{Vazdekis2010}.
-
-	% \begin{table}
-	% 	\caption{Comparisons to the literature}
-	% 	\label{tab:litAbsorption}
-	% 	\begin{tabular}{c c c c}
-	% 		\hline
-	% 		\hline
-	% 		Index 		& N$_{gals}	& Offset 	& Dispersion \\
-	% 					& 			& $\AA$		& $\AA$ \\
-	% 		\hline
-	% 		\multicolumn{4}{c}{\citet{Vazdekis2010}} \\
-	% 		\hline
-	% 		H$_\beta$ 	& 46		& -0.02		& 0.25	\\
-	% 		Fe5015		& 46		& 0.66		& 0.34	\\
-	% 		Mg$_b$ 		& 46		& 0.06		& 0.33	\\
-	% 		\hline
-	% 		\multicolumn{4}{c}{\citet{Rampazzo2005} (VIMOS)}
-	% 		\hline
-	% 		G4300 		& 3 		& 			& \\
-	% 		Fe4383 		& 3 		& 			& \\
-	% 		Ca4455 		& 3 		& 			& \\
-	% 		Fe4531 		& 3 		& 			& \\
-	% 		H$_\beta$ 	& 3 		& 			& \\
-	% 		Fe5015 		& 3 		& 			& \\
-	% 		Mg$_b$ 		& 3 		& 			& \\
-	% 		\hline
-	% 		\multicolumn{4}{c}{\citet{Rampazzo2005} (MUSE)}
-	% 		\hline
-
-	% 		\hline
-	% 	\end{tabular}
-	% \end{table}
-
-% \section{Discussion}
-% 	\label{sec:discuss}
-% 	\subsection{Selection Bias}
-% 	\label{subsec:bias}
-% 	It was originally intended that this sample should be volume limited, however the selection criteria for the parent sample \citep{Ekers1989} are based on apparent qualities rather than absolute (radio flux density and apparent V-band apparent magnitude).
-The effect is shown as redshift bias in figure \ref{fig:redshift_bias}.
-This shows a clear redshift dependence in $P_\mathrm{2.7 GHz}$ as well as (with the exception of NGC 612, a known radio galaxy anomaly) a bias towards low redshift for higher $\lambda_{Re}$.
-Interestingly, though $M_k$ is well spread in redshift.
-
-% 	\subsection{BPT}
-% 	\label{subsec:BPT}
-% 	The BPT diagrams can be useful diagnostics for the dominant source of ionization. In the age of the IFU, the diagrams can be used in a spatially resolved manner to produce maps of ionizing source.
-
-% 	It is worth taking a moment to
-
-% 	Much of the current literature use the BPT diagram as an absolute diagnostic tool, were everything below the \_\_\_\_\_\_\_\_\_\_ line is assumed to be entirely due to star formation, while everything above both the \_\_\_\_\_\_ and the \_\_\_\_\_ lines is due to a Seyfert 2 type AGN, and the remaining region is due to a LINER type AGN.
-This is not how it was originally intended to be used.
-In fact the \_\_\_\_\_\_\_\_ line marks the upper limit of where star formation \textit{could} be the sole source of ionization.
-Above the \_\_\_\_\_ line is where an AGN \textit{could} be the sole source of ionization.
-The region between is where is were either \textit{could} be the sole source of ionization.
-
-% 	\subsection{KDC stellar populations}
-% 	\label{subsec:KDCsize}
-% 	The relationship between the size of a KDC, it's age and the properties of the host galaxy was first set out in \citet{McDermid2006}.
-Here is was found that two populations of KDCs existed: the first was very small, but could be any age, and was typically embedded in a fast rotator host.
-The second was any size, but old, and was embedded in a slow rotator.
-
-% 	Figure \ref{fig:KDCsize} shows all KDCs in our sample fit the relationship found by the SAURON group: they are all large and old.
-This adds weight to the suggestion that they are embedded in intrinsically slow rotators.
-Given the distance of our objects, we lack the resolution to properly resolve the small KDCs with in the fast rotators, despite the fast rotators being biased to be observed at a lower redshift.
-
-% \section{Conclusion}
-% 	\label{sec:conc}
-% 	We have presented the VIMOS and MUSE observations of our sample of low-powered radio galaxies.
-We find a diverse range of kinematic features and classifications as well as varying detection rates in both brightness and extent.
 
@@
 \appendix
-
-% \input{appendix.tex}
+\section{Maps}
+	\label{sec:Maps}
 

### 2018-01-15 paper.tex
EoDC:
Integrated MNRAS template

Work on stellar kinematics section

 On branch master
 Changes to be committed:
	new file:   M_k_binned.png
	new file:   lambda_R_ellipticity.png
	modified:   paper.tex

@@
-%\documentclass[a4paper,11pt]{article}
-\documentclass[fleqn,usenatbib,useAMS]{mnras}
-\usepackage{amssymb}
-\usepackage{natbib} % references in text to look like MNRAS/ApJ/A&A
-% \usepackage{hyperref} % references become hyperlinks to bibliography
-% \hypersetup{
-% 	colorlinks,
-% 	citecolor=black,
-% 	filecolor=black,
-% 	linkcolor=black,
-% 	urlcolor=black
-% }
-\usepackage{amsmath} % align enviroment 
-% \usepackage{gensymb} % degree symbol in math enviroments
+% mnras_template.tex
+%
+% LaTeX template for creating an MNRAS paper
+%
+% v3.0 released 14 May 2015
+% (version numbers match those of mnras.cls)
+%
+% Copyright (C) Royal Astronomical Society 2015
+% Authors:
+% Keith T. Smith (Royal Astronomical Society)
+
+% Change log
+%
+% v3.0 May 2015
+%    Renamed to match the new package name
+%    Version number matches mnras.cls
+%    A few minor tweaks to wording
+% v1.0 September 2013
+%    Beta testing only - never publicly released
+%    First version: a simple (ish) template for creating an MNRAS paper
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Basic setup. Most papers should leave these options alone.
+\documentclass[a4paper,fleqn,usenatbib]{mnras}
+
+% MNRAS is set in Times font. If you don't have this installed (most LaTeX
+% installations will be fine) or prefer the old Computer Modern fonts, comment
+% out the following line
+\usepackage{newtxtext,newtxmath}
+% Depending on your LaTeX fonts installation, you might get better results with one of these:
+%\usepackage{mathptmx}
+%\usepackage{txfonts}
+
+% Use vector fonts, so it zooms properly in on-screen viewing software
+% Don't change these lines unless you know what you are doing
+\usepackage[T1]{fontenc}
+\usepackage{ae,aecompl}
+
+%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
+
+% Only include extra packages if you really need them. Common packages are:
+\usepackage{graphicx}	% Including figure files
+\usepackage{amsmath}	% Advanced maths commands
+\usepackage{amssymb}	% Extra maths symbols
+
+\usepackage[flushleft, referable]{threeparttablex} % Adding notes under tables
 \usepackage{mhchem} 	% typeset chemistry symbols
-% \usepackage{ccaption} % for contcaption to continue figure onto multiple pages
-\usepackage[flushleft, referable]{threeparttablex} % Adding notes under tables
-\usepackage{multirow} % for multirow command
-\usepackage{url}
-\urlstyle{same}
+\usepackage{multicol} 	% Multi-column entries in tables
+% \usepackage{natbib} % references in text to look like MNRAS/ApJ/A&A
+% \usepackage{multirow} % for multirow command
+% \usepackage{array} % For wrapping text in cell in tables
 
-\usepackage{array} % For wrapping text in cell in tables
-% \newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}} % centered wrapped text in tables
-\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} % 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
+
+% Please keep new commands to a minimum, and use \newcommand not \def to avoid
+% overwriting existing commands. Example:
+%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
+\defcitealias{Thomas2010}{TMJ} % TMJ alias
+% \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} % 
 \newcommand{\bracket}[1]{[#1]} % to be able to use [] in arguments
 
-\defcitealias{Thomas2010}{TMJ} % TMJ alias
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\title{An IFS study of Low-powered Radio Galaxies}
+%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
+
+% Title of the paper, and the short title which is used in the headers.
+% Keep the title short and informative.
+\title[An IFS study of Low-powered Radio Galaxies]{An IFS study of Low-powered Radio Galaxies}
+
+% The list of authors, and the short list which is used in the headers.
+% If you need two or more lines of authors, add an extra line using \newauthor
 \author[J. Warren et al.]{
@@
 Hans de Ruiter$^{3}$
-and Arturo Mignano$^{3}$
+and \newauthor
+Arturo Mignano$^{3}$
 \\
@@
 
+% These dates will be filled out by the publisher
+\date{Accepted XXX. Received YYY; in original form ZZZ}
+
+% Enter the current year, for the copyright statements etc.
+\pubyear{2018}
+
+% Don't change these lines
 \begin{document}
+\label{firstpage}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}
 \maketitle
 
-%\date{Oxford, \today} % date is given automatically at top of page in mnras formatting
+% Abstract of the paper
+\begin{abstract}
+This is a simple template for authors to write new MNRAS papers.
+The abstract should briefly describe the aims, methods, and main results of the paper.
+It should be a single paragraph not more than 250 words (200 words for Letters).
+No references should appear in the abstract.
+\end{abstract}
 
-\begin{abstract}
+% Select between one and six entries from the list of approved keywords.
+% Don't make up new ones.
+\begin{keywords}
+% keyword1 -- keyword2 -- keyword3
+\end{keywords}
 
-\end{abstract}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
 
@@
 Of these we focus on the former since these are by far the most common mode in the local universe (possibly as far as $z \sim 1$ \citep{Rigby2008}), and so to discuss radio AGN feedback is to consider feedback from FR I sources \citep{DeYoung2010}.
-Indeed, while there is broad consensus \citep{Heckman1986, Baum1992} that the brightest RGs (mostly FR IIs) are caused when a massive galaxy merges with a gas rich galaxy (a wet merger) giving a plentiful fuel reservoir to the AGN \citep{Baum1992}, there is much more debate when it comes to low-powered ($P_\mathrm{1.4 GHz} \lesssim 10^{24.5} \, \mathrm{W Hz^{-1}}$) RGs (mostly FR I).
+Indeed, while there is broad consensus \citep{Heckman1986, Baum1992} that the brightest RGs (mostly FR IIs) are caused when a massive galaxy merges with a gas rich galaxy (a wet merger) giving a plentiful fuel reservoir to the AGN \citep{Baum1992}, there is much more debate when it comes to low-powered ($P_\text{1.4 GHz} \lesssim 10^{24.5} \, \mathrm{W Hz^{-1}}$) RGs (mostly FR I).
 Suggestions fall into two categories: an extrapolation of radio-loud galaxies (i.e.
@@
 % More to add to intro - e.g. summery of paper
+
+	We refer to the combined Atlas$^\text{3D}$ and MASSIVE sample as the A+M sample.
 
@@
 	\begin{table*}
-		\centering
-	\begin{threeparttable}
-		\caption{Key sample characteristics of the Southern Sample galaxies.}
+		% \centering
+	% \begin{threeparttable}
+		\caption{Key sample characteristics of the Southern Sample galaxies.
+Col.\,1: host galaxy name.
+Col.\,2: radio source name from Parkes Southern Radio Source Catalogue.
+We hereafter refer to the last galaxy by its PKS name only.
+Col.\,3: redshift.
+Col.\,4: National Radio Astronomy Observatory (NRAO) Very Large Array (VLA) Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}.
+Col.\,5: Two Micron All Sky Survey (2MASS) $K$-band apparent magnitude (with errors of $\pm 0.025$ mag; \citealt{Skrutskie2006}).
+Col.\,6: dust morphologies from (a) \citet{Govoni2000}, (b) \citet{Lauer2005}, (c) \citet{Bettoni2001}, (d) \citet{Sandage1979}, (e) \citet{Colbert2001}.}
 		\label{tab:sample}
@@
 		\end{tabular}
-		\begin{tablenotes}
-		\footnotesize
-		\note Col.\,1: host galaxy name.
+	% 	\begin{tablenotes}
+	% 	\footnotesize
+	% 	\note Col.\,1: host galaxy name.
 Col.\,2: radio source name from Parkes Southern Radio Source Catalogue.
@@
 Col.\,6: dust morphologies from (a) \citet{Govoni2000}, (b) \citet{Lauer2005}, (c) \citet{Bettoni2001}, (d) \citet{Sandage1979}, (e) \citet{Colbert2001}.
-		\item We hereafter refer to the last galaxy by its PKS name only.
-		\end{tablenotes}
-	\end{threeparttable}
+	% 	\item We hereafter refer to the last galaxy by its PKS name only.
+	% 	\end{tablenotes}
+	% \end{threeparttable}
 	\end{table*}
@@
 These additional steps mean that the datacubes are not perfectly flux-calibrated, but all the corrections are multiplicative and thus will not effect equivalent width or line ratio measurements.
-From comparisons to the MUSE data (see Section \ref{sec:MUSE}), we then estimate the flux calibration of the resulting datacubes.
+From comparisons to the MUSE data (see Section \ref{subsec:MUSE}), we then estimate the flux calibration of the resulting datacubes.
+
+	These method are not completely effective and some artefacts are still present in the data, however in most cases the data is of sufficient quality for our purposes.
+For the worst effected datacubes, we have archival observations (see Section \ref{subsec:MUSE}).
 
@@
 		Finally, we trimmed all the MUSE cubes to the central $30\arcsec \times 30\arcsec$ ($150 \times 150$\,spaxels) only, to (a) avoid the regions used for the pseudo-sky spectrum and (b) reduce the computing resources required for spatial binning (see Section \ref{sec:analysis}).
-In any case, the bins would be so large in the outer parts as to be effectively useless (see Fig\,\ref{fig:egSNR}).
+In any case, the bins would likely be so large in the outer parts as to be effectively useless.
 
@@
 	\label{sec:analysis}
-	From this point on, the VIMOS and MUSE datasets are treated almost identically, the only difference (other than the different spectral ranges and resolutions) being that the MUSE datacubes are spatially binned to a higher signal-to-noise ratio (S/N) using Voronoi binning\footnote{\url{http://www-astro.physics.ox.ac.uk/~mxc/software/}} \citep{Cappellari2003}.
+	From this point on, the VIMOS and MUSE datasets are treated almost identically, the only difference (other than the different spectral ranges and resolutions) being that the MUSE datacubes are spatially binned to a higher signal-to-noise ratio (S/N) using Voronoi binning\footnote{http://www-astro.physics.ox.ac.uk/~mxc/software/} \citep{Cappellari2003}.
 For our purposes, we define the `signal' and `noise' of each spaxel as the median value of its spectrum and noise spectrum, respectively.
@@
 summed across both spatial dimensions of the datacube) spectrum.
-We use the penalized-fitting (\textsc{pPXF}) routine\footnote{\url{http://www-astro.physics.ox.ac.uk/~mxc/software/}} of \citet{Cappellari2004} and \citet{Cappellari2016a} with the Medium-resolution Issac Newton Telescope (INT) Library of Empirical Spectra (MILES) library \citep{Sanchez-Blazquez2006, Falcon-Barroso2011a} to find the best-fitting line-of-sight velocity distribution (LOSVD; as parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion).
+We use the penalized-fitting (\textsc{pPXF}) routine\footnote{http://www-astro.physics.ox.ac.uk/~mxc/software/} of \citet{Cappellari2004} and \citet{Cappellari2016a} with the Medium-resolution Issac Newton Telescope (INT) Library of Empirical Spectra (MILES) library \citep{Sanchez-Blazquez2006, Falcon-Barroso2011a} to find the best-fitting line-of-sight velocity distribution (LOSVD; as parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion).
 The final mean velocity of a given galaxy, is used as its precise spectroscopic redshift and is given in Table \ref{tab:sample}.
@@
 		\begin{table}
-	 		\centering
-	 	\begin{threeparttable}
-	 		\caption{Emission lines considered in the \textsc{pPXF} fits.}
+	 		% \centering
+	 	% \begin{threeparttable}
+	 		\caption{Emission lines considered in the \textsc{pPXF} fits.
+Col\,1: Emission line name.
+Col\,2: Emission line rest-frame wavelength.
+Col\,3: Doublet rest-frame wavelength for forbidden lines.
+Col\,4: The fixed ratio of the amplitudes of the lines within a doublet.
+`Free' indicates the amplitudes of both doublet constituents are fit independently of each other.}
 	 		\label{tab:EmissionLine}
@@
 	 		\end{tabular}
-	 		\begin{tablenotes}
-	 		\note Col\,1: Emission line name.
+	 	% 	\begin{tablenotes}
+	 	% 	\note Col\,1: Emission line name.
 Col\,2: Emission line rest-frame wavelength.
@@
 `Free' indicates the amplitudes of both doublet constituents are fit independently of each other.
-	 		\end{tablenotes}
-	 	\end{threeparttable}
+	 	% 	\end{tablenotes}
+	 	% \end{threeparttable}
 	 	\end{table}
@@
 
-		\subsubection{Correcting for Stellar Velocity Dispersion}
+		\subsubsection{Correcting for Stellar Velocity Dispersion}
 			We correct for the effect of the different velocity dispersions of the stars which varyingly spread absorption features such that differing fractions of the absorption is outside of the central bandpasses.
@@
 
+	\subsection{Other Parameters}
+		\subsubsection{Ellipticity}
+			In this paper, ellipticity is that of the best-fitting ellipse to the surface-brightness map with an mean radius $R_\text{m}$, of 1 effective radius $R_\text{e}$.
+% Firstly the centre of the galaxy is found as the luminosity weighted centre using the \textsc{python} routine \textsc{find\_galaxy}, which is part of the \textsc{mge} package\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/} by \citet{Cappellari2002}.
+			as found by the \textsc{idl} routine \textsc{kinemetry}\footnote{http://davor.krajnovic.org/idl/} by \citet{Krajnovic2006} which finds the best-fitting ellipses at a range of evenly spaced semi-major axes.
+%This is achieved by performing harmonic expansion of maps along ellipses with a given semi-major axis and, when used for even moments (e.g.\ surface brightness, velocity dispersion, h$_4$ etc.), minimizing the amplitude of the first and second harmonics.
+			The results include the ellipticity, $\epsilon$ and position angle $PA_\text{phot}$ of the best-fitting ellipse for each semi-major axis.
+The fit is repeated for increasing semi-major axis until $<$75\% of the ellipse is not contained within the field of view.
+
+			In reality, the field of view does not always contain 1 $R_\text{e}$.
+Where this is the case, we follow the method by \citet{Emsellem2007}, where $R_\text{m}$ is redefined as $R_\text{m} \equiv \sqrt{A_\text{s}/\pi}$, where $A_\text{s}$ is the area of the ellipse contained within the field of view.
+For a given galaxy, we fit ellipses as described above, up to $R_\text{m} = R_\text{max}$, where $A_\text{s}$ reaches a maximum difference if 15\% to the area of the fitted ellipse, $A_\text{ellipse}$.
+The value $\epsilon_\text{e}$, the ellipticity at 1 $R_\text{e}$ or $R_\text{max}$, whichever is smallest, is given in Col.\,3 of Table \ref{tab:classify}.
+
+		\subsubsection{Kinematic Position Angle}
+			The kinematic position angle, $PA_\text{kin}$, is defined as the angle of the axis perpendicular to the apparent angular momentum vector westwards from North.
+A global value of $PA_\text{kin}$ is found using the \textsc{python} routine \textsc{fit\_kinematic\_pa}\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/\#pa\_kin} which finds $PA_\text{kin}$ of the symmetrised mean velocity map, as described in appendix C of \citet{Krajnovic2006}.
+%This routine finds a symmetric (about $PA_\text{kin}$) velocity field, by replacing the mean velocity, $V$, in each bin with
+			% \begin{equation}
+			% 	V'(x, y) = \frac{V(x,y) + V(x, -y) - V(-x,y) - V(-x,-y))}{4} \,,
+			% \end{equation}
+			% where $x$ and $y$ are the centroid coordinates of a given bin, with the origin at the centre of the galaxy and the x axis aligned along $PA_\text{kin}$.
+Linear interpolation is used where necessary.
+
+			Col.\,4 in Table \ref{tab:classify} lists the misalignments between the photometric and kinematic position angles, $\Gamma_\text{kin} \equiv \arcsin(\sin[PA_\text{phot} - PA_\text{kin}])$.
+
+		\subsubsection{Specific Angular Momentum Parameter, $\lambda_\mathrm{R_e}$}
+			We also make use of the Atlas$^\text{3D}$ specific angular momentum parameter, $\lambda_\text{R}$ \citep{Emsellem2007} evaluated at 1 $R_\text{e}$, where 
+			\begin{equation}
+				\lambda_\mathrm{R_e} \equiv \frac{\sum_{i=1}^{N} F_i R_i |V_i|}{\sum_{i=1}^{N} F_i R_i \sqrt{V_i^2 + \sigma_i^2}}
+			\end{equation}
+			where $F_i$ is the flux of the $i^\text{th}$ bin, $R_i$ its distance from the centre and $V_i$ and $\sigma_i$ its mean stellar velocity and velocity dispersion, respectively.
+The sum is computed over all $N$ bins with a radius $R_\text{e}$.
+
 \section{Stellar Kinematics}
@@
 Here we use these maps to classify each galaxy according to the Atlas$^\text{3D}$ regular/non-regular rotator and fast/slow rotator classification schemes of \citet{Krajnovic2006} and \citet{Cappellari2016}, respectively, as well as the qualitative kinematic classes of \citet{Krajnovic2011}.
-
-	% Ellipticity is measured as the ellipticity of the best-fitting ellipse to the surface-brightness map with an mean radius $R_\mathrm{m}$, of 1 effective radius $R_\mathrm{e}$.
-Firstly the centre of the galaxy is found as the luminosity weighted centre using the \textsc{python} routine \textsc{find\_galaxy}, which is part of the \textsc{mge} package\footnote{\url{http://www-astro.physics.ox.ac.uk/\~mxc/software/}} by \citet{Cappellari2002}.
-This is then used as an input for the \textsc{idl} routine \textsc{kinemetry}\footnote{\url{http://davor.krajnovic.org/idl/}} by \citet{Krajnovic2006} which finds the best-fitting ellipses at a range of evenly spaced semi-major axes.
-This is achieved by performing harmonic expansion of maps along ellipses with a given semi-major axis and, when used for even moments (e.g.\ surface brightness, velocity dispersion, h$_4$ etc.), minimizing the amplitude of the first and second harmonics.
-The results include the ellipticity, $\epsilon$ and position angle $PA_\text{phot}$ of the best-fitting ellipse for each semi-major axis.
-The fit is repeated for increasing semi-major axis until $<$75\% of the ellipse is not contained within the field of view.
-
-	% In reality, the field of view does not always contain 1 $R_\mathrm{e}$.
-Where this is the case, we follow the method by \citet{Emsellem2007}, were $R_\mathrm{m}$ is redefined as $R_\mathrm{m} \equiv \sqrt{A_\mathrm{s}/\pi}$, where $A_\mathrm{s}$ is the area of the ellipse contained within the field of view.
-For a given galaxy, we fit ellipses as described above, up to $R_\mathrm{m} = R_\mathrm{max}$, where $A_\mathrm{s}$ reaches a maximum difference if 15\% to the area of the fitted ellipse, $A_\text{ellipse}$.
-The value $\epsilon_\mathrm{e}$, the ellipticity at 1 $R_\mathrm{e}$ or $R_\text{max}$, whichever is smallest, is given in Table \ref{tab:classify}.
-
-	% Misalignment
-
-	All other measurements (e.g.
-the specific angular momentum parapmeter $\lambda_\mathrm{R_e}$) and the classifications are made using the methods and critia described in the referenced literature above, with the results shown in Table \ref{tab:classify}.
+We use the criteria described in the referenced literature for each of these classification, with the results shown in Table \ref{tab:classify}.
 
 	\begin{table*}
-		\centering
-	\begin{threeparttable}
-		\caption{Kinematic classifications}
+		% \centering
+	% \begin{threeparttable}
+		\caption{Kinematic classifications.
+Col.\,1: Galaxy name.
+Col.\,2: $\lambda_\text{R}$ evaluated at $R_\text{e}$.
+Col.\,3: Ellipticity at $R_\text{e}$.
+Col.\,4: Misalignment angle between the kinematic and photometric position angles.
+Col.\,5: Fast-/slow-rotator (FR/SR) classification.
+Col.\,6: Regular-rotator (RR) or non-regular-rotator (NRR).
+Col.\,7: Kinematic features.
+Col.\,8: Kinematic group.}
 		\label{tab:classify}
@@
 			\hline
-			Galaxy		& $\lambda_\mathrm{R_e}$ & $\epsilon_\mathrm{e}$  & $\Gamma_\text{kin}$ & FR/SR 	& RR/NRR 	& Feature & Group 	\\
+			Galaxy		& $\lambda_\mathrm{R_e}$ & $\epsilon_\text{e}$  & $\Gamma_\text{kin}$ & FR/SR 	& RR/NRR 	& Feature & Group 	\\
 			 & & & (deg) \\
@@
 			\hline
+			\multicolumn{8}{l}{$^{a}$Tentative classification. A higher signal-to-noise ratio (S/N) in the outer regions of the field of view is required for confirmation.}
+
 		\end{tabular}
-		\begin{tablenotes}
-		\footnotesize
-		\note Col.\,1: Galaxy name.
-Col.\,2: $\lambda_\mathrm{R}$ evaluated at $R_\mathrm{e}$.
-Col.\,3: Ellipticity at $R_\mathrm{e}$.
+	% 	\begin{tablenotes}
+	% 	\footnotesize
+	% 	\note Col.\,1: Galaxy name.
+Col.\,2: $\lambda_\text{R}$ evaluated at $R_\text{e}$.
+Col.\,3: Ellipticity at $R_\text{e}$.
 Col.\,4: Misalignment angle between the kinematic and photometric position angles.
@@
 Col.\,8: Kinematic group.
-		\item [a] Tentative classification. A higher signal-to-noise ratio (S/N) in the outer regions of the field of view is required for confirmation.
-		\end{tablenotes}
-	\end{threeparttable}
+	% 	\item [a] Tentative classification. A higher signal-to-noise ratio (S/N) in the outer regions of the field of view is required for confirmation.
+	% 	\end{tablenotes}
+	% \end{threeparttable}
 	\end{table*}
+
+	We find 4/11, or $(36\pm15)$\%, of our sample galaxies are regular rotators.
+This compares to 82\% of the Atlas$^\text{3D}$ sample being classified as regular rotators \citep{Krajnovic2011}.
+However the likely-hood of a given galaxy being a regular rotator is highly mass dependent with the likely-hood decreasing with increasing mass.
+Thus since our Southern sample are all extremely massive galaxies, we expect to find a higher fraction of non-regular rotators than the Atlas$^\text{3D}$ survey.
+
+	\begin{figure}
+		\includegraphics[width=\columnwidth]{lambda_R_ellipticity.png}
+		\caption{$\lambda_\mathrm{R_e}$\,--\,ellipticity diagram.
+VIMOS and MUSE measurements are shown in red and blue, respectively.
+For comparison, Atlas$^\text{3D}$ galaxies \citep{Emsellem2011} are shown in black and MASSIVE galaxies \citep{Veale2017} in grey.
+The theoretical limit (edge-on systems) of disc-dominated galaxies is shown in solid magenta, with lines of constant intrinsic angular momentum but varying inclination in dotted magenta.
+The black solid lines show the limits of the fast-/slow-rotator classes.
+The MASSIVE survey does not report substructure, so the MASSIVE sample galaxies are shown with filled circles.}
+		\label{fig:lambdaR_ellip}
+	\end{figure}
+
+	5 out of 11 galaxies, or $(45\pm13)$\%, are slow rotators.
+This is between that of the Atlas$^\text{3D}$ and MASSIVE projects, who find 13.1\% and 77.5\% of their sample galaxies to be slow rotators, respectively.
+As for the regular/non-regular rotators classification scheme, slow rotators are more likely to be found in higher mass galaxies and the three samples (Atlas$^\text{3D}$, MASSIVE and our Southern sample) have very different mass distributions (see upper panel of Fig.\,\ref{fig:SRmassFraction}).
+
+	In order to account for the difference in mass distribution, we find the expected fraction of slow rotators in the Southern sample, $f'$, corrected to the mass distribution of the combined Atlas$^\text{3D}$ and MASSIVE samples (hereafter the A+M sample), as
+	\begin{equation}
+		f' = \sum_{i=0}^N N^\text{SS}_i f^\text{AM}_i \, , 
+	\end{equation}
+	where $N^\text{SS}_i$ is the number of Southern sample galaxies in the $i^\text{th}$ mass bin, $N^\text{AM}_i$ is the fraction of slow rotators in the $i^\text{th}$ mass bin in the A+M combined sample and $N$ is the total number of mass bins.
+In our case we use the $K$-band absolute magnitude ($M_K$) as a proxy for stellar mass, with bins of 0.5 mag.
+This gives an expected fraction of $f' = 0.64 \pm 0.06$, just consistent with our finding of $(45\pm13)$\% of the Southern sample galaxies being slow rotators.
+Again the large uncertainty reflects the low number statistics of the Southern sample.
+There is, therefore, no discernible difference in the fraction of galaxies that are slow-rotators between our radio-selected Southern sample and the optically-selected A+M sample, once differences in the mass distributions are taken into account.
+
+	\begin{figure}
+		\includegraphics[width=\columnwidth]{M_k_binned.png}
+		\caption{Upper panel: mass distribution of the A+M sample (black) and of our Southern sample (red).
+Lower panel: fraction of slow rotators within each mass bin.
+The labels list the number of slow rotators and total number of galaxies in each bin.}
+		\label{fig:SRmassFraction}
+	\end{figure}
+
+	In addition to this, we attempt to identify the kinematic features defined by \citet{Krajnovic2011} in an algorithmic way.
+However, the artefacts from the VIMOS quadrants confuse ellipse fitting algorithms so only maps derived from the MUSE data are classified in this way; kinematic features in maps derived from the VIMOS data are identified by eye.
+These classification are listed in Col.\,7 of Table \ref{tab:classify} and the corresponding kinematic group to which a given galaxy belongs to is given is Col.\,8.
+We observe 3 KDCs (although PKS 718-34 is only a tentative classification) such that $29\pm19$\% of non-regular rotators in our Southern sample definitely (not including PKS 718-34) contain KDCs (or $43\pm19$\% including PKS 718-34), with the large uncertainty reflecting the low-number statistics.
+This is consistent with the Atlas$^\text{3D}$ survey who found find $25\pm7$\% of non-regular rotators host KDCs \citep{Krajnovic2011}.
+
+% Misaligned systems may appear aligned in certain projections (though aligned systems will be aligned in all projections) and as such $\Gamma_\text{kin}$ cannot be used to describe the intrinsic shape of an individual galaxy, but, as described in Section \ref{sec:ETG}, it can be used in a statistical manner.
+We find all the regular rotators in our Southern sample, are consistent with having aligned photometry and kinematic position angles to within 11\degree, while non-regular rotators have a large range of values of $\Gamma_\text{kin}$.
+IC 1531, NGC7075 and PKS 718-34 all have very large uncertainties in the value of $PA_\text{phot}$ due to the VIMOS quadrant artefacts causing the fitting routine of \textsc{kinemetry} to become unreliable.
+
+		% The lack of misalignments in regular rotators is consistent with \citet{Cappellari2007}, \citet{Krajnovic2011} and \citet{Fogarty2015}, who all showed that regular rotators almost always have aligned photometric and kinematic axes with very little scatter and that regular rotators with a significant misalignment are either interacting or strongly barred.
+The lack of misalignments suggests that the regular rotators (including those within our Southern sample) are consistent with being axisymmetric \citep{Cappellari2016}.
+
+		% Misalignments between the photometric and kinematic position angles are routinely observed for non-regular rotators.
+This generally implies a more triaxial intrinsic shape, although large misalignments are extremely rarely observed in galaxies with $\epsilon > 0.4$, suggesting that non-regular rotators are more spherical in shape \citep{Cappellari2016}.
+The non-regular rotators in our Southern sample indeed all have $\epsilon < 0.4$ showing that they are consistent with a fairly spherical, triaxial intrinsic shape.
 
@@
 
-\section*{Acknowledgments}
-% \addcontentsline{toc}{section}{Acknowledgments} % add to contents - not sure if MNRAS want this...
+\section*{Acknowledgements}
 
-%\FloatBarrier
+The Acknowledgements section is not numbered. Here you can thank helpful
+colleagues, acknowledge funding agencies, telescopes and facilities used etc.
+Try to keep it short.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
+
+% The best way to enter references is to use BibTeX:
+
 \bibliographystyle{mnras}
+\bibliography{refs} % if your bibtex file is called example.bib
 
-\bibliography{refs}{}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Don't change these lines
+\bsp	% typesetting comment
+\label{lastpage}
 \end{document}
+
+% End of mnras_template.tex

### 2018-01-16 paper.tex
EoDC:
Futher work on paper.

 On branch master
 Changes to be committed:
	new file:   KDC_size_age.png
	new file:   Mg_sigma.png
	modified:   paper.tex

@@
 	\begin{table*}
-		% \centering
+		\centering
 	% \begin{threeparttable}
@@
 		Each bin is fit independently again using \textsc{pPXF} with the MILES library.
-For the fit regions around potential emission lines are masked, and a fourth order polynomial additive continuum correction is used.
+For the fit, regions around potential emission lines (list below) are masked, and a fourth order polynomial additive continuum correction is used.
 A Monte--Carlo (MC) estimate of the uncertainties is used.
@@
 		\label{subsec:EmissionLines}
-		We fit the ionized gas fluxes and kinematics from the emission lines listed in Table \ref{tab:EmissionLine}, using Gaussian templates are used to independently fit emission lines from the interstellar medium (ISM), with a single LOSVDs, independently of the stellar kinematics.
-However, to minimize template mismatch, whereby emission lines are erroneously fitted to the edges of badly modeled and thus subtracted absorption features, we follow the method set out in \citet{Sarzi2005}, whereby the stellar component is first fitted as above with masked potential emission line regions, followed by the unmasking and fitting of the [\ion{O}{iii}] doublet which sets the kinematics for all the emission lines and finally the amplitude of the remaining emission lines.
-Some of the forbidden emission lines have the ratio of their amplitudes fixed (see Table \ref{tab:EmissionLine}, Col.\,4).
+		We fit the ionized gas fluxes and kinematics for the emission lines [\ion{O}{ii}], H$\delta$, H$\gamma$, H$\beta$, [\ion{O}{iii}], [\ion{N}{I}], [\ion{O}{i}], [\ion{N}{ii}], H$\alpha$ and [\ion{S}{ii}] using Gaussian templates.
+This independently fits emission lines from the interstellar medium (ISM), with a single LOSVDs (again parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion), independently of the stellar kinematics.
+In the cases of the [\ion{O}{iii}], [\ion{O}{i}] and [\ion{N}{ii}] doublets, the two components of the doublets are fit with a fixed flux ratio of 1:0.34.
+The [\ion{N}{i}] doublet has a fixed ratio of 1:0.65 \citep{Safier1992}.
+The two components of the [\ion{O}{ii}] and [\ion{S}{ii}] doublets are fit independently.
+To minimize template mismatch, whereby emission lines are erroneously fitted to the edges of badly modeled and thus subtracted absorption features, we follow the method set out in \citet{Sarzi2005}, whereby the stellar component is first fitted as above with masked potential emission line regions, followed by the unmasking and fitting of the [\ion{O}{iii}] doublet which sets the kinematics for all the emission lines and finally the amplitude of the remaining emission lines.
+%Some of the forbidden emission lines have the ratio of their amplitudes fixed (see Table \ref{tab:EmissionLine}, Col.\,4).
 
-		\begin{table}
-	 		% \centering
-	 	% \begin{threeparttable}
-	 		\caption{Emission lines considered in the \textsc{pPXF} fits.
+		% \begin{table}
+	 % 		% \centering
+	 % 	% \begin{threeparttable}
+	 % 		\caption{Emission lines considered in the \textsc{pPXF} fits.
 Col\,1: Emission line name.
@@
 `Free' indicates the amplitudes of both doublet constituents are fit independently of each other.}
-	 		\label{tab:EmissionLine}
-	 		\begin{tabular}{l c c c}
-	 		\hline
-	 		\hline
-	 		Emission & Rest-frame & Doublet rest-frame & Amplitude  \\
-	 		Line & wavelength & wavelength & ratio \\
-	 		 & (\AA) & (\AA) \\
-	 		\hline
-	 		\bracket{\ion{O}{ii}} 	& 3726.03 & 3728.82 & Free \\
-	 		H\,$\delta$ 	& 4101.76 & -- & -- \\
-	 		H\,$\gamma$ 	& 4340.47 & -- & -- \\
-	 		H\,$\beta$ 		& 4861.33 & -- & -- \\
-	 		\bracket{\ion{O}{iii}}	& 4958.92 & 5006.84 & 0.35 \\
-	 		\bracket{\ion{N}{i}} 	& 5199.36 & 5201.86 & 0.65 \\
-	 		\bracket{\ion{O}{i}} 	& 6300.30 & 6363.67 & 0.33 \\
-	 		\bracket{\ion{N}{ii}} 	& 6548.03 & 6583.41 & 0.34 \\
-	 		H\,$\alpha$ 	& 6562.30 & -- & -- \\
-	 		\bracket{\ion{S}{ii}} 	& 6716.47 & 6730.85 & Free \\
-	 		\hline
-	 		\hline
-	 		\end{tabular}
-	 	% 	\begin{tablenotes}
-	 	% 	\note Col\,1: Emission line name.
+	 % 		\label{tab:EmissionLine}
+	 % 		\begin{tabular}{l c c c}
+	 % 		\hline
+	 % 		\hline
+	 % 		Emission & Rest-frame & Doublet rest-frame & Amplitude  \\
+	 % 		Line & wavelength & wavelength & ratio \\
+	 % 		 & (\AA) & (\AA) \\
+	 % 		\hline
+	 % 		\bracket{\ion{O}{ii}} 	& 3726.03 & 3728.82 & Free \\
+	 % 		H$\delta$ 	& 4101.76 & -- & -- \\
+	 % 		H$\gamma$ 	& 4340.47 & -- & -- \\
+	 % 		H$\beta$ 		& 4861.33 & -- & -- \\
+	 % 		\bracket{\ion{O}{iii}}	& 4958.92 & 5006.84 & 0.35 \\
+	 % 		\bracket{\ion{N}{i}} 	& 5199.36 & 5201.86 & 0.65 \\
+	 % 		\bracket{\ion{O}{i}} 	& 6300.30 & 6363.67 & 0.33 \\
+	 % 		\bracket{\ion{N}{ii}} 	& 6548.03 & 6583.41 & 0.34 \\
+	 % 		H$\alpha$ 	& 6562.30 & -- & -- \\
+	 % 		\bracket{\ion{S}{ii}} 	& 6716.47 & 6730.85 & Free \\
+	 % 		\hline
+	 % 		\hline
+	 % 		\end{tabular}
+	 % 	% 	\begin{tablenotes}
+	 % 	% 	\note Col\,1: Emission line name.
 Col\,2: Emission line rest-frame wavelength.
@@
 `Free' indicates the amplitudes of both doublet constituents are fit independently of each other.
-	 	% 	\end{tablenotes}
-	 	% \end{threeparttable}
-	 	\end{table}
+	 % 	% 	\end{tablenotes}
+	 % 	% \end{threeparttable}
+	 % 	\end{table}
 
-	\subsection{Absorption Line Strengths and Stellar Populations}
+	\subsection{Absorption Line Strengths}
 		\label{subsec:absorption}
@@
 		\subsubsection{Correcting for Stellar Velocity Dispersion}
+			\label{subsubsec:EmissionFit}
 			We correct for the effect of the different velocity dispersions of the stars which varyingly spread absorption features such that differing fractions of the absorption is outside of the central bandpasses.
@@
 
+	\subsection{Regular/Non-regular Rotators}
 		We find 4/11, or $(36\pm15)$\%, of our sample galaxies are regular rotators.
@@
 
+	\subsection{Fast/Slow Rotators}
 		\begin{figure}
@@
 
+	\subsection{Kinematic Features}
 		In addition to this, we attempt to identify the kinematic features defined by \citet{Krajnovic2011} in an algorithmic way.
@@
 
-% Misaligned systems may appear aligned in certain projections (though aligned systems will be aligned in all projections) and as such $\Gamma_\text{kin}$ cannot be used to describe the intrinsic shape of an individual galaxy, but, as described in Section \ref{sec:ETG}, it can be used in a statistical manner.
-We find all the regular rotators in our Southern sample, are consistent with having aligned photometry and kinematic position angles to within 11\degree, while non-regular rotators have a large range of values of $\Gamma_\text{kin}$.
+	\subsection{Intrinsic Shape}
+		The misalignment angle between the photometric and kinematic position angle is given in Col.\,4 of Table \ref{tab:classify}.
+Misaligned systems may appear aligned in certain projections, but though aligned systems will be aligned in all projections, and a low value of $\Gamma_\text{kin}$ cannot be used to describe the intrinsic shape of an individual galaxy, but it can be interpreted within a statistical framework.
+However, a high value of $\Gamma_\text{kin}$ can give an insight into the intrinsic shape of an individual galaxy.
+We find all the regular rotators in our Southern sample, are consistent with having aligned photometry and kinematic position angles to within 11\degr, while non-regular rotators have a large range of values of $\Gamma_\text{kin}$.
 IC 1531, NGC7075 and PKS 718-34 all have very large uncertainties in the value of $PA_\text{phot}$ due to the VIMOS quadrant artefacts causing the fitting routine of \textsc{kinemetry} to become unreliable.
 
-		% The lack of misalignments in regular rotators is consistent with \citet{Cappellari2007}, \citet{Krajnovic2011} and \citet{Fogarty2015}, who all showed that regular rotators almost always have aligned photometric and kinematic axes with very little scatter and that regular rotators with a significant misalignment are either interacting or strongly barred.
+		The lack of misalignments in regular rotators is consistent with \citet{Cappellari2007}, \citet{Krajnovic2011} and \citet{Fogarty2015}, who all showed that regular rotators almost always have aligned photometric and kinematic axes with very little scatter and that regular rotators with a significant misalignment are either interacting or strongly barred.
 The lack of misalignments suggests that the regular rotators (including those within our Southern sample) are consistent with being axisymmetric \citep{Cappellari2016}.
 
-		% Misalignments between the photometric and kinematic position angles are routinely observed for non-regular rotators.
+		Misalignments between the photometric and kinematic position angles are routinely observed for non-regular rotators.
 This generally implies a more triaxial intrinsic shape, although large misalignments are extremely rarely observed in galaxies with $\epsilon > 0.4$, suggesting that non-regular rotators are more spherical in shape \citep{Cappellari2016}.
@@
 
-\section{Absorption Line Strengths and Stellar Populations}
+\section{Absorption Line Strengths}
+	\label{sec:absorption}
+	Using the methods described in Section \ref{subsec:absorption} we produce maps of the absorption line strength indices for each galaxy (shown in Appendix \ref{sec:Maps}).
+Here we measure the Mg\,--\,velocity dispersion relation and compare our absorption line strength measurements to the literature.
+
+	\subsection{Mg\,--\,$\sigma$ relation}
+		\label{subsec:Mgsigma}
+		The Mg$_2$ absorption line index of \citet{Trager1998} has overlapping bandpasses with the Mg\,b index (also of \citeauthor{Trager1998}), but includes the MgH molecular absorption line, and is hence considered a molecular index and is measured in units of magnitude.
+\citet{Bender1993} observed the tight relationship between the global Mg$_2$ absorption line strength and logarithm of the central velocity dispersion, $\sigma_0$, in elliptical galaxies.
+They also noticed that residuals to the linear best-fitting appeared to be intrinsic as they have a near Gaussian shape about the median values, but do not seem to be correlated to any other galaxy property.
+
+		Since part of the red continuum band of the Mg$_2$ index is outside of the spectral range of VIMOS, we instead use the Mg\,b index.
+\citet{Ziegler1997} show there is an approximately linear relationship between Mg\,b and Mg$_2$, with a gradient of 14.3--15.5\,mag\,\AA$^{-1}$\ depending on metallicity.
+We thus use Mg\,b as a proxy for Mg$_2$.
+
+		Using an aperture with a radius of 2 arcsec on each datacube, we measure $\sigma_0$ and Mg\,b at a spectral resolution of 8.4\,\AA\ full-width half-maximum (FWHM), chosen such that the transformation functions of \citet{Vazdekis2010} can be used to change the literature measurements from the Lick/IDS system to the LIS.
+The results are shown in Fig.\,\ref{fig:globalMg} with the best-fitting linear relationship (found using \textsc{lts\_linefit} by \citealt{Cappellari2013}) shown by the solid black line.
+This has a gradient of $2.3 \pm 0.5 \,\mathrm{\AA\,dex^{-1}}$) and intrinsic scatter of $0.13 \pm 0.10 \, \mathrm{\AA}$.
+%Individual measurements for each galaxy are given in table \ref{tab:globalMg}.
+		This is in very good agreement with the gradient found by \citet{Ziegler1997} for a sample of elliptical galaxies within Virgo and Coma using data from \citet{Dressler1987} of $2.5\,\mathrm{\AA\,dex^{-1}}$ (blue dotted line in Fig.\,\ref{fig:globalMg}), with an intrinsic scatter of 0.16\,\AA\ for galaxies with $\log \sigma_0 \geqslant 2.3$.
+
+		\begin{figure}
+			\includegraphics[width=\columnwidth]{Mg_sigma.png}
+			\caption[Global Mg\,b\,--\,$\sigma$]{The Mg\,b\,--\,velocity dispersion relation using a 2\arcsec aperture.
+We find a similar gradient to our best-fitting (solid) as that found by \citet[; dotted line]{Ziegler1997}.}
+			\label{fig:globalMg}
+		\end{figure}
+
+	\subsection{Comparison to the Literature}
+		\label{subsec:Lit}
+		Given that there is no well defined list of corrections (and methods) that is universally followed, care must be taken when making comparisons to the literature.
+When comparing to a particular paper we correct for the same effects described in the paper, but using our methods, as described in Section \ref{subsec:Absorption}.
+As in Section \ref{subsec:Mgsigma} we use a resolution of 8.4\,\AA\ FWHM in order to use the transformation function provided by \citet{Vazdekis2010} from Lick/IDS system to the LIS.
+
+		Table \ref{tab:litAbsorption} summarises our comparisons to the literature.
+For the comparison to \citet{Vazdekis2010}, we analysed the SAURON dataset\footnote{\url{http://www.strw.leidenuniv.nl/sauron/}} \citep{Emsellem2004} using the same analysis pipeline as for our Southern Sample.
+
+		\begin{table}
+			\centering
+		% \begin{threeparttable}
+			\caption{Comparisons of measured absorption line indices to the literature.
+Comparisons to \citet{Rampazzo2005} are sampled at 7 radial apertures for each galaxy: 1.5, 2.5 and 10.0 arcsec and R$_e$/10, R$_e$/8, R$_e$/4 and R$_e$/2.
+Col.\,1: Index.
+Col.\,2: Number of galaxies in comparison.
+Col.\,3: Offset equals the mean of the measurements from the literature subtract our measurements.
+Col.\,4: Dispersion equals the standard deviation of the measurements from the literature subtract our measurements.}
+			\label{tab:litAbsorption}
+			% \begin{tabular*}{0.8\textwidth}{@{\extracolsep{\fill}}l r r r}
+			\begin{tabular}{l r r r}
+				\hline
+				\hline
+				Index 		& \multicolumn{1}{c}{N$_\mathrm{gals}$} & \multicolumn{1}{c}{Offset} & \multicolumn{1}{c}{Dispersion} \\
+							& 		&\multicolumn{1}{c}{\AA}& \multicolumn{1}{c}{\AA} \\
+				\hline
+				\multicolumn{4}{c}{\citet{Vazdekis2010} (SAURON)} \\
+				\hline
+				H\,$\beta$ 	& 46		& -0.02\leavevmode\phantom{0}& 0.25\leavevmode\phantom{0}	\\
+				Fe5015		& 46		& 0.66\leavevmode\phantom{0}& 0.34\leavevmode\phantom{0}	\\
+				Mg\,b 		& 46		& 0.06\leavevmode\phantom{0}& 0.33\leavevmode\phantom{0}	\\
+				\hline
+				\multicolumn{4}{c}{\citet{Rampazzo2005} (VIMOS)} \\
+				\hline
+				G4300 		& 3 		& 2.29\leavevmode\phantom{0}& 0.11\leavevmode\phantom{0}	\\
+				Fe4383 		& 3 		& 0.39\leavevmode\phantom{0}& 0.23\leavevmode\phantom{0}	\\
+				Ca4455 		& 3 		& -0.19\leavevmode\phantom{0}& 0.09\leavevmode\phantom{0}	\\
+				Fe4531 		& 3 		& 0.16\leavevmode\phantom{0}& 0.26\leavevmode\phantom{0}	\\
+				H\,$\beta$ 	& 3 		& 0.17\leavevmode\phantom{0}& 0.12\leavevmode\phantom{0}	\\
+				Fe5015 		& 3 		& -0.73\leavevmode\phantom{0}& 0.48\leavevmode\phantom{0}	\\
+				Mg\,b 		& 3 		& -0.43\leavevmode\phantom{0}& 0.17\leavevmode\phantom{0}	\\
+				\hline
+				\multicolumn{4}{c}{\citet{Rampazzo2005} (MUSE)} \\
+				\hline
+				H\,$\beta$ 	& 2 		& -0.28\leavevmode\phantom{0}& 0.17\leavevmode\phantom{0}	\\ 
+				Fe5015 		& 2 		& 0.87\leavevmode\phantom{0}& 0.34\leavevmode\phantom{0}	\\ 
+				Mg\,b 		& 2 		& 0.31\leavevmode\phantom{0}& 0.14\leavevmode\phantom{0}	\\
+				Fe5270 		& 2 		& -0.11\leavevmode\phantom{0}& 0.15\leavevmode\phantom{0}	\\
+				Fe5335 		& 2 		& 0.08\leavevmode\phantom{0}& 0.15\leavevmode\phantom{0}	\\
+				Fe5406 		& 2 		& 0.16\leavevmode\phantom{0}& 0.07\leavevmode\phantom{0}	\\
+				Fe5709 		& 2 		& 0.11\leavevmode\phantom{0}& 0.10\leavevmode\phantom{0}	\\
+				Fe5782 		& 2 		& -0.03\leavevmode\phantom{0}& 0.11\leavevmode\phantom{0}	\\
+				NaD 		& 2 		& 0.90\leavevmode\phantom{0}& 0.41\leavevmode\phantom{0}	\\
+				TiO1 (mag)	& 2 		& -0.004	& 0.003	\\
+				TiO2 (mag)	& 2 		& -0.011	& 0.007	\\
+				\hline
+				\multicolumn{4}{c}{\citet{Ogando2008} (VIMOS)} \\
+				\hline
+				H\,$\beta$ 	& 6 		& 0.07\leavevmode\phantom{0}& 0.60\leavevmode\phantom{0}	\\
+				Fe5015 		& 6 		& -0.09\leavevmode\phantom{0}& 0.15\leavevmode\phantom{0}	\\
+				Mg\,b 		& 6 		& -0.70\leavevmode\phantom{0}& 0.08\leavevmode\phantom{0}	\\
+				\hline
+				\multicolumn{4}{c}{\citet{Ogando2008} (MUSE)} \\
+				\hline
+				H\,$\beta$ 	& 3 		& -0.04\leavevmode\phantom{0}& 0.23\leavevmode\phantom{0}	\\ 
+				Fe5015 		& 3 		& -0.16\leavevmode\phantom{0}& 0.33\leavevmode\phantom{0}	\\ 
+				Mg\,b 		& 3 		& -1.10\leavevmode\phantom{0}& 0.26\leavevmode\phantom{0}	\\
+				Fe5270 		& 3 		& -0.66\leavevmode\phantom{0}& 0.16\leavevmode\phantom{0}	\\
+				Fe5335 		& 3 		& -0.66\leavevmode\phantom{0}& 0.11\leavevmode\phantom{0}	\\
+				Fe5406 		& 3 		& -0.51\leavevmode\phantom{0}& 0.06\leavevmode\phantom{0}	\\
+				Fe5709 		& 3 		& -0.22\leavevmode\phantom{0}& 0.08\leavevmode\phantom{0}	\\
+				NaD 		& 3 		& -1.57\leavevmode\phantom{0}& 0.16\leavevmode\phantom{0}	\\
+				\hline
+				\hline
+			\end{tabular}
+		% 	\begin{tablenotes}
+		% 	\footnotesize
+		% 	\note Comparisons to \citet{Rampazzo2005} are sampled at 7 radial apertures for each galaxy: 1.5, 2.5 and 10.0 arcsec and R$_e$/10, R$_e$/8, R$_e$/4 and R$_e$/2. 
+		% 	\item Col.\,1: Index.
+Col.\,2: Number of galaxies in comparison.
+Col.\,3: Offset equals the mean of the measurements from the literature subtract our measurements.
+Col.\,4: Dispersion equals the standard deviation of the measurements from the literature subtract our measurements.
+		% 	\end{tablenotes}
+		% \end{threeparttable}
+		\end{table}
+
+		We find a very large offset for the G4300 index with respect to the results of \citet{Rampazzo2005}.
+As noted above, this index is extremely sensitive to the stellar velocity dispersion correction and we measure an average difference in the stellar velocity dispersion to that measured by \citet{Rampazzo2005} of $21\,\mathrm{km\,s^{-1}}$.
+This may be enough to account for the difference in the measurements.
+
+		We also observe that the offset in the Fe5015 index is also quite large in comparisons with \citet{Rampazzo2005} and \citet{Vazdekis2010}.
+In the case of the comparison with \citet{Rampazzo2005} we suggest that the difference is due to differences in method for accounting for the [\ion{O}{iii}] emission lines, however the origin of the offset is less clear in case of the comparison with \citet{Vazdekis2010}.
+
+		Other than G4300 and Fe5015, the comparisons show fairly consistent agreement with literature measurements although the dispersion of the comparisons are fairly large.
+We suggest that the translation between Lick and LIS systems may be the source of this spread.
+
+\section{Stellar Populations}
 	\label{sec:stellarPop}
+	We have assumed that a given spectrum from our Southern sample can be well approximated by a SSP.
+We use the method described in Section \ref{subsubsec:StellarPop} to produce maps of the most-likely SSP characteristics: age ($t$), metallicity ($Z/H$) and alpha-element enhancement ($\alpha$/Fe) from the absorption line strength maps (see Appendix \ref{sec:Maps}).
+
+	In general, our sample galaxies show old, metal rich and alpha enhanced SSPs; qualities which ETGs are well known for.
+The exceptions are NGC 612 and NGC 1316.
+NGC 1316 shows a very young stellar population (our fit of $t \approx 2$\,Gyr agrees with that of \citealt{Kuntschner2000}, but is conflicting with the older and less metal rich stellar population of \citealt{Koleva2011} who found $t=4.5 \pm 0.3 \,\mathrm{Gyr}$ and $\mathrm{[Fe/H]}=0.12 \pm 0.01 \,\mathrm{dex}$ for an aperture covering the central 0.1 kpc).
+NGC 3557 is notable for containing a significantly younger ($t\approx 4$\,Gyr) core of about 10\arcsec\ diameter and NGC 3100 has a branch of young stars ($\approx 4$\,Gyr) along the southeast branch of the molecular gas (cyan contours).
+
+	\subsection{Radial Gradients in Stellar Populations}
+		\label{subsec:popGrad}
+
+		\citet{Koleva2011} showed that while individual galaxies can have a wide range of radial gradients of age and metallicity, the mean gradient (within a mass bin) is uniform across a large mass range.
+They assume a linear relationship between $\log t$ or [Fe/H] and $\log (R/\mathrm{R_e})$.
+We repeat this fit with our Southern Sample with the results shown in Table \ref{tab:popGrad}.
+
+		\begin{table}
+			\centering
+			\caption{The radial gradients of the most-likely SSP models.}
+			\label{tab:popGrad}
+			\begin{tabular}{l c c}
+				\hline
+				\hline 
+				Galaxy 	& $\Delta_\text{log age}$ & $\Delta_\text{[Fe/H]}$ \\ 
+					& dex\,arcsec$^{-1}$ & dex\,arcsec$^{-1}$ \\
+				\hline
+				ESO 443-G024 & $0.019 \pm 0.013$ & $-0.01 \pm 0.02$ \\
+				IC 1459 	& $0.003 \pm 0.002$ & $0.00 \pm 0.06$ \\
+				IC 1531 	& $0.012 \pm 0.015$ & $0.01 \pm 0.02$ \\
+				IC 4296		& $0.000 \pm 0.002$ & $0.04 \pm 0.08$ \\
+				NGC 612 	& $0.068 \pm 0.060$ & $-0.11 \pm 0.02$ \\
+				NGC 1316 	& $0.001 \pm 0.002$ & $0.05 \pm 0.03$ \\
+				NGC 1399 	& $0.001 \pm 0.002$ & $0.10 \pm 0.09$ \\
+				NGC 3100 	& $0.000 \pm 0.010$ & $-0.06 \pm 0.01$ \\
+				NGC 3557 	& $0.048 \pm 0.039$ & $-0.05 \pm 0.05$ \\
+				NGC 7075 	& $0.007 \pm 0.011$ & $-0.07 \pm 0.02$ \\
+				PKS 718-34  & $0.002 \pm 0.009$ & $-0.17 \pm 0.03$ \\
+				\hline
+				\hline
+			\end{tabular}
+		\end{table}
+
+		We find average gradients of $\Delta_\text{log age} = 0.014\pm0.007 \,\mathrm{dex \, arcsec^{-1}}$ and $\Delta_\text{[Fe/H]} = -0.03\pm0.01 \, \mathrm{dex \, arcsec^{-1}}$.
+This is consistent with \citet{Koleva2011} who, for elliptical galaxies found average gradients of $0.06\pm0.09 \, \mathrm{dex \, arcsec^{-1}}$ and $-0.26\pm0.08 \, \mathrm{dex \, arcsec^{-1}}$ for the age and metallicity gradients, respectively.
+For S0s they find flatter corresponding gradients of $0.01\pm0.11\, \mathrm{dex \, arcsec^{-1}}$ and $-0.12\pm0.13\, \mathrm{dex \, arcsec^{-1}}$.
+
+	\subsection{Kinematically-Decoupled Cores}
+		\label{subsec:popKDC}
+		\citet{Kuntschner2010} found that kinematically-decoupled cores (KDCs) exist in two classes: they are either small or contain an old stellar population.
+The size of the KDC is defined as the radius of the region surrounding the KDC where the superposition of the two components (the KDC and the host galaxy) results in a local minimum in the mean velocity.
+The age of the most-likely SSP model for the spatially integrated spectrum within an aperture 1\arcsec\ on the centre of the galaxy is taken as the KDC's age.
+
+		The small KDCs are too small to be spatially resolved by our data, and thus are not considered here.
+The large KDCs are typically embedded in slow rotators.
+They have no limit on the age of their stellar populations suggesting that the stars within the KDC dominate in total mass as well as surface brightness.
+Thus, they do not fade into their host galaxies as they age unlike the small KDCs \citep{Kuntschner2010}.
+\citet{Bois2011} showed major mergers may well result in such large KDCs if the initial spin axis of the progenitor galaxy with the lowest bulge-to-disc ratio (later-type) is anti-parallel to the orbital angular momentum vector.
+
+		In Fig.\,\ref{fig:KDC} we show the age and size of the 3 KDCs hosted by galaxies in our Southern sample.
+We include PKS 718-34 here but stress it is only tentatively classified as containing a KDC.
+As can be seen from Fig.\,\ref{fig:KDC}, PKS 718-34 would be an extremely large KDC, but is still is consistent with the findings of \citet{Kuntschner2010}.
+
+		\begin{figure}
+			\includegraphics[width=\columnwidth]{KDC_size_age.png}
+			\caption[KDC dichotomy]{The KDC size\,--\,age relation.
+KDCs exist in two classes: old or small.
+VIMOS is in red, MUSE in blue and SAURON from \citet{Kuntschner2010} in black and gray for fast and slow rotators respectively.}
+			\label{fig:KDC}
+		\end{figure}
+
+\section{Ionized Gas Distribution, Kinematics and Ionization}
+	\label{sec:gas}
+	Using the methods described in Section \ref{subsubsec:EmissionFit}, we find the best-fitting line-of-sight velocity distribution (LOSVD; assumed to be Gaussian and parametrised by the mean velocity and velocity dispersion only) of the emission lines in each bin.
+Images of the Southern Sample galaxies in the [\ion{O}{iii}]$\lambda\lambda$4957,5007 lines are shown in Appendix \ref{sec:Maps} (we choose to show [\ion{O}{iii}] as detections of all emission lines require a detection of [\ion{O}{iii}] first, see Section \ref{subsubsec:EmissionFit}).
+Only 4 galaxies of the Southern Sample have emission lines detected outside of their central region (IC 1459, NGC 612, NGC 1316 and NGC 3100).
+Of the remaining 7 galaxies, NGC 1399 and PKS 718-34 have no detection of H$\beta$ in their spatially-resolved map (although we do detect H$\beta$ in the spatially-integrated spectrum of NGC 1399; see below), while the other 5 galaxies are only detected in their centre.
+All other emission lines have similar distributions, but with different fluxes.
+
+	As can be seen from the maps in Appendix \ref{sec:Maps}, both NGC 612 and NGC 3100 have significant off-centre clouds of ionized gas.
+The latter is spatial coincident with both the radio jet and the gap in the CO ring (this is discussed further in Section \ref{subsec:BPT}), while former seems to no link with either the radio jet (a massive scale jet extending several $\sim 200$\,kpc to the east and west of the galaxy centre) or the CO.
+
+	\begin{table*}
+		\centering
+	% \begin{threeparttable}
+		\caption{Gas masses of the Southern Sample galaxies.
+Col.\,1: Galaxy.
+Col.\,2: \ion{H}{ii} mass derived from the H$\beta$ line in the VIMOS data, assuming a Balmer decrement of 2.85.
+Col.\,3: \ion{H}{ii} mass derived from the H$\alpha$ line in the MUSE data.
+Col.\,4: Balmer decrement measured from the MUSE data.
+Col.\,5: Main source of ionizing radiation (see Section \ref{sec:Diagnostics} for a description of the different classes).
+-- means we have no data.}
+		\label{tab:gasMass}
+		% \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l r r r l}
+		\begin{tabular}{l c c c c}
+			\hline
+			\hline
+			Galaxy & \multicolumn{2}{c}{\ion{H}{ii} Mass} & Balmer & LINER/ \\
+			& VIMOS\tnote{a} & MUSE & Decrement & Seyfert \\
+			& ($\log\mathrm{M_\odot}$) & ($\log\mathrm{M_\odot}$) & \\
+			\hline
+			ESO 443-G024 & $5.02 \pm 0.01$ 	& --  		& -- & LINER \\
+			IC 1459 	& $5.21 \pm 0.01$	& $5.50 \pm 0.01$ & $4.54 \pm 0.12$ & LINER-AGN\\
+			IC 1531 	& $5.09 \pm 0.01$	& -- 		& -- & Seyfert 2\\
+			IC 4296		& $5.43 \pm 0.01$	& $< 4.48$ 	& \tnote{b} & LINER-AGN \\
+			NGC 612 	& $6.00 \pm 0.01$ 	& -- 		& -- & LINER-AGN \\
+			NGC 1316 	& -- 				& $ 5.29 \pm 0.01$ & $3.52 \pm 0.11$ & LINER-AGN \\
+			NGC 1399 	& $< 3.86$ 			& $ 4.54 \pm 0.01$ & $< 21.4$\tnote{c} & LINER \\
+			NGC 3100 	& $5.26 \pm 0.01$	& -- 		& -- & LINER-AGN \\
+			NGC 3557 	& $4.61 \pm 0.02$ 	& -- 		& -- & LINER \\
+			NGC 7075 	& $4.68 \pm 0.01$	& -- 		& -- & LINER \\
+			PKS 718-34  & $< 5.08$	 		& -- 		& -- & Passive \\
+			\hline
+			\hline
+			\multicolumn{4}{l}{$^{a}$The VIMOS flux calibration and thus the derived gas masses are only approximate (see Section \ref{sec:obs} for more detail on the flux calibration)}.
+			\multicolumn{4}{l}{$^{b}$Both H$\alpha$ and H$\beta$ are not detected with A/N $>2.5$, so no information can be gained.}
+			\multicolumn{8}{l}{$^{c}$H$\beta$ is not detected with A/N $> 2.5$, so the fit is unreliable (hence an upper limit).}
+		\end{tabular}
+	% 	\begin{tablenotes}
+	% 	\footnotesize
+	% 	\note Col.\,1: Galaxy.
+Col.\,2: \ion{H}{ii} mass derived from the H$\beta$ line in the VIMOS data, assuming a Balmer decrement of 2.85.
+Col.\,3: \ion{H}{ii} mass derived from the H$\alpha$ line in the MUSE data.
+Col.\,4: Balmer decrement measured from the MUSE data.
+Col.\,5: Main source of ionizing radiation (see Section \ref{sec:Diagnostics} for a description of the different classes).
+-- means we have no data.
+	% 	\item [a] The VIMOS flux calibration and thus the derived gas masses are only approximate (see Section \ref{subsec:VIMOSreduction} for more detail on the flux calibration).
+	% 	\item [b] Both H$\alpha$ and H$\beta$ are not detected with A/N $>2.5$, so no information can be gained.
+	% 	\item [c] H$\beta$ is not detected with A/N $> 2.5$, so the fit is unreliable (hence an upper limit). 
+	% 	\end{tablenotes}
+	% \end{threeparttable}
+	\end{table*}
+
+	Total ionized gas masses are derived using the prescription of \citet{Sarzi2005}.
+This is a very rough calculation and the values should not be used for quantitative applications.
+The approach follows \citet{Kim1989}, whereby
+	\begin{equation}
+		\left(\frac{M_\text{\ion{H}{ii}}}{M_\odot}\right) = 280 \left(\frac{D}{10\, \mathrm{Mpc}}\right)^2 \left(\frac{F(\mathrm{H\alpha})}{10^{-14} \, \mathrm{erg \, s^{-1} \, cm^{-2}}}\right) \left(\frac{10^3 \, \mathrm{cm^{-3}}}{n_\mathrm{e}}\right) \, ,
+	\end{equation}
+	where $M_\text{\ion{H}{ii}}$ is the total mass of \ion{H}{ii} in the galaxy, $D$ is the galaxy distance, and $F(\mathrm{H\alpha})$ is the H$\alpha$ flux measured from the spectrum created by summing spatially all spaxels within an aperture of $\frac{R_\mathrm{e}}{2}$ (chosen to exclude outer noisy regions of the observations, but include spatially extended gas regions).
+This method assumes an electron density $n_\mathrm{e} = 100 \, \mathrm{cm^{-3}}$, a temperature of $10^4$ K and case-B recombination (electrons above 13.6\,eV are not reabsorbed; e.g.\ \citealt[p.\,74]{Osterbrock1974}).
+Like \citet{Sarzi2005}, we only claim a detection if the amplitude-to-noise ratio (A/N) is $>4$ for [\ion{O}{iii}] and $>2.5$ for H$\beta$ or H$\alpha$.
+Upper limits are calculated using the $1\sigma$ noise level (see Section \ref{subsubsec:EmissionFit}).
+
+	Our calculated gas masses are given Table \ref{tab:gasMass} and are at the upper limit of, and possibly exceed, the typical masses observed in ETGs.
+Given that our sample contains particularly massive galaxies, high ionized gas masses are not unexpected, however.
 

### 2018-01-17 paper.tex
EoDC:
Further work ISM section

 On branch master
 Changes to be committed:
	new file:   EqW_fit.png
	new file:   Halpha_profile.png
	new file:   Hbeta_profile.png
	new file:   nuclear_MEx.png
	modified:   paper.tex
	new file:   ratio_fit.png

@@
 		\subsubsection{Ellipticity}
+			\label{subsubsec:ellip}
 			In this paper, ellipticity is that of the best-fitting ellipse to the surface-brightness map with an mean radius $R_\text{m}$, of 1 effective radius $R_\text{e}$.
@@
 		\subsubsection{Kinematic Position Angle}
+			\label{subsubsec:KinPA}
 			The kinematic position angle, $PA_\text{kin}$, is defined as the angle of the axis perpendicular to the apparent angular momentum vector westwards from North.
@@
 
-			Col.\,4 in Table \ref{tab:classify} lists the misalignments between the photometric and kinematic position angles, $\Gamma_\text{kin} \equiv \arcsin(\sin[PA_\text{phot} - PA_\text{kin}])$.
+			Col.\,4 in Table \ref{tab:classify} lists the misalignments between the photometric and stellar kinematic position angles, $\Gamma_\text{kin} \equiv \arcsin(\sin[PA_\text{phot} - PA_\text{kin}])$.
 
@@
 		Given that there is no well defined list of corrections (and methods) that is universally followed, care must be taken when making comparisons to the literature.
-When comparing to a particular paper we correct for the same effects described in the paper, but using our methods, as described in Section \ref{subsec:Absorption}.
+When comparing to a particular paper we correct for the same effects described in the paper, but using our methods, as described in Section \ref{subsec:absorption}.
 As in Section \ref{subsec:Mgsigma} we use a resolution of 8.4\,\AA\ FWHM in order to use the transformation function provided by \citet{Vazdekis2010} from Lick/IDS system to the LIS.
@@
 	We have assumed that a given spectrum from our Southern sample can be well approximated by a SSP.
-We use the method described in Section \ref{subsubsec:StellarPop} to produce maps of the most-likely SSP characteristics: age ($t$), metallicity ($Z/H$) and alpha-element enhancement ($\alpha$/Fe) from the absorption line strength maps (see Appendix \ref{sec:Maps}).
+We use the method described in Section \ref{subsubsec:stellarPop} to produce maps of the most-likely SSP characteristics: age ($t$), metallicity ($Z/H$) and alpha-element enhancement ($\alpha$/Fe) from the absorption line strength maps (see Appendix \ref{sec:Maps}).
 
@@
 	As can be seen from the maps in Appendix \ref{sec:Maps}, both NGC 612 and NGC 3100 have significant off-centre clouds of ionized gas.
-The latter is spatial coincident with both the radio jet and the gap in the CO ring (this is discussed further in Section \ref{subsec:BPT}), while former seems to no link with either the radio jet (a massive scale jet extending several $\sim 200$\,kpc to the east and west of the galaxy centre) or the CO.
+The latter is spatial coincident with both the radio jet and the gap in the CO ring, while former seems to no link with either the radio jet (a massive scale jet extending several $\sim 200$\,kpc to the east and west of the galaxy centre) or the CO.
 
@@
 Col.\,4: Balmer decrement measured from the MUSE data.
-Col.\,5: Main source of ionizing radiation (see Section \ref{sec:Diagnostics} for a description of the different classes).
+Col.\,5: Main source of ionizing radiation (see Section \ref{subsec:Diagnostics} for a description of the different classes).
 -- means we have no data.}
@@
 Col.\,4: Balmer decrement measured from the MUSE data.
-Col.\,5: Main source of ionizing radiation (see Section \ref{sec:Diagnostics} for a description of the different classes).
+Col.\,5: Main source of ionizing radiation (see Section \ref{subsec:Diagnostics} for a description of the different classes).
 -- means we have no data.
@@
 Given that our sample contains particularly massive galaxies, high ionized gas masses are not unexpected, however.
+
+	\subsection{Ionized Gas Kinematics}
+		\label{subsec:GasKin}
+		Map of the best-fitting kinematics (mean velocity and velocity dispersion), as found with the methods described in Section \ref{subsubsec:EmissionFit} for the 4 galaxies (IC 1459, NGC 612, NGC 1316 and NGC 3100) with detected spatially-extended emission lines are shown in Appendix \ref{sec:Maps}.
+Due to that fact that, unlike stars, gas is dissipational, it is to be expected that given sufficient time, the ISM will always settle into a disc.
+These maps show that the ISM of the Southern sample galaxies varies from largely settled discs in IC 1459 and NGC 612 to more disordered kinematics of NGC 3100 and a possible inflow in NGC 1316.
+
+		It is immediately clear when comparing the mean stellar velocity maps to the mean gas velocity maps that where gas is detected, its angular momentum is not often aligned with that of the stars.
+A misalignment between the kinematics of the stars and gas suggests an external origin for the gas (e.g.\ accretion or wet merger).
+However it should be noted that the converses is not necessarily true: aligned kinematics is consistent with an internal origin (e.g.\ stellar-mass loss), but it does \emph{not} require it \citep[e.g.][]{Davis2011a}.
+
+		We now comment on each galaxy in turn.
+
+		\paragraph{IC 1459} has ionized gas counter-rotating with respect to the stellar kinematically-decoupled core, and also rotating independently from the rest of the galaxy.
+\citet{Franx1988} claim that the rotation of the gas is aligned with that of the stars outside of the KDC, however we observe outer stellar kinematics to be non-rotating.
+As the stellar disc did not survive the merger even that created the KDC, it is unlikely that the gas in IC 1459 progenitor galaxy survived.
+The lost gas may, however, have been re-accreted.
+Alternatively, the ISM may have yet another external origin.
+
+		\paragraph{NGC 612} has well aligned stellar and gaseous kinematics.
+The misalignment between the position angle of the stellar and gas kinematics (using the method described in Section \ref{subsubsec:KinPA}) is just $1\fdg0\pm0\fdg7$, consistent with an internal origin for the gas.
+This adds to the evidence that NGC 612 has not undergone a major merger (major mergers exhaust galaxies of their gas and destroy a stellar disc) and suggests that, the fueling and powering of the radio jet must be a purely secular process.
+
+		\paragraph{NGC 1316} is a complex object.
+Since there are redshifted emission lines with respect to the rest frame of the galaxy on both sides of the galaxy, the gas is not in a settled disc and that there must be some inflow/outflows.
+		% We used a fitting routine based on the method of \citet{Swinbank2012}, \citet{Stott2016} and Tiley et.al.\ (in prep.) to fit an exponential disc (middle panel of Fig.\ \ref{fig:Inflow}) to the ionized gas mean velocity map (left panel), with the residuals shown in the right panel of Fig.\ \ref{fig:Inflow}.
+This shows a large residual on the southwest side of the galaxy, which we interpret as an inflow towards the nucleus, almost perpendicular to the radio jet.
+However, there are still significant residuals in other parts of the galaxy, suggesting that the model may not be a good representation of the reality of the galaxy, thus other interpretations are possible, and better quality data (longer exposure times) are required to add certainty to this interpretation.
+Nevertheless, it is clear that the gas in not in a settled disc.
+		Without filling in some of the regions were we do not detect emission lines through additional observations, it is impossible to judge the state or even existence of a disc.
+
+		% \begin{figure}
+		% 	\centering
+		% 	\includegraphics[width=\textwidth]{ngc1316_inflow.png}
+		% 	\caption[Inflows in NGC 1316]{Ionized gas inflows in NGC 1316.
+Left: [\ion{O}{iii}] mean velocity map.
+Middle: best-fitting model.
+Right: Residual map = mean velocity - model.
+A large region, redshifted with respect to the galaxy, can be seen in the southwest which we interpret as an inflow.
+Contours are as in Fig.\ \ref{fig:VIMOS_OIII}.}
+		% 	\label{fig:Inflow}
+		% \end{figure}
+
+		\paragraph{NGC 3100} has an interesting ISM morphology.
+The \ce{^{12}CO(2-1)} contours (shown in cyan in all figures) show a broken ring with the radio jet passing through the gaps in the ring (Ruffa et\,al., in prep.).
+We observe the ionized gas to be brightest in the gaps of this ring which we interpret as additional excitation of the gas due to shocks from the impact of the jet.
+The simplest comment that we can make of the ionized gas kinematics is that it is completely different than that of the stars.
+Secondly, that the centre of rotation of the gas appears to be offset from the centre of the galaxy (as defined by the stellar surface brightness) by several arcseconds to the west.
+
+		\subsubsection{Kinematic Misalignments}
+			\citet{Davis2011a} showed that $36\pm5$\% of fast rotators have ionized gas kinematics misaligned with respect to the stellar kinematics, while slow rotators have a flat distribution with respect to their misalignment angles \citep[see fig.\ 4]{Davis2011a}.
+This indicates that slow rotators are dominated by external sources of gas, while fast rotators can have either internal or external sources.
+This is consistent with our observations of the Southern Sample: the only slow rotator with detected ionized gas is IC 1459, which has significantly kinematically-misaligned gas; of the 3 fast rotators, only 1 (NGC 3100) is definitely misaligned, while NGC 612 is consistent with an internal gas origin and NGC 1316 is not clear.
+%, although the best-fitting exponential disc model (see Fig.\ \ref{fig:Inflow}) is definitely misaligned to the stellar kinematics.
+
+	\subsection{Ionization Sources}
+		\label{subsec:Diagnostics}
+		Determining the sources of ionizing radiation in galaxies using emission line ratios, such as Baldwin\,--\,Phillips\,--\,Terlevich (BPT) plots (\citealt{Baldwin1981}; revised by \citealt{Kewley2001, Kewley2006} and \citealt{Kauffmann2003a}), has become increasingly widespread exercise.
+That said, there are several important caveats.
+Firstly, great care must be taken when applying each diagnostic; much of the literature misinterprets the resulting classifications.
+Secondly, in the absence of spatially-resolved spectra, low-ionization nuclear emission-line region (LINER) classifications have often been taken as a marker for jet-mode active galactic nuclei (AGN).
+However, several recent surveys have shown that many of these may not be bona fide AGN \citep[e.g.][]{Sarzi2005, Sarzi2010, Singh2013, Belfiore2016a}.
+In these cases, the emission may not even originate exclusively from the centres of the galaxies, the location of the putative AGN.
+This led to the creation of the low-ionization emission-line region (LIER) classification, with the same criteria as LINERs, but not necessarily restricted to the nuclear regions.
+
+		The problem with classifying ETGs by their emission lines is that they often have very little ionized gas and weak ionizing radiation fields, so that it is often difficult to detect emission lines from their ISM.
+Furthermore, the BPT plots require a larger spectral range than many integral-field spectrographs (IFS) deliver.
+This has given rise to a number of other, analogous, classifying plots, that we take advantage of here.
+A description of our ionization source classifying process follows below.
+
+		Firstly, we preferentially use the BPT plots for the galaxies observed with MUSE (that has the required spectral range).
+This allows us to classify galaxies into star-forming, LINER/LIER or Seyfert 2 classes.
+For the emission-line fluxes derived from the VIMOS datacubes, we use the [\ion{N}{i}]/H$\beta$ versus [\ion{O}{iii}]/H$\beta$ plot of \citet[hereafter the SAURON plot]{Sarzi2010}.
+Unlike the BPT plots, \citet{Sarzi2010} do not define classification boundaries.
+Using Eq.\,\ref{eq:N_dec} we translate the [\ion{N}{ii}]/H$\alpha$ BPT plot classification boundaries of \citet{Kewley2001} and \citet{Kauffmann2003a} to the [\ion{N}{i}]/H$\beta$ SAURON plot.
+This allows us to classify galaxies into star-forming or LINER/Seyfert 2 classes.
+We also use the so-called WHaN2 plot (H$\alpha$ equivalent width versus [\ion{N}{ii}]/H$\alpha$) from \citet{CidFernandes2011}.
+Using Eqs.\,\ref{eq:EqW_dec} and \ref{eq:N_dec}, we transform the boundary lines into a H$\beta$ equivalent width versus [\ion{N}{i}]/H$\beta$ (WHbN1) plot for the VIMOS data.
+This allows us to classify galaxies into star-forming, strong AGN (Seyfert 2), weak AGN (LINER) or retired classes.
+
+		To check if the LINER classifications are due to a central radiation source (such as an AGN) or extended sources (such as weak star formation or post-asymptotic giant branch stars; pAGB stars), we examine the H$\alpha$ and H$\beta$ flux radial profiles of our galaxies with extended detected ionized gas (see Section \ref{subsubsec:Hb}).
+Finally we use the mass\,--\,excitation (MEx) plot of \cite{Nyland2016}, using parameters derived from the central region of the galaxies, only measured within a 3\arcsec wide aperture (see Section \ref{subsubsec:MEx}).
+This allows us to classify into star-forming, Seyfert 2, LINER, transition or passive classes, with LINER galaxies subdivided into those whose LINER behaviour is (LINER-AGN) or is not attributed to a central AGN.
+
+		% \subsection{BPT Diagnostics}
+		% 	\label{subsec:BPT}
+		% 	Firstly, in Fig.\,\ref{fig:BPT}, we examine our galaxies using the classic BPT diagnostic plots.
+For the plots using [\ion{N}{ii}]/H$\alpha$, [\ion{S}{ii}]/H$\alpha$ and [\ion{O}{i}]/H$\alpha$ versus [\ion{O}{iii}]/H$\beta$, we can only use the emission-line fluxes derived from our MUSE datacubes, as the lines necessary for gauging the hardness of the ionizing radiation field are outside the spectral range of VIMOS.
+Only two MUSE galaxies have detections of the necessary emission lines: IC 1459 and NGC 1316.
+Both occupy very similar positions in the BPT plots, on or close to the boundary between the Seyfert 2 and LINER classes.
+On the whole, the central bins tend to be on the LINER side.
+
+		% 	\begin{figure}
+		% 		\centering
+		% 		\includegraphics[width=.9\textwidth]{chapter5/BPT.png}
+		% 		\caption[BPT plots]{BPT plots for IC 1459 and NGC 1316.
+The colour scale (blue to yellow) represents increasing distance from the galaxy centre.
+The classification boundaries are from \citet{Kewley2006}.\label{fig:BPT}}
+		% 	% \end{figure}
+
+		% 	% \begin{figure}
+		% 	% 	\centering
+		% 		\includegraphics[width=0.7\textwidth]{chapter5/SAURON.png}
+		% 		\caption[An alternative diagnostic plot]{SAURON diagnostic plot for the line ratios available in the VIMOS datacubes.
+To show the expected position of LINERs on the SAURON plot, the MAPPINGS-III shock model grid of \citet{Allen2008} is shown in green.
+The solid lines are lines of constant shock velocity (from 150 to 1000\,$\mathrm{km\,s^{-1}}$) and the dotted lines are lines of constant magnetic parameter $b \equiv B/\sqrt{n}$ (from 0.5 to 4.0), where $B$ is the magnetic field strength and $N$ the (pre-shock) particle number density \citep{Dopita1996}.
+All models assume an electron density of $n_\mathrm{e} = 1\,\mathrm{cm^{-3}}$.\label{fig:SAURON}}
+		% 	\end{figure}
+
+		% 	\citet{Sarzi2010} showed that Seyferts, LINERs and star-forming galaxies are reasonable separated in the SAURON diagnostic plot.
+To exploit the VIMOS datacubes we thus use the [\ion{N}{ii}]\,--\,[\ion{N}{i}] relation derived in Section \ref{subsec:Ndec}, along with the Balmer decrement, to transform the \citet{Kewley2001} extreme starburst and the \citet{Kauffmann2003a} pure star-formation boundaries in the [\ion{N}{ii}]/H$\alpha$ versus [\ion{O}{iii}]/H$\beta$ plot to boundaries in the SAURON plot.
+For the MUSE datacubes, only IC 1459 and NGC 1316 have detections of [\ion{N}{i}].
+Given that we already have the superior classic BPT plots for these galaxies, we only show the VIMOS-derived SAURON diagnostic plot.
+This is shown in Fig.\,\ref{fig:SAURON} for all 6 VIMOS galaxies with detectable, spatially-resolved emission lines.
+All exhibit LINER-AGN behaviour.
+
+		% 	NGC 3100 appears to occupy to distinct regions in the SAURON diagnostic plot (Fig.\ \ref{fig:SAURON}).
+If the ionization is due to shocks from the impact of the jet, then using the shock models of \citet{Allen2008}, we can see that the right-hand group of bins have been ionized by a higher shock velocity that the left-hand group.
+As can be seen in Fig.\ \ref{fig:ngc3100_NI_Hb}, these bins are directly in the gap (presumable created by the jet blowing a hole) in the CO ring.
+
+		% 	\begin{figure}
+		% 		\centering
+		% 		\includegraphics[width=0.5\textwidth]{chapter5/vimos/ngc3100_NI_Hb.png}
+		% 		\caption[NGC 3100 \bracket{\ion{N}{i}}/H$\beta$ line ratio map]{The [\ion{N}{i}]/H$\beta$ line ratio map of NGC 3100, showing the hardest ionization field is in gap in the CO ring (cyan contours), spatially coincident with the radio jet (green contours).
+Surface brightness contours are in black.}
+		% 		\label{fig:ngc3100_NI_Hb}
+		% 	\end{figure}
+
+		% \subsection{WHaN2 Plots}
+		% 	\label{subsec:WHaN2}
+		% 	\begin{figure}
+		% 		\centering
+		% 		\includegraphics[width=0.8\textwidth]{chapter5/WHaN2.png}
+		% 		\caption[WHaN2 plot for IC 4296]{WHaN2 plot for IC 4296. The colour scale (blue to yellow) represents increasing distance from the galaxy centre.}
+		% 		\label{fig:WHaN2}
+		% 	\end{figure}
+
+		% 	\begin{figure}
+		% 		\centering
+		% 		\includegraphics[width=0.8\textwidth]{chapter5/WHbN1.png}
+		% 		\caption[VIMOS WHbN1 plot]{VIMOS WHbN1 plot. All galaxies have decreasing H$\beta$ emission with increasing distance from the galaxy centre.}
+		% 		\label{fig:WHbN1}
+		% 	\end{figure}
+
+		% 	The final spatially-resolved line ratio diagnostic plot that we use is that of the equivalent width of H$\alpha$ versus $\log([\text{\ion{N}{ii}}]/H\alpha)$, known as the WHaN2 plot \citep{CidFernandes2011}.
+We interpret the strong AGN, weak AGN and retired regions on this plot as Seyfert 2, LINER-AGN and LIER classifications, respectively.
+Passive (i.e.\ line-less) galaxies are marked with crosses instead of circles.
+Fig.\,\ref{fig:WHaN2} shows the WHaN2 plot for the MUSE derived emission lines of IC 4296 where almost all the bins fall within the weak AGN (LINER-AGN) class.
+This is consistent with the measurements from the VIMOS observations of the IC 4296 as shown in the SAURON diagnostic plot, where IC 4296 is well within the shocks grid (i.e.\ LINERs; see Fig.\ \ref{fig:SAURON}).
+We do not include IC 1459 and NGC 1316, as they have already been classified via the classic BPT plots (see Section \ref{subsec:BPT}).
+
+		% 	For the emission lines measured from the VIMOS datacubes, we use H$\beta$ as a proxy for H$\alpha$ and [\ion{N}{i}] as a proxy for [\ion{N}{ii}] utilising the relations found in Section \ref{subsec:Ndec} to transform the classification boundaries (see Section \ref{subsec:Ndec}).
+We call the resulting diagnostic plot the WHbN1 plot, shown in Fig.\,\ref{fig:WHbN1}.
+While in Section \ref{subsec:BPT} (Fig.\,\ref{fig:SAURON}) we showed that most of these galaxies had line ratios consistent with being ionized by shocks such as in LINER-like galaxies, Fig.\,\ref{fig:WHbN1} shows that for IC 1459 and NGC 3100, the ionizing photons originate from the AGN.
+
+		\subsubsection{H$\alpha$ and H$\beta$ Profiles}
+			\label{subsubsec:Hb}
+
+			\begin{figure}
+				\centering
+				\includegraphics[width=\columnwidth]{Hbeta_profile.png}
+				\caption[VIMOS H$\beta$ radial profiles]{H$\beta$ flux radial profiles derived from the VIMOS datacubes. Solid red lines show $F(\mathrm{H\beta}) \propto r^{-2}$.}
+				\label{fig:Hb_profile_VIMOS}
+			\end{figure}
+
+			\begin{figure}
+				\centering
+				\includegraphics[width=0.73\columnwidth]{Halpha_profile.png}
+				\caption[MUSE H$\alpha$ radial profiles]{H$\alpha$ flux radial profiles derived from the MUSE datacubes. Solid red lines show $F(\mathrm{H\alpha}) \propto r^{-2}$.}
+				\label{fig:Ha_profile_MUSE}
+			\end{figure}
+
+			As discussed above, many galaxies classified as LINERs are in fact LIERs \citep[see e.g.][]{Sarzi2005, Sarzi2010, Singh2013, Belfiore2016}, i.e.\ the source of the ionizing radiation is not concentrated in the nuclear regions of the galaxies.
+To check if the ionizing radiation is entirely due to an AGN throughout the host galaxy, we plot the H$\alpha$ and H$\beta$ flux radial profiles for the MUSE and VIMOS data in Figs.\,\ref{fig:Ha_profile_MUSE} and \ref{fig:Hb_profile_VIMOS}, respectively.
+A point source, such as an AGN, will result in a profile having a $r^{-2}$ shape, where $r$ is the distance of the bin from the galaxy centre.
+A shallower profile points to a spatially-extended source, presumably non-circumnuclear stellar processes such as star formation or radiation from pAGB stars, as the dominant cause of the ionization in the outer parts of the galaxy (i.e.\ LIER rather than LINER).
+All the galaxies with spatially-extended Balmer emission in our Southern Sample revel a central point source as the dominant source of the ionizing photons.
+The H$\beta$ profile of NGC 612 has a larger scatter suggesting that stellar processes also have some impact (likely radiation from pAGB stars, as these galaxies are ETGs and therefore likely have low star-formation rates).
+
+		\subsubsection{MEx Diagnostic Plots}
+			\label{subsubsec:MEx}
+			\begin{figure}
+				\includegraphics[width=\columnwidth]{nuclear_MEx.png}
+				\caption[Nuclear mass\,--\,excitation plot]{Nuclear MEx plot, allowing to classify the sources of the ionizing radiation within the central 3\arcsec.
+Data points derived from the VIMOS and MUSE datacubes are in red and blue, respectively.
+Crosses mark galaxies with [\ion{O}{iii}]$\lambda$5007 equivalent width $> 0.8$\,\AA, while filled circles show galaxies with [\ion{O}{iii}]$\lambda$5007 equivalent width $\leqslant 0.8$\,\AA.
+The VIMOS and MUSE data points of IC 1459 are linked with a black dashed line.
+Classification boundaries are from \citet{Nyland2016}.}
+				\label{fig:MEx}
+			\end{figure}
+
+			The mass\,--\,excitation (MEx) plot of \citet{Juneau2011} is useful to classify galaxies with intermediate excitation levels ($0.5 < \mathrm{[\ion{O}{iii}]/H\beta} < 8.0$), particularly as it does not depend on faint lines such as the [\ion{N}{I}] doublet.
+We use here the calibrations by \citet{Nyland2016}, including an attempt to separate LINERs powered by AGN from those powered by pAGB stars (the former have [\ion{O}{iii}] equivalent widths $>0.8$\,\AA).
+We use an aperture of 3\arcsec\ to plot the nuclear MEx for our Southern Sample galaxies, and the resulting diagnostic plot is shown in Fig.\,\ref{fig:MEx}.
 
@@
 
+\section{Extrapolating VIMOS Data}
+	\label{sec:Decrement}
+	\begin{figure}
+		\includegraphics[width=\columnwidth]{ratio_fit.png}
+		\caption[\bracket{\ion{N}{ii}}/H$\alpha$ vs \bracket{\ion{N}{i}}/H$\beta$]{Upper panel: [\ion{N}{ii}]/H$\alpha$ vs [\ion{N}{i}]/H$\beta$ line ratios for the galaxies IC 1459 and NGC 1316, used to transform the classification boundaries e.g.\ the classic [\ion{N}{ii}] BPT plot to the SARUON diagnostic plot.
+Lower panel: Residuals = ([\ion{N}{ii}]/H$\alpha$ - best-fit)/[\ion{N}{i}]/H$\beta$.
+The solid line shows the best-fitting (Eq.\ \ref{eq:N_dec}) in both panels, while the dashed and dotted lines show the 68 and 99 percentiles, respectively.}
+		\label{fig:ratio_relation}
+	\end{figure}
+
+	\begin{figure}
+		\includegraphics[width=\columnwidth]{EQw_fit.png}
+		\caption[Comparing H$\alpha$ and H$\beta$ equivalent widths]{Upper panel: H$\alpha$ vs H$\beta$ equivalent widths for the galaxies IC 1459 and NGC 1316 used to transform the classification boundaries of diagnostics involving the H$\alpha$ equivalent width to those involving H$\beta$.
+Lower panel: Residuals = (EW(H$\alpha$) - best-fit)/EW(H$\beta$).
+The solid line shows the best-fitting (Eq.\ \ref{eq:EqW_dec}) in both panels, while the dashed and dotted lines show the 68 and 99 percentiles, respectively.}
+		\label{fig:EqW_relation}
+	\end{figure}
+
+	% The Balmer decrement, $d_\mathrm{H}$, is the ratio of the H$\alpha$ to H$\beta$ fluxes.
+There are good theoretical motivations for this ratio to be near constant at $d_\mathrm{H} = 2.86$, under a wide variety of conditions.
+In reality, however, higher values are routinely observed.
+These can be explained as due to either the presence of dust causing extinction (whereby emission lines at shorter wavelengths appear dimmer than expected from their redder counterparts due to dust preferentially scattering and absorbing bluer light) or some mechanism that populates hydrogen levels from the ground up.
+Such mechanisms may be important in high-density environments, such as within powerful (type 1) AGN \citep[e.g.][]{Shields1974, Netzer1975}.
+	%
+	% The majority ($\approx 60$\%) of ETGs and all LINER and Seyfert galaxies are dusty \citep[e.g.][]{Martini2013}. 
+	% Such galaxies reveal clear dust lanes in \textit{Hubble Space Telescope (HST)} observations \citep[e.g.][]{Martini2013}, are bright in the infrared (where the thermal emission from dust is seen as a dust ``bump''; e.g.\ \citealt{Jura1987, Knapp1992}), and possess other emission lines \citep[e.g.\ \bracket{\ion{S}{ii}};][]{Wampler1968} showing similar reddening.
+Thus, assuming the observed steepening of the Balmer decrement is entirely due to dust, the ratio of the observed decrement to the theoretical value of 2.86 is a good estimate of the dust reddening.
+
+	If we assume that different ionization states of a given atomic species occur in the same spatial location, then shielding is not important or at least is linear in its effect on the emission-line ratios.
+Given that the different states are then produced under the same conditions, it is natural to expect a simple relationship between their emission line fluxes, similar to the Balmer decrement.
+We exploit such relationships to transform classification boundaries from diagnostic plots which use emission lines outside of the spectral range of VIMOS to diagnostics which can be measured with our VIMOS data e.g.\ transform from the classic BPT [\ion{N}{ii}]/H$\alpha$ versus [\ion{O}{iii}]/H$\beta$ to [\ion{N}{i}]/H$\beta$ versus [\ion{O}{iii}]/H$\beta$ diagnostic plot (hereafter the SAURON diagnostic plot) of \citet{Sarzi2010}.
+We achieve this by finding a best-fitting relationship between the relevant measurements taken in each bin of the galaxies for which we have the relevant detections in our MUSE data (due to the lack of detectable emission line in the observations of IC 4296 and NGC 1399, we therefore use the observations of IC 1459 and NGC 1316).
+This relationship is then applied to the diagnostic boundary lines in the relevant plots below.
+We emphasize that these are purely empirical relationships and thus differ substantially from the Balmer decrement with its strong theoretical basis (although these relationships include the effect of the Balmer decrement).
+
+	The two transformations that we use are from [\ion{N}{ii}]/H$\alpha$ to [\ion{N}{i}]/H$\beta$ line ratios and from the H$\alpha$ to the H$\beta$ equivalent widths.
+In both cases we fit a linear relationship $y = Ax + B$ using the least-trimmed squares routine, \textsc{lts\_linefit}\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/\#lts} of \citet{Cappellari2013} due to its robust handling of the uncertainties along both axes.
+These are shown in Figs.\ \ref{fig:ratio_relation} and \ref{fig:EqW_relation}, where we find
+	\begin{equation}
+		\frac{[\text{\ion{N}{ii}}]}{H\alpha} = \, (0.38 \pm 0.02) \frac{[\text{\ion{N}{i}}]}{H\beta} + (1.80 \pm 0.02)
+	\end{equation}
+	and	
+	\begin{equation}}
+		\mathrm{EW}(H\alpha) = \, (2.92 \pm 0.03) \mathrm{EW}(H\beta) - (0.16 \pm 0.02) \, ,
+			\label{eq:EqW_dec}
+	\end{equation}
+	respectively.
+Since it is sometimes observed that [\ion{N}{ii}]/H$\alpha < 1.80$, which if blindly applying the relationship found above, results in an unphysical [\ion{N}{i}]/H$\beta < 0$ (i.e.\ negative flux), we instead rearrange and use
+	\begin{equation}
+		\frac{[\text{\ion{N}{i}}]}{H\beta} = \, 
+		\begin{cases}
+			(0.38 \pm 0.02) \frac{[\text{\ion{N}{iI}}]}{H\alpha} + (1.80 \pm 0.02), & \text{if}\ \frac{[\text{\ion{N}{ii}}]}{H\alpha} < 2 \\
+			(0.38 \pm 0.02) \frac{[\text{\ion{N}{ii}}]}{H\alpha}, & \text{otherwise.}
+		\end{cases}
+		\label{eq:N_dec}
+	\end{equation}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-01-20 paper.tex
EoDC:
Only introduction and abstract to write?

Working on routine to produce the maps for the appendices.

 On branch master
 Changes to be committed:
	modified:   paper.tex
	new file:   produce_maps.py

@@
 \usepackage{mhchem} 	% typeset chemistry symbols
-\usepackage{multicol} 	% Multi-column entries in tables
+% \usepackage{multicol} 	% Multi-column entries in tables
 % \usepackage{natbib} % references in text to look like MNRAS/ApJ/A&A
 % \usepackage{multirow} % for multirow command
-% \usepackage{array} % For wrapping text in cell in tables
+\usepackage{array} % For wrapping text in cell in tables with multicolumntype
 
@@
 \defcitealias{Thomas2010}{TMJ} % TMJ alias
-% \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} % 
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} % Multi-column entries in tables with text wrapping 
 \newcommand{\bracket}[1]{[#1]} % to be able to use [] in arguments
@@
 			\hline
-			\multicolumn{8}{l}{$^{a}$Tentative classification. A higher signal-to-noise ratio (S/N) in the outer regions of the field of view is required for confirmation.}
+			\multicolumn{8}{L{.7\linewidth}}{$^{a}$Tentative classification. A higher signal-to-noise ratio (S/N) in the outer regions of the field of view is required for confirmation.}
 
@@
 			\hline
-			\multicolumn{4}{l}{$^{a}$The VIMOS flux calibration and thus the derived gas masses are only approximate (see Section \ref{sec:obs} for more detail on the flux calibration)}.
-			\multicolumn{4}{l}{$^{b}$Both H$\alpha$ and H$\beta$ are not detected with A/N $>2.5$, so no information can be gained.}
-			\multicolumn{8}{l}{$^{c}$H$\beta$ is not detected with A/N $> 2.5$, so the fit is unreliable (hence an upper limit).}
+			\multicolumn{5}{L{.7\linewidth}}{$^{a}$The VIMOS flux calibration and thus the derived gas masses are only approximate (see Section \ref{sec:obs} for more detail on the flux calibration).} \\
+			\multicolumn{5}{L{.7\linewidth}}{$^{b}$Both H$\alpha$ and H$\beta$ are not detected with A/N $>2.5$, so no information can be gained.} \\
+			\multicolumn{5}{L{.7\linewidth}}{$^{c}$H$\beta$ is not detected with A/N $> 2.5$, so the fit is unreliable (hence an upper limit).}
 		\end{tabular}
@@
 				\includegraphics[width=\columnwidth]{Hbeta_profile.png}
-				\caption[VIMOS H$\beta$ radial profiles]{H$\beta$ flux radial profiles derived from the VIMOS datacubes. Solid red lines show $F(\mathrm{H\beta}) \propto r^{-2}$.}
+				\caption{H$\beta$ flux radial profiles derived from the VIMOS datacubes. Solid red lines show $F(\mathrm{H\beta}) \propto r^{-2}$.}
 				\label{fig:Hb_profile_VIMOS}
@@
 				\includegraphics[width=0.73\columnwidth]{Halpha_profile.png}
-				\caption[MUSE H$\alpha$ radial profiles]{H$\alpha$ flux radial profiles derived from the MUSE datacubes. Solid red lines show $F(\mathrm{H\alpha}) \propto r^{-2}$.}
+				\caption{H$\alpha$ flux radial profiles derived from the MUSE datacubes. Solid red lines show $F(\mathrm{H\alpha}) \propto r^{-2}$.}
 				\label{fig:Ha_profile_MUSE}
@@
 				\includegraphics[width=\columnwidth]{nuclear_MEx.png}
-				\caption[Nuclear mass\,--\,excitation plot]{Nuclear MEx plot, allowing to classify the sources of the ionizing radiation within the central 3\arcsec.
+				\caption{Nuclear MEx plot, allowing to classify the sources of the ionizing radiation within the central 3\arcsec.
 Data points derived from the VIMOS and MUSE datacubes are in red and blue, respectively.
@@
 
+\section{Discussion and Conclusions}
+	\label{sec:discuss}
+	In Sections \ref{sec:StarKine} we show that in terms of the stellar kinematic properties, our radio-selected Southern sample are no different to ordinary optically-selected ETGs.
+Our sample shows a mixture of of regularly- and non-regularly-rotating behaviours, with both classes showing evidence of consistency with observations of the intrinsic shapes of ordinary regular and non-regular rotators.
+At this stage we observe that two (with a tentative third) galaxies host large KDCs.
+We also classify our sample galaxies into fast- and slow-rotators and find a consistent fraction ($45\pm13$\%) of slow-rotators to the ordinary ETG samples of the A+M sample, once the difference in the mass distribution between our Southern sample and the A+M sample are taken into account.
+
+	Radio-loud lenticular (S0) galaxies are extremely rare with only a handful of known cases \citep[e.g.][]{Heckman1982, Morganti2011}, presumably due to the associated mass functions of both S0s and radio galaxies: both massive S0s and low-mass radio galaxies are rare, with a similar transition masses from rare to more numerous.
+NGC 612 is one of those rare cases.
+
+	In terms of absorption line strengths and stellar populations (Section \ref{sec:absorption} and \ref{sec:stellarPop}), we find a remarkably similar gradient to the central Mg\,b verse stellar velocity dispersion relation to that of \citet{Ziegler1997}.
+Most of the galaxies in our Southern sample show typical ETG behavior: old, metal rich stellar populations, with a few exceptions: NGC 612 and NGC 1316 are both significantly younger than most ETGs and NGC 3557 has a young core.
+We observe that all 3 KDCs contain old stellar populations and are consistent with being merger remnants.
+We also show that the KDCs found in Section \ref{sec:StarKine} fit with the age\,--\,size relation found by \citet{Kuntschner2010} (see Section \ref{subsec:popKDC}).
+
+	If molecular (cold) gas is the fuel source that is accreted on to the the central black holes of our Southern sample in order to power the radio jets, unless it is accreted in a highly turbulent fashion, it might be expected that some of that gas might form stars \citep[e.g.][]{Collin1999, Diamond-Stanic2012, LaMassa2013}.
+If this is the case then a young stellar population might be expected to dominate in the very central (1--2) spaxels.
+We our best-fitting age maps show no evidence of this.
+
+	Section \ref{sec:gas} we show that galaxies in our Southern Sample have ionized gas masses of $10^4$\,--\,$10^6\,\mathrm{M_\odot}$.
+These are at the upper limit of, and possibly exceed, the typical masses observed in ETGs, although given that our sample contains particularly massive galaxies, high ionized gas masses are not unexpected.
+
+	The only slow rotator with detected, spatially-extended ionized gas, IC 1459, shows evidence through gas\,--\,star kinematic misalignment that the gas has an external origin, although it is possible that the gas has been re-accreted after it was first ejected during the merger that resulted in the stellar KDC.
+
+	Of the other 3 galaxies with detected, spatially-extended ionized gas (NGC 612, NGC 1316 and NGC 3100, all fast rotators), we find that one, NGC 3100, again has kinematic evidence of an external gas origin; another, NGC 612, is consistent with an internal origin; while the situation for the last one (NGC 1316) is not clear, although is definitely not in a settled disc.
+This is in keeping with the findings of \citet{Davis2011a}, who showed that $36\pm5$\% of fast rotators have ionized gas kinematics misaligned with respect to the stellar kinematics, while slow rotators have a flat distribution with respect to their misalignment angles.
+This indicates that slow rotators are dominated by external sources of gas, while fast rotators can have either internal or external sources.
+
+	All galaxies with detectable emission lines in our Southern Sample show LINER or Seyfert 2 characteristics.
+The only Seyfert 2 in our sample is the fast rotator, IC 1531.
+This is consistent with the results of \citet{Nyland2016}, who showed that all ETGs in the Atlas$^\text{3D}$ sample classified as Seyferts are also fast rotators.
+We find 9 of the 11 galaxies to be LINERs, 5 of which we conclusively attribute the ionizing photons to the central AGN.
+The final galaxy, PKS 718-34 has no emission line detections (i.e.\ passive).
+
+	Overall, we thus find that the warm ISM properties of our Southern Sample galaxies are consistent with those of other jet-mode AGN.
+These are ordinary ETGs experiencing an active phase, presumably due to the central black holes currently accreting gas in some form.
+
+	All these observations and findings, are consistent with those of typical massive ETGs.
+This is consistent with the hypothesis that radio-galaxies are ordinary massive ETGs experiencing a normal but short-lived active phase.
+
+% \section{Summary}
+% 	\label{sec:sum}
+% 	In the paper we present VIMOS and archival MUSE IFS observations of 11 low-powered radio galaxies.
+We find the best-fitting stellar kinematics and populations, as well as find the ionized gas spatial distribution, kinematics and dominant ionizing radiation source.
+We classify the kinematic maps according to the fast/slow rotator classification scheme of \citet{Cappellari2016} and find a consistent fraction of slow rotators for the mass distribution of our sample.
+
 \section*{Acknowledgements}
@@
 	\label{sec:Maps}
+
+	Here, we present spatially-resolved maps of our Southern Sample of the parameters measured and fitted to the IFS datacubes using the methods described in Section \ref{sec:analysis}.
+We present each galaxy in turn.
+
+	\subsection{ESO\,443-G24}
+		\begin{figure*}
+			\centering
+			\includegraphics[width=\textwidth]{eso443-g024.png}
+			\caption{}
+			\label{fig:eso443}
+		\end{figure*}
+
+	\subsection{IC\,1459}
+		\begin{figure*}
+			\centering
+			\includegraphics[width=\textwidth]{ic1459.png}
+			\caption{As Fig.\,\ref{fig:eso443}, but for IC\,1459}
+			% \label{fig:}
+		\end{figure*}
+
+	\subsection{IC\,1531}
+		\begin{figure*}
+			\centering
+			\includegraphics[width=\textwidth]{ic1531.png}
+			\caption{As Fig.\,\ref{fig:eso443}, but for IC\,1531}
+			% \label{fig:}
+		\end{figure*}
+
+	\subsection{IC\,4296}
+		\begin{figure*}
+			\centering
+			\includegraphics[width=\textwidth]{ic4296.png}
+			\caption{As Fig.\,\ref{fig:eso443}, but for IC\,4296}
+			% \label{fig:}
+		\end{figure*}
+
+	\subsection{NGC\,612}
+		\begin{figure*}
+			\centering
+			\includegraphics[width=\textwidth]{ngc0612.png}
+			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,612}
+			% \label{fig:}
+		\end{figure*}
+
+	\subsection{NGC\,1316}
+		\begin{figure*}
+			\centering
+			\includegraphics[width=\textwidth]{ngc1316.png}
+			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,1316}
+			% \label{fig:}
+		\end{figure*}
+
+	\subsection{NGC\,1399}
+		\begin{figure*}
+			\centering
+			\includegraphics[width=\textwidth]{ngc1399.png}
+			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,1399}
+			% \label{fig:}
+		\end{figure*}
+
+	\subsection{NGC\,3100}
+		\begin{figure*}
+			\centering
+			\includegraphics[width=\textwidth]{ngc3100.png}
+			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,3100}
+			% \label{fig:}
+		\end{figure*}
+
+	\subsection{NGC\,3557}
+		\begin{figure*}
+			\centering
+			\includegraphics[width=\textwidth]{ngc3557.png}
+			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,3557}
+			% \label{fig:}
+		\end{figure*}
+
+	\subsection{NGC\,7075}
+		\begin{figure*}
+			\centering
+			\includegraphics[width=\textwidth]{ngc7075.png}
+			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,7075}
+			% \label{fig:}
+		\end{figure*}
+
+	\subsection{PKS\,718-34}
+		\begin{figure*}
+			\centering
+			\includegraphics[width=\textwidth]{pks0718-34.png}
+			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,718-34}
+			% \label{fig:}
+		\end{figure*}
 

### 2018-01-20 produce_maps.py

@@ -1,0 +1,362 @@
+import cPickle as pickle
+import matplotlib.pyplot as plt 
+import numpy as np 
+from plot_velfield_nointerp import plot_velfield_nointerp
+from plot_results import add_
+from errors2 import get_dataCubeDirectory
+from prefig import Prefig
+from checkcomp import checkcomp
+cc = checkcomp()
+from astropy.io import fits 
+from sauron_colormap import sauron#2 as sauron
+from plot_results import set_lims
+
+
+from Bin import myArray
+class Ds(object):
+	def __init__(self):
+		self.x=np.array([0,0,0,1,1,1,2,2,40])
+		self.y=np.array([0,1,2,0,1,2,0,1,40])
+		self.bin_num = np.array([0,0,1,0,1,1,2,2,3])
+		self.xBar = np.array([0.5,1.5,2,40])
+		self.yBar = np.array([0.5,1.5,1,40])
+		self.SNRatio = np.array([0,1,1,2])
+		self.unbinned_flux = np.zeros((40,40))
+		self.number_of_bins = 4
+		self.components = {'stellar':comp()}
+		self.flux = np.array([0,1,1,2])
+
+	def absorption_line(self, p, uncert=False):
+		if uncert:
+			return [0,1,1,2], [0,1,1,2]
+		else:
+			return [0,1,1,2]
+
+class comp(object):
+	def __init__(self):
+		self.plot = {'vel':myArray([0,1,1,2], [0,1,1,2]), 
+			'sigma': myArray([0,1,1,2],[0,1,1,2])}
+
+
+def plot(galaxy, instrument='vimos', debug=True):
+	# opt = 'kin'
+	overplot={'CO':'c', 'radio':'g'}
+	if instrument=='vimos':
+		Prefig(size=np.array((6, 5))*6)
+		fig, axs = plt.subplots(5, 6)#, sharex=True, sharey=True)
+		plots = [[
+			'D.flux',
+			'',
+			"D.components['stellar'].plot['vel']",
+			"D.components['stellar'].plot['vel'].uncert",
+			"D.components['stellar'].plot['sigma']",
+			"D.components['stellar'].plot['sigma'].uncert"
+			],[
+			"D2.absorption_line('G4300')",
[…]

### 2018-01-21 produce_maps.py
Transfering produce_maps.py to uni comp
 On branch master
 Changes to be committed:
	modified:   produce_maps.py

@@ -182,7 +182,7 @@ def plot(galaxy, instrument='vimos', debug=True):
 	
 	print galaxy
 
-	vin_dir = '%s/Data/vimos/analysis' % (cc.base_dir)
+	vin_dir = '%s/Data/%s/analysis' % (cc.base_dir, instrument)
 	data_file =  "%s/galaxies.txt" % (vin_dir)
 	file_headings = np.loadtxt(data_file, dtype=str)[0]
 	col = np.where(file_headings=='SN_kin')[0][0]
@@ -194,9 +194,9 @@ def plot(galaxy, instrument='vimos', debug=True):
 	SN_target_kin=SN_target_kin_gals[i_gal]
 	SN_target_pop=SN_target_pop_gals[i_gal]
 
-	attr, vmin, vmax = np.loadtxt('%s/lims.txt' % (vin_dir), dtype=str, 
-		usecols=(0,1,2), skiprows=1, unpack=True)
-	vmin, vmax = vmin.astype(float), vmax.astype(float)
+	# attr, vmin, vmax = np.loadtxt('%s/lims.txt' % (vin_dir), dtype=str, 
+	# 	usecols=(0,1,2), skiprows=1, unpack=True)
+	# vmin, vmax = vmin.astype(float), vmax.astype(float)
 
 	vin_dir2 = str(vin_dir + '/%s/pop' % (galaxy)) 
 	vin_dir += '/%s/kin' % (galaxy) 
@@ -222,24 +222,27 @@ def plot(galaxy, instrument='vimos', debug=True):
 	for i, row in enumerate(plots):
 		for j, p in enumerate(row):
 			# print i, j, p
-			if p == 'flux':
+			if p == 'D.flux':
 				axs[i,j] = plot_velfield_nointerp(D.x, D.y, D.bin_num, 
 					D.xBar, D.yBar, eval(p), header, cmap='gist_yarg', 
 					flux_unbinned=D.unbinned_flux, galaxy=str_plots[i][j],
 					ax=axs[i,j])
 
 			elif p != '':
+				vmin, vmax = set_lims(eval(p), 
+					symmetric = p=="D.components['stellar'].plot['vel']",
+					positive = p!="D.components['stellar'].plot['vel']")
 				if 'D2' in p:
 					axs[i,j] = plot_velfield_nointerp(D2.x, D2.y, D2.bin_num, 
 						D2.xBar, D2.yBar, eval(p), header,  
[…]

### 2018-01-21 produce_maps.py
Take 2
 On branch master
 Changes to be committed:
	modified:   produce_maps.py

@@ -1,12 +1,17 @@
+## Routine to produce maps in a single grid for the MNRAS paper.
+
+from checkcomp import checkcomp
+cc = checkcomp()
+if cc.remote:
+	import matplotlib # 20160202 JP to stop lack-of X-windows error
+	matplotlib.use('Agg') # 20160202 JP to stop lack-of X-windows error
+import matplotlib.pyplot as plt # used for plotting
 import cPickle as pickle
-import matplotlib.pyplot as plt 
 import numpy as np 
 from plot_velfield_nointerp import plot_velfield_nointerp
 from plot_results import add_
 from errors2 import get_dataCubeDirectory
 from prefig import Prefig
-from checkcomp import checkcomp
-cc = checkcomp()
 from astropy.io import fits 
 from sauron_colormap import sauron#2 as sauron
 from plot_results import set_lims

### 2018-01-21 paper.tex
EoDC: Introduction and maps
 On branch master
 Changes to be committed:
	modified:   paper.tex
	modified:   produce_maps.py

@@
 
-	We refer to the combined Atlas$^\text{3D}$ and MASSIVE sample as the A+M sample.
+	It is becoming increasingly clear that active galactic nuclei (AGN) exist in two different modes, radiative and jet mode \citep[e.g.][]{Antonucci2012, Heckman2014}, raising speculation about differing mechanisms and possibly fuel sources for each.
+The former is thought to be the powerful engine that initially and rapidly shuts off star formation \citep[e.g.][]{Thomas2005, Thomas2010}, either by removing the cold gas from the galaxy entirely, heating it such that it joins the hot X-ray gas often present in massive galaxies \citep[e.g.][]{OSullivan2001}, or rendering it unusable for star formation (such as by stabilising it against collapse; e.g.\ \citealt{Martig2009}).
+After a single radiative-mode episode, the AGN is thought to subside to become jet dominated, repeatedly reheating the surrounding ISM to counter any cooling that might allow the cold gas reservoir to replenish (and subsequently form stars).
+
+	There is a strong consensus within the scientific literature that the most powerful radio galaxies are the result of gas-rich, major mergers causing large amounts of material to fall on to the black hole at the centre of the resulting galaxy, thus producing an immensely powerful AGN include a powerful radio jet \citep[e.g.][]{Malin1983, Quillen1992, Lim2000}.
+However, such galaxies are by construction extremely rare and are not representative of the general radio galaxy population.
+Most radio galaxies have low power, and their basic properties and origins are poorly constrained.
+One of the most popular suggestions is that they are bona-fide detections of jet-mode AGN.%, a class of AGN thought to maintain the dearth of star formation in early-type galaxies (ETGs), after most of the fuel for star formation has been removed by an earlier event.
+	They are known to be dusty with dust lanes having a tendency to be perpendicular to the jets \citep[e.g.][]{DeRuiter2002, VerdoesKleijn2005}.
+They have little ionized gas in the interstellar medium (ISM) \citep[e.g.][]{}, but often have significant quantities of hot X-ray gas \citep[e.g.][]{} (the cold phase of the ISM of radio galaxies will be examined in Ruffa et.al.\ in prep.).
+If the low star-formation rates typically seen in massive early-type galaxies (ETGs) are preserved by such jet-mode AGN, then all such ETGs must regularly go through similar active phases, and therefore low-powered radio galaxies should be much the same as their radio-quiet (quiescent phase) ETG counterparts.
+
+	% In jet-mode (also called radio- or maintenance-mode in the literature) AGN, the dominant form of emitted energy away from the black hole is the kinetic (i.e.\ mechanical) energy of the material that makes up the jet.
+Jet-mode AGN can be directly observed `feeding back' to their host galaxies, as jets often terminate at shocks (hot spots) that make up the walls of cavities observed in the hot (X-ray) haloes of the host galaxies.
+
+	% Jet-mode AGN tend to be radiatively inefficient, with Eddington ratios $<$ 1\%.
+This implies that the innermost regions of the accretion discs must be geometrically thick, with inflow times much less than the radiative cooling time-scales.
+The resulting inflows are known as advection-dominated accretion flows (ADAF; \citealt{Narayan1994}).
+Such systems are capable of launching jets.
+It is possible that there is a thin disc beyond the thick disc (further from the black hole), but it must be truncated by the thick disc \cite[e.g.][]{Abramowicz2002, Sadler2014}.
+Much of this is very difficult to resolve observationally, as the spatial scale is $< 100$ Schwarzschild radii, and many of the models remain degenerate \citep[e.g.][]{Quataert1999}.
+
+	% There is still much speculation about the nature of the fuel (and its origin) in jet-mode AGN, though a consensus seems to building in favour of an internal origin.
+Many people advocate hot gas as being the ultimate original fuel \citep[e.g.][]{Allen2006}.
+\citet{Hardcastle2007} suggest that it could be directly accreted through Bondi accretion \citep{Bondi1952}, a simple model where gas is accreted in a spherically-symmetric manner directly from the hot phase on to the black hole.
+Others invoke a cooling mechanism to allow the X-ray gas to condense into molecular (i.e.\ cold) gas before accretion.
+Yet others point to a higher higher detection rate of dust and molecular gas in RGs compared to the general population \citep[e.g.][]{Lim2000, DeRuiter2002, Leon2003, VerdoesKleijn2005}, suggesting that cold gas from either internal reservoirs or externally-accreted may be the fuel.
+\citet{DeRuiter2002} showed that, when dust is present, its mass is correlated with the radio power and there seems to be a bias towards dust lanes orientated orthogonally to radio jets \citep{VerdoesKleijn2005}.
+
+	% Beyond this, the source of the energy for powering the jet is still unclear.
+Energy may be extracted from the black hole via the \citet{Blandford1977} mechanism or variations thereof \citep[e.g.][]{Koide2002}, or from the accretion disc as discussed by \citet{Blandford1982} and others \citep[e.g.][]{Hujeirat2003}.
+
+	% It is thought that the duty cycle of a jet is very short; the jet is turned on for very short periods of time before turning off for extended periods.
+
+	% An obvious feedback mode is seen in the haloes of hot X-ray gas around galaxies, where radio jets terminate.
+The kinetic impacts of the jets create cavities or bubbles in the hot gas (first conceptualised by \citealt{Gull1973}).
+In cluster environments, these are buoyant and can separate, rising through the intra-cluster medium \citep[e.g.][]{Churazov2000, Churazov2001, McNamara2000}.
+However, the bubbles are intrinsically anisotropic, while star formation must be suppressed on a global scale.
+They also exhibit steep abundance gradients, showing that there is little mixing that could disperse energy via convection.
+Instead, from observations of the very brightest X-ray clusters such as Perseus \citep{Fabian2003, Fabian2006}, Virgo \citep{Forman2007}, Centaurus \citep{Sanders2008}, Abell 2052 \citep{Blanton2011} and simulations \citep[e.g.][]{Ruszkowski2004, Sijacki2006}, it appears that sound waves in the ISM are generated by the repetitive blowing of bubbles.
+The energy of the waves is likely sufficient to offset that lost by the gas via normal cooling mechanisms \citep{Fabian2003}.
+The low amplitude of these waves means that they are not detectable in all but the closest clusters (more distant clusters would require in excess of 10 days of continuous \textit{Chandra} observations; \citealt{Graham2008}).
+
+	% Even when the jets are turned off or only very weak, the galaxies may still contain low ionization nuclear emission-line regions (LINERs).
+It is worth noting that while the most powerful LINERs are likely to be low-luminosity AGN, many (indeed most SDSS-classified LINERs) are not; they belong to a recently-defined category known as LIERs i.e.\ the emission-line region is not nuclear (LINERs but without the `N'; e.g.\ \citealt{Sarzi2005, Sarzi2010, Singh2013, Belfiore2016a}).
+Such emission is mostly attributed to ionization from radiation from post-asymptotic giant branch (pAGB) stars.
+\citet{Capetti2011} suggested using an equivalent width of the [\ion{O}{iii}] emission line of $EW_\text{[\ion{O}{iii}]} = 1$\,\AA\ as a threshold for LIERs; galaxies with greater equivalent widths are likely low-luminosity AGN.
+
+	% As stated above, most radio emission from RGs results from synchrotron emission from the relativistic plasma within the jets, moving around the magnetic fields tangled in the jets.
+This means that all such RGs can be considered a jet detection (ignoring the very low radio-luminosity galaxies resulting from high levels of circumnuclear star formation).
+RGs are always jet-mode AGN, except at the highest radio luminosities where the bright radio jets are dominated (in terms of energy output) by the brighter still accretion disc.
+These are radiative-mode AGN (see Section \ref{subsubsec:RadiativeRadio}).
+
+	% All radio-selected AGN are massive, with very old stellar populations and high concentration indices \citep[e.g.][]{Best2005}.
+\citet{Best2005} also found that the fraction of galaxies with detectable radio emission is related to the galaxies' stellar and black hole masses by power laws with indices of 2.5 and 1.6, respectively.
+
+	To test this hypothesis, a complete sample of 11 nearby low-powered radio galaxies was constructed and observed with a suite of instruments.
+Here, we present the spatially-resolved stellar kinematics, stellar populations, and ionized gas distribution, kinematics and ionization derived from integral-field spectroscopic (IFS) observations with the Visible Multi-object Spectrograph (VIMOS) and archival data from the Multi-unit Spectroscopic Explorer (MUSE), both on the Very Large Telescope (VLT).
+We compare the characteristics and properties (accessible with $V$-band IFS data) of our sample of low-power radio galaxies to those of ordinary (i.e.\ optically-selected) ETGs from the Atlas$^\text{3D}$ and MASSIVE IFS surveys.
+We hereafter refer to the combined Atlas$^\text{3D}$ and MASSIVE sample as the A+M sample.
+
+	% For the stellar component of our sample galaxies, we use the kinematic maps to identify regular/non-regular rotators and kinematic substructures.
+In our sample 4 galaxies are regular rotators and two (with a tentative third) galaxies were found to contain kinematically decoupled cores (KDCs).
+We use the $\lambda_R$ specific angular momentum parameter from Atlas$^\text{3D}$ to classify the galaxies according to the fast/slow rotator classification scheme.
+We found a similar fraction ($45\pm13$\%) of slow rotators to the combined Atlas$^\text{3D}$ and MASSIVE samples, corrected for mass distribution.
+We also find the fast rotators tend to have aligned kinematic and photometric position angles, while the slow rotators can have any angle between the two position angles.
+The best-fitting stellar populations show our sample to be typical massive ETGs: i.e.\ mostly old, metal rich and alpha-element enhanced.
+We found and measure the radial stellar population gradients and found averages of $\Delta_\text{log age} = 0.014\pm0.007 \,\mathrm{dex \, arcsec^{-1}}$ and $\Delta_\text{[Fe/H]} = -0.03\pm0.01 \, \mathrm{dex \, arcsec^{-1}}$.
+The KDCs found previously were observed to be large and contain old stellar populations and are the result of galaxy mergers.
+
+	% Some of the literature suggestion that if cold gas is the fuel for the AGN then unless it is accreting in a highly turbulent way, it might be expected to form stars.
+However we see no evidence of a very young stellar population right at the centre of our sample galaxies.
+
+	% For the ionized gas components of our sample galaxies, the estimated gas masses were found to be in the range of $10^4$\,--\, $10^6\,\mathrm{M_\odot}$, which is the upper end of the range expected from optically-selected ETGs.
+This was the only suggestion we find that our sample galaxies may be intrinsically different than optically-selected ETGs.
+We detected spatially extended gas in 4 of our sample, with a range of kinematics.
+Two galaxies had ionized gas kinematics misaligned to that of the stars, suggesting and external origin to the gas, while the kinematics of one was aligned with that of its stars (consistent with an internal origin).
+The final galaxy was unsettled and thus not clear.
+
+	% Using the classic Baldwin\,--\,Phillips\,--\,Terlevich (BPT) diagnostic plots, as well as similar alternatives, for galaxies with observations outside of the wavelength range required for the BPT plots, we find the dominant ionization source for each galaxy.
+We find that 9 of our sample galaxies are low-ionized nuclear emission region galaxies (LINERs; 5 of which can be attributed to the radiation field from the AGN), 1 is a Seyfert II and 1 a passive (line-less) galaxy.
+
+	% All of the properties found are consistent with that of optically selected ETGs with a similar mass distribution.
+We thus find no conclusive difference between the stellar and ionized gas properties all of these ETGs except for a tentative suggestion of slightly higher ionized gas masses in our radio galaxies.
+If confirmed, the latter may be gas built up during the quiescent phase of ETGs, ultimately triggering the active (radio) phase itself then re-removing such gas from the galaxy.
+
+	% Some of the sample galaxies have clear evidence of merger events (e.g.\ large KDCs), but others have a complete lack of evidence of a merger, suggesting that radio galaxies can form without the requirement of a merger event.
+Indeed, it is well known that NGC 612 harbours a large extended gas disc with kinematics that are consistent with an internal origin of the gas.
+As such, in rare cases, it is possible that radio galaxies can be fueled through entirely secular processes.
 

### 2018-01-21 produce_maps.py

@@ -9,12 +9,9 @@ import matplotlib.pyplot as plt # used for plotting
 import cPickle as pickle
 import numpy as np 
 from plot_velfield_nointerp import plot_velfield_nointerp
-from plot_results import add_
-from errors2 import get_dataCubeDirectory
 from prefig import Prefig
 from astropy.io import fits 
 from sauron_colormap import sauron#2 as sauron
-from plot_results import set_lims
 
 
 from Bin import myArray
@@ -26,7 +23,10 @@ class Ds(object):
 		self.xBar = np.array([0.5,1.5,2,40])
 		self.yBar = np.array([0.5,1.5,1,40])
 		self.SNRatio = np.array([0,1,1,2])
-		self.unbinned_flux = np.zeros((40,40))
+		if 'home' in cc.device:
+			self.unbinned_flux = np.zeros((40,40))
+		else:
+			self.unbinned_flux = np.zeros((150,150))
 		self.number_of_bins = 4
 		self.components = {'stellar':comp()}
 		self.flux = np.array([0,1,1,2])
@@ -47,8 +47,17 @@ def plot(galaxy, instrument='vimos', debug=True):
 	# opt = 'kin'
 	overplot={'CO':'c', 'radio':'g'}
 	if instrument=='vimos':
-		Prefig(size=np.array((6, 5))*6)
-		fig, axs = plt.subplots(5, 6)#, sharex=True, sharey=True)
+		from plot_results import add_, set_lims
+		from errors2 import get_dataCubeDirectory
+		ext = 0
+
+		if galaxy in ['ngc0612', 'pks0718-34']:
+			Prefig(size=np.array((6, 4))*6)
+			fig, axs = plt.subplots(4, 6)
+		else:
+			Prefig(size=np.array((6, 5))*6)
+			fig, axs = plt.subplots(5, 6)#, sharex=True, sharey=True)
+
 		plots = [[
 			'D.flux',
 			'',
@@ -109,6 +118,10 @@ def plot(galaxy, instrument='vimos', debug=True):
 			''
 			]]
 	elif instrument == 'muse':
+		from plot_results_muse import add_, set_lims
+		from errors2_muse import get_dataCubeDirectory
+		ext = 1
+
 		Prefig(size=np.array((6, 7))*6)
[…]

### 2018-01-24 paper.tex
EoDC: abstract written
Finished v0.9 - for my own read through and check

 On branch master
 Changes to be committed:
	modified:   paper.tex
	modified:   produce_maps.py

@@
 \begin{abstract}
-This is a simple template for authors to write new MNRAS papers.
-The abstract should briefly describe the aims, methods, and main results of the paper.
-It should be a single paragraph not more than 250 words (200 words for Letters).
-No references should appear in the abstract.
+The most powerful radio galaxies are well studied with good a good understanding of their formations processes, however they are intrinsically rare objects and not representative of the general population of radio galaxies.
+Low-powered radio galaxies are comparatively poorly studied with many conflicting viewpoints regarding their origin and the extent of the effect of feedback from them.
+
+In this paper, we present a complete sample of 11 nearby low-powered radio galaxies, observed with a suite of instruments.
+This paper focuses on the spatially-resolved stellar kinematics, stellar populations, and ionized gas distribution, kinematics and ionization derived from optical IFS observations.
+We compare the characteristics and properties of our sample to those of ordinary (i.e.\ optically-selected) ETGs from the Atlas$^\text{3D}$ and MASSIVE IFS surveys.
+These include the fast/slow rotator classification fraction, kinematic substructures, absorption line strength radial gradients, general stellar population properties, ionized gas distribution and kinematics and the dominant source of ionizing photons.
+
+We tentatively find that our radio-selected ETGs contain a higher mass in of ionized gas than expected from optically-selected ETGs, but after accounting for the differences in the mass distribution, we find no further differences between the two samples in the characteristics that can be studied with optical IFU data.
+We suggest that this is consistent with the notion that low-powered radio galaxies are ordinary ETGs experiencing a brief active phase which maintains their low star-formation rates (also known as maintenance or jet-mode AGN).
 \end{abstract}
 
-% Select between one and six entries from the list of approved keywords.
-% Don't make up new ones.
 \begin{keywords}
-% keyword1 -- keyword2 -- keyword3
+galaxies: kinematics and dynamics -- galaxies: abundances -- galaxies: active -- galaxies: jets -- galaxies: structure
 \end{keywords}

### 2018-01-24 produce_maps.py

@@ -122,8 +122,8 @@ def plot(galaxy, instrument='vimos', debug=True):
 		from errors2_muse import get_dataCubeDirectory
 		ext = 1
 
-		Prefig(size=np.array((6, 7))*6)
-		fig, axs = plt.subplots(7, 6)#, sharex=True, sharey=True)
+		Prefig(size=np.array((6, 6))*6)
+		fig, axs = plt.subplots(6, 6)#, sharex=True, sharey=True)
 
 		plots = [[
 			'D.flux',
@@ -154,9 +154,9 @@ def plot(galaxy, instrument='vimos', debug=True):
 			"D2.absorption_line('NaD')",
 			"D2.absorption_line('NaD',uncert=True)[1]"
 			],[
-			"D2.absorption_line('TiO1,remove_badpix=True')",
+			"D2.absorption_line('TiO1',remove_badpix=True)",
 			"D2.absorption_line('TiO1',uncert=True,remove_badpix=True)[1]",
-			"D2.absorption_line('TiO2,remove_badpix=True')",
+			"D2.absorption_line('TiO2',remove_badpix=True)",
 			"D2.absorption_line('TiO2',uncert=True,remove_badpix=True)[1]",
 			'',
 			''

### 2018-01-25 produce_maps.py
EoDC: Added ionized gas maps
 On branch master
 Changes to be committed:
	modified:   produce_maps.py

@@ -44,23 +44,19 @@ class comp(object):
 
 
 def plot(galaxy, instrument='vimos', debug=True):
+	print galaxy, instrument
+
 	# opt = 'kin'
 	overplot={'CO':'c', 'radio':'g'}
 	if instrument=='vimos':
 		from plot_results import add_, set_lims
 		from errors2 import get_dataCubeDirectory
 		ext = 0
-
-		if galaxy in ['ngc0612', 'pks0718-34']:
-			Prefig(size=np.array((6, 4))*6)
-			fig, axs = plt.subplots(4, 6)
-		else:
-			Prefig(size=np.array((6, 5))*6)
-			fig, axs = plt.subplots(5, 6)#, sharex=True, sharey=True)
+		rows = 5
 
 		plots = [[
 			'D.flux',
-			'',
+			"D2.components['[OIII]5007d'].flux",
 			"D.components['stellar'].plot['vel']",
 			"D.components['stellar'].plot['vel'].uncert",
 			"D.components['stellar'].plot['sigma']",
@@ -90,7 +86,7 @@ def plot(galaxy, instrument='vimos', debug=True):
 
 		str_plots = [[
 			'Flux',
-			'',
+			r'[OIII]$\lambda\lambda$4959,5007 Flux',
 			"Stellar mean velocity",
 			"Stellar mean velocity\nuncertainty",
 			"Stellar velocity dispersion",
@@ -121,13 +117,11 @@ def plot(galaxy, instrument='vimos', debug=True):
 		from plot_results_muse import add_, set_lims
 		from errors2_muse import get_dataCubeDirectory
 		ext = 1
-
-		Prefig(size=np.array((6, 6))*6)
-		fig, axs = plt.subplots(6, 6)#, sharex=True, sharey=True)
-
+		rows = 6
+		
 		plots = [[
 			'D.flux',
-			'',
+			"D2.components['[OIII]5007d'].flux",
 			"D.components['stellar'].plot['vel']",
 			"D.components['stellar'].plot['vel'].uncert",
 			"D.components['stellar'].plot['sigma']",
@@ -164,7 +158,7 @@ def plot(galaxy, instrument='vimos', debug=True):
 
 		str_plots = [[
 			'Flux',
-			'',
+			r'[OIII]$\lambda\lambda$4959,5007 Flux',
[…]

### 2018-01-26 paper.tex
EoDC: Draft 0.9.1
Have done a read through and correction. Still waiting for uni comp to
run MUSE plots.

Corrected emission line maps

 On branch master
 Changes to be committed:
	modified:   paper.tex
	modified:   produce_maps.py

--- 2018-01-20 paper.tex
@@
 \begin{abstract}
-This is a simple template for authors to write new MNRAS papers.
-The abstract should briefly describe the aims, methods, and main results of the paper.
-It should be a single paragraph not more than 250 words (200 words for Letters).
-No references should appear in the abstract.
+The most powerful radio galaxies are well studied with a strong consensus in the literature regarding their formations processes.
+However they are intrinsically rare objects and not representative of the general population of radio galaxies.
+Low-powered radio galaxies are comparatively poorly studied with many conflicting viewpoints regarding their origin and the extent of the effect of feedback from them.
+
+In this paper, we present a complete sample of 11 nearby low-powered radio galaxies, observed with a suite of instruments.
+This paper focuses on the spatially-resolved stellar kinematics, stellar populations, and ionized gas distribution, kinematics and ionization derived from optical IFS observations, while other observation such as \ce{^{12}CO(2-1)} from Atacama Large Millimeter/sub-millimeter Array (ALMA) and radio continuum from the Very Large Array (VLA) will be presented in future papers, but are overlaid on our maps (cyan and red contours respectively, in Figs \ref{fig:eso443}-\ref{fig:pks718}).
+We compare the characteristics and properties of our sample to those of ordinary (i.e.\ optically-selected) ETGs using the Atlas$^\text{3D}$ and MASSIVE IFS surveys.
+These include the fast/slow rotator classification fraction, kinematic substructures, absorption line strength radial gradients, general stellar population properties, ionized gas distribution and kinematics and the dominant source of ionizing photons.
+
+We tentatively find that our radio-selected ETGs contain a higher mass in of ionized gas than expected, but after accounting for the differences in the mass distribution, we find no further differences between the two samples in the characteristics that can be studied with optical IFU data.
+We suggest that this is consistent with the notion that low-powered radio galaxies are ordinary ETGs experiencing a brief active phase which maintains their low star-formation rates (also known as maintenance or jet-mode AGN).
 \end{abstract}
 
-% Select between one and six entries from the list of approved keywords.
-% Don't make up new ones.
 \begin{keywords}
-% keyword1 -- keyword2 -- keyword3
+galaxies: kinematics and dynamics -- galaxies: abundances -- galaxies: active -- galaxies: jets -- galaxies: structure
 \end{keywords}
@@
 	\label{sec:intro}
-	% There are known to be strong scaling relations between the mass of the central supermassive black-hole (SMBH) and the global properties in a given galaxy, such as velocity dispersion, the $M-\sigma$ relation \citep{Ferrarese2000, Gebhardt2000, Graham2011}; Sersic index \citep{Graham2007, Savorgnan2013}; luminosity \citep{Laor2001, McLure2001, Lauer2007, Graham2012}; etc.
-AGN feedback is understood to be the mechanism by which the SMBH can expand its sphere of influence to galactic scales to affect these relationship.
-
-	% This is generally understood to be a feedback process, where large amounts of gas within the galaxy cools, falls on the SMBH.
-Here the black-hole imparts energy to the gas, causing outflows (or jets) and/or thermal emission.
-We observe this as an Active Galactic Nuclei (AGN) which can have distinctive emission across the electromagnetic spectrum.
-The exact mechanisms of imparting energy still remains an open question, with much theoretical and observational work ongoing.
-The outflows can then effect the outer parts of the galaxy, by methods such as fountain effects \citep{}, thermal heating \citep{DeYoung2010} and shocks created by the outflows \citep{}.
-
-	% One identifier of AGNs is a radio signature consistent with Synchrotron emission from the outflow i.e a radio galaxy (RG).
-These are typically categorized into one of two classes: Fanaroff-Riley (FR) I or FR II \citep{Fanaroff1974}.
-Of these we focus on the former since these are by far the most common mode in the local universe (possibly as far as $z \sim 1$ \citep{Rigby2008}), and so to discuss radio AGN feedback is to consider feedback from FR I sources \citep{DeYoung2010}.
-Indeed, while there is broad consensus \citep{Heckman1986, Baum1992} that the brightest RGs (mostly FR IIs) are caused when a massive galaxy merges with a gas rich galaxy (a wet merger) giving a plentiful fuel reservoir to the AGN \citep{Baum1992}, there is much more debate when it comes to low-powered ($P_\text{1.4 GHz} \lesssim 10^{24.5} \, \mathrm{W Hz^{-1}}$) RGs (mostly FR I).
-Suggestions fall into two categories: an extrapolation of radio-loud galaxies (i.e.
-a merger with either small gas reservoirs or low efficiency accretion onto the SMBH) or a highly efficient accretion of gas from secular origins (such as Bondi accretion of the hot X-ray component of the Inter-Stellar Medium (ISM) \citep{Allen2006} or from existing cold gas reservoirs \citep{Prandoni2010}).
-This project aims to add to this discussion using Integral Field Unit (IFU) observations in the visible band of nearby radio galaxies and comparing this with Atlas-3D sample \citep{Cappellari2011} as a control sample.
-
-% More to add to intro - e.g. summery of paper
-
-	We refer to the combined Atlas$^\text{3D}$ and MASSIVE sample as the A+M sample.
+	It is becoming increasingly clear that two different types of active galactic nuclei (AGN) exist, radiative and jet mode AGN \citep[e.g.][]{Antonucci2012, Heckman2014}, raising speculation about differing mechanisms and possibly fuel sources for each.
+The former is thought to be the powerful engine that initially and rapidly shuts off star formation in massive early-type galaxies (ETGs; e.g.
+\citealt{Thomas2005, Thomas2010}), either by removing the cold gas from the galaxy entirely, heating it such that it joins the hot X-ray gas often present in massive galaxies \citep[e.g.][]{OSullivan2001}, or rendering it unusable for star formation (such as by stabilising it against collapse; e.g.\ \citealt{Martig2009}).
+After a single radiative-mode episode, the AGN is thought to subside to become jet-dominated, repeatedly reheating the surrounding interstellar medium (ISM) to counter any cooling that might allow the cold gas reservoir to replenish (and subsequently form stars).
+
+	There is a strong consensus within the scientific literature that the most powerful radio galaxies are the result of gas-rich, major mergers causing large amounts of material to fall on to the black hole at the centre of the resulting galaxy, thus producing an immensely powerful AGN which includes a powerful radio jet \citep[e.g.][]{Malin1983, Quillen1992, Lim2000}.
+However, such galaxies are by construction extremely rare and are not representative of the general radio galaxy population.
+Most radio galaxies are low-powered, and their basic properties and origins are poorly constrained.
+One of the most popular suggestions is that they are bona-fide detections of jet-mode AGN.%, a class of AGN thought to maintain the dearth of star formation in early-type galaxies (ETGs), after most of the fuel for star formation has been removed by an earlier event.
+	These radio galaxies are known to be dusty with dust lanes having a tendency to be perpendicular to the jets \citep[e.g.][]{DeRuiter2002, VerdoesKleijn2005}.
+They have little ionized gas in the ISM \citep[e.g.][]{}, but often have significant quantities of hot X-ray gas (e.g.
+\citealt{}; the cold phase of the ISM of radio galaxies will be examined in Ruffa et.al.\ in prep.).
+If the low star-formation rates typically seen in massive ETGs are preserved by jet-mode AGN, then all such ETGs must regularly go through similar active phases, and therefore low-powered radio galaxies should be much the same as their radio-quiet (quiescent phase) ETG counterparts.
+
+	To test this hypothesis, a complete sample of 11 nearby low-powered radio galaxies was constructed \citep{} and observed with a suite of instruments.
+Here, we present the spatially-resolved stellar kinematics, stellar populations, and ionized gas distribution, kinematics and ionization derived from integral-field spectroscopic (IFS) observations with the Visible Multi-object Spectrograph (VIMOS) and archival data from the Multi-unit Spectroscopic Explorer (MUSE), both on the Very Large Telescope (VLT).
+We compare the characteristics and properties (accessible with $V$-band IFS data) of our sample of low-power radio galaxies to those of ordinary (i.e.\ optically-selected) ETGs from the Atlas$^\text{3D}$ and MASSIVE IFS surveys.
+We hereafter refer to the combined Atlas$^\text{3D}$ and MASSIVE sample as the A+M sample.
+
+	In Section \ref{sec:samp} we, set out the compete sample with our observations and data-reduction methods detailed in Section \ref{sec:obs}.
+Our data-analysis methods and routines are detailed in Section \ref{sec:analysis} (the maps of our sample produced with these methods are shown in Appendix \ref{sec:maps}).
+We present our findings regarding the stellar kinematics, absorption line strengths, stellar populations, ionized gas (distribution, kinematics and ionization) in Sections \ref{sec:StarKine}-\ref{sec:gas}, respectively.
+Finally, we discuss our results and conclude in Section \ref{sec:discuss}.
 
@@
 	% \begin{threeparttable}
-		\caption{Key sample characteristics of the Southern Sample galaxies.
+		\caption{Key characteristics of the Southern Sample galaxies.
 Col.\,1: host galaxy name.
@@
 Col.\,3: redshift.
-Col.\,4: National Radio Astronomy Observatory (NRAO) Very Large Array (VLA) Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}.
+Col.\,4: National Radio Astronomy Observatory (NRAO) VLA Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}.
 Col.\,5: Two Micron All Sky Survey (2MASS) $K$-band apparent magnitude (with errors of $\pm 0.025$ mag; \citealt{Skrutskie2006}).
@@
 
-	These criteria lead to a sample of 11 galaxies hereafter referred to as the Southern Sample. The key observed characteristics are summarised in Table \ref{tab:sample}.
-	%, while the derived characteristics are listed in Table \ref{tab:sampleDerived}. 
-	All galaxies have a FR I radio morphology according to the \citet{Fanaroff1974} scheme; the bulk of the radio emission is centrally-concentrated, as opposed to the FR II morphology where the brightest points are at the ends of the radio lobes.
+	These criteria lead to a sample of 11 galaxies hereafter referred to as the Southern Sample.
+The key observed characteristics are summarised in Table \ref{tab:sample}.
+All galaxies have a FR I radio morphology according to the \citet{Fanaroff1974} scheme.
 
@@
 	\label{sec:obs}
-	The sample was observed with the Visible Multi-Object Spectrograph (VIMOS), mounted on UT3 on the VLT in Paranal \citep{LeFevre2003}.
+	The sample was observed with VIMOS, mounted on the VLT in Paranal \citep{LeFevre2003}.
 All observations were taken with a spatial sampling of $0\farcs67$, using the high-resolution blue grism yielding a wavelength range of 3700-5520\,\AA\ with a spectral resolution of 1440 and sampling of 0.71\,\AA\,$\mathrm{pix^{-1}}$.
@@
 \textsc{Py3D} applies all standard IFS data-reductions steps: bias subtraction, spectrum identification, flatfielding and wavelength calibration.
-In addition, the data was flux calibrated using publicly available observations of the spectro-photometric standard star Feige 110 provided by ESO.
-All steps include methods to account for the bad fibres, flexure and cross-talk within VIMOS.
-
-	Following this, we noted that the cubes where still not properly calibrated.
+In addition, the data was flux calibrated using publicly available observations of the spectro-photometric standard star Feige 110 provided by the European Southern Observatory (ESO).
+All steps include methods designed to account for the bad fibres, flexure and cross-talk within VIMOS.
+
+	Following this, we noted that the cubes were still not properly calibrated.
 Three main issues remain: the quadrants have different intensities, clearly showing uncorrected throughput differences; diagonal intensity stripes are present in the reconstructed images at all wavelengths; and spectral features are observed \citep{Jullo2008} that are visually similar to fringe patterns caused by interference within the CCD between incident light and light reflected from the interfaces between layers of the CCD materials.
@@
 	These method are not completely effective and some artefacts are still present in the data, however in most cases the data is of sufficient quality for our purposes.
-For the worst effected datacubes, we have archival observations (see Section \ref{subsec:MUSE}).
+For the worst effected datacubes, we have archival MUSE observations (see Section \ref{subsec:MUSE}).
 
@@
 		\label{subsec:MUSE}
-		Four of the sample galaxies are in the Multi-unit Spectroscopic Explorer (MUSE) archive: IC 1459, IC 4296, NGC 1316 and NGC 1399.
+		Four of the sample galaxies are in the MUSE archive: IC 1459, IC 4296, NGC 1316 and NGC 1399.
 We include these in our analysis as they have better (spatial and spectral) resolution and sampling, a larger field-of-view and larger wavelength range than the VIMOS data.
@@
 To remove this over-subtraction, we developed our own pseudo-sky subtraction routine.
-A median spectrum was taken from four $20 \times 20$\,spaxel regions, one in from each spatial corner of the ESO reduced cube.
+A median spectrum was taken from four $20 \times 20$\,spaxel regions, one in each spatial corner of the ESO reduced cube.
 After checking that no stellar continuum could be fit to the medium sky spectrum (i.e.\ that very little light from the galaxy is contaminating the pseudo-sky regions), this median sky spectrum was subtracted from each spaxel in the cube.
@@
 	\label{sec:analysis}
-	From this point on, the VIMOS and MUSE datasets are treated almost identically, the only difference (other than the different spectral ranges and resolutions) being that the MUSE datacubes are spatially binned to a higher signal-to-noise ratio (S/N) using Voronoi binning\footnote{http://www-astro.physics.ox.ac.uk/~mxc/software/} \citep{Cappellari2003}.
+	Both VIMOS and MUSE datasets are spatially binned using Voronoi binning\footnote{\label{fn:Cappellari}http://www-astro.physics.ox.ac.uk/\~mxc/software/} \citep{Cappellari2003} and from this point on are treated almost identically, the only difference (other than the different spectral ranges and resolutions) being that the MUSE datacubes are spatially binned to a higher signal-to-noise ratio (S/N).
 For our purposes, we define the `signal' and `noise' of each spaxel as the median value of its spectrum and noise spectrum, respectively.
@@
 
-	Next we implement a routine to find optimal initial guesses of the redshift and velocity dispersion for each galaxy, to be used when fitting individual bins, by means of iterative fits to the spatially collapsed (i.e.
+	Next we implement a routine to find optimal initial values of the redshift and velocity dispersion for each galaxy, to be used when fitting individual bins, by means of iterative fits to the spatially collapsed (i.e.
 summed across both spatial dimensions of the datacube) spectrum.
-We use the penalized-fitting (\textsc{pPXF}) routine\footnote{http://www-astro.physics.ox.ac.uk/~mxc/software/} of \citet{Cappellari2004} and \citet{Cappellari2016a} with the Medium-resolution Issac Newton Telescope (INT) Library of Empirical Spectra (MILES) library \citep{Sanchez-Blazquez2006, Falcon-Barroso2011a} to find the best-fitting line-of-sight velocity distribution (LOSVD; as parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion).
+We use the penalized-fitting (\textsc{pPXF}) routine\footnotemark[\ref{fn:Cappellari}] of \citet{Cappellari2004} and \citet{Cappellari2016a} with the Medium-resolution Issac Newton Telescope (INT) Library of Empirical Spectra (MILES) library \citep{Sanchez-Blazquez2006, Falcon-Barroso2011a} to find the best-fitting line-of-sight velocity distribution (LOSVD; as parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion).
 The final mean velocity of a given galaxy, is used as its precise spectroscopic redshift and is given in Table \ref{tab:sample}.
@@
 		\label{subsec:starKin}
-		Each bin is fit independently again using \textsc{pPXF} with the MILES library.
-For the fit, regions around potential emission lines (list below) are masked, and a fourth order polynomial additive continuum correction is used.
+		Each bin is fit independently, again using \textsc{pPXF} with the MILES library.
+For the fit, regions around potential emission lines (listed in Section \ref{subsec:EmissionLines}) are masked, and a fourth order polynomial additive continuum correction is used.
 A Monte--Carlo (MC) estimate of the uncertainties is used.
@@
 		\label{subsec:EmissionLines}
-		We fit the ionized gas fluxes and kinematics for the emission lines [\ion{O}{ii}], H$\delta$, H$\gamma$, H$\beta$, [\ion{O}{iii}], [\ion{N}{I}], [\ion{O}{i}], [\ion{N}{ii}], H$\alpha$ and [\ion{S}{ii}] using Gaussian templates.
-This independently fits emission lines from the interstellar medium (ISM), with a single LOSVDs (again parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion), independently of the stellar kinematics.
-In the cases of the [\ion{O}{iii}], [\ion{O}{i}] and [\ion{N}{ii}] doublets, the two components of the doublets are fit with a fixed flux ratio of 1:0.34.
-The [\ion{N}{i}] doublet has a fixed ratio of 1:0.65 \citep{Safier1992}.
+		In this analysis we consider the following emission lines and doublets: [\ion{O}{ii}]$\lambda\lambda$3726,3729, H$\delta$, H$\gamma$, H$\beta$, [\ion{O}{iii}]$\lambda\lambda$4969,5007, [\ion{N}{I}]$\lambda\lambda$5199,5202, [\ion{O}{i}]$\lambda\lambda$6300,6363, [\ion{N}{ii}]$\lambda\lambda$6548,6583, H$\alpha$ and [\ion{S}{ii}]$\lambda\lambda$6716,6731.
+We fit the fluxes and kinematics for the emission lines using Gaussian templates, independently fitting the emission lines of the ISM, with a single LOSVDs (again parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion), from the stellar kinematics.
+In the cases of the [\ion{O}{iii}], [\ion{O}{i}] and [\ion{N}{ii}] doublets, the two components of the doublets are fit with a fixed flux ratio of 3:1.
+The [\ion{N}{i}] doublet has a fixed ratio of 3:2 \citep{Safier1992}.
 The two components of the [\ion{O}{ii}] and [\ion{S}{ii}] doublets are fit independently.
-To minimize template mismatch, whereby emission lines are erroneously fitted to the edges of badly modeled and thus subtracted absorption features, we follow the method set out in \citet{Sarzi2005}, whereby the stellar component is first fitted as above with masked potential emission line regions, followed by the unmasking and fitting of the [\ion{O}{iii}] doublet which sets the kinematics for all the emission lines and finally the amplitude of the remaining emission lines.
-%Some of the forbidden emission lines have the ratio of their amplitudes fixed (see Table \ref{tab:EmissionLine}, Col.\,4).
+To minimize template mismatch, whereby emission lines are erroneously fitted to the edges of badly modeled and thus subtracted absorption features, we follow the method set out in \citet{Sarzi2005}.
+In this method the stellar component is first fitted as above with masked potential emission line regions, followed by the unmasking and fitting of the [\ion{O}{iii}] doublet which sets the kinematics for all the emission lines and finally the amplitude of the remaining emission lines is fitted.
 
@@
 		\label{subsec:absorption}
-		Due to the lack of calibration observations of Lick/Cassegrain Image Dissector Scanner spectrograph system (hereafter Lick/IDS system; \citealt{Faber1985, Worthey1994}) we use the line index system (LIS) of \citet{Vazdekis2010} instead.
+		Due to the lack of calibration observations of Lick/Cassegrain Image Dissector Scanner spectrograph system (hereafter Lick/IDS system; \citealt{Faber1985, Worthey1994}) standard galaxies, we use the line index system (LIS) of \citet{Vazdekis2010} instead.
 This relies on flux calibrations instead of correcting to the continuum shape and wavelength dependent resolution of the Lick/IDS system.
 We use the index definitions of \citet{Trager1998}, measuring the following indices: G4300, Fe4383, Ca4455, Fe4531, H\,$\beta$, Fe5015, Mg\,b, Fe5270, Fe5335, Fe5406, Fe5709, Fe5782, NaD, TiO1 and TiO2.
-TiO1 and TiO2 are considered molecular absorption lines and are measured in magnitude units, while all others are atomic and measured in angstroms.
-
-		Quoted line strengths are corrected for both emission line and the effect of the velocity dispersion of the stars. These corrections are detailed below.
+%TiO1 and TiO2 are considered molecular absorption lines and are measured in magnitude units, while all others are atomic and measured in angstroms.
+
+		Quoted line strengths are corrected for both emission line and the effect of the velocity dispersion of the stars as detailed below.
 
@@
 			We correct for the effect of the different velocity dispersions of the stars which varyingly spread absorption features such that differing fractions of the absorption is outside of the central bandpasses.
-To do this, we create a best-fitting spectrum (as in the previous step) which is \textit{not} convolved with the best-fitting LOSVD.
+To do this, we create a stellar best-fitting spectrum which is \textit{not} convolved with the best-fitting LOSVD.
 A given index, $I$, is then measured for both this `unconvolved' spectrum ($I^\text{unc}$) and the convolved best-fitting spectrum ($I^\text{conv}$), and the ratio of these two indices is used as a multiplicative correction factor for the index measured ($I^\text{obs}$), such that the corrected index ($I^\text{corr}$) is given by
@@
 % Firstly the centre of the galaxy is found as the luminosity weighted centre using the \textsc{python} routine \textsc{find\_galaxy}, which is part of the \textsc{mge} package\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/} by \citet{Cappellari2002}.
-			as found by the \textsc{idl} routine \textsc{kinemetry}\footnote{http://davor.krajnovic.org/idl/} by \citet{Krajnovic2006} which finds the best-fitting ellipses at a range of evenly spaced semi-major axes.
+			as found by the \textsc{idl} routine \textsc{kinemetry}\footnote{http://davor.krajnovic.org/idl/} by \citet{Krajnovic2006}, which finds the best-fitting ellipses at a range of evenly spaced semi-major axes.
 %This is achieved by performing harmonic expansion of maps along ellipses with a given semi-major axis and, when used for even moments (e.g.\ surface brightness, velocity dispersion, h$_4$ etc.), minimizing the amplitude of the first and second harmonics.
-			The results include the ellipticity, $\epsilon$ and position angle $PA_\text{phot}$ of the best-fitting ellipse for each semi-major axis.
+			The results include the ellipticity, $\epsilon$ and position angle, $PA_\text{phot}$ of the best-fitting ellipse for each semi-major axis.
 The fit is repeated for increasing semi-major axis until $<$75\% of the ellipse is not contained within the field of view.
@@
 			The kinematic position angle, $PA_\text{kin}$, is defined as the angle of the axis perpendicular to the apparent angular momentum vector westwards from North.
-A global value of $PA_\text{kin}$ is found using the \textsc{python} routine \textsc{fit\_kinematic\_pa}\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/\#pa\_kin} which finds $PA_\text{kin}$ of the symmetrised mean velocity map, as described in appendix C of \citet{Krajnovic2006}.
+A global value of $PA_\text{kin}$ is found using the \textsc{python} routine \textsc{fit\_kinematic\_pa}\footnotemark[\ref{fn:Cappellari}] which finds $PA_\text{kin}$ of the symmetrised mean velocity map, as described in appendix C of \citet{Krajnovic2006}.
 %This routine finds a symmetric (about $PA_\text{kin}$) velocity field, by replacing the mean velocity, $V$, in each bin with
@@
 			where $F_i$ is the flux of the $i^\text{th}$ bin, $R_i$ its distance from the centre and $V_i$ and $\sigma_i$ its mean stellar velocity and velocity dispersion, respectively.
-The sum is computed over all $N$ bins with a radius $R_\text{e}$.
+The sum is computed over all $N$ bins within $1R_\text{e}$ of the centre of the galaxy.
 
@@
 	Using the methods above, we produce stellar kinematic maps for all datacubes (shown in Section \ref{sec:Maps}).
-Here we use these maps to classify each galaxy according to the Atlas$^\text{3D}$ regular/non-regular rotator and fast/slow rotator classification schemes of \citet{Krajnovic2006} and \citet{Cappellari2016}, respectively, as well as the qualitative kinematic classes of \citet{Krajnovic2011}.
+Here, we use these maps to classify each galaxy according to the Atlas$^\text{3D}$ regular/non-regular rotator and fast/slow rotator classification schemes of \citet{Krajnovic2006} and \citet{Cappellari2016}, respectively, as well as the qualitative kinematic classes of \citet{Krajnovic2011}.
 We use the criteria described in the referenced literature for each of these classification, with the results shown in Table \ref{tab:classify}.
@@
 	% \begin{threeparttable}
-		\caption{Kinematic classifications.
+		\caption{Kinematic classifications of the Southern Sample galaxies.
 Col.\,1: Galaxy name.
@@
 Col.\,6: Regular-rotator (RR) or non-regular-rotator (NRR).
-Col.\,7: Kinematic features.
+Col.\,7: Kinematic features: kinematically-decoupled core (KDC) or low-velocity (LV).
 Col.\,8: Kinematic group.}
@@
 			\hline
-			\multicolumn{8}{L{.7\linewidth}}{$^{a}$Tentative classification. A higher signal-to-noise ratio (S/N) in the outer regions of the field of view is required for confirmation.}
+			\multicolumn{8}{L{.7\linewidth}}{$^{a}$Tentative classification. A higher S/N in the outer regions of the field of view is required for confirmation.}
 
@@
 	\subsection{Regular/Non-regular Rotators}
+		\label{subsec:RR}
 		We find 4/11, or $(36\pm15)$\%, of our sample galaxies are regular rotators.
@@
 		5 out of 11 galaxies, or $(45\pm13)$\%, are slow rotators.
-This is between that of the Atlas$^\text{3D}$ and MASSIVE projects, who find 13.1\% and 77.5\% of their sample galaxies to be slow rotators, respectively.
-As for the regular/non-regular rotators classification scheme, slow rotators are more likely to be found in higher mass galaxies and the three samples (Atlas$^\text{3D}$, MASSIVE and our Southern sample) have very different mass distributions (see upper panel of Fig.\,\ref{fig:SRmassFraction}).
-
-		In order to account for the difference in mass distribution, we find the expected fraction of slow rotators in the Southern sample, $f'$, corrected to the mass distribution of the combined Atlas$^\text{3D}$ and MASSIVE samples (hereafter the A+M sample), as
+This is between that of the Atlas$^\text{3D}$ and MASSIVE projects, who find 13.1\% and 77.5\% of their respective sample galaxies to be slow rotators.
+As in the regular/non-regular rotators classification scheme (Section \ref{subsec:RR}), slow rotators are more likely to be found in higher mass galaxies and the three samples (Atlas$^\text{3D}$, MASSIVE and our Southern sample) have very different mass distributions (see upper panel of Fig.\,\ref{fig:SRmassFraction}).
+
+		In order to account for the difference in mass distribution, we find the expected fraction of slow rotators in the Southern sample, $f'$, corrected to the mass distribution of the A+M sample, as
 		\begin{equation}
@@
 		\end{equation}
-		where $N^\text{SS}_i$ is the number of Southern sample galaxies in the $i^\text{th}$ mass bin, $N^\text{AM}_i$ is the fraction of slow rotators in the $i^\text{th}$ mass bin in the A+M combined sample and $N$ is the total number of mass bins.
+		where $N^\text{SS}_i$ is the number of Southern sample galaxies in the $i^\text{th}$ mass bin, $N^\text{AM}_i$ is the fraction of slow rotators in the $i^\text{th}$ mass bin in the A+M sample and $N$ is the total number of mass bins.
 In our case we use the $K$-band absolute magnitude ($M_K$) as a proxy for stellar mass, with bins of 0.5 mag.
@@
 	\subsection{Kinematic Features}
-		In addition to this, we attempt to identify the kinematic features defined by \citet{Krajnovic2011} in an algorithmic way.
+		We attempt to identify the kinematic features defined by \citet{Krajnovic2011} in an algorithmic way.
 However, the artefacts from the VIMOS quadrants confuse ellipse fitting algorithms so only maps derived from the MUSE data are classified in this way; kinematic features in maps derived from the VIMOS data are identified by eye.
@@
 	\subsection{Intrinsic Shape}
-		The misalignment angle between the photometric and kinematic position angle is given in Col.\,4 of Table \ref{tab:classify}.
-Misaligned systems may appear aligned in certain projections, but though aligned systems will be aligned in all projections, and a low value of $\Gamma_\text{kin}$ cannot be used to describe the intrinsic shape of an individual galaxy, but it can be interpreted within a statistical framework.
+		The misalignment angle, $\Gamma_\text{kin}$, between the photometric and kinematic position angle is given in Col.\,4 of Table \ref{tab:classify}.
+Intrinsically misaligned systems may appear aligned in certain projections, but aligned systems will be aligned in all projections, and therefore a low value of $\Gamma_\text{kin}$ cannot be used to describe the intrinsic shape of an individual galaxy, but they can be interpreted within a statistical framework as in \citet{Cappellari2007}.
 However, a high value of $\Gamma_\text{kin}$ can give an insight into the intrinsic shape of an individual galaxy.
@@
 This generally implies a more triaxial intrinsic shape, although large misalignments are extremely rarely observed in galaxies with $\epsilon > 0.4$, suggesting that non-regular rotators are more spherical in shape \citep{Cappellari2016}.
-The non-regular rotators in our Southern sample indeed all have $\epsilon < 0.4$ showing that they are consistent with a fairly spherical, triaxial intrinsic shape.
+The non-regular rotators in our Southern sample indeed all have $\epsilon < 0.4$ and a broad range of misalignment angles and are thus consistent with a fairly spherical, triaxial intrinsic shape.
 
@@
 \citet{Bender1993} observed the tight relationship between the global Mg$_2$ absorption line strength and logarithm of the central velocity dispersion, $\sigma_0$, in elliptical galaxies.
-They also noticed that residuals to the linear best-fitting appeared to be intrinsic as they have a near Gaussian shape about the median values, but do not seem to be correlated to any other galaxy property.
-
-		Since part of the red continuum band of the Mg$_2$ index is outside of the spectral range of VIMOS, we instead use the Mg\,b index.
-\citet{Ziegler1997} show there is an approximately linear relationship between Mg\,b and Mg$_2$, with a gradient of 14.3--15.5\,mag\,\AA$^{-1}$\ depending on metallicity.
+They also noticed that residuals to the best-fitting line appeared to be intrinsic as they have a near Gaussian distribution about the median values and do not seem to be correlated to any other galaxy property.
+
+		Part of the red continuum band of the Mg$_2$ index is outside of the spectral range of VIMOS, but \citet{Ziegler1997} show there is an approximately linear relationship between Mg\,b and Mg$_2$, with a gradient of 14.3--15.5\,mag\,\AA$^{-1}$\ depending on metallicity.
 We thus use Mg\,b as a proxy for Mg$_2$.
 
-		Using an aperture with a radius of 2 arcsec on each datacube, we measure $\sigma_0$ and Mg\,b at a spectral resolution of 8.4\,\AA\ full-width half-maximum (FWHM), chosen such that the transformation functions of \citet{Vazdekis2010} can be used to change the literature measurements from the Lick/IDS system to the LIS.
-The results are shown in Fig.\,\ref{fig:globalMg} with the best-fitting linear relationship (found using \textsc{lts\_linefit} by \citealt{Cappellari2013}) shown by the solid black line.
-This has a gradient of $2.3 \pm 0.5 \,\mathrm{\AA\,dex^{-1}}$) and intrinsic scatter of $0.13 \pm 0.10 \, \mathrm{\AA}$.
+		Using an aperture with a radius of 2\arcsec\ on each datacube, we measure $\sigma_0$ and Mg\,b at a spectral resolution of 8.4\,\AA\ full-width half-maximum (FWHM), chosen such that the transformation functions of \citet{Vazdekis2010} can be used to change the literature measurements from the Lick/IDS system to the LIS.
+The results are shown in Fig.\,\ref{fig:globalMg} with the best-fitting linear relationship (found using \textsc{lts\_linefit}\footnotemark[\ref{Cappellari}] by \citealt{Cappellari2013}) shown by the solid black line.
+This has a gradient of $2.3 \pm 0.5 \,\mathrm{\text{\AA}\,dex^{-1}}$) and intrinsic scatter of $0.13 \pm 0.10 \,$\AA.
 %Individual measurements for each galaxy are given in table \ref{tab:globalMg}.
-		This is in very good agreement with the gradient found by \citet{Ziegler1997} for a sample of elliptical galaxies within Virgo and Coma using data from \citet{Dressler1987} of $2.5\,\mathrm{\AA\,dex^{-1}}$ (blue dotted line in Fig.\,\ref{fig:globalMg}), with an intrinsic scatter of 0.16\,\AA\ for galaxies with $\log \sigma_0 \geqslant 2.3$.
+		This is in very good agreement with the gradient found by \citet{Ziegler1997} for a sample of elliptical galaxies within Virgo and Coma using data from \citet{Dressler1987} of $2.5\,\mathrm{\text{\AA}\,dex^{-1}}$ (blue dotted line in Fig.\,\ref{fig:globalMg}), with an intrinsic scatter of 0.16\,\AA\ for galaxies with $\log \sigma_0 \geqslant 2.3$\,dex.
 
@@
 			\includegraphics[width=\columnwidth]{Mg_sigma.png}
-			\caption[Global Mg\,b\,--\,$\sigma$]{The Mg\,b\,--\,velocity dispersion relation using a 2\arcsec aperture.
+			\caption[Global Mg\,b\,--\,$\sigma$]{The Mg\,b\,--\,velocity dispersion relation using a 2\arcsec\ aperture.
 We find a similar gradient to our best-fitting (solid) as that found by \citet[; dotted line]{Ziegler1997}.}
@@
 		\label{subsec:Lit}
-		Given that there is no well defined list of corrections (and methods) that is universally followed, care must be taken when making comparisons to the literature.
+		Given that there is no well defined list of corrections (and correction methods) that is universally followed, care must be taken when making comparisons to the literature.
 When comparing to a particular paper we correct for the same effects described in the paper, but using our methods, as described in Section \ref{subsec:absorption}.
@@
 		We find a very large offset for the G4300 index with respect to the results of \citet{Rampazzo2005}.
-As noted above, this index is extremely sensitive to the stellar velocity dispersion correction and we measure an average difference in the stellar velocity dispersion to that measured by \citet{Rampazzo2005} of $21\,\mathrm{km\,s^{-1}}$.
+This index is extremely sensitive to the stellar velocity dispersion correction and we measure an average difference in the stellar velocity dispersion to that measured by \citet{Rampazzo2005} of $21\,\mathrm{km\,s^{-1}}$.
 This may be enough to account for the difference in the measurements.
@@
 NGC 1316 shows a very young stellar population (our fit of $t \approx 2$\,Gyr agrees with that of \citealt{Kuntschner2000}, but is conflicting with the older and less metal rich stellar population of \citealt{Koleva2011} who found $t=4.5 \pm 0.3 \,\mathrm{Gyr}$ and $\mathrm{[Fe/H]}=0.12 \pm 0.01 \,\mathrm{dex}$ for an aperture covering the central 0.1 kpc).
-NGC 3557 is notable for containing a significantly younger ($t\approx 4$\,Gyr) core of about 10\arcsec\ diameter and NGC 3100 has a branch of young stars ($\approx 4$\,Gyr) along the southeast branch of the molecular gas (cyan contours).
+We also find NGC 612 to have a young stellar population of $t\approx 4\,\mathrm{Gyr}$.
+NGC 3557 is notable for containing a significantly younger ($t\approx 4$\,Gyr) core of about 10\arcsec\ diameter and NGC 3100 has a branch of young stars ($\approx 4$\,Gyr) along the southeast branch of the molecular gas (cyan contours in Fig \ref{fig:ngc3100}).
 
@@
 
-		\citet{Koleva2011} showed that while individual galaxies can have a wide range of radial gradients of age and metallicity, the mean gradient (within a mass bin) is uniform across a large mass range.
+		\citet{Koleva2011} showed that while individual galaxies can have a wide range of radial gradients of age and metallicity, the mean gradient (within a mass bin) is approximately constant across a large mass range.
 They assume a linear relationship between $\log t$ or [Fe/H] and $\log (R/\mathrm{R_e})$.
@@
 			\centering
-			\caption{The radial gradients of the most-likely SSP models.}
+			\caption{The radial gradients of the most-likely SSP models. Both gradients are dimensionless.}
 			\label{tab:popGrad}
@@
 				Galaxy 	& $\Delta_\text{log age}$ & $\Delta_\text{[Fe/H]}$ \\ 
-					& dex\,arcsec$^{-1}$ & dex\,arcsec$^{-1}$ \\
+					% & dex\,arcsec$^{-1}$ & dex\,arcsec$^{-1}$ \\
 				\hline
@@
 
-		We find average gradients of $\Delta_\text{log age} = 0.014\pm0.007 \,\mathrm{dex \, arcsec^{-1}}$ and $\Delta_\text{[Fe/H]} = -0.03\pm0.01 \, \mathrm{dex \, arcsec^{-1}}$.
-This is consistent with \citet{Koleva2011} who, for elliptical galaxies found average gradients of $0.06\pm0.09 \, \mathrm{dex \, arcsec^{-1}}$ and $-0.26\pm0.08 \, \mathrm{dex \, arcsec^{-1}}$ for the age and metallicity gradients, respectively.
-For S0s they find flatter corresponding gradients of $0.01\pm0.11\, \mathrm{dex \, arcsec^{-1}}$ and $-0.12\pm0.13\, \mathrm{dex \, arcsec^{-1}}$.
+		We find average gradients of $\Delta_\text{log age} = 0.014\pm0.007$ and $\Delta_\text{[Fe/H]} = -0.03\pm0.01$.
+This is consistent with \citet{Koleva2011} who, for elliptical galaxies found average gradients of $0.06\pm0.09$ and $-0.26\pm0.08$ for the age and metallicity gradients, respectively.
+For lenticular galaxies (S0s) they find flatter corresponding gradients of $0.01\pm0.11$ and $-0.12\pm0.13$.
 
@@
 		\label{subsec:popKDC}
-		\citet{Kuntschner2010} found that kinematically-decoupled cores (KDCs) exist in two classes: they are either small or contain an old stellar population.
+		\citet{Kuntschner2010} found that KDCs exist in two classes: they are either small with various stellar ages or typically larger but containing an old stellar population.
 The size of the KDC is defined as the radius of the region surrounding the KDC where the superposition of the two components (the KDC and the host galaxy) results in a local minimum in the mean velocity.
@@
 		The small KDCs are too small to be spatially resolved by our data, and thus are not considered here.
-The large KDCs are typically embedded in slow rotators.
-They have no limit on the age of their stellar populations suggesting that the stars within the KDC dominate in total mass as well as surface brightness.
+The larger, old KDCs are typically embedded in slow rotators.
+They have no upper limit on the age of their stellar populations suggesting that the stars within the KDC dominate in total mass as well as surface brightness.
 Thus, they do not fade into their host galaxies as they age unlike the small KDCs \citep{Kuntschner2010}.
@@
 We include PKS 718-34 here but stress it is only tentatively classified as containing a KDC.
-As can be seen from Fig.\,\ref{fig:KDC}, PKS 718-34 would be an extremely large KDC, but is still is consistent with the findings of \citet{Kuntschner2010}.
+As can be seen from Fig.\,\ref{fig:KDC}, PKS 718-34 would be an extremely large KDC, but is still consistent with the findings of \citet{Kuntschner2010}.
 
@@
 			\caption[KDC dichotomy]{The KDC size\,--\,age relation.
-KDCs exist in two classes: old or small.
-VIMOS is in red, MUSE in blue and SAURON from \citet{Kuntschner2010} in black and gray for fast and slow rotators respectively.}
+KDCs exist in two classes: old and embedded in a slow rotator or small and embedded in a fast rotator.
+Observations with VIMOS are in red, MUSE in blue and SAURON from \citet{Kuntschner2010} in black and gray for fast and slow rotators respectively.}
 			\label{fig:KDC}
@@
 	Using the methods described in Section \ref{subsubsec:EmissionFit}, we find the best-fitting line-of-sight velocity distribution (LOSVD; assumed to be Gaussian and parametrised by the mean velocity and velocity dispersion only) of the emission lines in each bin.
-Images of the Southern Sample galaxies in the [\ion{O}{iii}]$\lambda\lambda$4957,5007 lines are shown in Appendix \ref{sec:Maps} (we choose to show [\ion{O}{iii}] as detections of all emission lines require a detection of [\ion{O}{iii}] first, see Section \ref{subsubsec:EmissionFit}).
+Images of the Southern Sample galaxies in the [\ion{O}{iii}]$\lambda\lambda$4957,5007 doublet are shown in Appendix \ref{sec:Maps} (we choose to show [\ion{O}{iii}] as detections of all emission lines require a detection of [\ion{O}{iii}] first, see Section \ref{subsubsec:EmissionFit}).
+
 	Only 4 galaxies of the Southern Sample have emission lines detected outside of their central region (IC 1459, NGC 612, NGC 1316 and NGC 3100).
-Of the remaining 7 galaxies, NGC 1399 and PKS 718-34 have no detection of H$\beta$ in their spatially-resolved map (although we do detect H$\beta$ in the spatially-integrated spectrum of NGC 1399; see below), while the other 5 galaxies are only detected in their centre.
+Of the remaining 7 galaxies, NGC 1399 and PKS 718-34 have no detection of H$\beta$ in their spatially-resolved map (although we do detect H$\beta$ in the spatially-integrated spectrum of NGC 1399; see Table \ref{tab:gasMass}), while the other 5 galaxies are only detected in their centre.
 All other emission lines have similar distributions, but with different fluxes.
@@
 	\end{equation}
-	where $M_\text{\ion{H}{ii}}$ is the total mass of \ion{H}{ii} in the galaxy, $D$ is the galaxy distance, and $F(\mathrm{H\alpha})$ is the H$\alpha$ flux measured from the spectrum created by summing spatially all spaxels within an aperture of $\frac{R_\mathrm{e}}{2}$ (chosen to exclude outer noisy regions of the observations, but include spatially extended gas regions).
+	where $M_\text{\ion{H}{ii}}$ is the total mass of \ion{H}{ii} in the galaxy, $D$ is the galaxy distance, and $F(\mathrm{H\alpha})$ is the H$\alpha$ flux measured from the spectrum created by summing spatially all spaxels within an aperture of $\frac{R_\mathrm{e}}{2}$ (chosen to exclude noisy outer regions of the observations, but still includes the bulk of the gas in system with significant spatially-extended gas).
 This method assumes an electron density $n_\mathrm{e} = 100 \, \mathrm{cm^{-3}}$, a temperature of $10^4$ K and case-B recombination (electrons above 13.6\,eV are not reabsorbed; e.g.\ \citealt[p.\,74]{Osterbrock1974}).
 Like \citet{Sarzi2005}, we only claim a detection if the amplitude-to-noise ratio (A/N) is $>4$ for [\ion{O}{iii}] and $>2.5$ for H$\beta$ or H$\alpha$.
-Upper limits are calculated using the $1\sigma$ noise level (see Section \ref{subsubsec:EmissionFit}).
+When these conditions are not met, upper limits are calculated using the $1\sigma$ noise level (see Section \ref{subsubsec:EmissionFit}).
 
@@
 Due to that fact that, unlike stars, gas is dissipational, it is to be expected that given sufficient time, the ISM will always settle into a disc.
-These maps show that the ISM of the Southern sample galaxies varies from largely settled discs in IC 1459 and NGC 612 to more disordered kinematics of NGC 3100 and a possible inflow in NGC 1316.
-
-		It is immediately clear when comparing the mean stellar velocity maps to the mean gas velocity maps that where gas is detected, its angular momentum is not often aligned with that of the stars.
+These maps show that the warm component of the ISM (the ionized gas) of the Southern sample galaxies varies from largely settled discs in IC 1459 and NGC 612 to more disordered kinematics of NGC 3100 and a possible inflow in NGC 1316.
+
+		It is immediately clear when comparing the stellar mean velocity maps to the ionized gas mean velocity maps that where gas is detected, its angular momentum is not often aligned with that of the stars.
 A misalignment between the kinematics of the stars and gas suggests an external origin for the gas (e.g.\ accretion or wet merger).
@@
 
-		\paragraph{IC 1459} has ionized gas counter-rotating with respect to the stellar kinematically-decoupled core, and also rotating independently from the rest of the galaxy.
-\citet{Franx1988} claim that the rotation of the gas is aligned with that of the stars outside of the KDC, however we observe outer stellar kinematics to be non-rotating.
+		\textbf{IC 1459} has ionized gas counter-rotating with respect to the stellar KDC, and also rotating independently from the rest of the galaxy.
+\citet{Franx1988} claim that the rotation of the gas is aligned with that of the stars outside of the KDC, however we observe the outer stellar kinematics to be non-rotating.
 As the stellar disc did not survive the merger even that created the KDC, it is unlikely that the gas in IC 1459 progenitor galaxy survived.
@@
 
-		\paragraph{NGC 612} has well aligned stellar and gaseous kinematics.
+		\textbf{NGC 612} has well aligned stellar and gaseous kinematics.
 The misalignment between the position angle of the stellar and gas kinematics (using the method described in Section \ref{subsubsec:KinPA}) is just $1\fdg0\pm0\fdg7$, consistent with an internal origin for the gas.
@@
 
-		\paragraph{NGC 1316} is a complex object.
+		\textbf{NGC 1316} is a complex object.
 Since there are redshifted emission lines with respect to the rest frame of the galaxy on both sides of the galaxy, the gas is not in a settled disc and that there must be some inflow/outflows.
@@
 
-		\paragraph{NGC 3100} has an interesting ISM morphology.
-The \ce{^{12}CO(2-1)} contours (shown in cyan in all figures) show a broken ring with the radio jet passing through the gaps in the ring (Ruffa et\,al., in prep.).
+		\textbf{NGC 3100} has an interesting ISM morphology.
+The \ce{^{12}CO(2-1)} contours (shown in cyan in all maps) show a broken ring with the radio jet passing through the gaps in the ring (Ruffa et\,al., in prep.).
 We observe the ionized gas to be brightest in the gaps of this ring which we interpret as additional excitation of the gas due to shocks from the impact of the jet.
@@
 This indicates that slow rotators are dominated by external sources of gas, while fast rotators can have either internal or external sources.
-This is consistent with our observations of the Southern Sample: the only slow rotator with detected ionized gas is IC 1459, which has significantly kinematically-misaligned gas; of the 3 fast rotators, only 1 (NGC 3100) is definitely misaligned, while NGC 612 is consistent with an internal gas origin and NGC 1316 is not clear.
+This is consistent with our observations of the Southern Sample: the only slow rotator with detected ionized gas is IC 1459, which has significantly kinematically-misaligned gas, while of the 3 fast rotators, only 1 (NGC 3100) is definitely misaligned, while NGC 612 is consistent with an internal gas origin and NGC 1316 is unclear.
 %, although the best-fitting exponential disc model (see Fig.\ \ref{fig:Inflow}) is definitely misaligned to the stellar kinematics.
@@
 		\label{subsec:Diagnostics}
-		Determining the sources of ionizing radiation in galaxies using emission line ratios, such as Baldwin\,--\,Phillips\,--\,Terlevich (BPT) plots (\citealt{Baldwin1981}; revised by \citealt{Kewley2001, Kewley2006} and \citealt{Kauffmann2003a}), has become increasingly widespread exercise.
+		Determining the sources of ionizing radiation in galaxies using emission line ratios, such as Baldwin\,--\,Phillips\,--\,Terlevich (BPT) plots (\citealt{Baldwin1981}; revised by \citealt{Kewley2001, Kewley2006} and \citealt{Kauffmann2003a}), has become an increasingly widespread exercise.
 That said, there are several important caveats.
 Firstly, great care must be taken when applying each diagnostic; much of the literature misinterprets the resulting classifications.
-Secondly, in the absence of spatially-resolved spectra, low-ionization nuclear emission-line region (LINER) classifications have often been taken as a marker for jet-mode active galactic nuclei (AGN).
+Secondly, in the absence of spatially-resolved spectra, low-ionization nuclear emission-line region (LINER) classifications have often been taken as a marker for jet-mode AGN.
 However, several recent surveys have shown that many of these may not be bona fide AGN \citep[e.g.][]{Sarzi2005, Sarzi2010, Singh2013, Belfiore2016a}.
@@
 		The problem with classifying ETGs by their emission lines is that they often have very little ionized gas and weak ionizing radiation fields, so that it is often difficult to detect emission lines from their ISM.
-Furthermore, the BPT plots require a larger spectral range than many integral-field spectrographs (IFS) deliver.
+Furthermore, the BPT plots require a larger spectral range than many IFS deliver.
 This has given rise to a number of other, analogous, classifying plots, that we take advantage of here.
@@
 
-		Firstly, we preferentially use the BPT plots for the galaxies observed with MUSE (that has the required spectral range).
+		Firstly, we preferentially use the BPT plots for the galaxies observed with MUSE (MUSE has the required spectral range).
 This allows us to classify galaxies into star-forming, LINER/LIER or Seyfert 2 classes.
@@
 		To check if the LINER classifications are due to a central radiation source (such as an AGN) or extended sources (such as weak star formation or post-asymptotic giant branch stars; pAGB stars), we examine the H$\alpha$ and H$\beta$ flux radial profiles of our galaxies with extended detected ionized gas (see Section \ref{subsubsec:Hb}).
-Finally we use the mass\,--\,excitation (MEx) plot of \cite{Nyland2016}, using parameters derived from the central region of the galaxies, only measured within a 3\arcsec wide aperture (see Section \ref{subsubsec:MEx}).
-This allows us to classify into star-forming, Seyfert 2, LINER, transition or passive classes, with LINER galaxies subdivided into those whose LINER behaviour is (LINER-AGN) or is not attributed to a central AGN.
+Finally we use the mass\,--\,excitation (MEx) plot of \cite{Nyland2016}, using parameters derived from the spatially-integrated spectra within an aperture of radius 3\arcsec\ thus only probing the central region of the galaxies (see Section \ref{subsubsec:MEx}).
+This allows us to classify the remaining galaxies into star-forming, Seyfert 2, LINER, transition or passive classes, and subdivide LINER galaxies into those whose LINER characteristics are attributable to a central AGN (labeled as LINER-AGN in Table \ref{tab:gasMass}) and those whose LINER characteristics are not.
+We expand on the final two steps in the sections below.
 
@@
 				\centering
+				\includegraphics[width=0.73\columnwidth]{Halpha_profile.png}
+				\caption{H$\alpha$ flux radial profiles derived from the MUSE datacubes. Solid red lines show $F(\mathrm{H\alpha}) \propto r^{-2}$.}
+				\label{fig:Ha_profile_MUSE}
+			\end{figure}
+
+			\begin{figure}
+				\centering
 				\includegraphics[width=\columnwidth]{Hbeta_profile.png}
@@
 				\label{fig:Hb_profile_VIMOS}
-			\end{figure}
-
-			\begin{figure}
-				\centering
-				\includegraphics[width=0.73\columnwidth]{Halpha_profile.png}
-				\caption{H$\alpha$ flux radial profiles derived from the MUSE datacubes. Solid red lines show $F(\mathrm{H\alpha}) \propto r^{-2}$.}
-				\label{fig:Ha_profile_MUSE}
 			\end{figure}
@@
 	\label{sec:discuss}
-	In Sections \ref{sec:StarKine} we show that in terms of the stellar kinematic properties, our radio-selected Southern sample are no different to ordinary optically-selected ETGs.
+	In Section \ref{sec:StarKine} we show that in terms of the stellar kinematic properties, our radio-selected Southern sample are no different to ordinary optically-selected ETGs.
 Our sample shows a mixture of of regularly- and non-regularly-rotating behaviours, with both classes showing evidence of consistency with observations of the intrinsic shapes of ordinary regular and non-regular rotators.
@@
 
-	Radio-loud lenticular (S0) galaxies are extremely rare with only a handful of known cases \citep[e.g.][]{Heckman1982, Morganti2011}, presumably due to the associated mass functions of both S0s and radio galaxies: both massive S0s and low-mass radio galaxies are rare, with a similar transition masses from rare to more numerous.
+	Radio-loud S0s are extremely rare with only a handful of known cases \citep[e.g.][]{Heckman1982, Morganti2011}, presumably due to the associated mass functions of both S0s and radio galaxies: both massive S0s and low-mass radio galaxies are rare, with a similar transition masses from rare to more numerous.
 NGC 612 is one of those rare cases.
 
-	In terms of absorption line strengths and stellar populations (Section \ref{sec:absorption} and \ref{sec:stellarPop}), we find a remarkably similar gradient to the central Mg\,b verse stellar velocity dispersion relation to that of \citet{Ziegler1997}.
-Most of the galaxies in our Southern sample show typical ETG behavior: old, metal rich stellar populations, with a few exceptions: NGC 612 and NGC 1316 are both significantly younger than most ETGs and NGC 3557 has a young core.
+	In terms of absorption line strengths and stellar populations (Sections \ref{sec:absorption} and \ref{sec:stellarPop}), we find a remarkably similar gradient to the central Mg\,b verse stellar velocity dispersion relation to that of \citet{Ziegler1997}.
+Most of the galaxies in our Southern sample show typical ETG behavior: old, metal-rich stellar populations, with a few exceptions: NGC 612 and NGC 1316 are both significantly younger than most ETGs and NGC 3557 has a young core.
 We observe that all 3 KDCs contain old stellar populations and are consistent with being merger remnants.
-We also show that the KDCs found in Section \ref{sec:StarKine} fit with the age\,--\,size relation found by \citet{Kuntschner2010} (see Section \ref{subsec:popKDC}).
+We also show that the KDCs found in Section \ref{sec:StarKine} fit with the age\,--\,size relation found by \citet{Kuntschner2010} (see Section \ref{subsec:popKDC}) for KDCs in optically-selected ETGs.
 
@@
 If this is the case then a young stellar population might be expected to dominate in the very central (1--2) spaxels.
-We our best-fitting age maps show no evidence of this.
-
-	Section \ref{sec:gas} we show that galaxies in our Southern Sample have ionized gas masses of $10^4$\,--\,$10^6\,\mathrm{M_\odot}$.
+We our best-fitting age maps (bottom-left panel of Figs \ref{fig:eso443}-\ref{fig:pks718}) show no evidence of this.
+
+	In Section \ref{sec:gas} we show that galaxies in our Southern Sample have ionized gas masses of $10^4$\,--\,$10^6\,\mathrm{M_\odot}$.
 These are at the upper limit of, and possibly exceed, the typical masses observed in ETGs, although given that our sample contains particularly massive galaxies, high ionized gas masses are not unexpected.
@@
 
-	Overall, we thus find that the warm ISM properties of our Southern Sample galaxies are consistent with those of other jet-mode AGN.
-These are ordinary ETGs experiencing an active phase, presumably due to the central black holes currently accreting gas in some form.
-
-	All these observations and findings, are consistent with those of typical massive ETGs.
-This is consistent with the hypothesis that radio-galaxies are ordinary massive ETGs experiencing a normal but short-lived active phase.
-
-% \section{Summary}
-% 	\label{sec:sum}
-% 	In the paper we present VIMOS and archival MUSE IFS observations of 11 low-powered radio galaxies.
-We find the best-fitting stellar kinematics and populations, as well as find the ionized gas spatial distribution, kinematics and dominant ionizing radiation source.
-We classify the kinematic maps according to the fast/slow rotator classification scheme of \citet{Cappellari2016} and find a consistent fraction of slow rotators for the mass distribution of our sample.
+	Overall, we thus find that the warm ISM properties of our Southern Sample galaxies are consistent with those of other optically-selected ETGs.
+This is consistent with low-powered radio galaxies being bona-fide detections of jet-mode AGN and therefore our sample galaxies are ordinary massive ETGs experiencing a normal but short-lived active phase, presumably due to the central black holes currently accreting gas in some form.
 
 \section*{Acknowledgements}
-
-The Acknowledgements section is not numbered. Here you can thank helpful
-colleagues, acknowledge funding agencies, telescopes and facilities used etc.
-Try to keep it short.
 
@@
 			\includegraphics[width=\textwidth]{eso443-g024.png}
-			\caption{}
+			\caption{Spatially-resolved map of measurements derived from VIMOS observations for ESO\,433-G24.
+The measurement is given in the top-left of each panel and the colour-scale limits are given in the bottom-right.
+The surface brightness (isophotes) are shown as black contours in all maps, while the \ce{^{12}CO(2-1)} contours from ALMA are in cyan and radio continuum contours from the VLA are in green.
+The radio band displayed depends on the data available in the archive and which images had a similar resolution and scales.}
 			\label{fig:eso443}
@@
 			\includegraphics[width=\textwidth]{ic1459.png}
-			\caption{As Fig.\,\ref{fig:eso443}, but for IC\,1459}
-			% \label{fig:}
+			\caption{As Fig.\,\ref{fig:eso443}, but for IC\,1459 and derived from MUSE observations.}
+			\label{fig:ic1459}
 		\end{figure*}
@@
 			\includegraphics[width=\textwidth]{ic1531.png}
-			\caption{As Fig.\,\ref{fig:eso443}, but for IC\,1531}
-			% \label{fig:}
+			\caption{As Fig.\,\ref{fig:eso443}, but for IC\,1531.}
+			\label{fig:ic1531}
 		\end{figure*}
@@
 			\includegraphics[width=\textwidth]{ic4296.png}
-			\caption{As Fig.\,\ref{fig:eso443}, but for IC\,4296}
-			% \label{fig:}
+			\caption{As Fig.\,\ref{fig:eso443}, but for IC\,4296 and derived from MUSE observations.}
+			\label{fig:ic4296}
 		\end{figure*}
@@
 			\includegraphics[width=\textwidth]{ngc0612.png}
-			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,612}
-			% \label{fig:}
+			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,612.}
+			\label{fig:ngc612}
 		\end{figure*}
@@
 			\includegraphics[width=\textwidth]{ngc1316.png}
-			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,1316}
-			% \label{fig:}
+			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,1316 and derived from MUSE observations.}
+			\label{fig:ngc1316}
 		\end{figure*}
@@
 			\includegraphics[width=\textwidth]{ngc1399.png}
-			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,1399}
-			% \label{fig:}
+			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,1399 and derived from MUSE observations.}
+			\label{fig:ngc1399}
 		\end{figure*}
@@
 			\includegraphics[width=\textwidth]{ngc3100.png}
-			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,3100}
-			% \label{fig:}
+			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,3100.}
+			\label{fig:ngc3100}
 		\end{figure*}
@@
 			\includegraphics[width=\textwidth]{ngc3557.png}
-			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,3557}
-			% \label{fig:}
+			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,3557.}
+			\label{fig:ngc3557}
 		\end{figure*}
@@
 			\includegraphics[width=\textwidth]{ngc7075.png}
-			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,7075}
-			% \label{fig:}
+			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,7075.}
+			\label{fig:ngc7075}
 		\end{figure*}
@@
 			\includegraphics[width=\textwidth]{pks0718-34.png}
-			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,718-34}
-			% \label{fig:}
+			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,718-34.}
+			\label{fig:pks718}
 		\end{figure*}
+
+\pagebreak
 

### 2018-01-26 produce_maps.py

@@ -28,19 +28,20 @@ class Ds(object):
 		else:
 			self.unbinned_flux = np.zeros((150,150))
 		self.number_of_bins = 4
-		self.components = {'stellar':comp()}
+		self.components = {'stellar':comp(), '[OIII]5007d':comp()}
 		self.flux = np.array([0,1,1,2])
 
-	def absorption_line(self, p, uncert=False):
+	def absorption_line(self, p, uncert=False, remove_badpix=False):
 		if uncert:
-			return [0,1,1,2], [0,1,1,2]
+			return np.array([0,1,1,2]), np.array([0,1,1,2])
 		else:
-			return [0,1,1,2]
+			return np.array([0,1,1,2])
 
 class comp(object):
 	def __init__(self):
-		self.plot = {'vel':myArray([0,1,1,2], [0,1,1,2]), 
-			'sigma': myArray([0,1,1,2],[0,1,1,2])}
+		self.plot = {'vel':myArray(np.array([0,1,1,2]), np.array([0,1,1,2])), 
+			'sigma': myArray(np.array([0,1,1,2]), np.array([0,1,1,2]))}
+		self.flux = np.array([0,1,1,2])
 
 
 def plot(galaxy, instrument='vimos', debug=True):
@@ -259,7 +260,7 @@ def plot(galaxy, instrument='vimos', debug=True):
 	# Flux
 	for i, row in enumerate(plots):
 		for j, p in enumerate(row):
-			# print i, j, p3w=]-=
+			print i, j, p
 			if galaxy in ['ngc0612', 'pks0718-34'] and 'Mg_b' in p:
 				break # break out of for-loop
 			elif 'flux' in p:
@@ -268,30 +269,10 @@ def plot(galaxy, instrument='vimos', debug=True):
 					flux_unbinned=D.unbinned_flux, galaxy=str_plots[i][j],
 					ax=axs[i,j])
 
-			elif p != '':
-				vmin, vmax = set_lims(eval(p), 
-					symmetric = p=="D.components['stellar'].plot['vel']",
-					positive = p!="D.components['stellar'].plot['vel']")
-				if 'D2' in p:
-					axs[i,j] = plot_velfield_nointerp(D2.x, D2.y, D2.bin_num, 
-						D2.xBar, D2.yBar, eval(p), header,  
-						vmin=vmin, vmax=vmax, 
[…]

### 2018-01-27 paper.tex
EoDC:
Final references and added units on maps and sorted negative limits that
should not be negative.

 On branch master
 Changes to be committed:
	modified:   paper.tex
	modified:   produce_maps.py
	modified:   refs.bib

@@
 	These radio galaxies are known to be dusty with dust lanes having a tendency to be perpendicular to the jets \citep[e.g.][]{DeRuiter2002, VerdoesKleijn2005}.
-They have little ionized gas in the ISM \citep[e.g.][]{}, but often have significant quantities of hot X-ray gas (e.g.
-\citealt{}; the cold phase of the ISM of radio galaxies will be examined in Ruffa et.al.\ in prep.).
+They have little ionized gas in the ISM \citep[e.g.][]{Sarzi2005}, but often have significant quantities of hot X-ray gas (e.g.
+\citealt{Canizares1987}; the cold phase of the ISM of radio galaxies will be examined in Ruffa et.al.\ in prep.).
 If the low star-formation rates typically seen in massive ETGs are preserved by jet-mode AGN, then all such ETGs must regularly go through similar active phases, and therefore low-powered radio galaxies should be much the same as their radio-quiet (quiescent phase) ETG counterparts.
 
-	To test this hypothesis, a complete sample of 11 nearby low-powered radio galaxies was constructed \citep{} and observed with a suite of instruments.
+	To test this hypothesis, a complete sample of 11 nearby low-powered radio galaxies was constructed \citet{Prandoni2010} and observed with a suite of instruments.
 Here, we present the spatially-resolved stellar kinematics, stellar populations, and ionized gas distribution, kinematics and ionization derived from integral-field spectroscopic (IFS) observations with the Visible Multi-object Spectrograph (VIMOS) and archival data from the Multi-unit Spectroscopic Explorer (MUSE), both on the Very Large Telescope (VLT).

### 2018-01-27 produce_maps.py

@@ -114,6 +114,36 @@ def plot(galaxy, instrument='vimos', debug=True):
 			'',
 			''
 			]]
+		units = [[
+			'',
+			'',
+			r'km s$^{-1}$',
+			r'km s$^{-1}$',
+			r'km s$^{-1}$',
+			r'km s$^{-1}$'
+			],[
+			r'$\AA$',
+			r'$\AA$',
+			r'$\AA$',
+			r'$\AA$',
+			r'$\AA$',
+			r'$\AA$'
+			],[
+			r'$\AA$',
+			r'$\AA$',
+			r'$\AA$',
+			r'$\AA$',
+			r'$\AA$',
+			r'$\AA$'
+			],[
+			r'$\AA$',
+			r'$\AA$',
+			'',
+			'',
+			'',
+			''
+			]]
+
 	elif instrument == 'muse':
 		from plot_results_muse import add_, set_lims
 		from errors2_muse import get_dataCubeDirectory
@@ -193,6 +223,42 @@ def plot(galaxy, instrument='vimos', debug=True):
 			'',
 			''
 			]]
+		units = [[
+			'',
+			'',
+			r'km s$^{-1}$',
+			r'km s$^{-1}$',
+			r'km s$^{-1}$',
+			r'km s$^{-1}$'
+			],[
+			r'$\AA$',
+			r'$\AA$',
+			r'$\AA$',
+			r'$\AA$',
+			r'$\AA$',
+			r'$\AA$'
+			],[
+			r'$\AA$',
+			r'$\AA$',
+			r'$\AA$',
+			r'$\AA$',
+			r'$\AA$',
+			r'$\AA$'
+			],[
+			r'$\AA$',
+			r'$\AA$',
+			r'$\AA$',
+			r'$\AA$',
+			r'$\AA$',
+			r'$\AA$'
+			],[
+			'mag',
+			'mag',
+			'mag',
+			'mag',
+			'',
+			''
+			]]
 	if galaxy in ['ngc0612', 'pks0718-34']:
 		rows -= 1 # No Mgb
 	if galaxy in ['ic1459', 'ngc0612', 'ngc1316', 'ngc3100']:
@@ -213,7 +279,15 @@ def plot(galaxy, instrument='vimos', debug=True):
 			'',
 			''
 			])
-			
+		units.insert(1,[
+			r'km s$^{-1}$',
+			r'km s$^{-1}$',
+			r'km s$^{-1}$',
[…]

### 2018-01-28 paper.tex
EoDC: Version 1
 On branch master
 Changes to be committed:
	modified:   paper.tex

@@
 \usepackage{newtxtext,newtxmath}
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
 
@@
 \usepackage{mhchem} 	% typeset chemistry symbols
-% \usepackage{multicol} 	% Multi-column entries in tables
-% \usepackage{natbib} % references in text to look like MNRAS/ApJ/A&A
-% \usepackage{multirow} % for multirow command
 \usepackage{array} % For wrapping text in cell in tables with multicolumntype
@@
 	\label{sec:analysis}
-	Both VIMOS and MUSE datasets are spatially binned using Voronoi binning\footnote{\label{fn:Cappellari}http://www-astro.physics.ox.ac.uk/\~mxc/software/} \citep{Cappellari2003} and from this point on are treated almost identically, the only difference (other than the different spectral ranges and resolutions) being that the MUSE datacubes are spatially binned to a higher signal-to-noise ratio (S/N).
+	Both VIMOS and MUSE datasets are spatially binned using Voronoi binning\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/} \citep{Cappellari2003} and from this point on are treated almost identically, the only difference (other than the different spectral ranges and resolutions) being that the MUSE datacubes are spatially binned to a higher signal-to-noise ratio (S/N).
 For our purposes, we define the `signal' and `noise' of each spaxel as the median value of its spectrum and noise spectrum, respectively.
@@
 summed across both spatial dimensions of the datacube) spectrum.
-We use the penalized-fitting (\textsc{pPXF}) routine\footnotemark[\ref{fn:Cappellari}] of \citet{Cappellari2004} and \citet{Cappellari2016a} with the Medium-resolution Issac Newton Telescope (INT) Library of Empirical Spectra (MILES) library \citep{Sanchez-Blazquez2006, Falcon-Barroso2011a} to find the best-fitting line-of-sight velocity distribution (LOSVD; as parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion).
+We use the penalized-fitting (\textsc{pPXF}) routine\footnotemark[1] of \citet{Cappellari2004} and \citet{Cappellari2016a} with the Medium-resolution Issac Newton Telescope (INT) Library of Empirical Spectra (MILES) library \citep{Sanchez-Blazquez2006, Falcon-Barroso2011a} to find the best-fitting line-of-sight velocity distribution (LOSVD; as parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion).
 The final mean velocity of a given galaxy, is used as its precise spectroscopic redshift and is given in Table \ref{tab:sample}.
@@
 			The kinematic position angle, $PA_\text{kin}$, is defined as the angle of the axis perpendicular to the apparent angular momentum vector westwards from North.
-A global value of $PA_\text{kin}$ is found using the \textsc{python} routine \textsc{fit\_kinematic\_pa}\footnotemark[\ref{fn:Cappellari}] which finds $PA_\text{kin}$ of the symmetrised mean velocity map, as described in appendix C of \citet{Krajnovic2006}.
+A global value of $PA_\text{kin}$ is found using the \textsc{python} routine \textsc{fit\_kinematic\_pa}\footnotemark[1] which finds $PA_\text{kin}$ of the symmetrised mean velocity map, as described in appendix C of \citet{Krajnovic2006}.
 %This routine finds a symmetric (about $PA_\text{kin}$) velocity field, by replacing the mean velocity, $V$, in each bin with
@@
 
-\pagebreak
+% \clearpage
 

### 2018-01-29 paper.tex
Added in Acknowlegements
 On branch master
 Changes to be committed:
	modified:   paper.tex

@@
 \section*{Acknowledgements}
+JW acknowledges funding from the Science and Technology Facilities Council Grant Code 1577871.
+This research makes extensive use of observation from VIMOS \citep{LeFevre2003} and archival data from MUSE \citep{Bacon2010}.
+We also make use of observations from the APEX \citep{Gusten2006} and the ALMA.
+ALMA is a partnership of ESO (representing its member states), the National Science Foundation (NSF; USA) and the National Institutes of Natural Sciences (NINS; Japan), together with the National Research Council (NRC; Canada), the Ministry of Science and Technology (MOST; Taiwan) and Academia Sinica Institute of Astronomy and Astrophysics (ASIAA; Taiwan), and Korea Astronomy and Space Science Institute (KASI; Republic of Korea), in cooperation with the Republic of Chile.
+The Joint ALMA Observatory is operated by ESO, Associated Universities Inc./National Radio Astronomy Observatory (AUI/NRAO; USA) and National Astronomical Observatory of Japan (NAOJ).
+We also make use of data products from the 2MASS, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center (IPAC)/California Institute of Technology, funded by the National Aeronautics and Space Administration (NASA) and NSF.
+We also make use of the Set of Identifications, Measurements and Bibliography for astronomical Data (SIMBAD) database and Portal tool, operated at the Strasbourg astronomical Data Centre (CDS), France.
+This research has made use of the following resources and programs: arXiv.org; the Astrophysics Data System (ADS); \textsc{astropy}, a community-developed core \textsc{python} package for astronomy \citep{TheAstropyCollaboration2013}; \textsc{kinemetry} \citep{Krajnovic2006}; \textsc{ipython} \citep{Perez2007}; \textsc{matplotlib} \citep{Hunter2007}; \textsc{p3d} \citep{Sandin2010, Sandin2011}; \textsc{pPXF} \citep{Cappellari2004}; \textsc{py3d} \citep{Sanchez2011, Husemann2013, Husemann2014}; \textsc{scipy} \citep{Oliphant2007, Millman2011}; \textsc{numpy} \citep{VanderWalt2011}; \textsc{spectools} (Ryan Houghton and Simon Zieleniewski, private comm.); and \textsc{voronoi\_2d\_binning} \citep[including the SAURON colourmaps; ][]{Cappellari2003}.
 

### 2018-09-18 paper.tex
Propergating alterations to thesis to paper
 On branch master
 Changes to be committed:
	modified:   KDC_size_age.png
	modified:   M_k_binned.png
	modified:   Mg_sigma.png
	modified:   lambda_R_ellipticity.png
	modified:   nuclear_MEx.png
	modified:   paper.tex
	modified:   produce_maps.py
	modified:   refs.bib

@@
 
-\usepackage[flushleft, referable]{threeparttablex} % Adding notes under tables
-\usepackage{mhchem} 	% typeset chemistry symbols
+% \usepackage[flushleft, referable]{threeparttablex} % Adding notes under tables
+\usepackage[version=4]{mhchem} 	% typeset chemistry symbols
 \usepackage{array} % For wrapping text in cell in tables with multicolumntype
+% \usepackage{pdflscape} % for landscape pages
+
+% *****************************************************************
+% THis is my setting to avoid a particular LaTeX error due to links running
+% onto new pages.
+\hypersetup{draft}
+% *****************************************************************
 
@@
 
-In this paper, we present a complete sample of 11 nearby low-powered radio galaxies, observed with a suite of instruments.
-This paper focuses on the spatially-resolved stellar kinematics, stellar populations, and ionized gas distribution, kinematics and ionization derived from optical IFS observations, while other observation such as \ce{^{12}CO(2-1)} from Atacama Large Millimeter/sub-millimeter Array (ALMA) and radio continuum from the Very Large Array (VLA) will be presented in future papers, but are overlaid on our maps (cyan and red contours respectively, in Figs \ref{fig:eso443}-\ref{fig:pks718}).
+We present a complete sample of 11 nearby low-powered radio galaxies, observed with a suite of instruments.
+This paper focuses on the spatially-resolved stellar kinematics, stellar populations, and ionized gas distribution, kinematics and ionization derived from optical IFS observations%, while other observation such as \ce{^{12}CO(2-1)} from Atacama Large Millimetre/sub-millimetre Array (ALMA) and radio continuum from the Very Large Array (VLA) will be presented in future papers
+.
 We compare the characteristics and properties of our sample to those of ordinary (i.e.\ optically-selected) ETGs using the Atlas$^\text{3D}$ and MASSIVE IFS surveys.
@@
 	\label{sec:intro}
-	It is becoming increasingly clear that two different types of active galactic nuclei (AGN) exist, radiative and jet mode AGN \citep[e.g.][]{Antonucci2012, Heckman2014}, raising speculation about differing mechanisms and possibly fuel sources for each.
+	It is becoming increasingly clear that active galactic nuclei (AGN) can be separated into two different types, radiative and jet mode AGN \citep[e.g.][]{Antonucci2012, Heckman2014}, raising speculation about differing mechanisms and possibly fuel sources for each.
 The former is thought to be the powerful engine that initially and rapidly shuts off star formation in massive early-type galaxies (ETGs; e.g.
@@
 			\hline 
-			ESO 443-G024 & 1258-321 	& 0.01703	& $1387 \pm 45$		& 8.51 & no dust\tnote{a}	\\ 
-			IC 1459 	& 2254-367 		& 0.00565 	& $1280 \pm 45$		& 6.81 & dust lane\tnote{b}	\\
+			ESO 443-G024 & 1258-321 	& 0.01703	& $1387 \pm 45$		& 8.51 & no dust$^{a}$	\\ 
+			IC 1459 	& 2254-367 		& 0.00565 	& $1280 \pm 45$		& 6.81 & dust lane$^{b}$	\\
 			IC 1531 	& 0007-325 		& 0.02553 	& \leavevmode\phantom{0}$388 \pm 12$		& 9.55 & --					\\
-			IC 4296		& 1333-\leavevmode\phantom{0}33 		& 0.01248 	& $1342 \pm 41$		& 7.50 & edge-on disc\tnote{b} \\
-			NGC 612 	& 0131-\leavevmode\phantom{0}36 		& 0.02954 	& \leavevmode\phantom{0}$585 \pm 18$		& 9.58 & dust lane\tnote{c}	\\
-			NGC 1316 	& 0320-\leavevmode\phantom{0}37 & 0.00591 	& \leavevmode\phantom{0}$255 \pm 10$		& 5.59 & dust patches\tnote{b} \\
-			NGC 1399 	& 0336-\leavevmode\phantom{0}35 & 0.00472 	& \leavevmode\phantom{0}$209 \pm \leavevmode\phantom{0}7$	& 6.31 & no dust\tnote{b}	\\
-			NGC 3100 	& 0958-314 		& 0.00879 	& \leavevmode\phantom{0}$530 \pm 16$		& 8.08 & dust lane\tnote{d}	\\
-			NGC 3557 	& 1107-372 		& 0.01016 	& \leavevmode\phantom{0}$484 \pm 16$		& 7.20 & face-on disc\tnote{b}\\
+			IC 4296		& 1333-\leavevmode\phantom{0}33 		& 0.01248 	& $1342 \pm 41$		& 7.50 & edge-on disc$^{b}$ \\
+			NGC 612 	& 0131-\leavevmode\phantom{0}36 		& 0.02954 	& \leavevmode\phantom{0}$585 \pm 18$		& 9.58 & dust lane$^{c}$	\\
+			NGC 1316 	& 0320-\leavevmode\phantom{0}37 & 0.00591 	& \leavevmode\phantom{0}$255 \pm 10$		& 5.59 & dust patches$^{b}$ \\
+			NGC 1399 	& 0336-\leavevmode\phantom{0}35 & 0.00472 	& \leavevmode\phantom{0}$209 \pm \leavevmode\phantom{0}7$	& 6.31 & no dust$^{b}$	\\
+			NGC 3100 	& 0958-314 		& 0.00879 	& \leavevmode\phantom{0}$530 \pm 16$		& 8.08 & dust lane$^{d}$	\\
+			NGC 3557 	& 1107-372 		& 0.01016 	& \leavevmode\phantom{0}$484 \pm 16$		& 7.20 & face-on disc$^{b}$\\
 			NGC 7075 	& 2128-388 		& 0.01819 	& \leavevmode\phantom{0}$837 \pm 28$		& 9.56 & --					\\
-			--			& 0718-\leavevmode\phantom{0}34 		& 0.02897 	& $1119 \pm 41$		& 9.97 & dust patches\tnote{e} \\
+			--			& 0718-\leavevmode\phantom{0}34 		& 0.02897 	& $1119 \pm 41$		& 9.97 & dust patches$^{e}$ \\
 			\hline
@@
 	\label{sec:obs}
-	The sample was observed with VIMOS, mounted on the VLT in Paranal \citep{LeFevre2003}.
+	The sample has been observed with a suit of instruments spanning the radio to optical wavelengths (archival images from the \textit{Chandra space telescope} are also available for some of the sample).
+This paper focuses on the optical IFS observations made with VIMOS, mounted on the VLT in Paranal \citep{LeFevre2003}.
 All observations were taken with a spatial sampling of $0\farcs67$, using the high-resolution blue grism yielding a wavelength range of 3700-5520\,\AA\ with a spectral resolution of 1440 and sampling of 0.71\,\AA\,$\mathrm{pix^{-1}}$.
@@
 	\label{sec:analysis}
-	Both VIMOS and MUSE datasets are spatially binned using Voronoi binning\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/} \citep{Cappellari2003} and from this point on are treated almost identically, the only difference (other than the different spectral ranges and resolutions) being that the MUSE datacubes are spatially binned to a higher signal-to-noise ratio (S/N).
+	Both VIMOS and MUSE datasets are spatially binned using Voronoi binning\footnote{http://www-astro.physics.ox.ac.uk/~mxc/software/} \citep{Cappellari2003} and from this point on are treated almost identically, the only difference (other than the different spectral ranges and resolutions) being that the MUSE datacubes are spatially binned to a higher signal-to-noise ratio (S/N).
 For our purposes, we define the `signal' and `noise' of each spaxel as the median value of its spectrum and noise spectrum, respectively.
@@
 summed across both spatial dimensions of the datacube) spectrum.
-We use the penalized-fitting (\textsc{pPXF}) routine\footnotemark[1] of \citet{Cappellari2004} and \citet{Cappellari2016a} with the Medium-resolution Issac Newton Telescope (INT) Library of Empirical Spectra (MILES) library \citep{Sanchez-Blazquez2006, Falcon-Barroso2011a} to find the best-fitting line-of-sight velocity distribution (LOSVD; as parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion).
+We use the penalized-fitting (\textsc{pPXF}) routine\footnotemark[1] of \citet{Cappellari2004} and \citet{Cappellari2016a} with the Medium-resolution Isaac Newton Telescope (INT) Library of Empirical Spectra (MILES) library \citep{Sanchez-Blazquez2006, Falcon-Barroso2011a} to find the best-fitting line-of-sight stellar velocity distribution (LOSVD; as parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion).
 The final mean velocity of a given galaxy, is used as its precise spectroscopic redshift and is given in Table \ref{tab:sample}.
 Beyond this point, each bin is analysed independently.
+
+	It was noted that for the MUSE observations of NGC 1316, the NaD absorption feature (which as generally attributed to absorption from the ISM and is thus affected by the kinematics of the ISM) was significantly effecting the quality of the stellar best-fitting spectrum.
+For this reason, the wavelength range of NGC 1316 spectra was limited to $<5800 \, \AA$ whilst fitting for the stellar spectra only.
 
@@
 For the fit, regions around potential emission lines (listed in Section \ref{subsec:EmissionLines}) are masked, and a fourth order polynomial additive continuum correction is used.
-A Monte--Carlo (MC) estimate of the uncertainties is used.
+The residuals between the best-fitting spectrum and the input spectrum are smoothed in wavelength using a weighted, moving average.
+This is then summed in quadrature with the noise spectrum (as propagated through the data reduction pipeline) to produce a combined `residual noise' spectrum.
+A Monte--Carlo (MC) method is used to propagate this residual noise to give to give the quoted uncertainties.
 
@@
 		\label{subsec:EmissionLines}
-		In this analysis we consider the following emission lines and doublets: [\ion{O}{ii}]$\lambda\lambda$3726,3729, H$\delta$, H$\gamma$, H$\beta$, [\ion{O}{iii}]$\lambda\lambda$4969,5007, [\ion{N}{I}]$\lambda\lambda$5199,5202, [\ion{O}{i}]$\lambda\lambda$6300,6363, [\ion{N}{ii}]$\lambda\lambda$6548,6583, H$\alpha$ and [\ion{S}{ii}]$\lambda\lambda$6716,6731.
+		In this analysis we consider the following emission lines and doublets: H$\gamma$, H$\beta$, [\ion{O}{iii}]$\lambda\lambda$4969,5007, [\ion{N}{I}]$\lambda\lambda$5199,5202, [\ion{O}{i}]$\lambda\lambda$6300,6363, [\ion{N}{ii}]$\lambda\lambda$6548,6583, H$\alpha$ and [\ion{S}{ii}]$\lambda\lambda$6716,6731.
 We fit the fluxes and kinematics for the emission lines using Gaussian templates, independently fitting the emission lines of the ISM, with a single LOSVDs (again parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion), from the stellar kinematics.
@@
 The two components of the [\ion{O}{ii}] and [\ion{S}{ii}] doublets are fit independently.
-To minimize template mismatch, whereby emission lines are erroneously fitted to the edges of badly modeled and thus subtracted absorption features, we follow the method set out in \citet{Sarzi2005}.
+To minimize template mismatch, whereby emission lines are erroneously fitted to the edges of badly modelled and thus subtracted absorption features, we follow the method set out in \citet{Sarzi2005}.
 In this method the stellar component is first fitted as above with masked potential emission line regions, followed by the unmasking and fitting of the [\ion{O}{iii}] doublet which sets the kinematics for all the emission lines and finally the amplitude of the remaining emission lines is fitted.
@@
 			\label{subsubsec:EmissionFit}
-			We correct for the effect of the different velocity dispersions of the stars which varyingly spread absorption features such that differing fractions of the absorption is outside of the central bandpasses.
+			We correct for the effect of the different velocity dispersions of the stars which varyingly spread absorption features such that differing fractions of the absorption are outside of the central bandpasses.
 To do this, we create a stellar best-fitting spectrum which is \textit{not} convolved with the best-fitting LOSVD.
+Note that for NGC 1316, indices at wavelengths longer than 5800 \AA\ are calculated using the extrapolated best-fitting \textit{pPXF} fit.
 A given index, $I$, is then measured for both this `unconvolved' spectrum ($I^\text{unc}$) and the convolved best-fitting spectrum ($I^\text{conv}$), and the ratio of these two indices is used as a multiplicative correction factor for the index measured ($I^\text{obs}$), such that the corrected index ($I^\text{corr}$) is given by
@@
 		\label{subsubsec:stellarPop}
-		In each bin, using the measured absorption line strengths, we identify the best-fitting single stellar population (SSP) model from the models of \citeauthor{Thomas2010} (\citeyear{Thomas2010}; hereafter \citetalias{Thomas2010}) using \textsc{emcee}, a \textsc{python}, affine-invariant Markov chain Monte--Carlo (MCMC) fitting package \citep{Foreman-Mackey2013}.
+		In each bin, using the measured absorption line strengths, we identify the best-fitting single stellar population (SSP) model from an interpolated grid of models using \textsc{emcee}, a \textsc{python}, affine-invariant Markov chain Monte--Carlo (MCMC) fitting package \citep{Foreman-Mackey2013}.
+This grid is created by linearly interpolating between the models of \citeauthor{Thomas2010} (\citeyear{Thomas2010}; hereafter \citetalias{Thomas2010}).
 The \citetalias{Thomas2010} models are chosen because they are based on high-resolution, flux-calibrated spectra and therefore not requiring absorption line strength measurement to be in the Lick/IDS system.
@@
 Where this is the case, we follow the method by \citet{Emsellem2007}, where $R_\text{m}$ is redefined as $R_\text{m} \equiv \sqrt{A_\text{s}/\pi}$, where $A_\text{s}$ is the area of the ellipse contained within the field of view.
-For a given galaxy, we fit ellipses as described above, up to $R_\text{m} = R_\text{max}$, where $A_\text{s}$ reaches a maximum difference if 15\% to the area of the fitted ellipse, $A_\text{ellipse}$.
+For a given galaxy, we fit ellipses as described above, up to $R_\text{m} = R_\text{max}$, where $A_\text{s}$ reaches a maximum difference of 15\% to the area of the fitted ellipse, $A_\text{ellipse}$.
 The value $\epsilon_\text{e}$, the ellipticity at 1 $R_\text{e}$ or $R_\text{max}$, whichever is smallest, is given in Col.\,3 of Table \ref{tab:classify}.
@@
 	\label{sec:StarKine}
-	Using the methods above, we produce stellar kinematic maps for all datacubes (shown in Section \ref{sec:Maps}).
+	Using the methods above, we produce stellar kinematic maps for all datacubes (shown in Section \ref{sec:maps}).
 Here, we use these maps to classify each galaxy according to the Atlas$^\text{3D}$ regular/non-regular rotator and fast/slow rotator classification schemes of \citet{Krajnovic2006} and \citet{Cappellari2016}, respectively, as well as the qualitative kinematic classes of \citet{Krajnovic2011}.
@@
 			NGC 7075 	& 0.068 & 0.04 & \leavevmode\phantom{$-$}$36\pm50$ & SR & NRR & -- & b \\
-			PKS 718-34  & 0.159 & 0.17 & \leavevmode\phantom{$-$}$15\pm25$ & FR & NRR & KDC\tnote{a} & b\\
+			PKS 718-34  & 0.159 & 0.17 & \leavevmode\phantom{$-$}$15\pm25$ & FR & NRR & KDC$^{a}$ & b\\
 			\hline
@@
 This compares to 82\% of the Atlas$^\text{3D}$ sample being classified as regular rotators \citep{Krajnovic2011}.
-However the likely-hood of a given galaxy being a regular rotator is highly mass dependent with the likely-hood decreasing with increasing mass.
+However the likelihood of a given galaxy being a regular rotator is highly mass dependent with the likelihood decreasing with increasing mass.
 Thus since our Southern sample are all extremely massive galaxies, we expect to find a higher fraction of non-regular rotators than the Atlas$^\text{3D}$ survey.
@@
 		\begin{equation}
-			f' = \sum_{i=0}^N N^\text{SS}_i f^\text{AM}_i \, , 
+			f' = \frac{\sum_{i=0}^N N^\mathrm{SS}_i f^\mathrm{AM}_i}{\sum_{i=0}^N N^\mathrm{SS}} \, , 
 		\end{equation}
@@
 	\label{sec:absorption}
-	Using the methods described in Section \ref{subsec:absorption} we produce maps of the absorption line strength indices for each galaxy (shown in Appendix \ref{sec:Maps}).
+	Using the methods described in Section \ref{subsec:absorption} we produce maps of the absorption line strength indices for each galaxy (shown in Appendix \ref{sec:maps}).
 Here we measure the Mg\,--\,velocity dispersion relation and compare our absorption line strength measurements to the literature.
@@
 		Using an aperture with a radius of 2\arcsec\ on each datacube, we measure $\sigma_0$ and Mg\,b at a spectral resolution of 8.4\,\AA\ full-width half-maximum (FWHM), chosen such that the transformation functions of \citet{Vazdekis2010} can be used to change the literature measurements from the Lick/IDS system to the LIS.
-The results are shown in Fig.\,\ref{fig:globalMg} with the best-fitting linear relationship (found using \textsc{lts\_linefit}\footnotemark[\ref{Cappellari}] by \citealt{Cappellari2013}) shown by the solid black line.
-This has a gradient of $2.3 \pm 0.5 \,\mathrm{\text{\AA}\,dex^{-1}}$) and intrinsic scatter of $0.13 \pm 0.10 \,$\AA.
-%Individual measurements for each galaxy are given in table \ref{tab:globalMg}.
-		This is in very good agreement with the gradient found by \citet{Ziegler1997} for a sample of elliptical galaxies within Virgo and Coma using data from \citet{Dressler1987} of $2.5\,\mathrm{\text{\AA}\,dex^{-1}}$ (blue dotted line in Fig.\,\ref{fig:globalMg}), with an intrinsic scatter of 0.16\,\AA\ for galaxies with $\log \sigma_0 \geqslant 2.3$\,dex.
+The results are shown in Fig.\,\ref{fig:globalMg} with the best-fitting linear relationship (found using \textsc{lts\_linefit} %\footnotemark[\ref{Cappellari}]
+		by \citealt{Cappellari2013}) shown by the solid black line.
+This has a gradient of $3.3 \pm 1.0 \,\mathrm{\text{\AA}\,dex^{-1}}$.
+It was noticed that NGC 1316 is a possible outlier.
+Removing NGC 1316 from the fit gives a gradient of $2.5 \pm 0.7 \,\mathrm{\AA\,dex^{-1}}$ (green dashed line in Fig.\,\ref{fig:globalMg}).
+Both fits are in very good agreement with the gradient found by \citet{Ziegler1997} for a sample of elliptical galaxies within Virgo and Coma using data from \citet{Dressler1987} of $2.5\,\mathrm{\text{\AA}\,dex^{-1}}$ (blue dotted line in Fig.\,\ref{fig:globalMg}), with an intrinsic scatter of 0.16\,\AA\ for galaxies with $\log \sigma_0 \geqslant 2.3$\,dex.
 
@@
 			\includegraphics[width=\columnwidth]{Mg_sigma.png}
-			\caption[Global Mg\,b\,--\,$\sigma$]{The Mg\,b\,--\,velocity dispersion relation using a 2\arcsec\ aperture.
-We find a similar gradient to our best-fitting (solid) as that found by \citet[; dotted line]{Ziegler1997}.}
+			\caption[Global Mg\,b\,--\,$\sigma$]{The Mg\,b\,--\,velocity dispersion relation using a 2\arcsec aperture.
+We find a similar gradient to our best-fitting (solid black) line as that found by \citet[; blue dotted line]{Ziegler1997}, while removing NGC 1316 from the fit (green dashed) results in an extremely good agreement with \citet{Ziegler1997}.}
 			\label{fig:globalMg}
@@
 			\caption{Comparisons of measured absorption line indices to the literature.
-Comparisons to \citet{Rampazzo2005} are sampled at 7 radial apertures for each galaxy: 1.5, 2.5 and 10.0 arcsec and R$_e$/10, R$_e$/8, R$_e$/4 and R$_e$/2.
+Comparisons to \citet{Rampazzo2005} are sampled at 7 radial apertures for each galaxy: 1.5, 2.5 and 10.0\arcsec\ and R$_e$/10, R$_e$/8, R$_e$/4 and R$_e$/2.
 Col.\,1: Index.
@@
 		We also observe that the offset in the Fe5015 index is also quite large in comparisons with \citet{Rampazzo2005} and \citet{Vazdekis2010}.
-In the case of the comparison with \citet{Rampazzo2005} we suggest that the difference is due to differences in method for accounting for the [\ion{O}{iii}] emission lines, however the origin of the offset is less clear in case of the comparison with \citet{Vazdekis2010}.
+In the case of the comparison with \citet{Rampazzo2005} we suggest that the difference is due to differences in method for accounting for the [\ion{O}{iii}] emission doublet, however the origin of the offset is less clear in case of the comparison with \citet{Vazdekis2010}.
 
@@
 	We have assumed that a given spectrum from our Southern sample can be well approximated by a SSP.
-We use the method described in Section \ref{subsubsec:stellarPop} to produce maps of the most-likely SSP characteristics: age ($t$), metallicity ($Z/H$) and alpha-element enhancement ($\alpha$/Fe) from the absorption line strength maps (see Appendix \ref{sec:Maps}).
+We use the method described in Section \ref{subsubsec:stellarPop} to produce maps of the most-likely SSP characteristics: age ($t$), metallicity ($Z/H$) and alpha-element enhancement ($\alpha$/Fe) from the absorption line strength maps (see Appendix \ref{sec:maps}).
 
 	In general, our sample galaxies show old, metal rich and alpha enhanced SSPs; qualities which ETGs are well known for.
-The exceptions are NGC 612 and NGC 1316.
+The exception is NGC 612 and NGC 1316.
 NGC 1316 shows a very young stellar population (our fit of $t \approx 2$\,Gyr agrees with that of \citealt{Kuntschner2000}, but is conflicting with the older and less metal rich stellar population of \citealt{Koleva2011} who found $t=4.5 \pm 0.3 \,\mathrm{Gyr}$ and $\mathrm{[Fe/H]}=0.12 \pm 0.01 \,\mathrm{dex}$ for an aperture covering the central 0.1 kpc).
 We also find NGC 612 to have a young stellar population of $t\approx 4\,\mathrm{Gyr}$.
-NGC 3557 is notable for containing a significantly younger ($t\approx 4$\,Gyr) core of about 10\arcsec\ diameter and NGC 3100 has a branch of young stars ($\approx 4$\,Gyr) along the southeast branch of the molecular gas (cyan contours in Fig \ref{fig:ngc3100}).
+NGC 3557 is notable for containing a significantly younger ($t\approx 4$\,Gyr) core of about 10\arcsec\ diameter and NGC 3100 has a branch of young stars ($\approx 4$\,Gyr) along the south-east branch of the molecular gas (white contours in Fig \ref{fig:ngc3100}).
 
@@
 They assume a linear relationship between $\log t$ or [Fe/H] and $\log (R/\mathrm{R_e})$.
-We repeat this fit with our Southern Sample with the results shown in Table \ref{tab:popGrad}.
-
-		\begin{table}
-			\centering
-			\caption{The radial gradients of the most-likely SSP models. Both gradients are dimensionless.}
-			\label{tab:popGrad}
-			\begin{tabular}{l c c}
-				\hline
-				\hline 
-				Galaxy 	& $\Delta_\text{log age}$ & $\Delta_\text{[Fe/H]}$ \\ 
-					% & dex\,arcsec$^{-1}$ & dex\,arcsec$^{-1}$ \\
-				\hline
-				ESO 443-G024 & $0.019 \pm 0.013$ & $-0.01 \pm 0.02$ \\
-				IC 1459 	& $0.003 \pm 0.002$ & $0.00 \pm 0.06$ \\
-				IC 1531 	& $0.012 \pm 0.015$ & $0.01 \pm 0.02$ \\
-				IC 4296		& $0.000 \pm 0.002$ & $0.04 \pm 0.08$ \\
-				NGC 612 	& $0.068 \pm 0.060$ & $-0.11 \pm 0.02$ \\
-				NGC 1316 	& $0.001 \pm 0.002$ & $0.05 \pm 0.03$ \\
-				NGC 1399 	& $0.001 \pm 0.002$ & $0.10 \pm 0.09$ \\
-				NGC 3100 	& $0.000 \pm 0.010$ & $-0.06 \pm 0.01$ \\
-				NGC 3557 	& $0.048 \pm 0.039$ & $-0.05 \pm 0.05$ \\
-				NGC 7075 	& $0.007 \pm 0.011$ & $-0.07 \pm 0.02$ \\
-				PKS 718-34  & $0.002 \pm 0.009$ & $-0.17 \pm 0.03$ \\
-				\hline
-				\hline
+We repeat this fit with our Southern Sample with the results shown in Table \ref{tab:derivedProp}.
+
+		\begin{table*}
+			\centering
+			\caption{Derived properties of the Southern Sample.
+Col.\,1: Galaxy.
+Col.\,2--3: Radial gradient of the age of most-likely SSP model.
+Col.\,4--5: Radial gradient of the metallicity of most-likely SSP model.
+Col.\,6--7: \ion{H}{ii} mass derived from the H$\beta$ (assuming a Balmer decrement of 2.85) or H$\alpha$ line in the VIMOS or MUSE data, respectively.
+Col.\,8: Balmer decrement measured from the MUSE data.
+Col.\,9: Main source of ionizing radiation (see Section \ref{subsec:Diagnostics} for a description of the different classes).
+-- indicates no data.}
+			\label{tab:derivedProp}
+			\begin{tabular}{l c c c c c c c c}
+				\hline
+				\hline 
+				Galaxy 	& \multicolumn{2}{c}{$\Delta_\text{log t}$} & \multicolumn{2}{c}{$\Delta_\text{[Fe/H]}$} & \multicolumn{2}{c}{\ion{H}{ii} Mass} & Balmer & LINER/ \\
+						& VIMOS & MUSE & VIMOS & MUSE & VIMOS$^{a}$ & MUSE & Decrement & Seyfert \\
+						& & & & & ($\log\mathrm{M_\odot}$) & ($\log\mathrm{M_\odot}$) & \\
+					\hline
+					ESO 443-G024 & $0.019 \pm 0.013$ & -- & $-0.01 \pm 0.02$ & -- & $5.02 \pm 0.01$ & -- & -- & LINER \\
+					IC 1459 	& $0.005 \pm 0.015$ & $0.003 \pm 0.002$ & $-0.02 \pm 0.02$ & $0.00 \pm 0.06$ & $5.21 \pm 0.01$ & $5.50 \pm 0.01$ & $4.54 \pm 0.12$ & LINER-AGN \\
+					IC 1531 	& $0.012 \pm 0.015$ & -- & $0.01 \pm 0.02$ & -- & $5.09 \pm 0.01$ & -- & -- & Seyfert 2\\
+					IC 4296		& $0.012 \pm 0.010$ & $0.000 \pm 0.002$ & $-0.03 \pm 0.01$ & $0.04 \pm 0.08$ & $5.43 \pm 0.01$	& $< 4.48$ 	& $^{b}$ & LINER-AGN \\
+					NGC 612 	& $0.068 \pm 0.060$ & -- & $-0.11 \pm 0.02$ & -- & $6.00 \pm 0.01$ 	& -- 		& -- & LINER-AGN \\
+					NGC 1316 	& -- & $0.001 \pm 0.002$ & -- &$0.05 \pm 0.03$ & -- 				& $ 5.29 \pm 0.01$ & $3.52 \pm 0.11$ & LINER-AGN \\
+					NGC 1399 	& $0.019 \pm 0.005$ & $0.001 \pm 0.002$ & $-0.02 \pm 0.03$ & $0.10 \pm 0.09$ & $< 3.86$ 			& $ 4.54 \pm 0.01$ & $< 21.4$ $^{c}$ & LINER \\
+					NGC 3100 	& $0.000 \pm 0.010$ & -- & $-0.06 \pm 0.01$ & -- & $5.26 \pm 0.01$	& -- 		& -- & LINER-AGN \\
+					NGC 3557 	& $0.048 \pm 0.039$ & -- & $-0.05 \pm 0.05$ & -- & $4.61 \pm 0.02$ 	& -- 		& -- & LINER \\
+					NGC 7075 	& $0.007 \pm 0.011$ & -- & $-0.07 \pm 0.02$ & -- & $4.68 \pm 0.01$	& -- 		& -- & LINER \\
+					PKS 718-34  & $0.002 \pm 0.009$ & -- & $-0.17 \pm 0.03$ & -- & $< 5.08$	 		& -- 		& -- & Passive \\
+				\hline
+				\hline
+				\multicolumn{9}{L{.95\linewidth}}{$^{a}$The VIMOS flux calibration and thus the derived gas masses are only approximate (see Section \ref{sec:obs} for more detail on the flux calibration).} \\
+				\multicolumn{9}{L{.95\linewidth}}{$^{b}$Both H$\alpha$ and H$\beta$ are not detected with A/N $>2.5$, so no information can be gained.} \\
+				\multicolumn{9}{L{.95\linewidth}}{$^{c}$H$\beta$ is not detected with A/N $> 2.5$, so the fit is unreliable. Instead the limits for a 2.5 A/N detection are shown.}
 			\end{tabular}
-		\end{table}
-
-		We find average gradients of $\Delta_\text{log age} = 0.014\pm0.007$ and $\Delta_\text{[Fe/H]} = -0.03\pm0.01$.
+		\end{table*}
+
+		We find average gradients of $\Delta_\text{log t} = 0.014\pm0.007$ and $\Delta_\text{[Fe/H]} = -0.03\pm0.01$.
 This is consistent with \citet{Koleva2011} who, for elliptical galaxies found average gradients of $0.06\pm0.09$ and $-0.26\pm0.08$ for the age and metallicity gradients, respectively.
-For lenticular galaxies (S0s) they find flatter corresponding gradients of $0.01\pm0.11$ and $-0.12\pm0.13$.
+For S0s they find flatter corresponding gradients of $0.01\pm0.11$ and $-0.12\pm0.13$.
 
@@
 		\label{subsec:popKDC}
-		\citet{Kuntschner2010} found that KDCs exist in two classes: they are either small with various stellar ages or typically larger but containing an old stellar population.
+		\citet{Kuntschner2010} found that KDCs can be separated two classes: they are either small with various stellar ages or typically larger but containing an old stellar population.
 The size of the KDC is defined as the radius of the region surrounding the KDC where the superposition of the two components (the KDC and the host galaxy) results in a local minimum in the mean velocity.
@@
 			\caption[KDC dichotomy]{The KDC size\,--\,age relation.
-KDCs exist in two classes: old and embedded in a slow rotator or small and embedded in a fast rotator.
-Observations with VIMOS are in red, MUSE in blue and SAURON from \citet{Kuntschner2010} in black and gray for fast and slow rotators respectively.}
+KDCs can be separated two classes: old and embedded in a slow rotator or small and embedded in a fast rotator.VIMOS observations are are in red, MUSE in blue and SAURON from \citet{Kuntschner2010} in black and grey for fast and slow rotators respectively.}
 			\label{fig:KDC}
@@
 	Using the methods described in Section \ref{subsubsec:EmissionFit}, we find the best-fitting line-of-sight velocity distribution (LOSVD; assumed to be Gaussian and parametrised by the mean velocity and velocity dispersion only) of the emission lines in each bin.
-Images of the Southern Sample galaxies in the [\ion{O}{iii}]$\lambda\lambda$4957,5007 doublet are shown in Appendix \ref{sec:Maps} (we choose to show [\ion{O}{iii}] as detections of all emission lines require a detection of [\ion{O}{iii}] first, see Section \ref{subsubsec:EmissionFit}).
+Images of the Southern Sample galaxies in the [\ion{O}{iii}]$\lambda\lambda$4957,5007 doublet are shown in Appendix \ref{sec:maps} (we choose to show [\ion{O}{iii}] as detections of all emission lines require a detection of [\ion{O}{iii}] first, see Section \ref{subsubsec:EmissionFit}).
 
 	Only 4 galaxies of the Southern Sample have emission lines detected outside of their central region (IC 1459, NGC 612, NGC 1316 and NGC 3100).
-Of the remaining 7 galaxies, NGC 1399 and PKS 718-34 have no detection of H$\beta$ in their spatially-resolved map (although we do detect H$\beta$ in the spatially-integrated spectrum of NGC 1399; see Table \ref{tab:gasMass}), while the other 5 galaxies are only detected in their centre.
+Of the remaining 7 galaxies, NGC 1399 and PKS 718-34 have no detection of H$\beta$ in their spatially-resolved map (although we do detect H$\beta$ in the spatially-integrated spectrum of NGC 1399; see Table \ref{tab:derivedProp}), while the other 5 galaxies are only detected in their centre.
 All other emission lines have similar distributions, but with different fluxes.
 
-	As can be seen from the maps in Appendix \ref{sec:Maps}, both NGC 612 and NGC 3100 have significant off-centre clouds of ionized gas.
-The latter is spatial coincident with both the radio jet and the gap in the CO ring, while former seems to no link with either the radio jet (a massive scale jet extending several $\sim 200$\,kpc to the east and west of the galaxy centre) or the CO.
-
-	\begin{table*}
-		\centering
-	% \begin{threeparttable}
-		\caption{Gas masses of the Southern Sample galaxies.
-Col.\,1: Galaxy.
-Col.\,2: \ion{H}{ii} mass derived from the H$\beta$ line in the VIMOS data, assuming a Balmer decrement of 2.85.
-Col.\,3: \ion{H}{ii} mass derived from the H$\alpha$ line in the MUSE data.
-Col.\,4: Balmer decrement measured from the MUSE data.
-Col.\,5: Main source of ionizing radiation (see Section \ref{subsec:Diagnostics} for a description of the different classes).
--- means we have no data.}
-		\label{tab:gasMass}
-		% \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l r r r l}
-		\begin{tabular}{l c c c c}
-			\hline
-			\hline
-			Galaxy & \multicolumn{2}{c}{\ion{H}{ii} Mass} & Balmer & LINER/ \\
-			& VIMOS\tnote{a} & MUSE & Decrement & Seyfert \\
-			& ($\log\mathrm{M_\odot}$) & ($\log\mathrm{M_\odot}$) & \\
-			\hline
-			ESO 443-G024 & $5.02 \pm 0.01$ 	& --  		& -- & LINER \\
-			IC 1459 	& $5.21 \pm 0.01$	& $5.50 \pm 0.01$ & $4.54 \pm 0.12$ & LINER-AGN\\
-			IC 1531 	& $5.09 \pm 0.01$	& -- 		& -- & Seyfert 2\\
-			IC 4296		& $5.43 \pm 0.01$	& $< 4.48$ 	& \tnote{b} & LINER-AGN \\
-			NGC 612 	& $6.00 \pm 0.01$ 	& -- 		& -- & LINER-AGN \\
-			NGC 1316 	& -- 				& $ 5.29 \pm 0.01$ & $3.52 \pm 0.11$ & LINER-AGN \\
-			NGC 1399 	& $< 3.86$ 			& $ 4.54 \pm 0.01$ & $< 21.4$\tnote{c} & LINER \\
-			NGC 3100 	& $5.26 \pm 0.01$	& -- 		& -- & LINER-AGN \\
-			NGC 3557 	& $4.61 \pm 0.02$ 	& -- 		& -- & LINER \\
-			NGC 7075 	& $4.68 \pm 0.01$	& -- 		& -- & LINER \\
-			PKS 718-34  & $< 5.08$	 		& -- 		& -- & Passive \\
-			\hline
-			\hline
-			\multicolumn{5}{L{.7\linewidth}}{$^{a}$The VIMOS flux calibration and thus the derived gas masses are only approximate (see Section \ref{sec:obs} for more detail on the flux calibration).} \\
-			\multicolumn{5}{L{.7\linewidth}}{$^{b}$Both H$\alpha$ and H$\beta$ are not detected with A/N $>2.5$, so no information can be gained.} \\
-			\multicolumn{5}{L{.7\linewidth}}{$^{c}$H$\beta$ is not detected with A/N $> 2.5$, so the fit is unreliable (hence an upper limit).}
-		\end{tabular}
-	% 	\begin{tablenotes}
-	% 	\footnotesize
-	% 	\note Col.\,1: Galaxy.
-Col.\,2: \ion{H}{ii} mass derived from the H$\beta$ line in the VIMOS data, assuming a Balmer decrement of 2.85.
-Col.\,3: \ion{H}{ii} mass derived from the H$\alpha$ line in the MUSE data.
-Col.\,4: Balmer decrement measured from the MUSE data.
-Col.\,5: Main source of ionizing radiation (see Section \ref{subsec:Diagnostics} for a description of the different classes).
--- means we have no data.
-	% 	\item [a] The VIMOS flux calibration and thus the derived gas masses are only approximate (see Section \ref{subsec:VIMOSreduction} for more detail on the flux calibration).
-	% 	\item [b] Both H$\alpha$ and H$\beta$ are not detected with A/N $>2.5$, so no information can be gained.
-	% 	\item [c] H$\beta$ is not detected with A/N $> 2.5$, so the fit is unreliable (hence an upper limit). 
-	% 	\end{tablenotes}
-	% \end{threeparttable}
-	\end{table*}
+	As can be seen from the maps in Appendix \ref{sec:maps}, both NGC 612 and NGC 3100 have significant off-centre clouds of ionized gas.
+The latter is spatial coincident with both the radio jet and the gap in the CO ring, while former seems to no link with either the radio jet (a massive jet extending $\sim 200$\,kpc to the east and west of the galaxy centre) or the CO.
 
@@
 	where $M_\text{\ion{H}{ii}}$ is the total mass of \ion{H}{ii} in the galaxy, $D$ is the galaxy distance, and $F(\mathrm{H\alpha})$ is the H$\alpha$ flux measured from the spectrum created by summing spatially all spaxels within an aperture of $\frac{R_\mathrm{e}}{2}$ (chosen to exclude noisy outer regions of the observations, but still includes the bulk of the gas in system with significant spatially-extended gas).
-This method assumes an electron density $n_\mathrm{e} = 100 \, \mathrm{cm^{-3}}$, a temperature of $10^4$ K and case-B recombination (electrons above 13.6\,eV are not reabsorbed; e.g.\ \citealt[p.\,74]{Osterbrock1974}).
-Like \citet{Sarzi2005}, we only claim a detection if the amplitude-to-noise ratio (A/N) is $>4$ for [\ion{O}{iii}] and $>2.5$ for H$\beta$ or H$\alpha$.
-When these conditions are not met, upper limits are calculated using the $1\sigma$ noise level (see Section \ref{subsubsec:EmissionFit}).
-
-	Our calculated gas masses are given Table \ref{tab:gasMass} and are at the upper limit of, and possibly exceed, the typical masses observed in ETGs.
+This method assumes an electron density $n_\mathrm{e} = 100 \, \mathrm{cm^{-3}}$, a temperature of $10^4$ K and case-B recombination.
+Like \citet{Sarzi2005}, we only claim a detection if the amplitude-to-noise ratio (A/N) is $>4$ for [\ion{O}{iii}] and $>2.5$ for H$\beta$ or H$\alpha$ lines for VIMOS and MUSE data, respectively.
+When these conditions are not met, upper limits are calculated using the using the 2.5 A/N level, assuming the gas has the same velocity dispersion as the stellar component.
+
+	Our calculated gas masses are given Table \ref{tab:derivedProp} and are at the upper limit of, and possibly exceed, the typical masses observed in ETGs.
 Given that our sample contains particularly massive galaxies, high ionized gas masses are not unexpected, however.
@@
 		\label{subsec:GasKin}
-		Map of the best-fitting kinematics (mean velocity and velocity dispersion), as found with the methods described in Section \ref{subsubsec:EmissionFit} for the 4 galaxies (IC 1459, NGC 612, NGC 1316 and NGC 3100) with detected spatially-extended emission lines are shown in Appendix \ref{sec:Maps}.
+		Map of the best-fitting kinematics (mean velocity and velocity dispersion), as found with the methods described in Section \ref{subsubsec:EmissionFit} for the 4 galaxies (IC 1459, NGC 612, NGC 1316 and NGC 3100) with detected spatially-extended emission lines are shown in Appendix \ref{sec:maps}.
 Due to that fact that, unlike stars, gas is dissipational, it is to be expected that given sufficient time, the ISM will always settle into a disc.
@@
 
-		It is immediately clear when comparing the stellar mean velocity maps to the ionized gas mean velocity maps that where gas is detected, its angular momentum is not often aligned with that of the stars.
+		It is immediately clear when comparing the stellar mean velocity maps to the ionized gas mean velocity maps that where gas is detected, its angular momentum is often not aligned with that of the stars.
 A misalignment between the kinematics of the stars and gas suggests an external origin for the gas (e.g.\ accretion or wet merger).
-However it should be noted that the converses is not necessarily true: aligned kinematics is consistent with an internal origin (e.g.\ stellar-mass loss), but it does \emph{not} require it \citep[e.g.][]{Davis2011a}.
+However it should be noted that the converse is not necessarily true: aligned kinematics is consistent with an internal origin (e.g.\ stellar-mass loss), but it does \emph{not} require it \citep[e.g.][]{Davis2011a}.
 
@@
 The misalignment between the position angle of the stellar and gas kinematics (using the method described in Section \ref{subsubsec:KinPA}) is just $1\fdg0\pm0\fdg7$, consistent with an internal origin for the gas.
-This adds to the evidence that NGC 612 has not undergone a major merger (major mergers exhaust galaxies of their gas and destroy a stellar disc) and suggests that, the fueling and powering of the radio jet must be a purely secular process.
+This adds to the evidence that NGC 612 has not undergone a recent major merger (major mergers exhaust galaxies of their gas and destroy a stellar disc) and suggests that, the fuelling and powering of the radio jet could be a purely secular process.
 
@@
 Since there are redshifted emission lines with respect to the rest frame of the galaxy on both sides of the galaxy, the gas is not in a settled disc and that there must be some inflow/outflows.
-		% We used a fitting routine based on the method of \citet{Swinbank2012}, \citet{Stott2016} and Tiley et.al.\ (in prep.) to fit an exponential disc (middle panel of Fig.\ \ref{fig:Inflow}) to the ionized gas mean velocity map (left panel), with the residuals shown in the right panel of Fig.\ \ref{fig:Inflow}.
-This shows a large residual on the southwest side of the galaxy, which we interpret as an inflow towards the nucleus, almost perpendicular to the radio jet.
-However, there are still significant residuals in other parts of the galaxy, suggesting that the model may not be a good representation of the reality of the galaxy, thus other interpretations are possible, and better quality data (longer exposure times) are required to add certainty to this interpretation.
+From visual inspection of the velocity field for the gas (Fig.\,\ref{fig:MUSE_Gaskine}) it is clear that a simple exponential disc model will not be well fitted to the data.
+We suggest that that the large velocity peak on the south-west side of the galaxy could be an inflow towards the nucleus, almost perpendicular to the radio jet, however we acknowledge that other interpretations are possible.
+Better quality data (longer exposure times) and more sophisticated models are required to add certainty to this interpretation.
 Nevertheless, it is clear that the gas in not in a settled disc.
-		Without filling in some of the regions were we do not detect emission lines through additional observations, it is impossible to judge the state or even existence of a disc.
-
-		% \begin{figure}
-		% 	\centering
-		% 	\includegraphics[width=\textwidth]{ngc1316_inflow.png}
-		% 	\caption[Inflows in NGC 1316]{Ionized gas inflows in NGC 1316.
-Left: [\ion{O}{iii}] mean velocity map.
-Middle: best-fitting model.
-Right: Residual map = mean velocity - model.
-A large region, redshifted with respect to the galaxy, can be seen in the southwest which we interpret as an inflow.
-Contours are as in Fig.\ \ref{fig:VIMOS_OIII}.}
-		% 	\label{fig:Inflow}
-		% \end{figure}
+
+		% Without filling in some of the regions were we do not detect emission lines through additional observations, it is impossible to judge the state or even existence of a disc.
 
 		\textbf{NGC 3100} has an interesting ISM morphology.
-The \ce{^{12}CO(2-1)} contours (shown in cyan in all maps) show a broken ring with the radio jet passing through the gaps in the ring (Ruffa et\,al., in prep.).
+The \ce{^{12}CO(2-1)} contours (shown in white in all maps) show a broken ring with the radio jet passing through the gaps in the ring (Ruffa et\,al., in prep.).
 We observe the ionized gas to be brightest in the gaps of this ring which we interpret as additional excitation of the gas due to shocks from the impact of the jet.
@@
 Secondly, in the absence of spatially-resolved spectra, low-ionization nuclear emission-line region (LINER) classifications have often been taken as a marker for jet-mode AGN.
-However, several recent surveys have shown that many of these may not be bona fide AGN \citep[e.g.][]{Sarzi2005, Sarzi2010, Singh2013, Belfiore2016a}.
+However, several recent surveys have shown that many of these may not be bona-fide AGN \citep[e.g.][]{Sarzi2005, Sarzi2010, Singh2013, Belfiore2016a}.
 In these cases, the emission may not even originate exclusively from the centres of the galaxies, the location of the putative AGN.
@@
 Finally we use the mass\,--\,excitation (MEx) plot of \cite{Nyland2016}, using parameters derived from the spatially-integrated spectra within an aperture of radius 3\arcsec\ thus only probing the central region of the galaxies (see Section \ref{subsubsec:MEx}).
-This allows us to classify the remaining galaxies into star-forming, Seyfert 2, LINER, transition or passive classes, and subdivide LINER galaxies into those whose LINER characteristics are attributable to a central AGN (labeled as LINER-AGN in Table \ref{tab:gasMass}) and those whose LINER characteristics are not.
+This allows us to classify the remaining galaxies into star-forming, Seyfert 2, LINER, transition or passive classes, and subdivide LINER galaxies into those whose LINER characteristics are attributable to a central AGN (labelled as LINER-AGN in Table \ref{tab:derivedProp}) and those whose LINER characteristics are not.
 We expand on the final two steps in the sections below.
@@
 		% 		\includegraphics[width=0.5\textwidth]{chapter5/vimos/ngc3100_NI_Hb.png}
-		% 		\caption[NGC 3100 \bracket{\ion{N}{i}}/H$\beta$ line ratio map]{The [\ion{N}{i}]/H$\beta$ line ratio map of NGC 3100, showing the hardest ionization field is in gap in the CO ring (cyan contours), spatially coincident with the radio jet (green contours).
+		% 		\caption[NGC 3100 \bracket{\ion{N}{i}}/H$\beta$ line ratio map]{The [\ion{N}{i}]/H$\beta$ line ratio map of NGC 3100, showing the hardest ionization field is in gap in the CO ring (white contours), spatially coincident with the radio jet (green contours).
 Surface brightness contours are in black.}
@@
 				\includegraphics[width=0.73\columnwidth]{Halpha_profile.png}
-				\caption{H$\alpha$ flux radial profiles derived from the MUSE datacubes. Solid red lines show $F(\mathrm{H\alpha}) \propto r^{-2}$.}
+				\caption{H$\alpha$ flux radial profiles derived from the MUSE datacubes.
+Solid red lines show $F(\mathrm{H\alpha}) \propto r^{-2}$ convolved with a Gaussian function of width equal to the mean seeing taken from the fits file headers.
+This accounts for the point-spread function (PSF) of the observations.\label{fig:Ha_profile_MUSE}}
 				\label{fig:Ha_profile_MUSE}
@@
 				\includegraphics[width=\columnwidth]{Hbeta_profile.png}
-				\caption{H$\beta$ flux radial profiles derived from the VIMOS datacubes. Solid red lines show $F(\mathrm{H\beta}) \propto r^{-2}$.}
-				\label{fig:Hb_profile_VIMOS}
+				\caption{H$\beta$ flux radial profiles derived from the VIMOS datacubes.
+Solid red lines show $F(\mathrm{H\beta}) \propto r^{-2}$ convolved with a Gaussian function of width equal to the mean seeing (see Table \ref{tab:observations}).
+This accounts for the PSF of the observations.
+\label{fig:Hb_profile_VIMOS}}
 			\end{figure}
@@
 A shallower profile points to a spatially-extended source, presumably non-circumnuclear stellar processes such as star formation or radiation from pAGB stars, as the dominant cause of the ionization in the outer parts of the galaxy (i.e.\ LIER rather than LINER).
-All the galaxies with spatially-extended Balmer emission in our Southern Sample revel a central point source as the dominant source of the ionizing photons.
+All the galaxies with spatially-extended Balmer emission in our Southern Sample reveal a central point source as the dominant source of the ionizing photons.
 The H$\beta$ profile of NGC 612 has a larger scatter suggesting that stellar processes also have some impact (likely radiation from pAGB stars, as these galaxies are ETGs and therefore likely have low star-formation rates).
@@
 	In Section \ref{sec:StarKine} we show that in terms of the stellar kinematic properties, our radio-selected Southern sample are no different to ordinary optically-selected ETGs.
-Our sample shows a mixture of of regularly- and non-regularly-rotating behaviours, with both classes showing evidence of consistency with observations of the intrinsic shapes of ordinary regular and non-regular rotators.
+Our sample shows a mixture of the regularly- and non-regularly-rotating behaviours, with both classes showing evidence of consistency with observations of the intrinsic shapes of ordinary regular and non-regular rotators.
 At this stage we observe that two (with a tentative third) galaxies host large KDCs.
@@
 	In terms of absorption line strengths and stellar populations (Sections \ref{sec:absorption} and \ref{sec:stellarPop}), we find a remarkably similar gradient to the central Mg\,b verse stellar velocity dispersion relation to that of \citet{Ziegler1997}.
-Most of the galaxies in our Southern sample show typical ETG behavior: old, metal-rich stellar populations, with a few exceptions: NGC 612 and NGC 1316 are both significantly younger than most ETGs and NGC 3557 has a young core.
+Most of the galaxies in our Southern sample show typical ETG behaviour: old, metal-rich stellar populations, with a few exceptions: NGC 612 and NGC 1316 are both significantly younger than most ETGs and NGC 3557 has a young core.
 We observe that all 3 KDCs contain old stellar populations and are consistent with being merger remnants.
@@
 
-	If molecular (cold) gas is the fuel source that is accreted on to the the central black holes of our Southern sample in order to power the radio jets, unless it is accreted in a highly turbulent fashion, it might be expected that some of that gas might form stars \citep[e.g.][]{Collin1999, Diamond-Stanic2012, LaMassa2013}.
-If this is the case then a young stellar population might be expected to dominate in the very central (1--2) spaxels.
-We our best-fitting age maps (bottom-left panel of Figs \ref{fig:eso443}-\ref{fig:pks718}) show no evidence of this.
+	If molecular (cold) gas is the fuel source that is accreted on to the central black holes of our Southern sample in order to power the radio jets, unless it is accreted in a highly turbulent fashion, it might be expected that some of that gas might form stars within the accretion disc \citep[e.g.][]{Collin1999, Diamond-Stanic2012, LaMassa2013}.
+If this were the case, and these young stellar populations are bright enough to dominate, they should stand out in the very central (1--2) spaxels.
+Having said that, detection of such a population may prove difficult due to masking by the AGN continuum, the presence of dust (see Table \ref{tab:sample} for a description of the dust morphologies of our sample) and the rapid rate a young stellar population fades.
+Indeed, our best-fitting age maps show no evidence of a young central stellar population.
+This is consistent with results by other authors such as \citet{GonzalezDelgado2004} and \citet{Sarzi2005b} with \textit{Hubble Space Telescope} (\textit{HST}) spectra and \citet{CidFernandes2004} with ground based spectra.
+Furthermore, in section \ref{subsec:Diagnostics}, we show that there is no evidence of an ionizing source with a potential which is consistent with ongoing star formation.
 
@@
 \appendix
-\section{Maps}
-	\label{sec:Maps}
-
-	Here, we present spatially-resolved maps of our Southern Sample of the parameters measured and fitted to the IFS datacubes using the methods described in Section \ref{sec:analysis}.
-We present each galaxy in turn.
-
-	\subsection{ESO\,443-G24}
-		\begin{figure*}
-			\centering
-			\includegraphics[width=\textwidth]{eso443-g024.png}
-			\caption{Spatially-resolved map of measurements derived from VIMOS observations for ESO\,433-G24.
-The measurement is given in the top-left of each panel and the colour-scale limits are given in the bottom-right.
-The surface brightness (isophotes) are shown as black contours in all maps, while the \ce{^{12}CO(2-1)} contours from ALMA are in cyan and radio continuum contours from the VLA are in green.
-The radio band displayed depends on the data available in the archive and which images had a similar resolution and scales.}
-			\label{fig:eso443}
-		\end{figure*}
-
-	\subsection{IC\,1459}
-		\begin{figure*}
-			\centering
-			\includegraphics[width=\textwidth]{ic1459.png}
-			\caption{As Fig.\,\ref{fig:eso443}, but for IC\,1459 and derived from MUSE observations.}
-			\label{fig:ic1459}
-		\end{figure*}
-
-	\subsection{IC\,1531}
-		\begin{figure*}
-			\centering
-			\includegraphics[width=\textwidth]{ic1531.png}
-			\caption{As Fig.\,\ref{fig:eso443}, but for IC\,1531.}
-			\label{fig:ic1531}
-		\end{figure*}
-
-	\subsection{IC\,4296}
-		\begin{figure*}
-			\centering
-			\includegraphics[width=\textwidth]{ic4296.png}
-			\caption{As Fig.\,\ref{fig:eso443}, but for IC\,4296 and derived from MUSE observations.}
-			\label{fig:ic4296}
-		\end{figure*}
-
-	\subsection{NGC\,612}
-		\begin{figure*}
-			\centering
-			\includegraphics[width=\textwidth]{ngc0612.png}
-			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,612.}
-			\label{fig:ngc612}
-		\end{figure*}
-
-	\subsection{NGC\,1316}
-		\begin{figure*}
-			\centering
-			\includegraphics[width=\textwidth]{ngc1316.png}
-			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,1316 and derived from MUSE observations.}
-			\label{fig:ngc1316}
-		\end{figure*}
-
-	\subsection{NGC\,1399}
-		\begin{figure*}
-			\centering
-			\includegraphics[width=\textwidth]{ngc1399.png}
-			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,1399 and derived from MUSE observations.}
-			\label{fig:ngc1399}
-		\end{figure*}
-
-	\subsection{NGC\,3100}
-		\begin{figure*}
-			\centering
-			\includegraphics[width=\textwidth]{ngc3100.png}
-			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,3100.}
-			\label{fig:ngc3100}
-		\end{figure*}
-
-	\subsection{NGC\,3557}
-		\begin{figure*}
-			\centering
-			\includegraphics[width=\textwidth]{ngc3557.png}
-			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,3557.}
-			\label{fig:ngc3557}
-		\end{figure*}
-
-	\subsection{NGC\,7075}
-		\begin{figure*}
-			\centering
-			\includegraphics[width=\textwidth]{ngc7075.png}
-			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,7075.}
-			\label{fig:ngc7075}
-		\end{figure*}
-
-	\subsection{PKS\,718-34}
-		\begin{figure*}
-			\centering
-			\includegraphics[width=\textwidth]{pks0718-34.png}
-			\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,718-34.}
-			\label{fig:pks718}
-		\end{figure*}
-
-% \clearpage
-
 \section{Extrapolating VIMOS Data}
@@
 	The two transformations that we use are from [\ion{N}{ii}]/H$\alpha$ to [\ion{N}{i}]/H$\beta$ line ratios and from the H$\alpha$ to the H$\beta$ equivalent widths.
-In both cases we fit a linear relationship $y = Ax + B$ using the least-trimmed squares routine, \textsc{lts\_linefit}\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/\#lts} of \citet{Cappellari2013} due to its robust handling of the uncertainties along both axes.
-These are shown in Figs.\ \ref{fig:ratio_relation} and \ref{fig:EqW_relation}, where we find
+In both cases we fit a linear relationship $y = Ax + B$ using the least-trimmed squares routine, \textsc{lts\_linefit}\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/\#lts}% \label{Cappellari}}
+	 of \citet{Cappellari2013} due to its robust handling of the uncertainties along both axes. These are shown in Figs.\ \ref{fig:ratio_relation} and \ref{fig:EqW_relation}, where we find
 	\begin{equation}
@@
 	and	
-	\begin{equation}}
+	\begin{equation}
 		\mathrm{EW}(H\alpha) = \, (2.92 \pm 0.03) \mathrm{EW}(H\beta) - (0.16 \pm 0.02) \, ,
@@
 
+% \begin{landscape}
+\section{Maps}
+	\label{sec:maps}
+
+	Here, we present spatially-resolved maps of our Southern Sample of the parameters measured and fitted to the IFS datacubes using the methods described in Section \ref{sec:analysis}.
+We present each galaxy in turn.
+
+	\begin{figure*}
+		\centering
+		\includegraphics[width=\textwidth]{eso443-g024.png}
+		\caption{Spatially-resolved map of measurements derived from VIMOS observations for ESO\,433-G24.
+The measurement is given in the top-left of each panel and the colour-scale limits are given in the bottom-right.
+The surface brightness (isophotes) are shown as black contours in all maps, while the \ce{^{12}CO(2-1)} contours from ALMA are in white and radio continuum contours from the VLA are in green.
+The radio band displayed depends on the data available in the archive and which images had a similar resolution and scales.}
+		\label{fig:eso443}
+	\end{figure*}
+
+	\begin{figure*}
+		\centering
+		\includegraphics[width=\textwidth]{ic1459.png}
+		\caption{As Fig.\,\ref{fig:eso443}, but for IC\,1459 and derived from MUSE observations.}
+		\label{fig:ic1459}
+	\end{figure*}
+
+	\begin{figure*}
+		\centering
+		\includegraphics[width=\textwidth]{ic1531.png}
+		\caption{As Fig.\,\ref{fig:eso443}, but for IC\,1531.}
+		\label{fig:ic1531}
+	\end{figure*}
+
+	\begin{figure*}
+		\centering
+		\includegraphics[width=\textwidth]{ic4296.png}
+		\caption{As Fig.\,\ref{fig:eso443}, but for IC\,4296 and derived from MUSE observations.}
+		\label{fig:ic4296}
+	\end{figure*}
+
+	\begin{figure*}
+		\centering
+		\includegraphics[width=\textwidth]{ngc0612.png}
+		\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,612.}
+		\label{fig:ngc612}
+	\end{figure*}
+
+	\begin{figure*}
+		\centering
+		\includegraphics[width=\textwidth]{ngc1316.png}
+		\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,1316 and derived from MUSE observations.}
+		\label{fig:ngc1316}
+	\end{figure*}
+
+	\begin{figure*}
+		\centering
+		\includegraphics[width=\textwidth]{ngc1399.png}
+		\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,1399 and derived from MUSE observations.}
+		\label{fig:ngc1399}
+	\end{figure*}
+
+	\begin{figure*}
+		\centering
+		\includegraphics[width=\textwidth]{ngc3100.png}
+		\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,3100.}
+		\label{fig:ngc3100}
+	\end{figure*}
+
+	\begin{figure*}
+		\centering
+		\includegraphics[width=\textwidth]{ngc3557.png}
+		\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,3557.}
+		\label{fig:ngc3557}
+	\end{figure*}
+
+	\begin{figure*}
+		\centering
+		\includegraphics[width=\textwidth]{ngc7075.png}
+		\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,7075.}
+		\label{fig:ngc7075}
+	\end{figure*}
+
+	\begin{figure*}
+		\centering
+		\includegraphics[width=\textwidth]{pks0718-34.png}
+		\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,718-34.}
+		\label{fig:pks718}
+	\end{figure*}
+
+% \end{landscape}
+
+% \clearpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-09-18 produce_maps.py

@@ -6,7 +6,8 @@ if cc.remote:
 	import matplotlib # 20160202 JP to stop lack-of X-windows error
 	matplotlib.use('Agg') # 20160202 JP to stop lack-of X-windows error
 import matplotlib.pyplot as plt # used for plotting
-import cPickle as pickle
+# import cPickle as pickle
+from Bin2 import Data
 import numpy as np 
 from plot_velfield_nointerp import plot_velfield_nointerp
 from prefig import Prefig
@@ -322,18 +323,20 @@ def plot(galaxy, instrument='vimos', debug=True):
 	vin_dir += '/%s/kin' % (galaxy) 
 
 	if not debug:
-		pickle_file = '%s/pickled' % (vin_dir)
-		pickleFile = open("%s/dataObj.pkl" % (pickle_file), 'rb')
-		D = pickle.load(pickleFile)
-		pickleFile.close()
-		pickle_file2 = '%s/pickled' % (vin_dir2)
-		pickleFile2 = open("%s/dataObj.pkl" % (pickle_file2), 'rb')
-		D2 = pickle.load(pickleFile2)
-		pickleFile2.close()		
+		# pickle_file = '%s/pickled' % (vin_dir)
+		# pickleFile = open("%s/dataObj.pkl" % (pickle_file), 'rb')
+		# D = pickle.load(pickleFile)
+		# pickleFile.close()
+		# pickle_file2 = '%s/pickled' % (vin_dir2)
+		# pickleFile2 = open("%s/dataObj.pkl" % (pickle_file2), 'rb')
+		# D2 = pickle.load(pickleFile2)
+		# pickleFile2.close()
+		D = Data(galaxy, instrument=instrument, opt='kin')
+		D2 = Data(galaxy, instrument=instrument, opt='pop')
 
 	for i, row in enumerate(plots):
 		for j, p in enumerate(row):
-			print i, j, p
+			# print i, j, p
 			if galaxy in ['ngc0612', 'pks0718-34'] and 'Mg_b' in p:
 				break # break out of for-loop
 			elif 'flux' in p:
@@ -398,37 +401,38 @@ def plot(galaxy, instrument='vimos', debug=True):
 				axs[i,j].remove()
 
 
-	age = np.zeros(D2.number_of_bins)
[…]

### 2018-11-07 paper.tex
correct spelling mistake

@@
 	There is a strong consensus within the scientific literature that the most powerful radio galaxies are the result of gas-rich, major mergers causing large amounts of material to fall on to the black hole at the centre of the resulting galaxy, thus producing an immensely powerful AGN which includes a powerful radio jet \citep[e.g.][]{Malin1983, Quillen1992, Lim2000}.
-However, such galaxies are by construction extremely rare and are not representative of the general radio galaxy population.
+However, such galaxies are extremely rare and are not representative of the general radio galaxy population.
 Most radio galaxies are low-powered, and their basic properties and origins are poorly constrained.
@@
 A median spectrum was taken from four $20 \times 20$\,spaxel regions, one in each spatial corner of the ESO reduced cube.
-After checking that no stellar continuum could be fit to the medium sky spectrum (i.e.\ that very little light from the galaxy is contaminating the pseudo-sky regions), this median sky spectrum was subtracted from each spaxel in the cube.
+After checking that no stellar continuum could be fit to the median sky spectrum (i.e.\ that very little light from the galaxy is contaminating the pseudo-sky regions), this median sky spectrum was subtracted from each spaxel in the cube.
 

### 2018-11-10 paper.tex
Minor alteration to the paper
On branch master
 Changes to be committed:
	modified:   paper.tex

@@
 \author[J. Warren et al.]{
-Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:joshua.warren@physics.ox.ac.uk}{joshua.warren@physics.ox.ac.uk}}
+Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:warrenj@gmx.com}{warrenj@gmx.com}}
+%Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:joshua.warren@physics.ox.ac.uk}{joshua.warren@physics.ox.ac.uk}}
 Martin Bureau,$^{1}$
@@
 The most powerful radio galaxies are well studied with a strong consensus in the literature regarding their formations processes.
-However they are intrinsically rare objects and not representative of the general population of radio galaxies.
+However, they are intrinsically rare objects and not representative of the general population of radio galaxies.
 Low-powered radio galaxies are comparatively poorly studied with many conflicting viewpoints regarding their origin and the extent of the effect of feedback from them.
@@
 We present a complete sample of 11 nearby low-powered radio galaxies, observed with a suite of instruments.
-This paper focuses on the spatially-resolved stellar kinematics, stellar populations, and ionized gas distribution, kinematics and ionization derived from optical IFS observations%, while other observation such as \ce{^{12}CO(2-1)} from Atacama Large Millimetre/sub-millimetre Array (ALMA) and radio continuum from the Very Large Array (VLA) will be presented in future papers
+This paper focuses on the spatially-resolved stellar kinematics and populations, and ionized gas distribution, kinematics and ionization derived from optical IFS observations%, while other observation such as \ce{^{12}CO(2-1)} from Atacama Large Millimetre/sub-millimetre Array (ALMA) and radio continuum from the Very Large Array (VLA) will be presented in future papers
 .
@@
 
-We tentatively find that our radio-selected ETGs contain a higher mass in of ionized gas than expected, but after accounting for the differences in the mass distribution, we find no further differences between the two samples in the characteristics that can be studied with optical IFU data.
+We tentatively find that our radio-selected ETGs contain a higher mass in of ionized gas than expected.
+However, after accounting for the differences in the mass distribution, we find no further differences between the two samples in the characteristics that can be studied with optical IFU data.
 We suggest that this is consistent with the notion that low-powered radio galaxies are ordinary ETGs experiencing a brief active phase which maintains their low star-formation rates (also known as maintenance or jet-mode AGN).
@@
 Most radio galaxies are low-powered, and their basic properties and origins are poorly constrained.
-One of the most popular suggestions is that they are bona-fide detections of jet-mode AGN.%, a class of AGN thought to maintain the dearth of star formation in early-type galaxies (ETGs), after most of the fuel for star formation has been removed by an earlier event.
+One of the most popular suggestions is that they are bona-fide detections of jet-mode AGN \citep[e.g.][]{Heckman2014}.%, a class of AGN thought to maintain the dearth of star formation in early-type galaxies (ETGs), after most of the fuel for star formation has been removed by an earlier event.
 	These radio galaxies are known to be dusty with dust lanes having a tendency to be perpendicular to the jets \citep[e.g.][]{DeRuiter2002, VerdoesKleijn2005}.
@@
 
-	To test this hypothesis, a complete sample of 11 nearby low-powered radio galaxies was constructed \citet{Prandoni2010} and observed with a suite of instruments.
-Here, we present the spatially-resolved stellar kinematics, stellar populations, and ionized gas distribution, kinematics and ionization derived from integral-field spectroscopic (IFS) observations with the Visible Multi-object Spectrograph (VIMOS) and archival data from the Multi-unit Spectroscopic Explorer (MUSE), both on the Very Large Telescope (VLT).
+	To test this hypothesis, a complete sample of 11 nearby low-powered radio galaxies was constructed by \citet{Prandoni2010} and observed with a suite of instruments.
+Here, we present the spatially-resolved stellar kinematics and populations, and ionized gas distribution, kinematics and ionization derived from integral-field spectroscopic (IFS) observations with the Visible Multi-object Spectrograph (VIMOS) and archival data from the Multi-unit Spectroscopic Explorer (MUSE), both on the Very Large Telescope (VLT).
 We compare the characteristics and properties (accessible with $V$-band IFS data) of our sample of low-power radio galaxies to those of ordinary (i.e.\ optically-selected) ETGs from the Atlas$^\text{3D}$ and MASSIVE IFS surveys.
-We hereafter refer to the combined Atlas$^\text{3D}$ and MASSIVE sample as the A+M sample.
-
-	In Section \ref{sec:samp} we, set out the compete sample with our observations and data-reduction methods detailed in Section \ref{sec:obs}.
+We hereafter refer to the combined Atlas$^\text{3D}$ \citep{Cappellari2011} and MASSIVE \citep{Ma2014} sample as the A+M sample.
+
+	In Section \ref{sec:samp} of this paper we set out the compete sample with our observations and data-reduction methods detailed in Section \ref{sec:obs}.
 Our data-analysis methods and routines are detailed in Section \ref{sec:analysis} (the maps of our sample produced with these methods are shown in Appendix \ref{sec:maps}).
@@
 The NGC 1316 and NGC 1399 MUSE datacubes were binned to a S/N of 50 for the analysis of the stellar kinematics and 100 for the analysis of the emission line kinematics and stellar populations.
+These target S/N were chosen in order to be as low as possible, while still returning meaningful information (as assessed by eye).
 
@@
 This is then summed in quadrature with the noise spectrum (as propagated through the data reduction pipeline) to produce a combined `residual noise' spectrum.
-A Monte--Carlo (MC) method is used to propagate this residual noise to give to give the quoted uncertainties.
+A Monte--Carlo (MC) method is used to propagate this residual noise to give to give the quoted uncertainties on all fitted values.
 
@@
 Note that for NGC 1316, indices at wavelengths longer than 5800 \AA\ are calculated using the extrapolated best-fitting \textit{pPXF} fit.
-A given index, $I$, is then measured for both this `unconvolved' spectrum ($I^\text{unc}$) and the convolved best-fitting spectrum ($I^\text{conv}$), and the ratio of these two indices is used as a multiplicative correction factor for the index measured ($I^\text{obs}$), such that the corrected index ($I^\text{corr}$) is given by
+A given index, $I$, is then measured for both this `unconvolved' spectrum ($I^\text{unc}$) and the convolved best-fitting spectrum ($I^\text{conv}$), and the ratio of these two indices is used as a multiplicative correction factor for the index measured in the observations ($I^\text{obs}$), such that the corrected index ($I^\text{corr}$) is given by
 			\begin{equation}
@@
 			\label{subsubsec:ellip}
-			In this paper, ellipticity is that of the best-fitting ellipse to the surface-brightness map with an mean radius $R_\text{m}$, of 1 effective radius $R_\text{e}$.
+			In this paper, ellipticity, $\epsilon$, is that of the best-fitting ellipse to the surface-brightness map with an mean radius $R_\text{m}$, of 1 effective radius $R_\text{e}$.
 % Firstly the centre of the galaxy is found as the luminosity weighted centre using the \textsc{python} routine \textsc{find\_galaxy}, which is part of the \textsc{mge} package\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/} by \citet{Cappellari2002}.
-			as found by the \textsc{idl} routine \textsc{kinemetry}\footnote{http://davor.krajnovic.org/idl/} by \citet{Krajnovic2006}, which finds the best-fitting ellipses at a range of evenly spaced semi-major axes.
+			as found by the \textsc{idl} routine \textsc{kinemetry}\footnote{http://davor.krajnovic.org/idl/} by \citet{Krajnovic2006}.%, which finds the best-fitting ellipses at a range of evenly spaced semi-major axes.
 %This is achieved by performing harmonic expansion of maps along ellipses with a given semi-major axis and, when used for even moments (e.g.\ surface brightness, velocity dispersion, h$_4$ etc.), minimizing the amplitude of the first and second harmonics.
-			The results include the ellipticity, $\epsilon$ and position angle, $PA_\text{phot}$ of the best-fitting ellipse for each semi-major axis.
+			The results include the ellipticity, $\epsilon$ and position angle, $PA_\text{phot}$ of the best-fitting ellipse.% for each semi-major axis.
 The fit is repeated for increasing semi-major axis until $<$75\% of the ellipse is not contained within the field of view.
@@
 	\label{sec:StarKine}
-	Using the methods above, we produce stellar kinematic maps for all datacubes (shown in Section \ref{sec:maps}).
+	Using the methods above, we produce stellar kinematic maps (shown in Appendix \ref{sec:maps}) for all datacubes.
 Here, we use these maps to classify each galaxy according to the Atlas$^\text{3D}$ regular/non-regular rotator and fast/slow rotator classification schemes of \citet{Krajnovic2006} and \citet{Cappellari2016}, respectively, as well as the qualitative kinematic classes of \citet{Krajnovic2011}.
@@
 		\label{subsec:RR}
-		We find 4/11, or $(36\pm15)$\%, of our sample galaxies are regular rotators.
+		We find 4 out of 11, or $(36\pm15)$\%, of our sample galaxies are regular rotators.
 This compares to 82\% of the Atlas$^\text{3D}$ sample being classified as regular rotators \citep{Krajnovic2011}.
@@
 
-		5 out of 11 galaxies, or $(45\pm13)$\%, are slow rotators.
+		5 out of 11 galaxies, or $(45\pm13)$\%, are slow rotators (see Fig.\,\ref{fig:lambdaR_ellip}).
 This is between that of the Atlas$^\text{3D}$ and MASSIVE projects, who find 13.1\% and 77.5\% of their respective sample galaxies to be slow rotators.
@@
 In our case we use the $K$-band absolute magnitude ($M_K$) as a proxy for stellar mass, with bins of 0.5 mag.
-This gives an expected fraction of $f' = 0.64 \pm 0.06$, just consistent with our finding of $(45\pm13)$\% of the Southern sample galaxies being slow rotators.
+This gives an expected fraction of $f' = 0.64 \pm 0.06$, which is consistent with our finding of $(45\pm13)$\% of the Southern sample galaxies being slow rotators.
 Again the large uncertainty reflects the low number statistics of the Southern sample.
@@
 	\subsection{Kinematic Features}
-		We attempt to identify the kinematic features defined by \citet{Krajnovic2011} in an algorithmic way.
-However, the artefacts from the VIMOS quadrants confuse ellipse fitting algorithms so only maps derived from the MUSE data are classified in this way; kinematic features in maps derived from the VIMOS data are identified by eye.
-These classification are listed in Col.\,7 of Table \ref{tab:classify} and the corresponding kinematic group to which a given galaxy belongs to is given is Col.\,8.
+		We attempt to identify the kinematic features defined by \citet{Krajnovic2011} in an algorithmic mannor, however, the artefacts from the VIMOS quadrants confuse ellipse fitting algorithms.
+Due to this, only maps derived from the MUSE data are classified in this way, while kinematic features in maps derived from the VIMOS data are identified by eye.
+These classification are listed in Col.\,7 of Table \ref{tab:classify} and the corresponding kinematic group \citep[also defined by][]{Krajnovic2011} to which a given galaxy belongs to is given is Col.\,8.
 We observe 3 KDCs (although PKS 718-34 is only a tentative classification) such that $29\pm19$\% of non-regular rotators in our Southern sample definitely (not including PKS 718-34) contain KDCs (or $43\pm19$\% including PKS 718-34), with the large uncertainty reflecting the low-number statistics.
@@
 		The misalignment angle, $\Gamma_\text{kin}$, between the photometric and kinematic position angle is given in Col.\,4 of Table \ref{tab:classify}.
-Intrinsically misaligned systems may appear aligned in certain projections, but aligned systems will be aligned in all projections, and therefore a low value of $\Gamma_\text{kin}$ cannot be used to describe the intrinsic shape of an individual galaxy, but they can be interpreted within a statistical framework as in \citet{Cappellari2007}.
+IC 1531, NGC7075 and PKS 718-34 all have very large uncertainties in the value of $PA_\text{phot}$ due to the VIMOS quadrant artefacts causing the fitting routine of \textsc{kinemetry} to become unreliable.
+
+		While intrinsically misaligned systems may appear aligned in certain projections, aligned systems will be aligned in all projections.
+Therefore a low value of $\Gamma_\text{kin}$ cannot be used to describe the intrinsic shape of an individual galaxy, but can only be interpreted within a statistical framework as in \citet{Cappellari2007}.
 However, a high value of $\Gamma_\text{kin}$ can give an insight into the intrinsic shape of an individual galaxy.
 We find all the regular rotators in our Southern sample, are consistent with having aligned photometry and kinematic position angles to within 11\degr, while non-regular rotators have a large range of values of $\Gamma_\text{kin}$.
-IC 1531, NGC7075 and PKS 718-34 all have very large uncertainties in the value of $PA_\text{phot}$ due to the VIMOS quadrant artefacts causing the fitting routine of \textsc{kinemetry} to become unreliable.
-
-		The lack of misalignments in regular rotators is consistent with \citet{Cappellari2007}, \citet{Krajnovic2011} and \citet{Fogarty2015}, who all showed that regular rotators almost always have aligned photometric and kinematic axes with very little scatter and that regular rotators with a significant misalignment are either interacting or strongly barred.
+
+		The lack of misalignments in regular rotators is consistent with \citet{Cappellari2007}, \citet{Krajnovic2011} and \citet{Fogarty2015}, who all show that regular rotators almost always have aligned photometric and kinematic axes with very little scatter.
+They also point out that regular rotators with a significant misalignment tend to be either interacting or strongly barred.
 The lack of misalignments suggests that the regular rotators (including those within our Southern sample) are consistent with being axisymmetric \citep{Cappellari2016}.
@@
 	\label{sec:absorption}
-	Using the methods described in Section \ref{subsec:absorption} we produce maps of the absorption line strength indices for each galaxy (shown in Appendix \ref{sec:maps}).
-Here we measure the Mg\,--\,velocity dispersion relation and compare our absorption line strength measurements to the literature.
+	Using the methods described in Section \ref{subsec:absorption}, we produce maps of the absorption line strength indices for each galaxy (shown in Appendix \ref{sec:maps}).
+In this section, we measure the Mg\,--\,velocity dispersion relation and compare our absorption line strength measurements to the literature.
 
@@
 		\label{subsec:Mgsigma}
-		The Mg$_2$ absorption line index of \citet{Trager1998} has overlapping bandpasses with the Mg\,b index (also of \citeauthor{Trager1998}), but includes the MgH molecular absorption line, and is hence considered a molecular index and is measured in units of magnitude.
+		%The Mg$_2$ absorption line index of \citet{Trager1998} has overlapping bandpasses with the Mg\,b index (also of \citeauthor{Trager1998}), but includes the MgH molecular absorption line, and is hence considered a molecular index and is measured in units of magnitude.
 		\citet{Bender1993} observed the tight relationship between the global Mg$_2$ absorption line strength and logarithm of the central velocity dispersion, $\sigma_0$, in elliptical galaxies.
@@
 		Part of the red continuum band of the Mg$_2$ index is outside of the spectral range of VIMOS, but \citet{Ziegler1997} show there is an approximately linear relationship between Mg\,b and Mg$_2$, with a gradient of 14.3--15.5\,mag\,\AA$^{-1}$\ depending on metallicity.
-We thus use Mg\,b as a proxy for Mg$_2$.
+Thus, following \citet{Ziegler1997}, we also use Mg\,b as a proxy for Mg$_2$.
 
 		Using an aperture with a radius of 2\arcsec\ on each datacube, we measure $\sigma_0$ and Mg\,b at a spectral resolution of 8.4\,\AA\ full-width half-maximum (FWHM), chosen such that the transformation functions of \citet{Vazdekis2010} can be used to change the literature measurements from the Lick/IDS system to the LIS.
-The results are shown in Fig.\,\ref{fig:globalMg} with the best-fitting linear relationship (found using \textsc{lts\_linefit} %\footnotemark[\ref{Cappellari}]
-		by \citealt{Cappellari2013}) shown by the solid black line.
+The results are shown in Fig.\,\ref{fig:globalMg} with the best-fitting linear relationship %(found using \textsc{lts\_linefit} %\footnotemark[\ref{Cappellari}]
+		%by \citealt{Cappellari2013}) 
+		shown by the solid black line.
 This has a gradient of $3.3 \pm 1.0 \,\mathrm{\text{\AA}\,dex^{-1}}$.
-It was noticed that NGC 1316 is a possible outlier.
+It was noted that NGC 1316 is a possible outlier.
 Removing NGC 1316 from the fit gives a gradient of $2.5 \pm 0.7 \,\mathrm{\AA\,dex^{-1}}$ (green dashed line in Fig.\,\ref{fig:globalMg}).
-Both fits are in very good agreement with the gradient found by \citet{Ziegler1997} for a sample of elliptical galaxies within Virgo and Coma using data from \citet{Dressler1987} of $2.5\,\mathrm{\text{\AA}\,dex^{-1}}$ (blue dotted line in Fig.\,\ref{fig:globalMg}), with an intrinsic scatter of 0.16\,\AA\ for galaxies with $\log \sigma_0 \geqslant 2.3$\,dex.
+Both fits are in very good agreement with the gradient found by \citet{Ziegler1997} (transformed to the LIS system using the functions of \citealt{Vazdekis2010}) for a sample of elliptical galaxies within Virgo and Coma %using data from \citet{Dressler1987}
+		of $2.7\,\mathrm{\text{\AA}\,dex^{-1}}$ (blue dotted line in Fig.\,\ref{fig:globalMg}).%, with an intrinsic scatter of 0.16\,\AA\ for galaxies with $\log \sigma_0 \geqslant 2.3$\,dex.
 
@@
 			\caption[Global Mg\,b\,--\,$\sigma$]{The Mg\,b\,--\,velocity dispersion relation using a 2\arcsec aperture.
-We find a similar gradient to our best-fitting (solid black) line as that found by \citet[; blue dotted line]{Ziegler1997}, while removing NGC 1316 from the fit (green dashed) results in an extremely good agreement with \citet{Ziegler1997}.}
+We find a similar gradient to our best-fitting (solid black) line as that found by \citet[transformed to LIS with the functions of \citealt{Vazdekis2010}; blue dotted line]{Ziegler1997}.
+Removing NGC 1316 from the fit (green dashed) results in an extremely good agreement with \citet{Ziegler1997}.}
 			\label{fig:globalMg}
@@
 
+%**********************************************************************
+%This plot no longer exists
+%**********************************************************************
 		\textbf{NGC 1316} is a complex object.
@@
 				\caption{H$\beta$ flux radial profiles derived from the VIMOS datacubes.
-Solid red lines show $F(\mathrm{H\beta}) \propto r^{-2}$ convolved with a Gaussian function of width equal to the mean seeing (see Table \ref{tab:observations}).
+Solid red lines show $F(\mathrm{H\beta}) \propto r^{-2}$ convolved with a Gaussian function of width equal to the mean seeing taken from the observation logs.
 This accounts for the PSF of the observations.

### 2018-11-11 paper.tex
Minor alterations to paper
Remove OIII maps from PKS0718-34 and NGC1399 maps.

 On branch master
 Changes to be committed:
	modified:   paper.tex
	modified:   produce_maps.py

@@
 When comparing to a particular paper we correct for the same effects described in the paper, but using our methods, as described in Section \ref{subsec:absorption}.
-As in Section \ref{subsec:Mgsigma} we use a resolution of 8.4\,\AA\ FWHM in order to use the transformation function provided by \citet{Vazdekis2010} from Lick/IDS system to the LIS.
+As in Section \ref{subsec:Mgsigma} we use a resolution of 8.4\,\AA\ FWHM in order to act on the literature values with the transformation function provided by \citet{Vazdekis2010} to provide a fair comparison between indices.
 
@@
 		We also observe that the offset in the Fe5015 index is also quite large in comparisons with \citet{Rampazzo2005} and \citet{Vazdekis2010}.
-In the case of the comparison with \citet{Rampazzo2005} we suggest that the difference is due to differences in method for accounting for the [\ion{O}{iii}] emission doublet, however the origin of the offset is less clear in case of the comparison with \citet{Vazdekis2010}.
+In the case of the comparison with \citet{Rampazzo2005} we suggest that the difference is due to differences in method for accounting for the [\ion{O}{iii}] emission doublet, however the origin of the offset is less clear when comparing to \citet{Vazdekis2010}.
 
@@
 	\label{sec:stellarPop}
-	We have assumed that a given spectrum from our Southern sample can be well approximated by a SSP.
-We use the method described in Section \ref{subsubsec:stellarPop} to produce maps of the most-likely SSP characteristics: age ($t$), metallicity ($Z/H$) and alpha-element enhancement ($\alpha$/Fe) from the absorption line strength maps (see Appendix \ref{sec:maps}).
-
-	In general, our sample galaxies show old, metal rich and alpha enhanced SSPs; qualities which ETGs are well known for.
-The exception is NGC 612 and NGC 1316.
+	Assuming that a given spectrum from our Southern sample can be well approximated by a SSP, we use the method described in Section \ref{subsubsec:stellarPop} to produce maps of the most-likely SSP characteristics: age ($t$), metallicity ($Z/H$) and alpha-element enhancement ($\alpha$/Fe) from the absorption line strength maps (see Appendix \ref{sec:maps}).
+
+	In general, the Southern sample show old, metal rich and alpha enhanced SSPs; qualities which ETGs are well known for.
+The exceptions are NGC 612 and NGC 1316.
 NGC 1316 shows a very young stellar population (our fit of $t \approx 2$\,Gyr agrees with that of \citealt{Kuntschner2000}, but is conflicting with the older and less metal rich stellar population of \citealt{Koleva2011} who found $t=4.5 \pm 0.3 \,\mathrm{Gyr}$ and $\mathrm{[Fe/H]}=0.12 \pm 0.01 \,\mathrm{dex}$ for an aperture covering the central 0.1 kpc).
 We also find NGC 612 to have a young stellar population of $t\approx 4\,\mathrm{Gyr}$.
-NGC 3557 is notable for containing a significantly younger ($t\approx 4$\,Gyr) core of about 10\arcsec\ diameter and NGC 3100 has a branch of young stars ($\approx 4$\,Gyr) along the south-east branch of the molecular gas (white contours in Fig \ref{fig:ngc3100}).
+NGC 3557 is notable for containing a significantly younger ($t\approx 4$\,Gyr) core of about 10\arcsec\ diameter and NGC 3100 has a branch of young stars ($\approx 4$\,Gyr) along the south-east branch of the molecular gas (white contours in Fig.\,\ref{fig:ngc3100}).
 
@@
 		\label{subsec:popKDC}
-		\citet{Kuntschner2010} found that KDCs can be separated two classes: they are either small with various stellar ages or typically larger but containing an old stellar population.
+		\citet{Kuntschner2010} showed that KDCs can be separated two classes: they are either small with various stellar ages or typically larger but containing an old stellar population.
 The size of the KDC is defined as the radius of the region surrounding the KDC where the superposition of the two components (the KDC and the host galaxy) results in a local minimum in the mean velocity.
@@
 
-		The small KDCs are too small to be spatially resolved by our data, and thus are not considered here.
-The larger, old KDCs are typically embedded in slow rotators.
-They have no upper limit on the age of their stellar populations suggesting that the stars within the KDC dominate in total mass as well as surface brightness.
-Thus, they do not fade into their host galaxies as they age unlike the small KDCs \citep{Kuntschner2010}.
+		The typical size of the smaller class of KDCs are too small to be spatially resolved by our data and thus are not considered here.
+The generally larger, old KDCs are typically embedded in slow rotators \citep{Kuntschner2010}.
+They have no upper limit on the age of their stellar populations suggesting that the stars within the KDC dominate in total mass as well as surface brightness, since they do not fade into their host galaxies as they age unlike the small KDCs \citep{Kuntschner2010}.
 \citet{Bois2011} showed major mergers may well result in such large KDCs if the initial spin axis of the progenitor galaxy with the lowest bulge-to-disc ratio (later-type) is anti-parallel to the orbital angular momentum vector.
@@
 		In Fig.\,\ref{fig:KDC} we show the age and size of the 3 KDCs hosted by galaxies in our Southern sample.
-We include PKS 718-34 here but stress it is only tentatively classified as containing a KDC.
-As can be seen from Fig.\,\ref{fig:KDC}, PKS 718-34 would be an extremely large KDC, but is still consistent with the findings of \citet{Kuntschner2010}.
+We include PKS 718-34 here but we stress it is only tentatively classified as containing a KDC.
+As can be seen from Fig.\,\ref{fig:KDC}, PKS 718-34 would be an extremely large KDC, but all three are still consistent with the findings of \citet{Kuntschner2010}.
 
@@
 	\label{sec:gas}
-	Using the methods described in Section \ref{subsubsec:EmissionFit}, we find the best-fitting line-of-sight velocity distribution (LOSVD; assumed to be Gaussian and parametrised by the mean velocity and velocity dispersion only) of the emission lines in each bin.
-Images of the Southern Sample galaxies in the [\ion{O}{iii}]$\lambda\lambda$4957,5007 doublet are shown in Appendix \ref{sec:maps} (we choose to show [\ion{O}{iii}] as detections of all emission lines require a detection of [\ion{O}{iii}] first, see Section \ref{subsubsec:EmissionFit}).
+	Using the methods described in Section \ref{subsubsec:EmissionFit}, we find the best-fitting LOSVD of the emission lines in each bin .
+As with the stellar LOSVD, this is assumed to be Gaussian in shape and parametrised by the mean velocity and velocity dispersion only.
+Images of the Southern Sample galaxies in the [\ion{O}{iii}]$\lambda\lambda$4957,5007 doublet are shown in Appendix \ref{sec:maps} (we choose to show [\ion{O}{iii}] as detections of all emission lines require a detection of [\ion{O}{iii}] first; see Section \ref{subsubsec:EmissionFit}).
 
 	Only 4 galaxies of the Southern Sample have emission lines detected outside of their central region (IC 1459, NGC 612, NGC 1316 and NGC 3100).
-Of the remaining 7 galaxies, NGC 1399 and PKS 718-34 have no detection of H$\beta$ in their spatially-resolved map (although we do detect H$\beta$ in the spatially-integrated spectrum of NGC 1399; see Table \ref{tab:derivedProp}), while the other 5 galaxies are only detected in their centre.
-All other emission lines have similar distributions, but with different fluxes.
+Of the remaining 7 galaxies, NGC 1399 and PKS 718-34 have no detections of emission lines in their spatially-resolved map (which are therefore not shown), while the other 5 galaxies are only detected in their centre.
+For a given galaxy, all emission lines have similar distributions, but different fluxes.
 

### 2018-11-11 produce_maps.py

@@ -339,6 +339,8 @@ def plot(galaxy, instrument='vimos', debug=True):
 			# print i, j, p
 			if galaxy in ['ngc0612', 'pks0718-34'] and 'Mg_b' in p:
 				break # break out of for-loop
+			elif galaxy in ['ngc1399', 'pks0718-34'] and 'OIII' in p:
+				axs[i,j].remove()
 			elif 'flux' in p:
 				if p == 'D.flux':
 					axs[i,j] = plot_velfield_nointerp(D.x, D.y, D.bin_num, 
@@ -356,11 +358,11 @@ def plot(galaxy, instrument='vimos', debug=True):
 						scale = 'log' if o == 'radio' else 'lin'
 						add_(o, color, axs[i,j], galaxy, nolegend=True, scale=scale)
 				if i > 0:
-					if plots[i-1][j] != '':
+					if plots[i-1][j] != '' and hasattr(axs[i-1,j], 'ax_dis'):
 						axs[i-1,j].ax_dis.set_xticklabels([])
 						axs[i-1,j].ax_dis.set_xlabel('')
 				if j > 0:
-					if plots[i][j-1] != '':
+					if plots[i][j-1] != '' and hasattr(axs[i,j-1], 'ax_dis'):
 						axs[i,j].ax_dis.set_yticklabels([])
 						axs[i,j].ax_dis.set_ylabel('')
 
@@ -388,11 +390,11 @@ def plot(galaxy, instrument='vimos', debug=True):
 						scale = 'log' if o == 'radio' else 'lin'
 						add_(o, color, axs[i,j], galaxy, nolegend=True, scale=scale)
 				if i > 0:
-					if plots[i-1][j] != '':
+					if plots[i-1][j] != '' and hasattr(axs[i-1,j], 'ax_dis'):
 						axs[i-1,j].ax_dis.set_xticklabels([])
 						axs[i-1,j].ax_dis.set_xlabel('')
 				if j > 0:
-					if plots[i][j-1] != '':
+					if plots[i][j-1] != '' and hasattr(axs[i,j-1], 'ax_dis'):
 						axs[i,j].ax_dis.set_yticklabels([])
 						axs[i,j].ax_dis.set_ylabel('')
 			
@@ -450,7 +452,9 @@ def plot(galaxy, instrument='vimos', debug=True):
 				scale = 'log' if o == 'radio' else 'lin'
 				add_(o, color, axs[-1,j], galaxy, nolegend=True, scale=scale)
[…]

### 2019-08-26 paper.tex
Changes made before/after sending to Martin...?
 Changes to be committed:
	modified:   paper.tex
	modified:   refs.bib

@@
 	As can be seen from the maps in Appendix \ref{sec:maps}, both NGC 612 and NGC 3100 have significant off-centre clouds of ionized gas.
-The latter is spatial coincident with both the radio jet and the gap in the CO ring, while former seems to no link with either the radio jet (a massive jet extending $\sim 200$\,kpc to the east and west of the galaxy centre) or the CO.
+The latter is spatial coincident with both the radio jet and the gap in the CO ring, while the former seems to have no link with either the radio jet (a massive jet extending $\sim 200$\,kpc to the east and west of the galaxy centre) or the CO.
 
@@
 	\end{equation}
-	where $M_\text{\ion{H}{ii}}$ is the total mass of \ion{H}{ii} in the galaxy, $D$ is the galaxy distance, and $F(\mathrm{H\alpha})$ is the H$\alpha$ flux measured from the spectrum created by summing spatially all spaxels within an aperture of $\frac{R_\mathrm{e}}{2}$ (chosen to exclude noisy outer regions of the observations, but still includes the bulk of the gas in system with significant spatially-extended gas).
-This method assumes an electron density $n_\mathrm{e} = 100 \, \mathrm{cm^{-3}}$, a temperature of $10^4$ K and case-B recombination.
+	where $M_\text{\ion{H}{ii}}$ is the total mass of \ion{H}{ii} in the galaxy, $D$ is the galaxy distance, and $F(\mathrm{H\alpha})$ is the H$\alpha$ flux measured from the spectrum created by spatially integrating across spaxels within an aperture of $\frac{R_\mathrm{e}}{2}$ (chosen to exclude noisy outer regions of the observations, but still includes the bulk of the gas in system with significant spatially-extended gas).
+As in \citet{Sarzi2005} we chose an electron density $n_\mathrm{e} = 100 \, \mathrm{cm^{-3}}$.
+This method assumes a temperature of $10^4$ K and case-B recombination \citep{Kim1989}.
 Like \citet{Sarzi2005}, we only claim a detection if the amplitude-to-noise ratio (A/N) is $>4$ for [\ion{O}{iii}] and $>2.5$ for H$\beta$ or H$\alpha$ lines for VIMOS and MUSE data, respectively.
@@
 
-	Our calculated gas masses are given Table \ref{tab:derivedProp} and are at the upper limit of, and possibly exceed, the typical masses observed in ETGs.
+	Our calculated gas masses are given Table \ref{tab:derivedProp} and are at the upper limit of, and possibly exceed, the typical masses observed in ETGs \citep[e.g.][]{Phillips1986, Zeilinger1996, Sarzi2005}.
 Given that our sample contains particularly massive galaxies, high ionized gas masses are not unexpected, however.
@@
 		\label{subsec:GasKin}
-		Map of the best-fitting kinematics (mean velocity and velocity dispersion), as found with the methods described in Section \ref{subsubsec:EmissionFit} for the 4 galaxies (IC 1459, NGC 612, NGC 1316 and NGC 3100) with detected spatially-extended emission lines are shown in Appendix \ref{sec:maps}.
+		Maps of the best-fitting kinematics (mean velocity and velocity dispersion), as found with the methods described in Section \ref{subsubsec:EmissionFit} for the 4 galaxies (IC 1459, NGC 612, NGC 1316 and NGC 3100) with detected spatially-extended emission lines are shown in Appendix \ref{sec:maps}.
 Due to that fact that, unlike stars, gas is dissipational, it is to be expected that given sufficient time, the ISM will always settle into a disc.
@@
 
-		We now comment on each galaxy in turn.
-
-		\textbf{IC 1459} has ionized gas counter-rotating with respect to the stellar KDC, and also rotating independently from the rest of the galaxy.
-\citet{Franx1988} claim that the rotation of the gas is aligned with that of the stars outside of the KDC, however we observe the outer stellar kinematics to be non-rotating.
+		We now comment on each of these 4 galaxies in turn.
+
+		\textbf{IC 1459} has ionized gas counter-rotating with respect to the stellar KDC, but also not aligned with the outer stars of host galaxy (i.e.
+beyond the KDC) since they are non-rotating: the ionized gas has a third, independent, axis of rotation.
+This is contrary to \citet{Franx1988} who claims that the rotation of the gas is aligned with that of the stars outside of the KDC.
 As the stellar disc did not survive the merger even that created the KDC, it is unlikely that the gas in IC 1459 progenitor galaxy survived.
-The lost gas may, however, have been re-accreted.
+The lost gas may, however, have been re-accreted such that the gas observed today contains a fossil record of the galaxy's original disc.
 Alternatively, the ISM may have yet another external origin.
@@
 The misalignment between the position angle of the stellar and gas kinematics (using the method described in Section \ref{subsubsec:KinPA}) is just $1\fdg0\pm0\fdg7$, consistent with an internal origin for the gas.
-This adds to the evidence that NGC 612 has not undergone a recent major merger (major mergers exhaust galaxies of their gas and destroy a stellar disc) and suggests that, the fuelling and powering of the radio jet could be a purely secular process.
+This adds to the evidence that NGC 612 has not undergone a recent major merger (major mergers exhaust galaxies of their gas and destroy a stellar disc), suggesting that the fuelling of the radio jet could be a purely secular process.
 
@@
 		\textbf{NGC 1316} is a complex object.
-Since there are redshifted emission lines with respect to the rest frame of the galaxy on both sides of the galaxy, the gas is not in a settled disc and that there must be some inflow/outflows.
-From visual inspection of the velocity field for the gas (Fig.\,\ref{fig:MUSE_Gaskine}) it is clear that a simple exponential disc model will not be well fitted to the data.
+The existence of redshifted emission lines with respect to the rest frame of the galaxy on both sides of the galaxy shows the gas is not in a settled disc and that there must be some inflow/outflows.
+From visual inspection of the velocity field for the gas (Fig.\,\ref{fig:ngc1316}) it is clear that a simple exponential disc model will not be well fitted to the data.
 We suggest that that the large velocity peak on the south-west side of the galaxy could be an inflow towards the nucleus, almost perpendicular to the radio jet, however we acknowledge that other interpretations are possible.
-Better quality data (longer exposure times) and more sophisticated models are required to add certainty to this interpretation.
-Nevertheless, it is clear that the gas in not in a settled disc.
+Better quality data (longer exposure times and wider fields of view) coupled with more sophisticated models are required to add certainty to this interpretation.
+%Nevertheless, it is clear that the gas in not in a settled disc.
 
@@
 For the emission-line fluxes derived from the VIMOS datacubes, we use the [\ion{N}{i}]/H$\beta$ versus [\ion{O}{iii}]/H$\beta$ plot of \citet[hereafter the SAURON plot]{Sarzi2010}.
-Unlike the BPT plots, \citet{Sarzi2010} do not define classification boundaries.
+Unlike the BPT plots, \citet{Sarzi2010} does not define classification boundaries.
 Using Eq.\,\ref{eq:N_dec} we translate the [\ion{N}{ii}]/H$\alpha$ BPT plot classification boundaries of \citet{Kewley2001} and \citet{Kauffmann2003a} to the [\ion{N}{i}]/H$\beta$ SAURON plot.
@@
 Finally we use the mass\,--\,excitation (MEx) plot of \cite{Nyland2016}, using parameters derived from the spatially-integrated spectra within an aperture of radius 3\arcsec\ thus only probing the central region of the galaxies (see Section \ref{subsubsec:MEx}).
-This allows us to classify the remaining galaxies into star-forming, Seyfert 2, LINER, transition or passive classes, and subdivide LINER galaxies into those whose LINER characteristics are attributable to a central AGN (labelled as LINER-AGN in Table \ref{tab:derivedProp}) and those whose LINER characteristics are not.
-We expand on the final two steps in the sections below.
+This allows us to classify the remaining galaxies into star-forming, Seyfert 2, LINER, transition or passive classes, and subdivide LINER galaxies into those whose LINER characteristics are attributable to a central AGN (labelled as LINER-AGN) and those whose LINER characteristics are not.
+As the least conventional, we expand on the final two steps in the sections below with the final classifications shown in Table \ref{tab:derivedProp}.
 
@@
 Solid red lines show $F(\mathrm{H\alpha}) \propto r^{-2}$ convolved with a Gaussian function of width equal to the mean seeing taken from the fits file headers.
-This accounts for the point-spread function (PSF) of the observations.\label{fig:Ha_profile_MUSE}}
+This accounts for the PSF of the observations.\label{fig:Ha_profile_MUSE}}
 				\label{fig:Ha_profile_MUSE}
@@
 To check if the ionizing radiation is entirely due to an AGN throughout the host galaxy, we plot the H$\alpha$ and H$\beta$ flux radial profiles for the MUSE and VIMOS data in Figs.\,\ref{fig:Ha_profile_MUSE} and \ref{fig:Hb_profile_VIMOS}, respectively.
-A point source, such as an AGN, will result in a profile having a $r^{-2}$ shape, where $r$ is the distance of the bin from the galaxy centre.
-A shallower profile points to a spatially-extended source, presumably non-circumnuclear stellar processes such as star formation or radiation from pAGB stars, as the dominant cause of the ionization in the outer parts of the galaxy (i.e.\ LIER rather than LINER).
-All the galaxies with spatially-extended Balmer emission in our Southern Sample reveal a central point source as the dominant source of the ionizing photons.
+A point source, such as an AGN, will result in a $r^{-2}$ profile (convolved with the point-spread function; PSF), where $r$ is the distance of the bin from the galaxy centre.
+A shallower profile points to a spatially-extended source, presumably non-circumnuclear stellar processes such as star formation or radiation from pAGB stars, as the dominant cause of the ionization in the outer parts of the galaxy (i.e.\ a LIER rather than LINER).
+
+			The profiles are shown in Figs.\,\ref{fig:Ha_profile_MUSE} and \ref{fig:Hb_profile_VIMOS} which show that all the galaxies with spatially-extended Balmer emission in our Southern Sample reveal a central point source as the dominant source of the ionizing photons.
 The H$\beta$ profile of NGC 612 has a larger scatter suggesting that stellar processes also have some impact (likely radiation from pAGB stars, as these galaxies are ETGs and therefore likely have low star-formation rates).
@@
 We use here the calibrations by \citet{Nyland2016}, including an attempt to separate LINERs powered by AGN from those powered by pAGB stars (the former have [\ion{O}{iii}] equivalent widths $>0.8$\,\AA).
-We use an aperture of 3\arcsec\ to plot the nuclear MEx for our Southern Sample galaxies, and the resulting diagnostic plot is shown in Fig.\,\ref{fig:MEx}.
+We focus on the nuclear region by using an aperture of 3\arcsec\ placed on our Southern Sample galaxies.
+The resulting diagnostic plot is shown in Fig.\,\ref{fig:MEx}.
 
@@
 
-	Overall, we thus find that the warm ISM properties of our Southern Sample galaxies are consistent with those of other optically-selected ETGs.
+	Overall, we find that the warm ISM properties of our Southern Sample galaxies are consistent with those of other optically-selected ETGs.
 This is consistent with low-powered radio galaxies being bona-fide detections of jet-mode AGN and therefore our sample galaxies are ordinary massive ETGs experiencing a normal but short-lived active phase, presumably due to the central black holes currently accreting gas in some form.
@@
 	respectively.
-Since it is sometimes observed that [\ion{N}{ii}]/H$\alpha < 1.80$, which if blindly applying the relationship found above, results in an unphysical [\ion{N}{i}]/H$\beta < 0$ (i.e.\ negative flux), we instead rearrange and use
+Since it is sometimes observed that [\ion{N}{ii}]/H$\alpha < 1.80$, which if blindly applying the relationship found above, results in an unphysical [\ion{N}{i}]/H$\beta < 0$ (i.e.\ negative flux), we instead use
 	\begin{equation}

### 2019-08-26 paper.tex
Changes from Martin - his notes are in {\bf ...}
 On branch master
 Changes to be committed:
	modified:   paper.tex
	modified:   refs.bib

--- 2018-11-10 paper.tex
@@
 % Keep the title short and informative.
-\title[An IFS study of Low-powered Radio Galaxies]{An IFS study of Low-powered Radio Galaxies}
+\title[IFS Study of Low-power Radio Galaxies]{An Integral-field
+  Spectroscopic Study of Low-power Radio Galaxies}
 
@@
 \author[J. Warren et al.]{
-Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:warrenj@gmx.com}{warrenj@gmx.com}}
+  Joshua Warren,$^{1}$\thanks{Contact e-mail:
+    \href{mailto:warrenj@gmx.com}{warrenj@gmx.com}}
 %Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:joshua.warren@physics.ox.ac.uk}{joshua.warren@physics.ox.ac.uk}}
-Martin Bureau,$^{1}$
-Bernd Hasemann,$^{2}$
-Isabella Prandoni,$^{3}$ \newauthor
-Francesco Santoro,$^{3}$
-Robert Laing,$^{3}$
-Paola Parma,$^{3}$
-Hans de Ruiter$^{3}$
-and \newauthor
-Arturo Mignano$^{3}$
+  Martin Bureau,$^{1,2}$ Bernd Hasemann,$^{3}$ Isabella
+  Prandoni,$^{4}$ \newauthor Francesco Santoro,$^{4}$ Robert
+  Laing,$^{4}$ Paola Parma,$^{4}$ Hans de Ruiter$^{4}$ and \newauthor
+  Arturo Mignano$^{4}$
   \\
-$^{1}$Sub-department of Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, UK\\
-$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. München, Germany\\
-$^{3}$INAF - Istituto di Radioastronomia, Via P. Gobetti 101, 40129 Bologna, Italy}
+  $^{1}$Sub-department of Astrophysics, Department of Physics,
+  University of Oxford, Denys Wilkinson Building, Keble Road, Oxford
+  OX1 3RH, UK\\
+  $^{2}$Yonsei Frontier Lab and Department of Astronomy, Yonsei
+  University, 50 Yonsei-ro, Seodaemun-gu, Seoul 03722, Republic of
+  Korea\\
+  $^{3}$European Southern Observatory, Karl-Schwarzschild-Str.\ 2,
+  85748 Garching b.\ M{\"u}nchen, Germany\\
+  $^{4}$INAF - Istituto di Radioastronomia, Via P.\ Gobetti 101, 40129
+  Bologna, Italy\\
+  $^*${\bf Should you/we add Ilaria Ruffa and/or Rosita Paladino
+    and/or Timothy Davis as authors (they are all on the first/ALMA
+    paper)?}\\{\bf I feel it is a little strange that Ilaria is not (so I
+    would argue we should add her), I am much less sure about
+    Rosita,}\\ {\bf and I suspect it is ok that Tim is not. Your call
+    though. Also needed are updated affiliations for Francesco and
+    Robert.}}
 
@@
 \begin{abstract}
-The most powerful radio galaxies are well studied with a strong consensus in the literature regarding their formations processes.
-However, they are intrinsically rare objects and not representative of the general population of radio galaxies.
-Low-powered radio galaxies are comparatively poorly studied with many conflicting viewpoints regarding their origin and the extent of the effect of feedback from them.
-
-We present a complete sample of 11 nearby low-powered radio galaxies, observed with a suite of instruments.
-This paper focuses on the spatially-resolved stellar kinematics and populations, and ionized gas distribution, kinematics and ionization derived from optical IFS observations%, while other observation such as \ce{^{12}CO(2-1)} from Atacama Large Millimetre/sub-millimetre Array (ALMA) and radio continuum from the Very Large Array (VLA) will be presented in future papers
-.
-We compare the characteristics and properties of our sample to those of ordinary (i.e.\ optically-selected) ETGs using the Atlas$^\text{3D}$ and MASSIVE IFS surveys.
-These include the fast/slow rotator classification fraction, kinematic substructures, absorption line strength radial gradients, general stellar population properties, ionized gas distribution and kinematics and the dominant source of ionizing photons.
-
-We tentatively find that our radio-selected ETGs contain a higher mass in of ionized gas than expected.
-However, after accounting for the differences in the mass distribution, we find no further differences between the two samples in the characteristics that can be studied with optical IFU data.
-We suggest that this is consistent with the notion that low-powered radio galaxies are ordinary ETGs experiencing a brief active phase which maintains their low star-formation rates (also known as maintenance or jet-mode AGN).
+  Although they are intrinsically rare and not representative of the
+  general population of radio galaxies, the most powerful radio
+  galaxies are well studied, with a strong consensus regarding their
+  formation processes. Despite being much more numerous, low-power
+  radio galaxies are comparatively poorly studied, with many
+  conflicting viewpoints regarding their origin and the importance of
+  feedback within them. Here we present a complete sample of $11$
+  nearby low-power radio galaxies, observed with a suite of
+  instruments. We focus on the spatially-resolved stellar kinematics
+  and populations, as well as the ionised gas distribution, kinematics
+  and ionisation mechanisms derived from optical integral-field
+  spectroscopic (IFS) observations.
+  % , while other observation such as \ce{^{12}CO(2-1)} from Atacama
+  % Large Millimetre/sub-millimetre Array (ALMA) and radio continuum
+  % from the Very Large Array (VLA) will be presented in future papers.
+  We compare the characteristics of our targets to those of ordinary
+  (i.e.\ optically-selected) early-type galaxies from other IFS
+  surveys.
+  % using the Atlas$^\text{3D}$ and MASSIVE IFS surveys.
+  Properties probed include the fast/slow rotator classification
+  fraction, kinematic sub-structures, absorption line strength radial
+  gradients, general stellar population properties, ionised gas
+  distribution and kinematics, and the dominant sources of ionising
+  photons. We tentatively find that our radio-selected early-types
+  contain a higher mass of ionised gas than expected. However, after
+  accounting for the differences in their mass distributions, we find
+  no further difference between the different samples in terms of the
+  characteristics that can be studied with optical IFSs. We suggest
+  that this is consistent with the notion that low-power radio
+  galaxies are ordinary early-type galaxies experiencing a brief
+  active phase that maintains their low star-formation rates (also
+  known as maintenance- or jet-mode active galactic nuclei).
 \end{abstract}
@@
 \label{sec:intro}
-	It is becoming increasingly clear that active galactic nuclei (AGN) can be separated into two different types, radiative and jet mode AGN \citep[e.g.][]{Antonucci2012, Heckman2014}, raising speculation about differing mechanisms and possibly fuel sources for each.
-The former is thought to be the powerful engine that initially and rapidly shuts off star formation in massive early-type galaxies (ETGs; e.g.
-\citealt{Thomas2005, Thomas2010}), either by removing the cold gas from the galaxy entirely, heating it such that it joins the hot X-ray gas often present in massive galaxies \citep[e.g.][]{OSullivan2001}, or rendering it unusable for star formation (such as by stabilising it against collapse; e.g.\ \citealt{Martig2009}).
-After a single radiative-mode episode, the AGN is thought to subside to become jet-dominated, repeatedly reheating the surrounding interstellar medium (ISM) to counter any cooling that might allow the cold gas reservoir to replenish (and subsequently form stars).
-
-	There is a strong consensus within the scientific literature that the most powerful radio galaxies are the result of gas-rich, major mergers causing large amounts of material to fall on to the black hole at the centre of the resulting galaxy, thus producing an immensely powerful AGN which includes a powerful radio jet \citep[e.g.][]{Malin1983, Quillen1992, Lim2000}.
-However, such galaxies are extremely rare and are not representative of the general radio galaxy population.
-Most radio galaxies are low-powered, and their basic properties and origins are poorly constrained.
-One of the most popular suggestions is that they are bona-fide detections of jet-mode AGN \citep[e.g.][]{Heckman2014}.%, a class of AGN thought to maintain the dearth of star formation in early-type galaxies (ETGs), after most of the fuel for star formation has been removed by an earlier event.
-	These radio galaxies are known to be dusty with dust lanes having a tendency to be perpendicular to the jets \citep[e.g.][]{DeRuiter2002, VerdoesKleijn2005}.
-They have little ionized gas in the ISM \citep[e.g.][]{Sarzi2005}, but often have significant quantities of hot X-ray gas (e.g.
-\citealt{Canizares1987}; the cold phase of the ISM of radio galaxies will be examined in Ruffa et.al.\ in prep.).
-If the low star-formation rates typically seen in massive ETGs are preserved by jet-mode AGN, then all such ETGs must regularly go through similar active phases, and therefore low-powered radio galaxies should be much the same as their radio-quiet (quiescent phase) ETG counterparts.
-
-	To test this hypothesis, a complete sample of 11 nearby low-powered radio galaxies was constructed by \citet{Prandoni2010} and observed with a suite of instruments.
-Here, we present the spatially-resolved stellar kinematics and populations, and ionized gas distribution, kinematics and ionization derived from integral-field spectroscopic (IFS) observations with the Visible Multi-object Spectrograph (VIMOS) and archival data from the Multi-unit Spectroscopic Explorer (MUSE), both on the Very Large Telescope (VLT).
-We compare the characteristics and properties (accessible with $V$-band IFS data) of our sample of low-power radio galaxies to those of ordinary (i.e.\ optically-selected) ETGs from the Atlas$^\text{3D}$ and MASSIVE IFS surveys.
-We hereafter refer to the combined Atlas$^\text{3D}$ \citep{Cappellari2011} and MASSIVE \citep{Ma2014} sample as the A+M sample.
-
-	In Section \ref{sec:samp} of this paper we set out the compete sample with our observations and data-reduction methods detailed in Section \ref{sec:obs}.
-Our data-analysis methods and routines are detailed in Section \ref{sec:analysis} (the maps of our sample produced with these methods are shown in Appendix \ref{sec:maps}).
-We present our findings regarding the stellar kinematics, absorption line strengths, stellar populations, ionized gas (distribution, kinematics and ionization) in Sections \ref{sec:StarKine}-\ref{sec:gas}, respectively.
-Finally, we discuss our results and conclude in Section \ref{sec:discuss}.
+
+It is becoming increasingly clear that active galactic nuclei (AGN)
+can be separated into two different types, radiative- and jet-mode AGN
+\citep[e.g.][]{Antonucci2012, Heckman2014}, raising speculation about
+differing mechanisms and possibly fuel sources for
+each. Radiative-mode AGN are thought to be the powerful engines that
+initially and rapidly shut off star formation in massive early-type
+galaxies (ETGs; e.g.\ \citealt{Thomas2005, Thomas2010}), by either
+removing the cold gas from the galaxy entirely, or by heating it such
+that it joins the hot (X-ray) gas often present in massive galaxies
+\citep[e.g.][]{OSullivan2001}.
+% , or rendering it unusable for star formation (such as by
+% stabilising it against collapse; e.g.\ \citealt{Martig2009}).
+After a single radiative-mode episode, the AGN is thought to subside
+to become jet-dominated, the jet repeatedly reheating the surrounding
+interstellar medium (ISM) to counter any cooling that might allow the
+cold gas reservoir to replenish (and subsequently form stars).
+
+There is a strong consensus in the literature that the most powerful
+radio galaxies are the result of gas-rich major mergers, that cause
+large amounts of material to fall on to the black hole at the centre
+of the resulting galaxy, thus producing an immensely powerful AGN that
+includes a powerful radio jet \citep[e.g.][]{Malin1983, Quillen1992,
+  Lim2000}. However, such galaxies are extremely rare and are not
+representative of the general radio galaxy population. Most radio
+galaxies are low powered, and their basic properties and origins are
+poorly constrained. One of the most popular suggestions is that they
+are bona-fide detections of jet-mode AGN \citep[e.g.][]{Heckman2014}.
+% , a class of AGN thought to maintain the dearth of star formation in
+% early-type galaxies (ETGs), after most of the fuel for star
+% formation has been removed by an earlier event.
+These low-power radio galaxies are known to be dusty, the dust lanes
+having a tendency to be perpendicular to the jets
+\citep[e.g.][]{DeRuiter2002, VerdoesKleijn2005}. They have little
+ionised gas \citep[e.g.][]{Sarzi2005}, but often have significant
+quantities of hot X-ray gas \citep[e.g.][]{Canizares1987}. The
+molecular ISM of our sample galaxies has already been examined in
+\citet{ruffa2019, ruffa2020}. If the low star-formation rates
+typically seen in massive ETGs are preserved by jet-mode AGN, then all
+these ETGs must regularly go through similarly active phases, and
+therefore low-power radio galaxies should be much the same as their
+radio-quiet (quiescent phase) ETG counterparts.
+
+To test this hypothesis, a complete sample of $11$ nearby low-power
+radio galaxies was constructed by \citet{Prandoni2010} and observed
+with a suite of instruments. Here, we present the spatially-resolved
+stellar kinematics and populations, as well as the ionised gas
+distribution, kinematics and ionisation mechanisms derived from
+integral-field spectroscopic (IFS) observations with the Visible
+Multi-object Spectrograph (VIMOS) and archival data from the
+Multi-unit Spectroscopic Explorer (MUSE), both on the Very Large
+Telescope (VLT). We then compare the characteristics (accessible with
+$V$-band IFS data) of our low-power radio galaxies to those of
+ordinary (i.e.\ optically-selected) ETGs from the Atlas$^\text{3D}$
+\citep{Cappellari2011} and MASSIVE \citep{Ma2014} IFS surveys. We
+hereafter refer to the combined Atlas$^\text{3D}$ and MASSIVE sample
+as the A+M sample.
+
+The structure of this paper is as follows. We describe our complete
+sample of low-power early-type radio galaxies in
+Section~\ref{sec:samp}, and present our observations and data
+reduction strategies in Section~\ref{sec:obs}. Our data analysis
+methods and routines are detailed in Section~\ref{sec:analysis}, while
+the various maps of our sample galaxies thereby produced are shown in
+Appendix~\ref{sec:maps}. Our findings regarding the stars (kinematics,
+absorption line strengths and populations) and ionised gas
+(distribution, kinematics and ionisation mechanisms) are presented in
+Sections~\ref{sec:StarKine}-\ref{sec:gas}. Our results are discussed
+in Section~\ref{sec:discuss}, where we also conclude briefly.
 
@@
 \label{sec:samp}
-	The Parkes 2.7 GHz survey \citep{Ekers1989} was used as a parent sample, as it contains radio sources (down to a flux density limit of 250\,mJy at 2.7\,GHz) with an optical counterpart (with an $V$-band apparent magnitude of $m_V \le 17.0$).
-Host galaxies with a redshift greater than 0.03 were discarded.
-It is worth noting that both the radio and optical limits are apparent measurements, and as such this is not a volume-limited sample.
-
-	\begin{table*}
-		\centering
+
+The Parkes $2.7$~GHz survey \citep{Ekers1989} was used as a parent
+sample from which to select our target galaxies, as it contains radio
+sources (down to a flux density limit of $250$~mJy at $2.7$~GHz) with
+an optical counterpart (with an integrated $V$-band apparent magnitude
+$m_V\le17.0$). Host galaxies with a redshift greater than $0.03$ were
+discarded. These criteria lead to a sample of $11$ galaxies, hereafter
+referred to as our Southern Sample, whose key characteristics are
+summarised in Table~\ref{tab:sample}. All galaxies have a FR~I radio
+morphology according to the \citet{Fanaroff1974} scheme. It is worth
+noting that both the radio and optical limits are based on apparent
+fluxes, so this is not a volume-limited sample.
+
+\begin{table*}[t]
+  \begin{center}
     % \begin{threeparttable}
-		\caption{Key characteristics of the Southern Sample galaxies.
-Col.\,1: host galaxy name.
-Col.\,2: radio source name from Parkes Southern Radio Source Catalogue.
-We hereafter refer to the last galaxy by its PKS name only.
-Col.\,3: redshift.
-Col.\,4: National Radio Astronomy Observatory (NRAO) VLA Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}.
-Col.\,5: Two Micron All Sky Survey (2MASS) $K$-band apparent magnitude (with errors of $\pm 0.025$ mag; \citealt{Skrutskie2006}).
-Col.\,6: dust morphologies from (a) \citet{Govoni2000}, (b) \citet{Lauer2005}, (c) \citet{Bettoni2001}, (d) \citet{Sandage1979}, (e) \citet{Colbert2001}.}
+    \caption{Key characteristics of our Southern Sample galaxies.}
     \label{tab:sample}
-		\begin{tabular}{l c c c c l}
+    \begin{tabular*}{0.7\textwidth}{@{\extracolsep{\fill}}l c c c c l}
       \hline
@@
       \hline 
-			ESO 443-G024 & 1258-321 	& 0.01703	& $1387 \pm 45$		& 8.51 & no dust$^{a}$	\\ 
-			IC 1459 	& 2254-367 		& 0.00565 	& $1280 \pm 45$		& 6.81 & dust lane$^{b}$	\\
-			IC 1531 	& 0007-325 		& 0.02553 	& \leavevmode\phantom{0}$388 \pm 12$		& 9.55 & --					\\
-			IC 4296		& 1333-\leavevmode\phantom{0}33 		& 0.01248 	& $1342 \pm 41$		& 7.50 & edge-on disc$^{b}$ \\
-			NGC 612 	& 0131-\leavevmode\phantom{0}36 		& 0.02954 	& \leavevmode\phantom{0}$585 \pm 18$		& 9.58 & dust lane$^{c}$	\\
-			NGC 1316 	& 0320-\leavevmode\phantom{0}37 & 0.00591 	& \leavevmode\phantom{0}$255 \pm 10$		& 5.59 & dust patches$^{b}$ \\
-			NGC 1399 	& 0336-\leavevmode\phantom{0}35 & 0.00472 	& \leavevmode\phantom{0}$209 \pm \leavevmode\phantom{0}7$	& 6.31 & no dust$^{b}$	\\
-			NGC 3100 	& 0958-314 		& 0.00879 	& \leavevmode\phantom{0}$530 \pm 16$		& 8.08 & dust lane$^{d}$	\\
-			NGC 3557 	& 1107-372 		& 0.01016 	& \leavevmode\phantom{0}$484 \pm 16$		& 7.20 & face-on disc$^{b}$\\
-			NGC 7075 	& 2128-388 		& 0.01819 	& \leavevmode\phantom{0}$837 \pm 28$		& 9.56 & --					\\
-			--			& 0718-\leavevmode\phantom{0}34 		& 0.02897 	& $1119 \pm 41$		& 9.97 & dust patches$^{e}$ \\
-			\hline
-			\hline
-		\end{tabular}
+      ESO~443-G024 & 1258-321 & $0.01703$ & $1387\pm45$ & $8.51$ & no dust$^\text{a}$\\ 
+      IC~1459 & 2254-367 & $0.00565$ & $1280\pm45$ & $6.81$ & dust lane$^\text{b}$\\
+      IC~1531 & 0007-325 & $0.02553$ & $\leavevmode\phantom{0}388\pm12$ & $9.55$ & --\\
+      IC~4296 & 1333-\leavevmode\phantom{0}33 & $0.01248$	& $1342\pm41$ & $7.50$ & edge-on disc$^\text{b}$\\
+      NGC~612 & 0131-\leavevmode\phantom{0}36 & $0.02954$ & $\leavevmode\phantom{0}585\pm18$ & $9.58$ & dust lane$^\text{c}$\\
+      NGC~1316 & 0320-\leavevmode\phantom{0}37 & $0.00591$ & $\leavevmode\phantom{0}255\pm10$ & $5.59$ & dust patches$^\text{b}$\\
+      NGC~1399 & 0336-\leavevmode\phantom{0}35 & $0.00472$ & $\leavevmode\phantom{0}209\pm\leavevmode\phantom{0}7$ & $6.31$ & no dust$^\text{b}$\\
+      NGC~3100 & 0958-314	& $0.00879$ & $\leavevmode\phantom{0}530\pm16$ & $8.08$ & dust lane$^\text{d}$\\
+      NGC~3557 & 1107-372 & $0.01016$ & $\leavevmode\phantom{0}484\pm16$ & $7.20$ & face-on disc$^\text{b}$\\
+      NGC~7075 & 2128-388 & $0.01819$ & $\leavevmode\phantom{0}837\pm28$ & $9.56$ & --\\
+      -- & 0718-\leavevmode\phantom{0}34 & $0.02897$ & $1119\pm41$ & $9.97$ & dust patches$^\text{e}$\\
+      \hline
+      \hline
+    \end{tabular*}
     % \begin{tablenotes}
-	% 	\footnotesize
-	% 	\note Col.\,1: host galaxy name.
-Col.\,2: radio source name from Parkes Southern Radio Source Catalogue.
-Col.\,3: redshift.
-Col.\,4: National Radio Astronomy Observatory (NRAO) Very Large Array (VLA) Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}.
-Col.\,5: Two Micron All Sky Survey (2MASS) $K$-band apparent magnitude (with errors of $\pm 0.025$ mag; \citealt{Skrutskie2006}).
-Col.\,6: dust morphologies from (a) \citet{Govoni2000}, (b) \citet{Lauer2005}, (c) \citet{Bettoni2001}, (d) \citet{Sandage1979}, (e) \citet{Colbert2001}.
-	% 	\item We hereafter refer to the last galaxy by its PKS name only.
+    \parbox[t]{0.7\textwidth}{\footnotesize\textit{Notes:} Col.~1:
+      galaxy name. Col.~2: radio source name from the Parkes Southern
+      Radio Source Catalogue (PKS). We hereafter refer to the last
+      galaxy by its PKS name only. Col.~3: redshift. Col.~4: National
+      Radio Astronomy Observatory (NRAO) VLA Sky Survey (NVSS)
+      $1.4$~GHz flux density \citep{Condon1998}. Col.~5: Two Micron
+      All Sky Survey (2MASS) $K$-band apparent magnitude (with
+      uncertainties of $\pm0.025$~mag;
+      \citealt{Skrutskie2006}). Col.~6: dust morphology from (a)
+      \citet{Govoni2000}, (b) \citet{Lauer2005}, (c)
+      \citet{Bettoni2001}, (d) \citet{Sandage1979} and (e)
+      \citet{Colbert2001}.}
     % \end{tablenotes}
     % \end{threeparttable}
+  \end{center}
 \end{table*}
 
-	These criteria lead to a sample of 11 galaxies hereafter referred to as the Southern Sample.
-The key observed characteristics are summarised in Table \ref{tab:sample}.
-All galaxies have a FR I radio morphology according to the \citet{Fanaroff1974} scheme.
-
-	The sample was initially observed with the Atacama Pathfinder Experiment \citep[APEX; ][]{Gusten2006}, with detections claimed for the \ce{^{12}CO(2-1)} transition for all galaxies.
-Some galaxies had extremely large line widths (up to a full-width half-maximum of $904 \, \mathrm{km \, s^{-1}}$ for IC 4296), but most showed a flat or double-horn spectrum indicative of ordered rotation \citep{Prandoni2012}.
-
-\section{Observing strategy and Data Reduction}
+Our Southern Sample was initially observed with the Atacama Pathfinder
+Experiment \citep[APEX; ][]{Gusten2006}, with a detection claimed in
+the \ce{^{12}CO(2-1)} transition for every galaxy
+\citep{Prandoni2012}. Some galaxies had an extremely large line width
+(up to a full width at half-maximum of $904$~km~s$^{-1}$ for IC~4296),
+but most showed a flat or double-horn spectrum suggestive of ordered
+rotation. Follow-up Atacama Large Millimeter/sub-millimeter Array
+(ALMA) observations were recently presented in \citet{ruffa2019,
+  ruffa2020}.
+
+\section{Observing Strategy and Data Reduction}
 \label{sec:obs}
-	The sample has been observed with a suit of instruments spanning the radio to optical wavelengths (archival images from the \textit{Chandra space telescope} are also available for some of the sample).
-This paper focuses on the optical IFS observations made with VIMOS, mounted on the VLT in Paranal \citep{LeFevre2003}.
-All observations were taken with a spatial sampling of $0\farcs67$, using the high-resolution blue grism yielding a wavelength range of 3700-5520\,\AA\ with a spectral resolution of 1440 and sampling of 0.71\,\AA\,$\mathrm{pix^{-1}}$.
-Each object was observed with a total integration time of $\approx 100$\,min on-source, equally spread over three observing blocks (OBs).
-Each OB also contained all the necessary observation for standard IFS data reduction.
-
-	VIMOS has several well-known though poorly-understood technical issues.
-These include several low transmission (bad) fibres, strong flexure, contamination from adjacent spectra on the CCD (cross-talk) and large differences in sensitivity across its 4 quadrants.
-To address these issues, we adopted a data-reduction pipeline produced using \textsc{Py3D}, a suite of programs based on the \textsc{python} versions of those developed for the Calar Alto Legacy Integral Field spectroscopy Area survey \citep[CALIFA;][]{Sanchez2012, Husemann2013} but later updated for VIMOS by \citet{Husemann2014}.
-\textsc{Py3D} applies all standard IFS data-reductions steps: bias subtraction, spectrum identification, flatfielding and wavelength calibration.
-In addition, the data was flux calibrated using publicly available observations of the spectro-photometric standard star Feige 110 provided by the European Southern Observatory (ESO).
-All steps include methods designed to account for the bad fibres, flexure and cross-talk within VIMOS.
-
-	Following this, we noted that the cubes were still not properly calibrated.
-Three main issues remain: the quadrants have different intensities, clearly showing uncorrected throughput differences; diagonal intensity stripes are present in the reconstructed images at all wavelengths; and spectral features are observed \citep{Jullo2008} that are visually similar to fringe patterns caused by interference within the CCD between incident light and light reflected from the interfaces between layers of the CCD materials.
-\citet{Lagerholm2012} present ad-hoc methods to correct for these issues, which we here adopt.
-These additional steps mean that the datacubes are not perfectly flux-calibrated, but all the corrections are multiplicative and thus will not effect equivalent width or line ratio measurements.
-From comparisons to the MUSE data (see Section \ref{subsec:MUSE}), we then estimate the flux calibration of the resulting datacubes.
-
-	These method are not completely effective and some artefacts are still present in the data, however in most cases the data is of sufficient quality for our purposes.
-For the worst effected datacubes, we have archival MUSE observations (see Section \ref{subsec:MUSE}).
-
-	The variance spectra are propagated throughout the data-reduction pipeline (including these ad-hoc corrections) and are square-rooted at this point, to be used as noise inputs in the following analyses (see Section \ref{sec:analysis}).
+
+\subsection{New VIMOS Data}
+\label{subsec:VIMOS}
+
+We have observed our Southern Sample targets with a suite of
+instruments spanning radio to optical wavelengths. Archival X-ray
+images from the \textit{Chandra space telescope} are also available
+for some of the sample galaxies. This paper focuses on optical IFS
+observations carried out with VIMOS, mounted on the VLT
+\citep{LeFevre2003}. All observations were obtained with a spatial
+sampling of $0\farcs67$, using the high-resolution blue grism yielding
+a wavelength range of $3700$--$5520$~\AA\ with a spectral resolution
+of $1440$ and a spectral sampling of $0.71$~\AA\ per pixel. Every
+object was observed with a total integration time of $\approx100$~min
+on-source, equally spread over three observing blocks (OBs). Each OB
+also contained all necessary observations for standard IFS data
+reduction.
+
+VIMOS has several well-known though poorly-understood technical
+problems. These include several low transmission (bad) fibres, strong
+flexure, contamination from adjacent spectra on the charged coupled
+device (CCD; cross-talk) and large differences of sensitivity across
+its four quadrants. To address these issues, we adopted a
+data-reduction pipeline built using \textsc{Py3D}, a suite of
+programmes based on the \textsc{python} versions of the codes
+developed for the Calar Alto Legacy Integral-field Spectroscopy Area
+survey \citep[CALIFA;][]{Sanchez2012, Husemann2013}, but later updated
+for VIMOS by \citet{Husemann2014}. \textsc{Py3D} applies all standard
+IFS data-reductions steps: bias subtraction, spectrum identification,
+flatfielding and wavelength calibration. The data were flux calibrated
+using publicly available observations of the spectro-photometric
+standard star Feige~110 provided by the European Southern Observatory
+(ESO). All steps include procedures designed to account for the bad
+fibres, flexure and cross-talk within VIMOS.
+
+Following this, we noted that the cubes were still not properly
+calibrated. Three main issues remained: the four quadrants had
+inconsistent intensities (clearly showing uncorrected throughput
+differences), diagonal intensity stripes were present in the
+reconstructed images at all wavelengths, and spectral features were
+observed that are visually similar to fringe patterns caused by
+interference within the CCD (between incident light and light
+reflected at the interfaces of the CCD layers;
+\citealt{Jullo2008}). \citet{Lagerholm2012} presented ad-hoc methods
+to correct for these issues, that we also adopt here. These additional
+steps result in datacubes that are not perfectly flux-calibrated, but
+all the corrections are multiplicative and will therefore not affect
+equivalent width or line ratio measurements. From comparisons to MUSE
+data of the same objects (see Section~\ref{subsec:MUSE}), we can
+assess the flux calibration of the resulting datacubes.
+
+Even these steps were unfortunately not totally effective, but we were
+unable to further improve the data reduction. Some artefacts remain in
+the data, but in most cases the data are of sufficient quality for our
+purposes. For the worst affected datacubes, we fortunately have
+alternative archival MUSE observations (see
+Section~\ref{subsec:MUSE}).
+
+The variance spectra are propagated throughout the data reduction
+pipeline (including the aforementioned ad-hoc corrections) and are
+square-rooted at this point, to be used as noise inputs in the
+following analyses (see~Section \ref{sec:analysis}).
 
@@
 \label{subsec:MUSE}
-		Four of the sample galaxies are in the MUSE archive: IC 1459, IC 4296, NGC 1316 and NGC 1399.
-We include these in our analysis as they have better (spatial and spectral) resolution and sampling, a larger field-of-view and larger wavelength range than the VIMOS data.
-
-		We used the pre-reduced (Phase 3) datacubes from ESO.
-These were generally of sufficient quality for our purpose, except in both IC 1459 and IC 4296 the sky appears to have been over-subtracted.
-To remove this over-subtraction, we developed our own pseudo-sky subtraction routine.
-A median spectrum was taken from four $20 \times 20$\,spaxel regions, one in each spatial corner of the ESO reduced cube.
-After checking that no stellar continuum could be fit to the median sky spectrum (i.e.\ that very little light from the galaxy is contaminating the pseudo-sky regions), this median sky spectrum was subtracted from each spaxel in the cube.
-
-		Finally, we trimmed all the MUSE cubes to the central $30\arcsec \times 30\arcsec$ ($150 \times 150$\,spaxels) only, to (a) avoid the regions used for the pseudo-sky spectrum and (b) reduce the computing resources required for spatial binning (see Section \ref{sec:analysis}).
-In any case, the bins would likely be so large in the outer parts as to be effectively useless.
+
+Four of our Southern Sample galaxies have archival MUSE data analogous
+to our VIMOS data: IC~1459, IC~4296, NGC~1316 and NGC~1399. We include
+these data in our analysis as they have better spatial and spectral
+resolutions and samplings, larger fields-of-view, larger wavelength
+ranges, and better signal-to-noise ratios ($S/N$) than the VIMOS
+data. There is also no significant issue with the data reduction.
+
+We used the pre-reduced (Phase~3) datacubes from ESO. These were
+generally of sufficient quality for our purpose, except for IC~1459
+and IC~4296, for which the sky appears to have been
+over-subtracted. To remedy this over-subtraction, we developed our own
+pseudo-sky subtraction routine. For each galaxy, a median spectrum was
+taken from four $20\times20$ spaxel$^2$ regions, one in each spatial
+corner of the ESO reduced cube. After checking that no stellar
+continuum could be fit to this median sky spectrum (i.e.\ that very
+little galaxy light contaminates the pseudo-sky regions), this
+spectrum was subtracted from each spaxel in the cube.
+
+Finally, we trimmed all the MUSE cubes to the central
+$30\arcsec\times30\arcsec$ ($150\times150$ spaxels$^2$) only, to (a)
+exclude the regions used for pseudo-sky subtraction and (b) reduce the
+computing resources required for spatial binning (see
+Section~\ref{sec:analysis}). In any case, the bins would likely be so
+large in the outer parts as to be effectively useless.
 
@@
 \label{sec:analysis}
-	Both VIMOS and MUSE datasets are spatially binned using Voronoi binning\footnote{http://www-astro.physics.ox.ac.uk/~mxc/software/} \citep{Cappellari2003} and from this point on are treated almost identically, the only difference (other than the different spectral ranges and resolutions) being that the MUSE datacubes are spatially binned to a higher signal-to-noise ratio (S/N).
-For our purposes, we define the `signal' and `noise' of each spaxel as the median value of its spectrum and noise spectrum, respectively.
-We require a S/N of 30 for all VIMOS datacubes and 50 for the IC 1459 and IC 4296 MUSE datacubes.
-The NGC 1316 and NGC 1399 MUSE datacubes were binned to a S/N of 50 for the analysis of the stellar kinematics and 100 for the analysis of the emission line kinematics and stellar populations.
-These target S/N were chosen in order to be as low as possible, while still returning meaningful information (as assessed by eye).
-
-	Next we implement a routine to find optimal initial values of the redshift and velocity dispersion for each galaxy, to be used when fitting individual bins, by means of iterative fits to the spatially collapsed (i.e.
-summed across both spatial dimensions of the datacube) spectrum.
-We use the penalized-fitting (\textsc{pPXF}) routine\footnotemark[1] of \citet{Cappellari2004} and \citet{Cappellari2016a} with the Medium-resolution Isaac Newton Telescope (INT) Library of Empirical Spectra (MILES) library \citep{Sanchez-Blazquez2006, Falcon-Barroso2011a} to find the best-fitting line-of-sight stellar velocity distribution (LOSVD; as parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion).
-The final mean velocity of a given galaxy, is used as its precise spectroscopic redshift and is given in Table \ref{tab:sample}.
-Beyond this point, each bin is analysed independently.
-
-	It was noted that for the MUSE observations of NGC 1316, the NaD absorption feature (which as generally attributed to absorption from the ISM and is thus affected by the kinematics of the ISM) was significantly effecting the quality of the stellar best-fitting spectrum.
-For this reason, the wavelength range of NGC 1316 spectra was limited to $<5800 \, \AA$ whilst fitting for the stellar spectra only.
+
+Both the VIMOS and MUSE datasets were spatially-binned using Voronoi
+binning\footnote{http://www-astro.physics.ox.ac.uk/~mxc/software/}
+\citep{Cappellari2003} and from this point on were treated almost
+identically, the only difference (other than the different spectral
+ranges and resolutions) being that the MUSE datacubes could and were
+spatially-binned to higher $S/N$. For our purposes, we define the
+`signal' and `noise' of each spaxel as the median value of its
+spectrum and noise spectrum, respectively. For each bin, we require
+$S/N\ge30$ for all VIMOS datacubes and $S/N\ge50$ for the IC~1459 and
+IC~4296 MUSE datacubes. The NGC~1316 and NGC~1399 MUSE datacubes were
+binned to $S/N\ge50$ for the stellar kinematics analysis and
+$S/N\ge100$ for the the emission line kinematics and stellar
+population analyses. These $S/N$ targets were chosen to be as low as
+possible while still yielding useful maps (assessed by eye).
+
+Next we implemented a routine to find the optimal initial values of
+the redshift and velocity dispersion for each galaxy, to be used
+subsequently when fitting individual bins. We used iterative fits to
+the spatially-collapsed spectrum of each galaxy, i.e.\ the spectrum
+resulting from summing across both spatial dimensions of the
+datacube. We utilised the penalized pixel fitting (\textsc{pPXF})
+routine\footnotemark[1] of \citet{Cappellari2004} and
+\citet{Cappellari2016a} with the Medium-resolution Isaac Newton
+Telescope (INT) Library of Empirical Spectra (MILES;
+\citealt{Sanchez-Blazquez2006, Falcon-Barroso2011a}) to find the
+best-fitting line-of-sight stellar velocity distribution (LOSVD) of
+each collapsed spectrum, as parametrised by the Gaussian parameters
+$V$, the mean velocity, and $\sigma$, the velocity dispersion. The
+final mean stellar velocity of each galaxy is adopted as its precise
+spectroscopic redshift and is listed in Table~\ref{tab:sample}. {\bf
+  (Shouldn't there be an uncertainty on this redshift/mean velocity?
+  List in Table~1.)} After this step, each bin is analysed
+independently.
+
+We note that for the MUSE observations of NGC~1316, the NaD absorption
+feature (generally attributed to absorption from the galaxy ISM and
+thus affected by the ISM kinematics) was significantly affecting the
+quality of the best-fitting {\bf (Spatially-collapsed? Clarify.)}
+stellar spectrum. For this reason, when fitting the stellar spectra
+only {\bf (i.e.\ Sections~\ref{subsec:starKin} and
+  \ref{subsec:absorption} but not \ref{subsec:EmissionLines}?
+  Clarify.)}, the wavelength range of the NGC~1316 spectra was
+restricted to $<5800$~\AA.
 
@@
 \label{subsec:starKin}
-		Each bin is fit independently, again using \textsc{pPXF} with the MILES library.
-For the fit, regions around potential emission lines (listed in Section \ref{subsec:EmissionLines}) are masked, and a fourth order polynomial additive continuum correction is used.
-The residuals between the best-fitting spectrum and the input spectrum are smoothed in wavelength using a weighted, moving average.
-This is then summed in quadrature with the noise spectrum (as propagated through the data reduction pipeline) to produce a combined `residual noise' spectrum.
-A Monte--Carlo (MC) method is used to propagate this residual noise to give to give the quoted uncertainties on all fitted values.
-
-	\subsection{Ionized Gas Distribution and Kinematics}
+
+To derive the stellar kinematics, each bin is fit independently, again
+using \textsc{pPXF} and the MILES library. For each fit, wavelength
+ranges around potential emission lines (listed in
+Section~\ref{subsec:EmissionLines}) are masked, and a fourth order
+polynomial additive continuum correction is used. The residuals
+between the best-fitting spectrum and the input spectrum are smoothed
+in wavelength using a weighted, moving average. This is then summed in
+quadrature with the noise spectrum (as propagated through the data
+reduction pipeline) to produce a combined `residual noise' spectrum. A
+Monte-Carlo (MC) approach is then used to propagate this residual
+noise through multiple independent fits and calculate the
+uncertainties quoted on all fitted values.
+
+\subsection{Ionised Gas Distribution and Kinematics}
 \label{subsec:EmissionLines}
-		In this analysis we consider the following emission lines and doublets: H$\gamma$, H$\beta$, [\ion{O}{iii}]$\lambda\lambda$4969,5007, [\ion{N}{I}]$\lambda\lambda$5199,5202, [\ion{O}{i}]$\lambda\lambda$6300,6363, [\ion{N}{ii}]$\lambda\lambda$6548,6583, H$\alpha$ and [\ion{S}{ii}]$\lambda\lambda$6716,6731.
-We fit the fluxes and kinematics for the emission lines using Gaussian templates, independently fitting the emission lines of the ISM, with a single LOSVDs (again parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion), from the stellar kinematics.
-In the cases of the [\ion{O}{iii}], [\ion{O}{i}] and [\ion{N}{ii}] doublets, the two components of the doublets are fit with a fixed flux ratio of 3:1.
-The [\ion{N}{i}] doublet has a fixed ratio of 3:2 \citep{Safier1992}.
-The two components of the [\ion{O}{ii}] and [\ion{S}{ii}] doublets are fit independently.
-To minimize template mismatch, whereby emission lines are erroneously fitted to the edges of badly modelled and thus subtracted absorption features, we follow the method set out in \citet{Sarzi2005}.
-In this method the stellar component is first fitted as above with masked potential emission line regions, followed by the unmasking and fitting of the [\ion{O}{iii}] doublet which sets the kinematics for all the emission lines and finally the amplitude of the remaining emission lines is fitted.
+
+In this analysis we consider the following emission lines and
+doublets: H$\gamma$, H$\beta$,
+[\ion{O}{iii}]$\lambda\lambda$4969,5007,
+[\ion{N}{I}]$\lambda\lambda$5199,5202,
+[\ion{O}{i}]$\lambda\lambda$6300,6363,
+[\ion{N}{ii}]$\lambda\lambda$6548,6583, H$\alpha$ and
+[\ion{S}{ii}]$\lambda\lambda$6716,6731 {\bf (Should the \ion{O}{ii}
+  doublet discussed a few lines below also be quoted here? Or should
+  the below be the \ion{O}{i} or \ion{O}{iii} doublet already quoted?
+  What about H$\delta$, also in your original table but now commented
+  out? Correct.)}. We fit the emission line fluxes and kinematics
+independently of the stellar kinematics, and their fluxes
+independently of each other (but see below), again adopting a single
+Gaussian template parametrised by $V$, the mean velocity, and
+$\sigma$, the velocity dispersion for all lines. However, in the cases
+of the [\ion{O}{iii}], [\ion{O}{i}] and [\ion{N}{ii}] doublets, the
+two components of each doublet are fit with a fixed flux ratio of
+$3:1$, while the [\ion{N}{i}] doublet is fit with a fixed flux ratio
+of $3:2$ \citep{Safier1992}. The two components of the [\ion{O}{ii}]
+and [\ion{S}{ii}] doublets are fit independently {\bf (See previous
+  comment about the \ion{O}{ii} doublet. Correct.)}. To minimise
+template mismatch, whereby emission lines are erroneously fitted to
+the edges of badly modelled and thus subtracted absorption features,
+we follow the procedure set out in \citet{Sarzi2005}. In this method,
+the stellar component is first fitted as above with potential emission
+line regions masked, followed by the unmasking and fitting of the
+[\ion{O}{iii}] doublet (that sets the kinematics of all other emission
+lines), and finally the fitting of the amplitudes of the remaining
+emission lines.
 
@@
 %   % \begin{threeparttable}
-	 % 		\caption{Emission lines considered in the \textsc{pPXF} fits.
-Col\,1: Emission line name.
-Col\,2: Emission line rest-frame wavelength.
-Col\,3: Doublet rest-frame wavelength for forbidden lines.
-Col\,4: The fixed ratio of the amplitudes of the lines within a doublet.
-`Free' indicates the amplitudes of both doublet constituents are fit independently of each other.}
+%   \caption{Emission lines considered in the \textsc{pPXF}
+%     fits. Col\,1: Emission line name. Col\,2: Emission line rest-frame
+%     wavelength. Col\,3: Doublet rest-frame wavelength for forbidden
+%     lines. Col\,4: The fixed ratio of the amplitudes of the lines
+%     within a doublet. `Free' indicates the amplitudes of both doublet
+%     constituents are fit independently of each other.}
 %   \label{tab:EmissionLine}
@@
 \label{subsec:absorption}
-		Due to the lack of calibration observations of Lick/Cassegrain Image Dissector Scanner spectrograph system (hereafter Lick/IDS system; \citealt{Faber1985, Worthey1994}) standard galaxies, we use the line index system (LIS) of \citet{Vazdekis2010} instead.
-This relies on flux calibrations instead of correcting to the continuum shape and wavelength dependent resolution of the Lick/IDS system.
-We use the index definitions of \citet{Trager1998}, measuring the following indices: G4300, Fe4383, Ca4455, Fe4531, H\,$\beta$, Fe5015, Mg\,b, Fe5270, Fe5335, Fe5406, Fe5709, Fe5782, NaD, TiO1 and TiO2.
-%TiO1 and TiO2 are considered molecular absorption lines and are measured in magnitude units, while all others are atomic and measured in angstroms.
-
-		Quoted line strengths are corrected for both emission line and the effect of the velocity dispersion of the stars as detailed below.
+
+For absorption line strength measurements, and due to the lack of
+calibration observations of Lick/Cassegrain Image Dissector Scanner
+spectrograph system (hereafter Lick/IDS system; \citealt{Faber1985,
+  Worthey1994}) standard galaxies, we use the line index system (LIS)
+of \citet{Vazdekis2010}. This relies on flux calibration instead of a
+correction to the continuum shape and wavelength-dependent resolution
+of the Lick/IDS system. We use the index definitions of
+\citet{Trager1998}, measuring the following indices: G4300, Fe4383,
+Ca4455, Fe4531, H$\beta$, Fe5015, Mg~$b$, Fe5270, Fe5335, Fe5406,
+Fe5709, Fe5782, NaD, TiO1 and TiO2.
+% TiO1 and TiO2 are considered molecular absorption lines and are
+% measured in magnitude units, while all others are atomic and
+% measured in angstroms.
+
+The line strengths quoted are corrected for both line emission and the
+effects of the stellar velocity dispersion, as detailed below.
 
 \subsubsection{Removing Emission Lines}
-			Emission lines are removed from the spectra by subtracting the best-fitting emission lines from Section \ref{subsec:EmissionLines} from the data and using only the stellar templates (and continuum correction) for reconstructing the best-fit for use in the velocity dispersion correction (see below).
+\label{subsubsec:RemovingEmission}
+
+Each emission line is removed from each spectrum by subtracting the
+best-fitting Gaussian from Section~\ref{subsec:EmissionLines} from the
+data, using only the stellar templates (and continuum correction)
+subsequently considered for the velocity dispersion correction (see
+below). {\bf (I do not understand the second part of this
+  sentence. Check/clarify/correct.)}
+% used for reconstructing the best-fit to
 
 \subsubsection{Correcting for Stellar Velocity Dispersion}
-			\label{subsubsec:EmissionFit}
-			We correct for the effect of the different velocity dispersions of the stars which varyingly spread absorption features such that differing fractions of the absorption are outside of the central bandpasses.
-To do this, we create a stellar best-fitting spectrum which is \textit{not} convolved with the best-fitting LOSVD.
-Note that for NGC 1316, indices at wavelengths longer than 5800 \AA\ are calculated using the extrapolated best-fitting \textit{pPXF} fit.
-A given index, $I$, is then measured for both this `unconvolved' spectrum ($I^\text{unc}$) and the convolved best-fitting spectrum ($I^\text{conv}$), and the ratio of these two indices is used as a multiplicative correction factor for the index measured in the observations ($I^\text{obs}$), such that the corrected index ($I^\text{corr}$) is given by
+\label{subsubsec:Correcting Dispersion}
+
+We also correct for the effects of the different velocity dispersions
+of the stars (across different galaxies), that varyingly spread
+absorption features such that differing fractions of the absorption
+are outside each index's central bandpass. To achieve this, we create
+a best-fitting stellar spectrum that is \textit{not} convolved with
+the best-fitting LOSVD, and we note that for NGC~1316, indices at
+wavelengths longer than $5800$~\AA\ are calculated using the
+extrapolated best pPXF fit. A given index $I$ is then measured for
+both this `unconvolved' spectrum ($I_\text{unc}$) and the convolved
+best-fitting spectrum ($I_\text{conv}$), and the ratio of these two
+indices is then used as a multiplicative correction factor for the
+index measured in the data ($I_\text{obs}$). The corrected index
+($I_\text{corr}$) is thus given by
 \begin{equation}
-				I^\text{corr} \equiv \frac{I^\text{unc}}{I^\text{conv}} I^\text{obs} \, .
+  I_\text{corr}\equiv\frac{I_\text{unc}}{I_\text{conv}}I_\text{obs}~.
 \end{equation}
-			These corrected indices are those reported and discussed in the sections below.
+It is these corrected indices that are reported and discussed in the
+following sections.
 
@@
 \label{subsubsec:stellarPop}
-		In each bin, using the measured absorption line strengths, we identify the best-fitting single stellar population (SSP) model from an interpolated grid of models using \textsc{emcee}, a \textsc{python}, affine-invariant Markov chain Monte--Carlo (MCMC) fitting package \citep{Foreman-Mackey2013}.
-This grid is created by linearly interpolating between the models of \citeauthor{Thomas2010} (\citeyear{Thomas2010}; hereafter \citetalias{Thomas2010}).
-The \citetalias{Thomas2010} models are chosen because they are based on high-resolution, flux-calibrated spectra and therefore not requiring absorption line strength measurement to be in the Lick/IDS system.
+
+In each bin, using the measured absorption line strengths, we identify
+the best-fitting single stellar population (SSP) model from an
+interpolated grid of models using \textsc{emcee}, a \textsc{python}
+affine-invariant Markov-chain Monte-Carlo (MCMC) fitting package
+\citep{Foreman-Mackey2013}. This grid is created by linearly
+interpolating between the models of \citeauthor{Thomas2010}
+(\citeyear{Thomas2010}; hereafter \citetalias{Thomas2010}). The
+\citetalias{Thomas2010} models are chosen because they are based on
+high-resolution flux-calibrated spectra, and therefore do not require
+the absorption line strength measurements to be in the Lick/IDS
+system.
 
 \subsection{Other Parameters}
+\label{subsec:OtherParameters}
+
 \subsubsection{Ellipticity}
 \label{subsubsec:ellip}
-			In this paper, ellipticity, $\epsilon$, is that of the best-fitting ellipse to the surface-brightness map with an mean radius $R_\text{m}$, of 1 effective radius $R_\text{e}$.
-% Firstly the centre of the galaxy is found as the luminosity weighted centre using the \textsc{python} routine \textsc{find\_galaxy}, which is part of the \textsc{mge} package\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/} by \citet{Cappellari2002}.
-			as found by the \textsc{idl} routine \textsc{kinemetry}\footnote{http://davor.krajnovic.org/idl/} by \citet{Krajnovic2006}.%, which finds the best-fitting ellipses at a range of evenly spaced semi-major axes.
-%This is achieved by performing harmonic expansion of maps along ellipses with a given semi-major axis and, when used for even moments (e.g.\ surface brightness, velocity dispersion, h$_4$ etc.), minimizing the amplitude of the first and second harmonics.
-			The results include the ellipticity, $\epsilon$ and position angle, $PA_\text{phot}$ of the best-fitting ellipse.% for each semi-major axis.
-The fit is repeated for increasing semi-major axis until $<$75\% of the ellipse is not contained within the field of view.
-
-			In reality, the field of view does not always contain 1 $R_\text{e}$.
-Where this is the case, we follow the method by \citet{Emsellem2007}, where $R_\text{m}$ is redefined as $R_\text{m} \equiv \sqrt{A_\text{s}/\pi}$, where $A_\text{s}$ is the area of the ellipse contained within the field of view.
-For a given galaxy, we fit ellipses as described above, up to $R_\text{m} = R_\text{max}$, where $A_\text{s}$ reaches a maximum difference of 15\% to the area of the fitted ellipse, $A_\text{ellipse}$.
-The value $\epsilon_\text{e}$, the ellipticity at 1 $R_\text{e}$ or $R_\text{max}$, whichever is smallest, is given in Col.\,3 of Table \ref{tab:classify}.
+
+In this paper, whenever possible the ellipticity adopted,
+$\epsilon_\text{e}$, is that of the best-fitting ellipse (to the
+surface-brightness map) with a mean radius $R_\text{m}$ of $1$
+effective (half-light) radius $R_\text{e}$,
+% Firstly the centre of the galaxy is found as the luminosity weighted
+% centre using the \textsc{python} routine \textsc{find\_galaxy}, that
+% is part of the \textsc{mge}
+% package\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/}
+% by \citet{Cappellari2002}.
+as found by the \textsc{Interactive Data Language (IDL)} routine
+\textsc{kinemetry}\footnote{http://davor.krajnovic.org/idl/} of
+\citet{Krajnovic2006}.
+% , that finds the best-fitting ellipses at a range of evenly spaced
+% semi-major axes. This is achieved by performing a harmonic expansion
+% of the map along ellipses with a given semi-major axis and, when
+% used for even moments (e.g.\ surface brightness, velocity
+% dispersion, kurtosis), minimising the amplitude of the first and
+% second harmonics.
+Results include the ellipticity $\epsilon$ and position angle
+$PA_\text{phot}$ of the best-fitting ellipse as a function of the
+ellipse semi-major axis.
+% for each semi-major axis. The fit is repeated for increasing
+% semi-major axes until $<$75\% of the ellipse is contained within the
+% field of view.
+
+In reality, the field of view does not always contain
+$1$~$R_\text{e}$. When this is the case, we follow the method of
+\citet{Emsellem2007}, where $R_\text{m}$ is redefined as
+$R_\text{m}\equiv\sqrt{A_\text{s}/\pi}$, where $A_\text{s}$ is the
+area of the {\bf (Largest? Clarify.)} ellipse contained within the
+field of view. {\bf (I do not understand the meaning of the following
+  sentence in {\it italics}. Rephrase/explain better. Perhaps even
+  simply remove? What are $R_\text{max}$ and $A_\text{ellipse}$?!)}
+{\it For a given galaxy, we fit ellipses as described above, up to
+  $R_\text{m}=R_\text{max}$, where $A_\text{s}$ reaches a maximum
+  difference of 15\% with respect to the area of the fitted ellipse,
+  $A_\text{ellipse}$}. The value $\epsilon_\text{e}$, the ellipticity
+at $1$~$R_\text{e}$ or $R_\text{max}$, whichever is smallest, is given
+in Column~3 of Table~\ref{tab:classify}.
+
+\begin{table*}[t]
+  \begin{center}
+    % \begin{threeparttable}
+    \caption{Kinematic classifications of our Southern Sample
+      galaxies.}
+    \label{tab:classify}
+    \begin{tabular*}{0.7\textwidth}{@{\extracolsep{\fill}}l c c c c c c c}
+    \hline
+    \hline
+    Galaxy & $\lambda_\mathrm{R_e}$ & $\epsilon_\text{e}$  & $\Gamma_\text{kin}$ & FR/SR 	& RR/NRR & Feature & Group 	\\
+           & & & (deg)\\
+      \hline 
+      ESO~443-G024 & $0.048$ & $0.35$ & $-18\pm\leavevmode\phantom{0}2$	& SR & NRR & KDC & c \\
+      IC~1459 & $0.125$ & $0.24$ & \leavevmode\phantom{0}$-3\pm\leavevmode\phantom{0}1$ & SR & NRR & KDC & c \\
+      IC~1531 & $0.101$ & $0.08$ & $-54\pm25$ & FR & NRR & LV & a \\
+      IC~4296 & $0.034$ & $0.03$ & $\leavevmode\phantom{-0}8\pm12$ & SR & \leavevmode\phantom{N}RR & -- & e \\
+      NGC~612 & $0.655$ & $0.36$ & $\leavevmode\phantom{-}12\pm\leavevmode\phantom{0}6$	& FR &\leavevmode\phantom{N}RR & -- & e \\
+      NGC~1316 & $0.100$ & $0.39$ & $\leavevmode\phantom{-0}6\pm\leavevmode\phantom{0}2$ & FR & NRR & -- & f \\
+      NGC~1399 & $0.090$ & $0.12$ & $-74\pm\leavevmode\phantom{0}5$ & SR & NRR & LV & a \\
+      NGC~3100 & $0.354$ & $0.24$ & \leavevmode\phantom{0}$-8\pm\leavevmode\phantom{0}2$ & FR &\leavevmode\phantom{N}RR & -- & e \\
+      NGC~3557 & $0.312$ & $0.20$ & $\leavevmode\phantom{-}16\pm\leavevmode\phantom{0}5$ & FR &\leavevmode\phantom{N}RR & -- & e\\
+      NGC~7075 & $0.068$ & $0.04$ & $\leavevmode\phantom{-}36\pm50$ & SR & NRR & -- & b \\
+      PKS~718-34 & $0.159$ & $0.17$ & $\leavevmode\phantom{-}15\pm25$ & FR & NRR & KDC & b\\
+      \hline
+      \hline    
+    \end{tabular*}
+    % \begin{tablenotes}
+    \parbox[t]{0.7\textwidth}{\footnotesize\textit{Notes:} Col.~1:
+      galaxy name. Col.~2: $\lambda_\text{R}$ evaluated at
+      $R_\text{e}$. Col.~3: ellipticity evaluated at $R_\text{e}$ or
+      $R_\text{max}$, whichever is smallest. Col.~4: misalignment
+      angle between the photometric and stellar kinematic position
+      angles. Col.~5: fast-/slow-rotator (FR/SR)
+      classification. Col.~6: regular-/non-regular-rotator (RR/NRR)
+      classification. Col.~7: kinematic features:
+      kinematically-decoupled core (KDC) or low-velocity (LV). Col.~8:
+      \citeauthor{Krajnovic2011}'s (\citeyear{Krajnovic2011})
+      kinematic group. The kinematic group of PKS~718-34 is tentative;
+      a higher $S/N$ is required in the outer parts of the field of
+      view for confirmation. {\bf (It would be better to calculate and
+        report/list uncertainties on $\lambda_\mathrm{R_e}$ and
+        $\epsilon_\text{e}$.)}}
+    % \end{tablenotes}
+    % \end{threeparttable}
+  \end{center}
+\end{table*}
 
@@
 \label{subsubsec:KinPA}
-			The kinematic position angle, $PA_\text{kin}$, is defined as the angle of the axis perpendicular to the apparent angular momentum vector westwards from North.
-A global value of $PA_\text{kin}$ is found using the \textsc{python} routine \textsc{fit\_kinematic\_pa}\footnotemark[1] which finds $PA_\text{kin}$ of the symmetrised mean velocity map, as described in appendix C of \citet{Krajnovic2006}.
-%This routine finds a symmetric (about $PA_\text{kin}$) velocity field, by replacing the mean velocity, $V$, in each bin with
+
+The kinematic position angle, $PA_\text{kin}$, is defined as the angle
+of the axis perpendicular to the apparent angular momentum vector,
+measured westward from North. {\bf (Are you sure this is westward and
+  not eastward? Position angles are usually defined from North to
+  East, the latter of course usually being to the left in astronomical
+  images. Check and correct if need be.)} A global value of
+$PA_\text{kin}$ is calculated using the \textsc{python} routine
+\textsc{fit\_kinematic\_pa}\footnotemark[1], that finds
+$PA_\text{kin}$ of the symmetrised mean velocity map, as described in
+Appendix~C of \citet{Krajnovic2006}.
+% This routine finds a symmetric (about $PA_\text{kin}$) velocity
+% field, by replacing the mean velocity, $V$, in each bin with
 % \begin{equation}
-			% 	V'(x, y) = \frac{V(x,y) + V(x, -y) - V(-x,y) - V(-x,-y))}{4} \,,
+% V'(x, y) = \frac{V(x,y) + V(x, -y) - V(-x,y) - V(-x,-y))}{4}~,
 % \end{equation}
-			% where $x$ and $y$ are the centroid coordinates of a given bin, with the origin at the centre of the galaxy and the x axis aligned along $PA_\text{kin}$.
-Linear interpolation is used where necessary.
-
-			Col.\,4 in Table \ref{tab:classify} lists the misalignments between the photometric and stellar kinematic position angles, $\Gamma_\text{kin} \equiv \arcsin(\sin[PA_\text{phot} - PA_\text{kin}])$.
-
-		\subsubsection{Specific Angular Momentum Parameter, $\lambda_\mathrm{R_e}$}
-			We also make use of the Atlas$^\text{3D}$ specific angular momentum parameter, $\lambda_\text{R}$ \citep{Emsellem2007} evaluated at 1 $R_\text{e}$, where 
+% where $x$ and $y$ are the centroid coordinates of a given bin, with
+% the origin at the centre of the galaxy and the x axis aligned along
+% $PA_\text{kin}$. Linear interpolation is used where necessary.
+
+Column~4 in Table~\ref{tab:classify} lists the misalignment angle
+between the photometric and stellar kinematic position angles,
+$\Gamma_\text{kin}\equiv\arcsin(\sin[PA_\text{phot}-PA_\text{kin}])$.
+{\bf (Why is that different from simply
+  $\Gamma_\text{kin}\equiv PA_\text{phot}-PA_\text{kin}$? Correct if
+  need be.)} {\bf (At which radius/ellipse semi-major axis is
+  $PA_\text{phot}$ taken/measured? Specify.)}
+
+\subsubsection{Specific Angular Momentum}
+\label{subsubsec:SpecificMomentum}
+
+We also make use of the Atlas$^\text{3D}$ specific angular momentum
+parameter, $\lambda_\text{R}$ \citep{Emsellem2007}, evaluated at
+$1$~$R_\text{e}$, where
 \begin{equation}
-				\lambda_\mathrm{R_e} \equiv \frac{\sum_{i=1}^{N} F_i R_i |V_i|}{\sum_{i=1}^{N} F_i R_i \sqrt{V_i^2 + \sigma_i^2}}
+  \lambda_\mathrm{R_e}\equiv\frac{\sum_{i=1}^{N}\,F_iR_i|V_i|}{\sum_{i=1}^{N}\,F_iR_i\sqrt{V_i^2+\sigma_i^2}}~,
 \end{equation}
-			where $F_i$ is the flux of the $i^\text{th}$ bin, $R_i$ its distance from the centre and $V_i$ and $\sigma_i$ its mean stellar velocity and velocity dispersion, respectively.
-The sum is computed over all $N$ bins within $1R_\text{e}$ of the centre of the galaxy.
+{\bf (Is $R_i$ really measured from the centre as stated, or rather
+  with respect to the kinematic minor axis/rotation axis?
+  State/explain if the latter.)} where $F_i$ is the flux of the
+$i^\text{th}$ bin, $R_i$ its distance from the centre, $V_i$ its mean
+stellar velocity and $\sigma_i$ its stellar velocity dispersion. The
+sum is computed over all $N$ bins within $1$~$R_\text{e}$ of the
+centre of the galaxy. {\bf (What do you do if the field of view does
+  not reach $1$~$R_\text{e}$? Specify/discuss (as for
+  $\epsilon_\text{e}$).)}
 
@@
 \label{sec:StarKine}
-	Using the methods above, we produce stellar kinematic maps (shown in Appendix \ref{sec:maps}) for all datacubes.
-Here, we use these maps to classify each galaxy according to the Atlas$^\text{3D}$ regular/non-regular rotator and fast/slow rotator classification schemes of \citet{Krajnovic2006} and \citet{Cappellari2016}, respectively, as well as the qualitative kinematic classes of \citet{Krajnovic2011}.
-We use the criteria described in the referenced literature for each of these classification, with the results shown in Table \ref{tab:classify}.
-
-	\begin{table*}
-		\centering
-	% \begin{threeparttable}
-		\caption{Kinematic classifications of the Southern Sample galaxies.
-Col.\,1: Galaxy name.
-Col.\,2: $\lambda_\text{R}$ evaluated at $R_\text{e}$.
-Col.\,3: Ellipticity at $R_\text{e}$.
-Col.\,4: Misalignment angle between the kinematic and photometric position angles.
-Col.\,5: Fast-/slow-rotator (FR/SR) classification.
-Col.\,6: Regular-rotator (RR) or non-regular-rotator (NRR).
-Col.\,7: Kinematic features: kinematically-decoupled core (KDC) or low-velocity (LV).
-Col.\,8: Kinematic group.}
-		\label{tab:classify}
-		\begin{tabular}{l c c c c c c c}
-			\hline
-			\hline
-			Galaxy		& $\lambda_\mathrm{R_e}$ & $\epsilon_\text{e}$  & $\Gamma_\text{kin}$ & FR/SR 	& RR/NRR 	& Feature & Group 	\\
-			 & & & (deg) \\
-			\hline 
-			ESO 443-G024 & 0.048 & 0.35 & $-18\pm\leavevmode\phantom{0}2$	& SR & NRR & KDC & c \\
-			IC 1459 	& 0.125 & 0.24 & \leavevmode\phantom{0}$-3\pm\leavevmode\phantom{0}1$ & SR & NRR & KDC & c \\
-			IC 1531 	& 0.101 & 0.08 & $-54\pm25$	& FR & NRR & LV & a \\
-			IC 4296		& 0.034 & 0.03 & \leavevmode\phantom{$-0$}$8\pm12$ & SR &\leavevmode\phantom{N}RR & -- & e \\
-			NGC 612 	& 0.655 & 0.36 & \leavevmode\phantom{$-$}$12\pm\leavevmode\phantom{0}6$	& FR &\leavevmode\phantom{N}RR & -- & e \\
-			NGC 1316 	& 0.100 & 0.39 & \leavevmode\phantom{$-0$}$6\pm\leavevmode\phantom{0}2$ & FR & NRR & -- & f \\
-			NGC 1399 	& 0.090 & 0.12 & $-74\pm\leavevmode\phantom{0}5$ & SR & NRR & LV & a \\
-			NGC 3100 	& 0.354 & 0.24 & \leavevmode\phantom{0}$-8\pm\leavevmode\phantom{0}2$ & FR &\leavevmode\phantom{N}RR & -- & e \\
-			NGC 3557 	& 0.312 & 0.20 & \leavevmode\phantom{$-$}$16\pm\leavevmode\phantom{0}5$ & FR &\leavevmode\phantom{N}RR & -- & e\\
-			NGC 7075 	& 0.068 & 0.04 & \leavevmode\phantom{$-$}$36\pm50$ & SR & NRR & -- & b \\
-			PKS 718-34  & 0.159 & 0.17 & \leavevmode\phantom{$-$}$15\pm25$ & FR & NRR & KDC$^{a}$ & b\\
-			\hline
-			\hline
-			\multicolumn{8}{L{.7\linewidth}}{$^{a}$Tentative classification. A higher S/N in the outer regions of the field of view is required for confirmation.}
-
-		\end{tabular}
-	% 	\begin{tablenotes}
-	% 	\footnotesize
-	% 	\note Col.\,1: Galaxy name.
-Col.\,2: $\lambda_\text{R}$ evaluated at $R_\text{e}$.
-Col.\,3: Ellipticity at $R_\text{e}$.
-Col.\,4: Misalignment angle between the kinematic and photometric position angles.
-Col.\,5: Fast-/slow-rotator (FR/SR) classification.
-Col.\,6: Regular-rotator (RR) or non-regular-rotator (NRR).
-Col.\,7: Kinematic features.
-Col.\,8: Kinematic group.
-	% 	\item [a] Tentative classification. A higher signal-to-noise ratio (S/N) in the outer regions of the field of view is required for confirmation.
-	% 	\end{tablenotes}
-	% \end{threeparttable}
-	\end{table*}
+
+Using the methods above, we produce stellar kinematic maps (shown in
+Appendix \ref{sec:maps}) for all datacubes. Here, we use these maps to
+classify each galaxy according to the Atlas$^\text{3D}$
+regular/non-regular rotator and fast/slow rotator classification
+schemes of \citet{Krajnovic2006} and \citet{Cappellari2016},
+respectively, as well as the qualitative kinematic classes of
+\citet{Krajnovic2011}.
+% We use the criteria described in the referenced literature for each
+% of these classification,
+The results are listed in Table~\ref{tab:classify}.
 
 \subsection{Regular/Non-regular Rotators}
-		\label{subsec:RR}
-		We find 4 out of 11, or $(36\pm15)$\%, of our sample galaxies are regular rotators.
-This compares to 82\% of the Atlas$^\text{3D}$ sample being classified as regular rotators \citep{Krajnovic2011}.
-However the likelihood of a given galaxy being a regular rotator is highly mass dependent with the likelihood decreasing with increasing mass.
-Thus since our Southern sample are all extremely massive galaxies, we expect to find a higher fraction of non-regular rotators than the Atlas$^\text{3D}$ survey.
+\label{subsec:RR-NRR}
+
+We find $4$ out of $11$, or $36\pm15\%$, of our sample galaxies are
+regular rotators. This compares to $82\%$ of the Atlas$^\text{3D}$
+galaxies being classified as regular rotators
+\citep{Krajnovic2011}. {\bf (Better to also quote the uncertainty on
+  that $82\%$ figure.)} However, the likelihood of a given galaxy
+being a regular rotator is highly mass dependent, the likelihood
+decreasing with increasing mass. As our Southern Sample galaxies are
+all extremely massive, we naturally expect to find a higher fraction
+of non-regular rotators than that of the Atlas$^\text{3D}$ sample.
+
+{\bf (Why not do a test here as in the next
+  Sub-section~\ref{subsec:FR-SR} but for the RR/NRR classification,
+  i.e.\ taking into account the mass differences of the two samples? I
+  suggest you do, and then move the description of that test to this
+  (first) sub-section. You then need not repeat the test description
+  in Sub-section~\ref{subsec:FR-SR}; just state the results.)}
 
 \subsection{Fast/Slow Rotators}
+\label{subsec:FR-SR}
+
+We find $5$ out of $11$ galaxies, or $45\pm13\%$, are slow rotators
+(see Fig.~\ref{fig:lambdaR_ellip}). This fraction is between that of
+the Atlas$^\text{3D}$ and MASSIVE surveys, that find respectively
+$13.1\%$ and $77.5\%$ of their sample galaxies to be slow
+rotators. {\bf (Again, better to also quote the uncertainties on those
+  two fractions. I doubt the decimal place is meaningful in either of
+  them.)} As in the regular-/non-regular-rotator classification scheme
+(Section~\ref{subsec:RR-NRR}), slow rotators are more likely to be
+found in higher mass galaxies, and the three samples
+(Atlas$^\text{3D}$, MASSIVE and our Southern Sample) have very
+different mass distributions (see the upper panel of
+Fig.~\ref{fig:SRmassFraction}).
+
 \begin{figure}
   \includegraphics[width=\columnwidth]{lambda_R_ellipticity.png}
-			\caption{$\lambda_\mathrm{R_e}$\,--\,ellipticity diagram.
-VIMOS and MUSE measurements are shown in red and blue, respectively.
-For comparison, Atlas$^\text{3D}$ galaxies \citep{Emsellem2011} are shown in black and MASSIVE galaxies \citep{Veale2017} in grey.
-The theoretical limit (edge-on systems) of disc-dominated galaxies is shown in solid magenta, with lines of constant intrinsic angular momentum but varying inclination in dotted magenta.
-The black solid lines show the limits of the fast-/slow-rotator classes.
-The MASSIVE survey does not report substructure, so the MASSIVE sample galaxies are shown with filled circles.}
+  \caption{$\lambda_\mathrm{R_e}$\,--\,ellipticity diagram. Our
+    Southern Sample VIMOS and MUSE measurements are shown in red and
+    blue, respectively. For comparison, Atlas$^\text{3D}$ galaxies
+    \citep{Emsellem2011} are shown in black and MASSIVE galaxies
+    \citep{Veale2017} in grey. Kinematic features are indicated by the
+    symbol shape. The MASSIVE survey does not report substructure, so
+    all MASSIVE sample galaxies are shown as filled circles. The
+    theoretical limit (edge-on systems) of disc-dominated galaxies is
+    indicated by the solid magenta line, with lines of constant
+    intrinsic angular momentum but varying inclination in dotted
+    magenta. The black solid lines indicate the limits of the
+    fast-/slow-rotator classes. {\bf (In the figure legend, ``Regular
+      Rotator'' should be ``Regular rotator''. The figure is also too
+      small (the symbols can not be distinguished). Either put the
+      legend on top or make the figure full width. Print it to check!
+      Finally, for this and all figures except those of Appendix~B, it
+      would be preferable to have small/minor tickmarks (with no
+      numerical label) as well as large/major tickmarks.)}}
   \label{fig:lambdaR_ellip}
@@
 
-		5 out of 11 galaxies, or $(45\pm13)$\%, are slow rotators (see Fig.\,\ref{fig:lambdaR_ellip}).
-This is between that of the Atlas$^\text{3D}$ and MASSIVE projects, who find 13.1\% and 77.5\% of their respective sample galaxies to be slow rotators.
-As in the regular/non-regular rotators classification scheme (Section \ref{subsec:RR}), slow rotators are more likely to be found in higher mass galaxies and the three samples (Atlas$^\text{3D}$, MASSIVE and our Southern sample) have very different mass distributions (see upper panel of Fig.\,\ref{fig:SRmassFraction}).
-
-		In order to account for the difference in mass distribution, we find the expected fraction of slow rotators in the Southern sample, $f'$, corrected to the mass distribution of the A+M sample, as
-		\begin{equation}
-			f' = \frac{\sum_{i=0}^N N^\mathrm{SS}_i f^\mathrm{AM}_i}{\sum_{i=0}^N N^\mathrm{SS}} \, , 
-		\end{equation}
-		where $N^\text{SS}_i$ is the number of Southern sample galaxies in the $i^\text{th}$ mass bin, $N^\text{AM}_i$ is the fraction of slow rotators in the $i^\text{th}$ mass bin in the A+M sample and $N$ is the total number of mass bins.
-In our case we use the $K$-band absolute magnitude ($M_K$) as a proxy for stellar mass, with bins of 0.5 mag.
-This gives an expected fraction of $f' = 0.64 \pm 0.06$, which is consistent with our finding of $(45\pm13)$\% of the Southern sample galaxies being slow rotators.
-Again the large uncertainty reflects the low number statistics of the Southern sample.
-There is, therefore, no discernible difference in the fraction of galaxies that are slow-rotators between our radio-selected Southern sample and the optically-selected A+M sample, once differences in the mass distributions are taken into account.
-
 \begin{figure}
   \includegraphics[width=\columnwidth]{M_k_binned.png}
-			\caption{Upper panel: mass distribution of the A+M sample (black) and of our Southern sample (red).
-Lower panel: fraction of slow rotators within each mass bin.
-The labels list the number of slow rotators and total number of galaxies in each bin.}
+  \caption{Upper panel: mass distribution of our Southern Sample (red,
+    right axis) and the A+M sample (black, left axis). Lower panel:
+    fraction of slow rotators within each mass bin, again
+    colour-coded. The labels list the number of slow rotators and
+    total number of galaxies in each bin. {\bf (In the y-axis label,
+      ``Southern sample'' should be ``Southern Sample''.)}}
   \label{fig:SRmassFraction}
@@
 
+To account for the differences of the mass distributions, we find the
+expected fraction of slow rotators in our Southern sample, $f'$,
+corrected to the mass distribution of the A+M sample, as
+\begin{equation}
+  f^\prime=\frac{\sum_{i=0}^N\,N^\mathrm{SS}_if^\mathrm{AM}_i}{\sum_{i=0}^N\,N^\mathrm{SS}_i}~, 
+\end{equation}
+where $N^\text{SS}_i$ is the number of Southern Sample galaxies in the
+$i^\text{th}$ mass bin, $f^\text{AM}_i$ is the fraction of slow
+rotators in the $i^\text{th}$ mass bin of the A+M sample, and the sum
+is computed over all $N$ mass bins. Here, we use the integrated
+$K$-band absolute magnitude ($M_K$) as a proxy for stellar mass, with
+bins of $0.5$~mag. This yields an expected fraction of slow rotators
+for our Southern sample galaxies of $f^\prime=0.64\pm0.06$, consistent
+with our measured fraction of $45\pm13\%$. The large uncertainty
+reflects the low number statistics of our Southern Sample. Once
+differences in the mass distributions are taken into account, there is
+therefore no discernible difference in the fraction of galaxies that
+are slow rotators between our radio-selected Southern Sample and the
+optically-selected A+M sample.
+
+{\bf (At the moment, the bottom panel of Fig.~\ref{fig:SRmassFraction}
+  is never referenced nor discussed anywhere. It should, even
+  briefly. Add some discussion of it.)}
+
 \subsection{Kinematic Features}
-		We attempt to identify the kinematic features defined by \citet{Krajnovic2011} in an algorithmic mannor, however, the artefacts from the VIMOS quadrants confuse ellipse fitting algorithms.
-Due to this, only maps derived from the MUSE data are classified in this way, while kinematic features in maps derived from the VIMOS data are identified by eye.
-These classification are listed in Col.\,7 of Table \ref{tab:classify} and the corresponding kinematic group \citep[also defined by][]{Krajnovic2011} to which a given galaxy belongs to is given is Col.\,8.
-We observe 3 KDCs (although PKS 718-34 is only a tentative classification) such that $29\pm19$\% of non-regular rotators in our Southern sample definitely (not including PKS 718-34) contain KDCs (or $43\pm19$\% including PKS 718-34), with the large uncertainty reflecting the low-number statistics.
-This is consistent with the Atlas$^\text{3D}$ survey who found find $25\pm7$\% of non-regular rotators host KDCs \citep{Krajnovic2011}.
+\label{subsec:kin_features}
+
+We attempted to identify the kinematic features defined by
+\citet{Krajnovic2011} in an algorithmic manner, but the artefacts from
+the different VIMOS quadrants confused ellipse-fitting
+algorithms. Only the maps derived from MUSE data were therefore
+classified in this automated way. The kinematic features in the VIMOS
+maps were identified by eye. The resulting classifications are listed
+in Column~7 of Table~\ref{tab:classify}, and the corresponding
+kinematic group to which a galaxy belongs (also defined by
+\citealt{Krajnovic2011}) is listed in Column~8. We identify $3$
+kinematically-decoupled cores (KDCs; although PKS~718-34 is only a
+tentative classification), such that $29\pm19\%$ of non-regular
+rotators in our Southern Sample definitely (not including PKS~718-34)
+contain a KDC (or $43\pm19\%$ including PKS~718-34), the large
+uncertainty again reflecting the low-number statistics. This is
+consistent with the Atlas$^\text{3D}$ survey, that found $25\pm7\%$ of
+non-regular rotators hosting a KDC \citep{Krajnovic2011}.
 
 \subsection{Intrinsic Shape}
-		The misalignment angle, $\Gamma_\text{kin}$, between the photometric and kinematic position angle is given in Col.\,4 of Table \ref{tab:classify}.
-IC 1531, NGC7075 and PKS 718-34 all have very large uncertainties in the value of $PA_\text{phot}$ due to the VIMOS quadrant artefacts causing the fitting routine of \textsc{kinemetry} to become unreliable.
-
-		While intrinsically misaligned systems may appear aligned in certain projections, aligned systems will be aligned in all projections.
-Therefore a low value of $\Gamma_\text{kin}$ cannot be used to describe the intrinsic shape of an individual galaxy, but can only be interpreted within a statistical framework as in \citet{Cappellari2007}.
-However, a high value of $\Gamma_\text{kin}$ can give an insight into the intrinsic shape of an individual galaxy.
-We find all the regular rotators in our Southern sample, are consistent with having aligned photometry and kinematic position angles to within 11\degr, while non-regular rotators have a large range of values of $\Gamma_\text{kin}$.
-
-		The lack of misalignments in regular rotators is consistent with \citet{Cappellari2007}, \citet{Krajnovic2011} and \citet{Fogarty2015}, who all show that regular rotators almost always have aligned photometric and kinematic axes with very little scatter.
-They also point out that regular rotators with a significant misalignment tend to be either interacting or strongly barred.
-The lack of misalignments suggests that the regular rotators (including those within our Southern sample) are consistent with being axisymmetric \citep{Cappellari2016}.
-
-		Misalignments between the photometric and kinematic position angles are routinely observed for non-regular rotators.
-This generally implies a more triaxial intrinsic shape, although large misalignments are extremely rarely observed in galaxies with $\epsilon > 0.4$, suggesting that non-regular rotators are more spherical in shape \citep{Cappellari2016}.
-The non-regular rotators in our Southern sample indeed all have $\epsilon < 0.4$ and a broad range of misalignment angles and are thus consistent with a fairly spherical, triaxial intrinsic shape.
+\label{subsec:int_shape}
+
+The misalignment angle $\Gamma_\text{kin}$ between the photometric and
+kinematic position angles is listed in Column~4 of
+Table~\ref{tab:classify}. IC~1531, NGC~7075 and PKS~718-34 all have
+very large $PA_\text{phot}$ uncertainties, again due to the different
+VIMOS quadrant artefacts causing the \textsc{kinemetry} fitting
+routine to become unreliable.
+
+{\bf (A solution to these large $PA_\text{phot}$ uncertainties would
+  be to measure $PA_\text{phot}$ not from the surface brightness maps
+  reconstructed from the IFS data, but rather from actual images, of
+  which there should be many easily available. Of course, you would
+  then need to make sure you know the orientation of these images
+  accurately. Try it?)}
+
+While intrinsically misaligned systems may appear aligned in certain
+projections, aligned systems will be aligned in all
+projections. Therefore, a low value of $\Gamma_\text{kin}$ cannot be
+used to describe the intrinsic shape of an individual galaxy, but can
+only be interpreted within a statistical framework (as in
+\citealt{Cappellari2007}). However, a high value of
+$\Gamma_\text{kin}$ does provide insight into the intrinsic shape of
+an individual galaxy. Here, we find all the regular rotators in our
+Southern Sample to be consistent with having aligned photometric and
+kinematic position angles (to within $11\degr$), while non-regular
+rotators have a large range of $\Gamma_\text{kin}$.
+
+The lack of misalignments in regular rotators is consistent with
+\citet{Cappellari2007}, \citet{Krajnovic2011} and \citet{Fogarty2015},
+who all showed that regular rotators almost always have aligned
+photometric and kinematic axes, with very little scatter. They also
+pointed out that regular rotators with a significant misalignment tend
+to be either interacting or strongly barred disc galaxies. This lack
+of misalignments thus suggests that the regular rotators (including
+those in our Southern Sample) are consistent with being axisymmetric
+\citep{Cappellari2016}.
+
+Misalignments between the photometric and kinematic position angles
+are routinely observed for non-regular rotators. This generally
+implies a more triaxial intrinsic shape, although large misalignments
+are extremely rarely observed in galaxies with $\epsilon>0.4$,
+suggesting that non-regular rotators are also more closely spherical
+\citep{Cappellari2016}. The non-regular rotators in our Southern
+Sample indeed all have $\epsilon<0.4$, with a broad range of
+misalignment angles, and are thus consistent with fairly spherical
+but mildly triaxial intrinsic shapes.
 
@@
 \label{sec:absorption}
-	Using the methods described in Section \ref{subsec:absorption}, we produce maps of the absorption line strength indices for each galaxy (shown in Appendix \ref{sec:maps}).
-In this section, we measure the Mg\,--\,velocity dispersion relation and compare our absorption line strength measurements to the literature.
+
+Using the methods described in Section~\ref{subsec:absorption}, we
+produce maps of the absorption line strength indices for each galaxy
+(shown in Appendix~\ref{sec:maps}). In this section, we thereafter
+measure the relation between Mg and stellar velocity dispersion and
+compare our absorption line strength measurements to other
+measurements in the literature.
 
 \subsection{Mg\,--\,$\sigma$ relation}
-		\label{subsec:Mgsigma}
-		%The Mg$_2$ absorption line index of \citet{Trager1998} has overlapping bandpasses with the Mg\,b index (also of \citeauthor{Trager1998}), but includes the MgH molecular absorption line, and is hence considered a molecular index and is measured in units of magnitude.
-		\citet{Bender1993} observed the tight relationship between the global Mg$_2$ absorption line strength and logarithm of the central velocity dispersion, $\sigma_0$, in elliptical galaxies.
-They also noticed that residuals to the best-fitting line appeared to be intrinsic as they have a near Gaussian distribution about the median values and do not seem to be correlated to any other galaxy property.
-
-		Part of the red continuum band of the Mg$_2$ index is outside of the spectral range of VIMOS, but \citet{Ziegler1997} show there is an approximately linear relationship between Mg\,b and Mg$_2$, with a gradient of 14.3--15.5\,mag\,\AA$^{-1}$\ depending on metallicity.
-Thus, following \citet{Ziegler1997}, we also use Mg\,b as a proxy for Mg$_2$.
-
-		Using an aperture with a radius of 2\arcsec\ on each datacube, we measure $\sigma_0$ and Mg\,b at a spectral resolution of 8.4\,\AA\ full-width half-maximum (FWHM), chosen such that the transformation functions of \citet{Vazdekis2010} can be used to change the literature measurements from the Lick/IDS system to the LIS.
-The results are shown in Fig.\,\ref{fig:globalMg} with the best-fitting linear relationship %(found using \textsc{lts\_linefit} %\footnotemark[\ref{Cappellari}]
-		%by \citealt{Cappellari2013}) 
-		shown by the solid black line.
-This has a gradient of $3.3 \pm 1.0 \,\mathrm{\text{\AA}\,dex^{-1}}$.
-It was noted that NGC 1316 is a possible outlier.
-Removing NGC 1316 from the fit gives a gradient of $2.5 \pm 0.7 \,\mathrm{\AA\,dex^{-1}}$ (green dashed line in Fig.\,\ref{fig:globalMg}).
-Both fits are in very good agreement with the gradient found by \citet{Ziegler1997} (transformed to the LIS system using the functions of \citealt{Vazdekis2010}) for a sample of elliptical galaxies within Virgo and Coma %using data from \citet{Dressler1987}
-		of $2.7\,\mathrm{\text{\AA}\,dex^{-1}}$ (blue dotted line in Fig.\,\ref{fig:globalMg}).%, with an intrinsic scatter of 0.16\,\AA\ for galaxies with $\log \sigma_0 \geqslant 2.3$\,dex.
+\label{subsec:Mg-sigma}
+
+% The Mg$_2$ absorption line index of \citet{Trager1998} has
+% overlapping bandpasses with the Mg\,b index (also of
+% \citeauthor{Trager1998}), but includes the MgH molecular absorption
+% line, and is hence considered a molecular index and is measured in
+% units of magnitude.
+
+\citet{Bender1993} observed a tight relationship between the global
+Mg$_2$ absorption line strength (a variant of the Mg~$b$ line
+strength) and the logarithm of the central stellar velocity
+dispersion, $\sigma_0$, in elliptical galaxies. They also noticed that
+the residuals from the best-fitting linear relation appeared to be
+intrinsic, with a near Gaussian distribution about the median value
+{\bf (Was that median value $\approx0$? If so, state explicitly. If
+  not, then the fit was either bad or there is something we do not
+  understand.)} and no correlation with any other galaxy property.
+
+Part of the red continuum band of the Mg$_2$ index is outside the
+spectral range of VIMOS, but \citet{Ziegler1997} showed there is an
+approximately linear relationship between Mg~$b$ and Mg$_2$, with a
+gradient of $14.3$\,--\,$15.5$~mag~\AA$^{-1}$ depending on
+metallicity. {\bf (Why the strange units? Is Mg$_2$ measured in mag
+  rather than \AA? If so, add a short note. If not, correct.)} Thus,
+following \citet{Ziegler1997}, we also use Mg~$b$ as a proxy for
+Mg$_2$.
+
+Using a central circular aperture with a radius of $2\arcsec$ in each
+datacube, we measure $\sigma_0$ and Mg~$b$ at a degraded spectral
+resolution of $8.4$~\AA\ full-width at half-maximum (FWHM), chosen
+such that the transformation functions of \citet{Vazdekis2010} can be
+used to change literature measurements from the Lick/IDS system to the
+LIS. The results are shown in Fig.~\ref{fig:globalMg}, with the
+best-fitting linear relationship
+% (found using \textsc{lts\_linefit} from \citealt{Cappellari2013})
+indicated by the solid black line, with a gradient of
+$3.3\pm1.0$~\AA~dex$^{-1}$. It was noted that NGC~1316 is a possible
+outlier. {\bf (Noted by who or where? Specify. Also mention that it
+  seems to again be an outlier here.)} Excluding NGC~1316 from the fit
+yields a gradient of $2.5\pm0.7$~\AA~dex$^{-1}$ (green dashed line in
+Fig.~\ref{fig:globalMg}). Both fits are in very good agreement with
+the gradient found by \citet{Ziegler1997} for a sample of elliptical
+galaxies in the Virgo and Coma clusters of galaxies
+% using data from \citet{Dressler1987}
+($2.7$~\AA~dex$^{-1}$, transformed to the LIS system using the
+functions of \citealt{Vazdekis2010}; blue dotted line in
+Fig.~\ref{fig:globalMg}). {\bf (Any uncertainty on this value of
+  $2.7$? If so, quote it.)}
+% , with an intrinsic scatter of 0.16\,\AA\ for galaxies with
+% $\log \sigma_0 \geqslant 2.3$\,dex.
+
+{\bf (One element I find confusing in this sub-section is that the
+  first paragraph mentions a ``global'' relation, but the third
+  paragraph and Fig.~3 use central $2\arcsec$ radius apertures that
+  are therefore ``central'' apertures. Which one is right? You need to
+  harmonise this. Also, in Fig.~\ref{fig:globalMg}, are you using the
+  full relation of \citet{Ziegler1997} or just their gradient (and you
+  then select a zero-point that suits you)? If the latter, then you
+  must state this in the text. In other words, is the near perfect
+  match of the green dashed and blue dotted lines truly a result or is
+  it partially by construction (i.e.\ because you matched the
+  zero-points yourself)? Clarify.)}
 
@@
   \includegraphics[width=\columnwidth]{Mg_sigma.png}
-			\caption[Global Mg\,b\,--\,$\sigma$]{The Mg\,b\,--\,velocity dispersion relation using a 2\arcsec aperture.
-We find a similar gradient to our best-fitting (solid black) line as that found by \citet[transformed to LIS with the functions of \citealt{Vazdekis2010}; blue dotted line]{Ziegler1997}.
-Removing NGC 1316 from the fit (green dashed) results in an extremely good agreement with \citet{Ziegler1997}.}
+  \caption[Global Mg\,b\,--\,$\sigma$]{The Mg~$b$\,--\,central stellar
+    velocity dispersion relation, using a central circular aperture of
+    $2\arcsec$ radius. VIMOS and MUSE measurements are shown in red
+    and blue, respectively. The best-fitting linear relation (solid
+    black line) has a similar gradient to that found by
+    \citeauthor{Ziegler1997} (\citeyear{Ziegler1997}; transformed to
+    LIS using the functions of \citealt{Vazdekis2010}; blue dotted
+    line). Removing NGC~1316 from the fit (green dashed line) results
+    in a nearly perfect agreement (the green dashed and blue dotted
+    lines are essentially indistinguishable). {\bf (In the legend,
+      ``same'' should be ``Same'', ``Ziegler97'' should be ``Ziegler
+      \& Bender (1997)'', and ``Fit excluding...'' should be
+      ``Best-fitting excluding...''. In the y-axis label, there should
+      be a space between ``$b$'' and ``(\AA)''. The x-axis label
+      should be ``$\log\,(\sigma_0/{\rm km~s^{-1}})$''.)}}
   \label{fig:globalMg}
@@
 
-	\subsection{Comparison to the Literature}
+\subsection{Comparisons to the Literature}
 \label{subsec:Lit}
-		Given that there is no well defined list of corrections (and correction methods) that is universally followed, care must be taken when making comparisons to the literature.
-When comparing to a particular paper we correct for the same effects described in the paper, but using our methods, as described in Section \ref{subsec:absorption}.
-As in Section \ref{subsec:Mgsigma} we use a resolution of 8.4\,\AA\ FWHM in order to use the transformation function provided by \citet{Vazdekis2010} from Lick/IDS system to the LIS.
-
-		Table \ref{tab:litAbsorption} summarises our comparisons to the literature.
-For the comparison to \citet{Vazdekis2010}, we analysed the SAURON dataset\footnote{\url{http://www.strw.leidenuniv.nl/sauron/}} \citep{Emsellem2004} using the same analysis pipeline as for our Southern Sample.
+
+Given that there is no well-defined list of corrections (or correction
+methods) that is universally accepted, care must be taken when
+comparing different line strength measurements. In what follows, when
+comparing to the measurements reported in a specific paper, we
+therefore correct for the same effects described in that paper, but
+using our methods (see Section~\ref{subsec:absorption}). To provide a
+fair comparison between indices, and to have the benefit of the
+transformation functions of \citet{Vazdekis2010} for literature
+measurements, we again use a degraded spectral resolution of
+$8.4$~\AA\ FWHM (see Section~\ref{subsec:Mg-sigma}).
+
+Table \ref{tab:litAbsorption} summarises our comparisons to multiple
+sets of literature measurements, where the offsets and dispersions
+listed are defined as the means and standard deviations of the
+differences between the literature measurements and ours. For the
+comparison to \citet{Vazdekis2010}, we re-analysed the Spectral Aeral
+Unit for Research on Optical Nebulae (SAURON)
+dataset\footnote{\url{http://www.strw.leidenuniv.nl/sauron/}}
+\citep{Emsellem2004} using the same analysis pipeline as for our
+Southern Sample. {\bf (Why not use the much larger Atlas$^{\rm 3D}$
+  dataset instead? Explain briefly if justified.)}
 
 \begin{table}
-			\centering
+  \begin{center}
   % \begin{threeparttable}
-			\caption{Comparisons of measured absorption line indices to the literature.
-Comparisons to \citet{Rampazzo2005} are sampled at 7 radial apertures for each galaxy: 1.5, 2.5 and 10.0\arcsec\ and R$_e$/10, R$_e$/8, R$_e$/4 and R$_e$/2.
-Col.\,1: Index.
-Col.\,2: Number of galaxies in comparison.
-Col.\,3: Offset equals the mean of the measurements from the literature subtract our measurements.
-Col.\,4: Dispersion equals the standard deviation of the measurements from the literature subtract our measurements.}
+    \caption{Comparisons of measured and literature absorption line
+      strength measurements.}
     \label{tab:litAbsorption}
-			% \begin{tabular*}{0.8\textwidth}{@{\extracolsep{\fill}}l r r r}
-			\begin{tabular}{l r r r}
-				\hline
-				\hline
-				Index 		& \multicolumn{1}{c}{N$_\mathrm{gals}$} & \multicolumn{1}{c}{Offset} & \multicolumn{1}{c}{Dispersion} \\
-							& 		&\multicolumn{1}{c}{\AA}& \multicolumn{1}{c}{\AA} \\
+    \begin{tabular*}{0.4\textwidth}{@{\extracolsep{\fill}}l r r r}
+      \hline
+      \hline
+      Index 		& \multicolumn{1}{c}{$N_\mathrm{gals}$} & \multicolumn{1}{c}{Offset} & \multicolumn{1}{c}{Dispersion} \\
+                        & 		& \multicolumn{1}{c}{(\AA)} & \multicolumn{1}{c}{(\AA)} \\
       \hline
@@
       \hline
-				H\,$\beta$ 	& 46		& -0.02\leavevmode\phantom{0}& 0.25\leavevmode\phantom{0}	\\
-				Fe5015		& 46		& 0.66\leavevmode\phantom{0}& 0.34\leavevmode\phantom{0}	\\
-				Mg\,b 		& 46		& 0.06\leavevmode\phantom{0}& 0.33\leavevmode\phantom{0}	\\
+      H$\beta$  	& $46$		& $-0.02\leavevmode\phantom{0}$ & $0.25\leavevmode\phantom{0}$\\
+      Fe5015		& $46$		& $0.66\leavevmode\phantom{0}$ & $0.34\leavevmode\phantom{0}$\\
+      Mg~$b$ 		& $46$		& $0.06\leavevmode\phantom{0}$ & $0.33\leavevmode\phantom{0}$\\
       \hline
@@
       \hline
-				G4300 		& 3 		& 2.29\leavevmode\phantom{0}& 0.11\leavevmode\phantom{0}	\\
-				Fe4383 		& 3 		& 0.39\leavevmode\phantom{0}& 0.23\leavevmode\phantom{0}	\\
-				Ca4455 		& 3 		& -0.19\leavevmode\phantom{0}& 0.09\leavevmode\phantom{0}	\\
-				Fe4531 		& 3 		& 0.16\leavevmode\phantom{0}& 0.26\leavevmode\phantom{0}	\\
-				H\,$\beta$ 	& 3 		& 0.17\leavevmode\phantom{0}& 0.12\leavevmode\phantom{0}	\\
-				Fe5015 		& 3 		& -0.73\leavevmode\phantom{0}& 0.48\leavevmode\phantom{0}	\\
-				Mg\,b 		& 3 		& -0.43\leavevmode\phantom{0}& 0.17\leavevmode\phantom{0}	\\
+      G4300 		& $3$ 		& $2.29\leavevmode\phantom{0}$ & $0.11\leavevmode\phantom{0}$\\
+      Fe4383 		& $3$ 		& $0.39\leavevmode\phantom{0}$ & $0.23\leavevmode\phantom{0}$\\
+      Ca4455 		& $3$ 		& $-0.19\leavevmode\phantom{0}$ & $0.09\leavevmode\phantom{0}$\\
+      Fe4531 		& $3$ 		& $0.16\leavevmode\phantom{0}$ & $0.26\leavevmode\phantom{0}$\\
+      H$\beta$  	& $3$ 		& $0.17\leavevmode\phantom{0}$ & $0.12\leavevmode\phantom{0}$\\
+      Fe5015 		& $3$ 		& $-0.73\leavevmode\phantom{0}$ & $0.48\leavevmode\phantom{0}$\\
+      Mg~$b$		& $3$ 		& $-0.43\leavevmode\phantom{0}$ & $0.17\leavevmode\phantom{0}$\\
       \hline
@@
       \hline
-				H\,$\beta$ 	& 2 		& -0.28\leavevmode\phantom{0}& 0.17\leavevmode\phantom{0}	\\ 
-				Fe5015 		& 2 		& 0.87\leavevmode\phantom{0}& 0.34\leavevmode\phantom{0}	\\ 
-				Mg\,b 		& 2 		& 0.31\leavevmode\phantom{0}& 0.14\leavevmode\phantom{0}	\\
-				Fe5270 		& 2 		& -0.11\leavevmode\phantom{0}& 0.15\leavevmode\phantom{0}	\\
-				Fe5335 		& 2 		& 0.08\leavevmode\phantom{0}& 0.15\leavevmode\phantom{0}	\\
-				Fe5406 		& 2 		& 0.16\leavevmode\phantom{0}& 0.07\leavevmode\phantom{0}	\\
-				Fe5709 		& 2 		& 0.11\leavevmode\phantom{0}& 0.10\leavevmode\phantom{0}	\\
-				Fe5782 		& 2 		& -0.03\leavevmode\phantom{0}& 0.11\leavevmode\phantom{0}	\\
-				NaD 		& 2 		& 0.90\leavevmode\phantom{0}& 0.41\leavevmode\phantom{0}	\\
-				TiO1 (mag)	& 2 		& -0.004	& 0.003	\\
-				TiO2 (mag)	& 2 		& -0.011	& 0.007	\\
+      H$\beta$  	& $2$ 		& $-0.28\leavevmode\phantom{0}$ & $0.17\leavevmode\phantom{0}$\\ 
+      Fe5015 		& $2$ 		& $0.87\leavevmode\phantom{0}$ & $0.34\leavevmode\phantom{0}$\\ 
+      Mg~$b$ 		& $2$ 		& $0.31\leavevmode\phantom{0}$ & $0.14\leavevmode\phantom{0}$\\
+      Fe5270 		& $2$ 		& $-0.11\leavevmode\phantom{0}$ & $0.15\leavevmode\phantom{0}$\\
+      Fe5335 		& $2$ 		& $0.08\leavevmode\phantom{0}$ & $0.15\leavevmode\phantom{0}$\\
+      Fe5406 		& $2$ 		& $0.16\leavevmode\phantom{0}$ & $0.07\leavevmode\phantom{0}$\\
+      Fe5709 		& $2$ 		& $0.11\leavevmode\phantom{0}$ & $0.10\leavevmode\phantom{0}$\\
+      Fe5782 		& $2$ 		& $-0.03\leavevmode\phantom{0}$ & $0.11\leavevmode\phantom{0}$\\
+      NaD 		& $2$ 		& $0.90\leavevmode\phantom{0}$ & $0.41\leavevmode\phantom{0}$\\
+      TiO1 (mag)	& $2$ 		& $-0.004$	& $0.003$\\
+      TiO2 (mag)	& $2$ 		& $-0.011$	& $0.007$\\
       \hline
@@
       \hline
-				H\,$\beta$ 	& 6 		& 0.07\leavevmode\phantom{0}& 0.60\leavevmode\phantom{0}	\\
-				Fe5015 		& 6 		& -0.09\leavevmode\phantom{0}& 0.15\leavevmode\phantom{0}	\\
-				Mg\,b 		& 6 		& -0.70\leavevmode\phantom{0}& 0.08\leavevmode\phantom{0}	\\
+      H$\beta$  	& $6$ 		& $0.07\leavevmode\phantom{0}$ & $0.60\leavevmode\phantom{0}$\\
+      Fe5015 		& $6$ 		& $-0.09\leavevmode\phantom{0}$ & $0.15\leavevmode\phantom{0}$\\
+      Mg~$b$ 		& $6$ 		& $-0.70\leavevmode\phantom{0}$ & $0.08\leavevmode\phantom{0}$\\
       \hline
@@
       \hline
-				H\,$\beta$ 	& 3 		& -0.04\leavevmode\phantom{0}& 0.23\leavevmode\phantom{0}	\\ 
-				Fe5015 		& 3 		& -0.16\leavevmode\phantom{0}& 0.33\leavevmode\phantom{0}	\\ 
-				Mg\,b 		& 3 		& -1.10\leavevmode\phantom{0}& 0.26\leavevmode\phantom{0}	\\
-				Fe5270 		& 3 		& -0.66\leavevmode\phantom{0}& 0.16\leavevmode\phantom{0}	\\
-				Fe5335 		& 3 		& -0.66\leavevmode\phantom{0}& 0.11\leavevmode\phantom{0}	\\
-				Fe5406 		& 3 		& -0.51\leavevmode\phantom{0}& 0.06\leavevmode\phantom{0}	\\
-				Fe5709 		& 3 		& -0.22\leavevmode\phantom{0}& 0.08\leavevmode\phantom{0}	\\
-				NaD 		& 3 		& -1.57\leavevmode\phantom{0}& 0.16\leavevmode\phantom{0}	\\
-				\hline
-				\hline
-			\end{tabular}
+      H$\beta$  	& $3$ 		& $-0.04\leavevmode\phantom{0}$ & $0.23\leavevmode\phantom{0}$\\ 
+      Fe5015 		& $3$ 		& $-0.16\leavevmode\phantom{0}$ & $0.33\leavevmode\phantom{0}$\\ 
+      Mg~$b$ 		& $3$ 		& $-1.10\leavevmode\phantom{0}$ & $0.26\leavevmode\phantom{0}$\\
+      Fe5270 		& $3$ 		& $-0.66\leavevmode\phantom{0}$ & $0.16\leavevmode\phantom{0}$\\
+      Fe5335 		& $3$ 		& $-0.66\leavevmode\phantom{0}$ & $0.11\leavevmode\phantom{0}$\\
+      Fe5406 		& $3$ 		& $-0.51\leavevmode\phantom{0}$ & $0.06\leavevmode\phantom{0}$\\
+      Fe5709 		& $3$ 		& $-0.22\leavevmode\phantom{0}$ & $0.08\leavevmode\phantom{0}$\\
+      NaD 		& $3$ 		& $-1.57\leavevmode\phantom{0}$ & $0.16\leavevmode\phantom{0}$\\
+      \hline
+      \hline
+    \end{tabular*}
     % \begin{tablenotes}
-		% 	\footnotesize
-		% 	\note Comparisons to \citet{Rampazzo2005} are sampled at 7 radial apertures for each galaxy: 1.5, 2.5 and 10.0 arcsec and R$_e$/10, R$_e$/8, R$_e$/4 and R$_e$/2. 
-		% 	\item Col.\,1: Index.
-Col.\,2: Number of galaxies in comparison.
-Col.\,3: Offset equals the mean of the measurements from the literature subtract our measurements.
-Col.\,4: Dispersion equals the standard deviation of the measurements from the literature subtract our measurements.
+    \parbox[t]{0.4\textwidth}{\footnotesize\textit{Notes:} Comparisons
+      to \citet{Rampazzo2005} are sampled at $7$ radial apertures for
+      each galaxy: $1.5$, $2.5$ and $10\farcs0$, and $R_\text{e}/10$,
+      $R_\text{e}/8$, $R_\text{e}/4$ and $R_\text{e}/2$. Col.~1: Line
+      strength index. Col.~2: Number of galaxies in
+      comparison. Cols.~3 and 4: Mean and standard deviation of the
+      differences between the literature measurements and ours.}
+  \end{center}
   % \end{tablenotes}
@@
 
-		We find a very large offset for the G4300 index with respect to the results of \citet{Rampazzo2005}.
-This index is extremely sensitive to the stellar velocity dispersion correction and we measure an average difference in the stellar velocity dispersion to that measured by \citet{Rampazzo2005} of $21\,\mathrm{km\,s^{-1}}$.
-This may be enough to account for the difference in the measurements.
-
-		We also observe that the offset in the Fe5015 index is also quite large in comparisons with \citet{Rampazzo2005} and \citet{Vazdekis2010}.
-In the case of the comparison with \citet{Rampazzo2005} we suggest that the difference is due to differences in method for accounting for the [\ion{O}{iii}] emission doublet, however the origin of the offset is less clear in case of the comparison with \citet{Vazdekis2010}.
-
-		Other than G4300 and Fe5015, the comparisons show fairly consistent agreement with literature measurements although the dispersion of the comparisons are fairly large.
-We suggest that the translation between Lick and LIS systems may be the source of this spread.
+We find a very large offset between the G4300 index measurements of
+\citet{Rampazzo2005} and ours. This index is however extremely
+sensitive to the stellar velocity dispersion correction, and we
+measure an average difference of the stellar velocity dispersions
+measured by \citet{Rampazzo2005} and us of $21$~km~s$^{-1}$. This may
+be enough to account for the offset of the measurements. {\bf (Why not
+  check this by changing the stellar velocity dispersions used in your
+  corrections to those of \citealt{Rampazzo2005}? Check.)}
+
+The offsets of our Fe5015 index measurements are also relatively large
+when compared to the measurements of \citet{Rampazzo2005} and
+\citet{Vazdekis2010}. The origin of this offset is unclear for the
+latter, but for the former it may be due to differences in the way the
+[\ion{O}{iii}] doublet emission is accounted for. {\bf (In both cases,
+  the offsets are smaller than $3\sigma$, in the sense that the stated
+  offset is less than $3$ times the stated dispersion. The offsets are
+  thus not really significant... is this discussion therefore really
+  worth it? A number of other indices from \citealt{Rampazzo2005} also
+  show equally significant offsets ($\approx2\sigma$). What about
+  them? I think this notion of the ``significance'' of the offsets
+  must be introduced/addressed to justify which offsets you choose to
+  discuss.)}
+
+Indices other than G4300 and Fe5015 generally have literature
+measurements that are fairly consistent with ours, although the
+dispersions of the measurements are fairly large (perhaps due to the
+transformations from Lick to LIS system indices).
+
+{\bf (A number of the offsets listed in the table actually {\em are}
+  significant (i.e.\ $>3\sigma$). In particular, a majority of the
+  offsets with the \citealt{Ogando2008} measurements are
+  significant. Why are these measurements so inconsistent? I think
+  this should be discussed.)}
 
@@
 \label{sec:stellarPop}
-	We have assumed that a given spectrum from our Southern sample can be well approximated by a SSP.
-We use the method described in Section \ref{subsubsec:stellarPop} to produce maps of the most-likely SSP characteristics: age ($t$), metallicity ($Z/H$) and alpha-element enhancement ($\alpha$/Fe) from the absorption line strength maps (see Appendix \ref{sec:maps}).
-
-	In general, our sample galaxies show old, metal rich and alpha enhanced SSPs; qualities which ETGs are well known for.
-The exception is NGC 612 and NGC 1316.
-NGC 1316 shows a very young stellar population (our fit of $t \approx 2$\,Gyr agrees with that of \citealt{Kuntschner2000}, but is conflicting with the older and less metal rich stellar population of \citealt{Koleva2011} who found $t=4.5 \pm 0.3 \,\mathrm{Gyr}$ and $\mathrm{[Fe/H]}=0.12 \pm 0.01 \,\mathrm{dex}$ for an aperture covering the central 0.1 kpc).
-We also find NGC 612 to have a young stellar population of $t\approx 4\,\mathrm{Gyr}$.
-NGC 3557 is notable for containing a significantly younger ($t\approx 4$\,Gyr) core of about 10\arcsec\ diameter and NGC 3100 has a branch of young stars ($\approx 4$\,Gyr) along the south-east branch of the molecular gas (white contours in Fig \ref{fig:ngc3100}).
+
+{\bf (Here, you just straightaway jump into a discussion of the
+  stellar populations, i.e.\ the derived quantities of age and
+  metallicity. I think this should be preceded (possibly in the
+  previous section) by a discussion of the line strengths themselves,
+  at least in the same spirit as what is done here for the
+  populations, i.e.\ radial gradients and KDCs (that are not discussed
+  in the preceding section on line strengths, that exclusively deals
+  with Mg\,--\,$\sigma$ and the litetature comparison). Add?)}
+
+Assuming that the individual spectra from our Southern Sample galaxies
+can be well approximated by a SSP, we use the methods and the
+absorption line strength maps described in
+Section~\ref{subsec:absorption} to produce maps of the most-likely SSP
+parameters (see Appendix~\ref{sec:maps}): age ($t$), metallicity
+($Z/H$) and alpha-element enhancement ($\alpha$/Fe). {\bf (You must
+  specify here (and presumably also in
+  Section~\ref{subsubsec:stellarPop}) whether the stellar population
+  parameters are mass- or luminosity-weighted.)}
+
+{\bf (I am confused here because in the paragraph above you refer to
+  $Z/H$ as your proxy for metallicity, but in the paragraph below you
+  keep talking about [Fe/H], and in the maps the labels are just
+  ``metalicity'' (yes, with the spelling mistake!). Which one is right
+  (metallicity, $Z/H$, [$Z/H$], Fe/H or [Fe/H]? Use only the right one
+  and be consistent.)}
+
+In general, our Southern Sample galaxies show old, metal-rich and
+alpha-enhanced SSPs, characteristics that are common in ETGs {\bf (Add
+  a classic reference here.)} The exceptions are NGC~612 and
+NGC~1316. NGC~1316 has a very young stellar population (our fit of
+$t\approx2$~Gyr is consistent with that of \citealt{Kuntschner2000},
+but is conflicting with the older and less metal-rich estimate of
+\citealt{Koleva2011}, who found $t=4.5\pm0.3$~Gyr and
+$\mathrm{[Fe/H]}=0.12\pm0.01$ for an aperture covering the central
+$0.1$~kpc). {\bf (Is that a circular or square aperture? If circular,
+  is $0.1$~kpc the radius or diameter? Clarify.)} We also find NGC~612
+to have an extended young stellar population of
+$t\approx4$~Gyr. Otherwise, NGC~3557 is notable for containing a
+significantly younger ($t\approx4$~Gyr) core of $\approx10\arcsec$ in
+diameter, and NGC~3100 has a branch of young stars ($t\approx4$\,Gyr)
+along the south-east branch of the molecular gas (white contours in
+Fig.~\ref{fig:ngc3100}). {\bf (I do not see the age feature you refer
+  to in the NGC3100 maps, and the CO is distributed North-East to
+  South-West, so there is no South-East CO ``branch''. Perhaps you
+  meant South-West (where there is indeed a blue region in the
+  H$\beta$ map, if not in the age map)? Also, there is no white
+  contour in the figure. The CO contours are in pale
+  blue/turquoise. Is that what you meant? In any case, this needs to
+  be corrected to reflect the truth.)}
 
@@
 
-		\citet{Koleva2011} showed that while individual galaxies can have a wide range of radial gradients of age and metallicity, the mean gradient (within a mass bin) is approximately constant across a large mass range.
-They assume a linear relationship between $\log t$ or [Fe/H] and $\log (R/\mathrm{R_e})$.
-We repeat this fit with our Southern Sample with the results shown in Table \ref{tab:derivedProp}.
+\citet{Koleva2011} showed that while there are wide ranges of radial
+gradients of age and metallicity across galaxy populations, the mean
+gradients are approximately constant across a large mass range. To
+probe this they assumed a linear relationship between $\log(t)$ or
+[Fe/H] and $\log(R/R_\text{e})$, i.e.\ as is common the gradients
+considered are logarithmic radial gradients. We repeated these fits
+with our Southern Sample galaxies, and the results are listed in
+Table~\ref{tab:derivedProp}.
 
 \begin{table*}
-			\centering
-			\caption{Derived properties of the Southern Sample.
-Col.\,1: Galaxy.
-Col.\,2--3: Radial gradient of the age of most-likely SSP model.
-Col.\,4--5: Radial gradient of the metallicity of most-likely SSP model.
-Col.\,6--7: \ion{H}{ii} mass derived from the H$\beta$ (assuming a Balmer decrement of 2.85) or H$\alpha$ line in the VIMOS or MUSE data, respectively.
-Col.\,8: Balmer decrement measured from the MUSE data.
-Col.\,9: Main source of ionizing radiation (see Section \ref{subsec:Diagnostics} for a description of the different classes).
--- indicates no data.}
+  \begin{center}
+    \caption{Derived stellar population and ionised gas properties of
+      our Southern Sample galaxies.}
     \label{tab:derivedProp}
-			\begin{tabular}{l c c c c c c c c}
-				\hline
-				\hline 
-				Galaxy 	& \multicolumn{2}{c}{$\Delta_\text{log t}$} & \multicolumn{2}{c}{$\Delta_\text{[Fe/H]}$} & \multicolumn{2}{c}{\ion{H}{ii} Mass} & Balmer & LINER/ \\
-						& VIMOS & MUSE & VIMOS & MUSE & VIMOS$^{a}$ & MUSE & Decrement & Seyfert \\
-						& & & & & ($\log\mathrm{M_\odot}$) & ($\log\mathrm{M_\odot}$) & \\
-					\hline
-					ESO 443-G024 & $0.019 \pm 0.013$ & -- & $-0.01 \pm 0.02$ & -- & $5.02 \pm 0.01$ & -- & -- & LINER \\
-					IC 1459 	& $0.005 \pm 0.015$ & $0.003 \pm 0.002$ & $-0.02 \pm 0.02$ & $0.00 \pm 0.06$ & $5.21 \pm 0.01$ & $5.50 \pm 0.01$ & $4.54 \pm 0.12$ & LINER-AGN \\
-					IC 1531 	& $0.012 \pm 0.015$ & -- & $0.01 \pm 0.02$ & -- & $5.09 \pm 0.01$ & -- & -- & Seyfert 2\\
-					IC 4296		& $0.012 \pm 0.010$ & $0.000 \pm 0.002$ & $-0.03 \pm 0.01$ & $0.04 \pm 0.08$ & $5.43 \pm 0.01$	& $< 4.48$ 	& $^{b}$ & LINER-AGN \\
-					NGC 612 	& $0.068 \pm 0.060$ & -- & $-0.11 \pm 0.02$ & -- & $6.00 \pm 0.01$ 	& -- 		& -- & LINER-AGN \\
-					NGC 1316 	& -- & $0.001 \pm 0.002$ & -- &$0.05 \pm 0.03$ & -- 				& $ 5.29 \pm 0.01$ & $3.52 \pm 0.11$ & LINER-AGN \\
-					NGC 1399 	& $0.019 \pm 0.005$ & $0.001 \pm 0.002$ & $-0.02 \pm 0.03$ & $0.10 \pm 0.09$ & $< 3.86$ 			& $ 4.54 \pm 0.01$ & $< 21.4$ $^{c}$ & LINER \\
-					NGC 3100 	& $0.000 \pm 0.010$ & -- & $-0.06 \pm 0.01$ & -- & $5.26 \pm 0.01$	& -- 		& -- & LINER-AGN \\
-					NGC 3557 	& $0.048 \pm 0.039$ & -- & $-0.05 \pm 0.05$ & -- & $4.61 \pm 0.02$ 	& -- 		& -- & LINER \\
-					NGC 7075 	& $0.007 \pm 0.011$ & -- & $-0.07 \pm 0.02$ & -- & $4.68 \pm 0.01$	& -- 		& -- & LINER \\
-					PKS 718-34  & $0.002 \pm 0.009$ & -- & $-0.17 \pm 0.03$ & -- & $< 5.08$	 		& -- 		& -- & Passive \\
-				\hline
-				\hline
-				\multicolumn{9}{L{.95\linewidth}}{$^{a}$The VIMOS flux calibration and thus the derived gas masses are only approximate (see Section \ref{sec:obs} for more detail on the flux calibration).} \\
-				\multicolumn{9}{L{.95\linewidth}}{$^{b}$Both H$\alpha$ and H$\beta$ are not detected with A/N $>2.5$, so no information can be gained.} \\
-				\multicolumn{9}{L{.95\linewidth}}{$^{c}$H$\beta$ is not detected with A/N $> 2.5$, so the fit is unreliable. Instead the limits for a 2.5 A/N detection are shown.}
-			\end{tabular}
+    \begin{tabular*}{0.95\textwidth}{@{\extracolsep{\fill}}l c c c c c c c c}
+      \hline
+      \hline 
+      Galaxy & \multicolumn{2}{c}{$\Delta\log(t)$} & \multicolumn{2}{c}{$\Delta\text{[Fe/H]}$} & \multicolumn{2}{c}{$\log(M_\text{\ion{H}{ii}}/\mathrm{M_\odot})$} & Balmer Dec. & Ionisation\\
+             & VIMOS & MUSE & VIMOS & MUSE & VIMOS$^\text{a}$ & MUSE & & \\
+      \hline
+      ESO~443-G024 & $0.019\pm0.013$ & -- & $-0.01\pm0.02$ & -- & $5.02\pm0.01$ & -- & -- & LINER \\
+      IC~1459 & $0.005\pm0.015$ & $0.003\pm0.002$ & $-0.02\pm0.02$ & $0.00\pm0.06$ & $5.21\pm0.01$ & $5.50\pm0.01$ & $4.54\pm0.12$ & LINER-AGN \\
+      IC~1531 & $0.012\pm0.015$ & -- & $\leavevmode\phantom{-}0.01\pm0.02$ & -- & $5.09\pm0.01$ & -- & -- & Seyfert 2\\
+      IC~4296 & $0.012\pm0.010$ & $0.000\pm0.002$ & $-0.03\pm0.01$ & $0.04\pm0.08$ & $5.43\pm0.01$ & $< 4.48$ & $^\text{b}$ & LINER-AGN \\
+      NGC~612 & $0.068\pm0.060$ & -- & $-0.11\pm0.02$ & -- & $6.00\pm0.01$ & --	& -- & LINER-AGN \\
+      NGC~1316 & -- & $0.001\pm0.002$ & -- &$0.05\pm0.03$ & -- & $ 5.29\pm0.01$ & $3.52\pm0.11$ & LINER-AGN \\
+      NGC~1399 & $0.019\pm0.005$ & $0.001\pm0.002$ & $-0.02\pm0.03$ & $0.10\pm0.09$ & $< 3.86$ & $ 4.54\pm0.01$ & $< 21.4^\text{c}$ & LINER \\
+      NGC~3100 & $0.000\pm0.010$ & -- & $-0.06\pm0.01$ & -- & $5.26\pm0.01$ & -- & -- & LINER-AGN \\
+      NGC~3557 & $0.048\pm0.039$ & -- & $-0.05\pm0.05$ & -- & $4.61\pm0.02$ & -- & -- & LINER \\
+      NGC~7075 & $0.007\pm0.011$ & -- & $-0.07\pm0.02$ & -- & $4.68\pm0.01$ & -- & -- & LINER \\
+      PKS~718-34 & $0.002\pm0.009$ & -- & $-0.17\pm0.03$ & -- & $< 5.08$ & -- & -- & Passive \\
+      \hline
+      \hline
+    \end{tabular*}
+    \parbox[t]{0.95\textwidth}{\footnotesize\textit{Notes:} Col.~1:
+      galaxy name. Cols.~2\,--\,3: logarithmic radial age gradient of
+      the most-likely SSP model. Cols.~4\,--\,5: logarithmic radial
+      metallicity gradient of the most-likely SSP
+      model. Cols.~6\,--\,7: \ion{H}{ii} mass derived from the
+      H$\beta$ (assuming a Balmer decrement of $2.85$) or H$\alpha$
+      line for the VIMOS or MUSE data, respectively. Col.~8: Balmer
+      decrement measured from the MUSE data. Col.~9: Primary
+      ionisation mechanism (see Section~\ref{subsec:Diagnostics} for a
+      description of the different mechanisms).\\
+      $^\text{a}$ The VIMOS flux calibration and thus the derived
+      \ion{H}{ii} masses are only approximate (see
+      Section~\ref{sec:obs} for more detail on the flux
+      calibration).\\
+      $^\text{b}$ Neither H$\alpha$ nor H$\beta$ is detected with
+      $A/N>2.5$, so no useful Balmer decrement can be measured.\\
+      $^\text{c}$ H$\beta$ is not detected with $A/N>2.5$, so the fit
+      is unreliable and only an upper limit on the Balmer decrement
+      (assuming an H$\beta$ detection with $A/N=2.5$) is reported.}
+  \end{center}
 \end{table*}
 
-		We find average gradients of $\Delta_\text{log t} = 0.014\pm0.007$ and $\Delta_\text{[Fe/H]} = -0.03\pm0.01$.
-This is consistent with \citet{Koleva2011} who, for elliptical galaxies found average gradients of $0.06\pm0.09$ and $-0.26\pm0.08$ for the age and metallicity gradients, respectively.
-For S0s they find flatter corresponding gradients of $0.01\pm0.11$ and $-0.12\pm0.13$.
-
-	\subsection{Kinematically-Decoupled Cores}
+We find average logarithmic radial gradients of
+$\Delta\log(t)=0.014\pm0.007$ and
+$\Delta\text{[Fe/H]}=-0.03\pm0.01$. These are consistent with the
+results of \citet{Koleva2011}, who found average gradients of
+respectively $0.06\pm0.09$ and $-0.26\pm0.08$ for elliptical galaxies,
+and respectively $0.01\pm0.11$ and $-0.12\pm0.13$ (i.e.\ flatter) for
+lenticular galaxies.
+
+\subsection{Kinematically-decoupled Cores}
 \label{subsec:popKDC}
-		\citet{Kuntschner2010} found that KDCs can be separated two classes: they are either small with various stellar ages or typically larger but containing an old stellar population.
-The size of the KDC is defined as the radius of the region surrounding the KDC where the superposition of the two components (the KDC and the host galaxy) results in a local minimum in the mean velocity.
-The age of the most-likely SSP model for the spatially integrated spectrum within an aperture 1\arcsec\ on the centre of the galaxy is taken as the KDC's age.
-
-		The small KDCs are too small to be spatially resolved by our data, and thus are not considered here.
-The larger, old KDCs are typically embedded in slow rotators.
-They have no upper limit on the age of their stellar populations suggesting that the stars within the KDC dominate in total mass as well as surface brightness.
-Thus, they do not fade into their host galaxies as they age unlike the small KDCs \citep{Kuntschner2010}.
-\citet{Bois2011} showed major mergers may well result in such large KDCs if the initial spin axis of the progenitor galaxy with the lowest bulge-to-disc ratio (later-type) is anti-parallel to the orbital angular momentum vector.
-
-		In Fig.\,\ref{fig:KDC} we show the age and size of the 3 KDCs hosted by galaxies in our Southern sample.
-We include PKS 718-34 here but stress it is only tentatively classified as containing a KDC.
-As can be seen from Fig.\,\ref{fig:KDC}, PKS 718-34 would be an extremely large KDC, but is still consistent with the findings of \citet{Kuntschner2010}.
+
+\citet{Kuntschner2010} showed that KDCs can be separated into two
+classes: either small with various stellar ages or typically larger
+but containing a homogeneously old stellar population. {\bf (I thought
+  the first to point this out was McDermid et al.\ (2006; see e.g.\
+  their Fig.~16), which should at least also be quoted here. Check and
+  possibly correct.)} The size of the KDC is defined as the radius
+where the superposition of the two kinematic components (the KDC and
+the host galaxy) results in a local minimum in the mean velocity. The
+age of the most-likely SSP model for the spatially integrated spectrum
+within a central aperture of $1\arcsec$ {\bf (Again, square or
+  circular, radius or diameter? Clarify.)} is taken as the KDC's
+age. {\bf (Are these two definitions (of the KDCs' sizes and ages)
+  those of \citealt{Kuntschner2010} or yours or both? Clarify.)}
+
+The typical size of the smaller class of KDCs (always hosted by fast
+rotators) is too small to be spatially resolved by our data, so these
+KDCs are not considered here. The generally larger, old KDCs are
+typically hosted by slow rotators \citep{Kuntschner2010}. They have no
+upper limit on their stellar ages, i.e.\ they do not fade into their
+host galaxies as they age unlike the small KDCs, suggesting the stars
+within these large KDCs dominate in mass as well as surface
+brightness. \citet{Bois2011} showed major mergers may well result in
+such large KDCs if the initial spin axis of the progenitor galaxy with
+the lowest bulge-to-disc ratio (i.e.\ the later-type galaxy) is
+anti-parallel to its orbital angular momentum vector.
+
+In Fig.~\ref{fig:KDC}, we show the age and size of each of the $3$
+KDCs identified in our Southern Sample galaxies. We include the
+PKS~718-34 KDC here, but we stress it is only tentatively classified
+as a KDC. As can be seen from Fig.~\ref{fig:KDC}, the KDC of
+PKS~718-34 would be extremely large, but nevertheless all $3$ KDCs are
+consistent with those found by \citet{Kuntschner2010}.
 
@@
   \includegraphics[width=\columnwidth]{KDC_size_age.png}
-			\caption[KDC dichotomy]{The KDC size\,--\,age relation.
-KDCs can be separated two classes: old and embedded in a slow rotator or small and embedded in a fast rotator.VIMOS observations are are in red, MUSE in blue and SAURON from \citet{Kuntschner2010} in black and grey for fast and slow rotators respectively.}
+  \caption[KDC dichotomy]{KDC size\,--\,age relation. KDCs can be
+    separated into two classes: old (and potentially large) and
+    embedded in a slow rotator or small (and generally young) and
+    embedded in a fast rotator. Our Southern Sample VIMOS and MUSE
+    measurements are shown in red and blue, respectively, while the
+    measurements from SAURON \citep{Kuntschner2010} are shown in black
+    and grey for respectively fast and slow rotators. {\bf (In the
+      legend, ``same'' should be ``Same'', ``Fast rotating'' should be
+      ``Fast-rotating'', and ``Slow rotating'' should be
+      ``Slow-rotating''. In the y-axis label, ``Gyrs'' should be
+      ``Gyr''.)}}
   \label{fig:KDC}
@@
 
-\section{Ionized Gas Distribution, Kinematics and Ionization}
+\section{Ionised Gas Source}
 \label{sec:gas}
-	Using the methods described in Section \ref{subsubsec:EmissionFit}, we find the best-fitting line-of-sight velocity distribution (LOSVD; assumed to be Gaussian and parametrised by the mean velocity and velocity dispersion only) of the emission lines in each bin.
-Images of the Southern Sample galaxies in the [\ion{O}{iii}]$\lambda\lambda$4957,5007 doublet are shown in Appendix \ref{sec:maps} (we choose to show [\ion{O}{iii}] as detections of all emission lines require a detection of [\ion{O}{iii}] first, see Section \ref{subsubsec:EmissionFit}).
-
-	Only 4 galaxies of the Southern Sample have emission lines detected outside of their central region (IC 1459, NGC 612, NGC 1316 and NGC 3100).
-Of the remaining 7 galaxies, NGC 1399 and PKS 718-34 have no detection of H$\beta$ in their spatially-resolved map (although we do detect H$\beta$ in the spatially-integrated spectrum of NGC 1399; see Table \ref{tab:derivedProp}), while the other 5 galaxies are only detected in their centre.
-All other emission lines have similar distributions, but with different fluxes.
-
-	As can be seen from the maps in Appendix \ref{sec:maps}, both NGC 612 and NGC 3100 have significant off-centre clouds of ionized gas.
-The latter is spatial coincident with both the radio jet and the gap in the CO ring, while former seems to no link with either the radio jet (a massive jet extending $\sim 200$\,kpc to the east and west of the galaxy centre) or the CO.
-
-	Total ionized gas masses are derived using the prescription of \citet{Sarzi2005}.
-This is a very rough calculation and the values should not be used for quantitative applications.
-The approach follows \citet{Kim1989}, whereby
+
+\subsection{Ionised Gas Distribution and Mass}
+\label{subsec:gas_mass}
+
+Using the methods described in Section~\ref{subsec:EmissionLines}, we
+find the best-fitting LOSVD of the emission lines in each bin of our
+Southern Sample galaxies. As with the stellar LOSVD, this is assumed
+to be Gaussian in shape and is thus parametrised by the mean velocity
+and velocity dispersion only. For each detected galaxy, the integrated
+flux map in the [\ion{O}{iii}]$\lambda\lambda$4957,5007 doublet is
+shown in Appendix~\ref{sec:maps} (we choose to show [\ion{O}{iii}], as
+detection of any of the other emission lines first requires a
+detection of [\ion{O}{iii}]; see
+Section~\ref{subsec:EmissionLines}). When the emission is spatially
+extended, we also show the [\ion{O}{iii}] mean velocity and velocity
+dispersion maps in Appendix~\ref{sec:maps}.
+
+Only $4$ galaxies (IC~1459, NGC~612, NGC~1316 and NGC~3100) of our
+Southern Sample have emission lines detected outside of their central
+region. Of the remaining $7$ galaxies, $5$ (IC~1531, IC~4296,
+NGC~3557, NGC~7075 and ESO~443-G024) are only detected in their centre
+(so only the integrated flux map is shown in Appendix~\ref{sec:maps}),
+and $2$ (NGC~1399 and PKS~718-34) have no detection of any emission
+line in a spatially-resolved manner (so no ionised gas map is shown in
+Appendix~\ref{sec:maps}). For each individual galaxy, all the emission
+lines have a similar distribution (but different fluxes). {\bf (It
+  would help in this paragraph to define what you mean by
+  ``centre''. E.g.\ ``a centred circular region of radius
+  $???\arcsec$'' or ``within $???\arcsec$ of the centre. Add.)}
+
+As can be seen from the maps in Appendix~\ref{sec:maps}, both NGC~612
+and NGC~3100 have significant off-centred ionised gas emission. {\bf
+  (What do you mean by ``significant'' here? Bright?
+  Clarify. Equivalently, why is the off-centred emission in IC~1459
+  and NGC~1316 not considered significant?)} In NGC~612, the ionised
+gas does not appear related to either the radio jet (extending
+$\approx200$~kpc to the East and West of the galaxy centre) or the CO,
+but in NGC~3100 the ionised gas is spatially coincident with both the
+radio jet and the gap in the CO ring.
+
+Total ionised gas masses can be derived using the prescription of
+\citet{Sarzi2005}. This is a very rough calculation, however, so the
+values should not be used for quantitative applications. The approach
+follows \citet{Kim1989}, whereby the total mass of \ion{H}{ii}
+($M_\text{\ion{H}{ii}}$) is given by
 \begin{equation}
-		\left(\frac{M_\text{\ion{H}{ii}}}{M_\odot}\right) = 280 \left(\frac{D}{10\, \mathrm{Mpc}}\right)^2 \left(\frac{F(\mathrm{H\alpha})}{10^{-14} \, \mathrm{erg \, s^{-1} \, cm^{-2}}}\right) \left(\frac{10^3 \, \mathrm{cm^{-3}}}{n_\mathrm{e}}\right) \, ,
+  \left(\frac{M_\text{\ion{H}{ii}}}{M_\odot}\right)=280\left(\frac{D}{10\,\mathrm{Mpc}}\right)^2\left(\frac{F(\mathrm{H\alpha})}{10^{-14}\,\mathrm{erg\,s^{-1}\,cm^{-2}}}\right)\left(\frac{10^3\,\mathrm{cm^{-3}}}{n_\mathrm{e}}\right)~,
 \end{equation}
-	where $M_\text{\ion{H}{ii}}$ is the total mass of \ion{H}{ii} in the galaxy, $D$ is the galaxy distance, and $F(\mathrm{H\alpha})$ is the H$\alpha$ flux measured from the spectrum created by summing spatially all spaxels within an aperture of $\frac{R_\mathrm{e}}{2}$ (chosen to exclude noisy outer regions of the observations, but still includes the bulk of the gas in system with significant spatially-extended gas).
-This method assumes an electron density $n_\mathrm{e} = 100 \, \mathrm{cm^{-3}}$, a temperature of $10^4$ K and case-B recombination.
-Like \citet{Sarzi2005}, we only claim a detection if the amplitude-to-noise ratio (A/N) is $>4$ for [\ion{O}{iii}] and $>2.5$ for H$\beta$ or H$\alpha$ lines for VIMOS and MUSE data, respectively.
-When these conditions are not met, upper limits are calculated using the using the 2.5 A/N level, assuming the gas has the same velocity dispersion as the stellar component.
-
-	Our calculated gas masses are given Table \ref{tab:derivedProp} and are at the upper limit of, and possibly exceed, the typical masses observed in ETGs.
-Given that our sample contains particularly massive galaxies, high ionized gas masses are not unexpected, however.
-
-	\subsection{Ionized Gas Kinematics}
+where $D$ is the galaxy distance, $F(\mathrm{H\alpha})$ is the
+H$\alpha$ flux measured from a spectrum created by spatially
+integrating over a central circular aperture of radius
+$R_\mathrm{e}/2$ (selected to exclude the noisy outer regions of the
+observations, but still include the bulk of the gas in galaxies with
+significant spatially-extended emission), and as in \citet{Sarzi2005}
+we choose an electron density $n_\mathrm{e}=100$~cm$^{-3}$. This
+method assumes an ionised gas temperature of $10^4$~K and case-B
+recombination \citep{Kim1989}. Like \citet{Sarzi2005}, we only claim a
+detection if the amplitude-to-noise ratio $A/N>4$ for [\ion{O}{iii}]
+and $>2.5$ for H$\beta$ (VIMOS data) or H$\alpha$ (MUSE data). When
+these two conditions are not met, upper limits are calculated assuming
+the gas has $A/N=2.5$ and the same velocity dispersion as the stars.
+
+Our calculated ionised gas masses are listed in
+Table~\ref{tab:derivedProp}. They are at the upper edge of, and
+possibly exceed, {\bf (Why ``possibly''? They either always exceed,
+  generally exceed, occasionally exceed, or never exceed! Check and
+  clarify.)} the typical masses observed in ETGs
+\citep[e.g.][]{Phillips1986, Zeilinger1996, Sarzi2005}. Given that our
+sample contains particularly massive galaxies, however, high ionised
+gas masses are not unexpected.
+
+\subsection{Ionised Gas Kinematics}
 \label{subsec:GasKin}
-		Map of the best-fitting kinematics (mean velocity and velocity dispersion), as found with the methods described in Section \ref{subsubsec:EmissionFit} for the 4 galaxies (IC 1459, NGC 612, NGC 1316 and NGC 3100) with detected spatially-extended emission lines are shown in Appendix \ref{sec:maps}.
-Due to that fact that, unlike stars, gas is dissipational, it is to be expected that given sufficient time, the ISM will always settle into a disc.
-These maps show that the warm component of the ISM (the ionized gas) of the Southern sample galaxies varies from largely settled discs in IC 1459 and NGC 612 to more disordered kinematics of NGC 3100 and a possible inflow in NGC 1316.
-
-		It is immediately clear when comparing the stellar mean velocity maps to the ionized gas mean velocity maps that where gas is detected, its angular momentum is often not aligned with that of the stars.
-A misalignment between the kinematics of the stars and gas suggests an external origin for the gas (e.g.\ accretion or wet merger).
-However it should be noted that the converse is not necessarily true: aligned kinematics is consistent with an internal origin (e.g.\ stellar-mass loss), but it does \emph{not} require it \citep[e.g.][]{Davis2011a}.
-
-		We now comment on each galaxy in turn.
-
-		\textbf{IC 1459} has ionized gas counter-rotating with respect to the stellar KDC, and also rotating independently from the rest of the galaxy.
-\citet{Franx1988} claim that the rotation of the gas is aligned with that of the stars outside of the KDC, however we observe the outer stellar kinematics to be non-rotating.
-As the stellar disc did not survive the merger even that created the KDC, it is unlikely that the gas in IC 1459 progenitor galaxy survived.
-The lost gas may, however, have been re-accreted.
-Alternatively, the ISM may have yet another external origin.
-
-		\textbf{NGC 612} has well aligned stellar and gaseous kinematics.
-The misalignment between the position angle of the stellar and gas kinematics (using the method described in Section \ref{subsubsec:KinPA}) is just $1\fdg0\pm0\fdg7$, consistent with an internal origin for the gas.
-This adds to the evidence that NGC 612 has not undergone a recent major merger (major mergers exhaust galaxies of their gas and destroy a stellar disc) and suggests that, the fuelling and powering of the radio jet could be a purely secular process.
+
+Maps of the best-fitting ionised gas kinematics (mean velocity and
+velocity dispersion), as measured with the methods described in
+Section~\ref{subsec:EmissionLines}, are shown in
+Appendix~\ref{sec:maps} for the $4$ galaxies with spatially-extended
+emission lines (IC~1459, NGC~612, NGC~1316 and NGC~3100). Because gas
+is dissipational (contrary to stars), it is expected that given
+sufficient time, the ISM will always settle into a disc. The maps in
+Appendix~\ref{sec:maps} show that the ionised gas (i.e.\ the warm
+component of the ISM) of our Southern Sample galaxies varies from
+largely settled discs (IC~1459 and NGC~612) to more disordered
+kinematics (NGC~3100) to a possible inflow (NGC~1316).
+
+It is immediately clear when comparing the stellar and ionised gas
+mean velocity maps that, where gas is detected, its rotation (or,
+equivalently, its projected angular momentum) is often not aligned
+with that of the stars. As noted before \citep[e.g.][]{Davis2011a}, a
+misalignment between the kinematics of the stars and gas suggests an
+external origin for the gas (e.g.\ accretion or wet merger). The
+converse is not necessarily true, i.e.\ aligned kinematics is
+consistent with an internal origin (e.g.\ stellar-mass loss) but does
+\emph{not} require it.
+
+We now comment in turn on the $4$ galaxies with spatially-extended
+ionised gas.
+
+{\bf (In the following paragraphs, as all $4$ galaxies are quite
+  famous (the first $3$ anyway), you should really quote the past
+  literature/papers when you discuss an aspect/feature/property that
+  has already been observed/shown/mentioned before, as many of these
+  aspects have. So do have a look at the literature on each object.)}
+
+\textbf{IC~1459} has ionised gas counter-rotating with respect to the
+stellar KDC, but it is also misaligned with respect to the outer stars
+of the host galaxy (i.e.\ the stars beyond the KDC), that are
+non-rotating (see Fig.~\ref{fig:ic1459}). The ionised gas thus appears
+to have a third, independent, axis of rotation. {\bf (I do not
+  understand why you state/claim that here. From the map shown, it
+  seems pretty clear to me that the stars in the outer parts of the
+  galaxy {\em are} rotating (i.e.\ the top-left is red and the
+  bottom-right is blue), and that they are rotating in a manner
+  consistent with the ionised gas, just as \citet{Franx1988}
+  claimed. Convince me otherwise of change your statement!)} This is
+contrary to \citet{Franx1988} who claims that the rotation of the gas
+is aligned with that of the stars outside of the KDC. As the stellar
+disc did not survive the merger event that created the KDC, {\bf (How
+  do you know there was a stellar disc to start with? Clarify or
+  rephrase.)} it is unlikely that the gas in the progenitor of IC~1459
+survived. However, the lost gas may have remained bound and been
+re-accreted, so that the gas observed today preserves a fossil record
+of the galaxy's original disc. Alternatively, the ISM may have yet
+another external origin.
+
+\textbf{NGC~612} has well aligned stellar and ionised gas kinematics
+(see Fig.~\ref{fig:ngc612}), the misalignment angle (measured as
+described in Section~\ref{subsubsec:KinPA}) being just
+$1\fdg0\pm0\fdg7$, thus consistent with an internal gas origin. This
+adds to the evidence {\bf (What is the other evidence?
+  Summarise/quote it or rephrase.)} that NGC~612 has not undergone a
+recent major merger (major mergers exhaust galaxies of their gas and
+destroy stellar discs), suggesting in turn that the fuelling of the
+radio jet could be a purely secular process.
 
 %**********************************************************************
-%This plot no longer exists
+%This plot no longer exists... Which plot?!
 %**********************************************************************
-		\textbf{NGC 1316} is a complex object.
-Since there are redshifted emission lines with respect to the rest frame of the galaxy on both sides of the galaxy, the gas is not in a settled disc and that there must be some inflow/outflows.
-From visual inspection of the velocity field for the gas (Fig.\,\ref{fig:MUSE_Gaskine}) it is clear that a simple exponential disc model will not be well fitted to the data.
-We suggest that that the large velocity peak on the south-west side of the galaxy could be an inflow towards the nucleus, almost perpendicular to the radio jet, however we acknowledge that other interpretations are possible.
-Better quality data (longer exposure times) and more sophisticated models are required to add certainty to this interpretation.
-Nevertheless, it is clear that the gas in not in a settled disc.
-
-		% Without filling in some of the regions were we do not detect emission lines through additional observations, it is impossible to judge the state or even existence of a disc.
-
-		\textbf{NGC 3100} has an interesting ISM morphology.
-The \ce{^{12}CO(2-1)} contours (shown in white in all maps) show a broken ring with the radio jet passing through the gaps in the ring (Ruffa et\,al., in prep.).
-We observe the ionized gas to be brightest in the gaps of this ring which we interpret as additional excitation of the gas due to shocks from the impact of the jet.
-The simplest comment that we can make of the ionized gas kinematics is that it is completely different than that of the stars.
-Secondly, that the centre of rotation of the gas appears to be offset from the centre of the galaxy (as defined by the stellar surface brightness) by several arcseconds to the west.
+
+\textbf{NGC~1316} is a complex object. The existence of redshifted
+emission lines with respect to the rest frame of the galaxy on both
+sides of the galaxy shows the gas is not in a settled disc and there
+must be some inflows/outflows. Even from a visual inspection of the
+ionised gas velocity field (see Fig.~\ref{fig:ngc1316}), it is clear
+that a simple exponential disc model will not fit the data well. We
+instead speculate that that the high-velocity peak to the South-West
+of the centre is an inflow towards the nucleus, {\bf (Is there any
+  evidence for this? If so, state them!)} almost perpendicular to the
+radio jet, although other interpretations are possible. Better quality
+data (better $S/N$ and a wider field of view) coupled with more
+sophisticated models are required to test this interpretation.
+% Nevertheless, it is clear that the gas in not in a settled disc.
+
+% Without filling in some of the regions were we do not detect
+% emission lines through additional observations, it is impossible to
+% judge the state or even existence of a disc.
+
+\textbf{NGC~3100} has an interesting ISM morphology. The
+\ce{^{12}CO(2-1)} integrated intensity contours (overlaid on the IFS
+maps in white; see Fig.~\ref{fig:ngc3100}) {\bf (Again, no white
+  contours in the figure... pale blue/turquoise contours?)} show a
+broken ring, the radio jet passing through the gaps, hence suggesting
+a jet-ring interaction \citep[see][]{ruffa2019, ruffa2020}. The
+ionised gas is brightest in those same gaps, that we interpret as
+additional excitation of the gas due to shocks from the impact of the
+jet. It is unclear if the ionised gas kinematics supports this
+interpretation, being completely different than that of the stars (and
+nearly totally blueshifted). The centre of rotation of the gas also
+appears to be offset from the centre of the galaxy (as defined by its
+stellar surface brightness), by several arcseconds to the west. {\bf
+  (I really do not understand how you can identify a centre of
+  rotation when there is no evidence of organised rotation at
+  all. Either convince me of that or remove/change that
+  comment. Perhaps mention the lack of obvious large-scale rotation
+  instead?!)}
 
 \subsubsection{Kinematic Misalignments}
-			\citet{Davis2011a} showed that $36\pm5$\% of fast rotators have ionized gas kinematics misaligned with respect to the stellar kinematics, while slow rotators have a flat distribution with respect to their misalignment angles \citep[see fig.\ 4]{Davis2011a}.
-This indicates that slow rotators are dominated by external sources of gas, while fast rotators can have either internal or external sources.
-This is consistent with our observations of the Southern Sample: the only slow rotator with detected ionized gas is IC 1459, which has significantly kinematically-misaligned gas, while of the 3 fast rotators, only 1 (NGC 3100) is definitely misaligned, while NGC 612 is consistent with an internal gas origin and NGC 1316 is unclear.
-%, although the best-fitting exponential disc model (see Fig.\ \ref{fig:Inflow}) is definitely misaligned to the stellar kinematics.
-
-	\subsection{Ionization Sources}
+\label{subsec:kinmis}
+
+\citet{Davis2011a} showed that only $36\pm5\%$ of fast rotators have
+ionised gas kinematics misaligned with respect to that of the stars,
+while slow rotators have a nearly flat distribution of misalignment
+angles (see, e.g., Fig.~4 of \citealt{Davis2011a}). This indicates
+that the source of ionised gas is primarily external in slow rotators,
+while it can be either external or internal in fast rotators. The
+observations of our Southern Sample are consistent with this: the only
+slow rotator with spatially-extended ionised gas is IC~1459, that has
+significantly kinematically-misaligned gas, while of the $3$ fast
+rotators with spatially-extended ionised gas, only $1$ (NGC~3100) is
+definitely misaligned (the misalignment angle of NGC~612 is consistent
+with an internal gas origin while that of NGC~1316 is unclear).
+% , although the best-fitting exponential disc model (see Fig.\
+% \ref{fig:Inflow}) is definitely misaligned to the stellar
+% kinematics.
+
+\subsection{Ionisation Sources}
 \label{subsec:Diagnostics}
-		Determining the sources of ionizing radiation in galaxies using emission line ratios, such as Baldwin\,--\,Phillips\,--\,Terlevich (BPT) plots (\citealt{Baldwin1981}; revised by \citealt{Kewley2001, Kewley2006} and \citealt{Kauffmann2003a}), has become an increasingly widespread exercise.
-That said, there are several important caveats.
-Firstly, great care must be taken when applying each diagnostic; much of the literature misinterprets the resulting classifications.
-Secondly, in the absence of spatially-resolved spectra, low-ionization nuclear emission-line region (LINER) classifications have often been taken as a marker for jet-mode AGN.
-However, several recent surveys have shown that many of these may not be bona-fide AGN \citep[e.g.][]{Sarzi2005, Sarzi2010, Singh2013, Belfiore2016a}.
-In these cases, the emission may not even originate exclusively from the centres of the galaxies, the location of the putative AGN.
-This led to the creation of the low-ionization emission-line region (LIER) classification, with the same criteria as LINERs, but not necessarily restricted to the nuclear regions.
-
-		The problem with classifying ETGs by their emission lines is that they often have very little ionized gas and weak ionizing radiation fields, so that it is often difficult to detect emission lines from their ISM.
-Furthermore, the BPT plots require a larger spectral range than many IFS deliver.
-This has given rise to a number of other, analogous, classifying plots, that we take advantage of here.
-A description of our ionization source classifying process follows below.
-
-		Firstly, we preferentially use the BPT plots for the galaxies observed with MUSE (MUSE has the required spectral range).
-This allows us to classify galaxies into star-forming, LINER/LIER or Seyfert 2 classes.
-For the emission-line fluxes derived from the VIMOS datacubes, we use the [\ion{N}{i}]/H$\beta$ versus [\ion{O}{iii}]/H$\beta$ plot of \citet[hereafter the SAURON plot]{Sarzi2010}.
-Unlike the BPT plots, \citet{Sarzi2010} do not define classification boundaries.
-Using Eq.\,\ref{eq:N_dec} we translate the [\ion{N}{ii}]/H$\alpha$ BPT plot classification boundaries of \citet{Kewley2001} and \citet{Kauffmann2003a} to the [\ion{N}{i}]/H$\beta$ SAURON plot.
-This allows us to classify galaxies into star-forming or LINER/Seyfert 2 classes.
-We also use the so-called WHaN2 plot (H$\alpha$ equivalent width versus [\ion{N}{ii}]/H$\alpha$) from \citet{CidFernandes2011}.
-Using Eqs.\,\ref{eq:EqW_dec} and \ref{eq:N_dec}, we transform the boundary lines into a H$\beta$ equivalent width versus [\ion{N}{i}]/H$\beta$ (WHbN1) plot for the VIMOS data.
-This allows us to classify galaxies into star-forming, strong AGN (Seyfert 2), weak AGN (LINER) or retired classes.
-
-		To check if the LINER classifications are due to a central radiation source (such as an AGN) or extended sources (such as weak star formation or post-asymptotic giant branch stars; pAGB stars), we examine the H$\alpha$ and H$\beta$ flux radial profiles of our galaxies with extended detected ionized gas (see Section \ref{subsubsec:Hb}).
-Finally we use the mass\,--\,excitation (MEx) plot of \cite{Nyland2016}, using parameters derived from the spatially-integrated spectra within an aperture of radius 3\arcsec\ thus only probing the central region of the galaxies (see Section \ref{subsubsec:MEx}).
-This allows us to classify the remaining galaxies into star-forming, Seyfert 2, LINER, transition or passive classes, and subdivide LINER galaxies into those whose LINER characteristics are attributable to a central AGN (labelled as LINER-AGN in Table \ref{tab:derivedProp}) and those whose LINER characteristics are not.
-We expand on the final two steps in the sections below.
+
+Determining the sources of ionising radiation in galaxies using
+emission line ratios, such as Baldwin\,--\,Phillips\,--\,Terlevich
+(BPT) plots (\citealt{Baldwin1981}; revised by e.g.\
+\citealt{Kewley2001, Kewley2006} and \citealt{Kauffmann2003a}), has
+become an increasingly widespread exercise. That said, there are
+several important caveats. Firstly, great care must be taken when
+applying each diagnostic; much of the literature misinterprets the
+resulting classifications. Secondly, in the absence of
+spatially-resolved spectra, low-ionisation nuclear emission-line
+region (LINER) classifications have often been taken as a marker for
+jet-mode AGN. However, several recent surveys have shown that many of
+these may not be bona-fide AGN \citep[e.g.][]{Sarzi2005, Sarzi2010,
+  Singh2013, Belfiore2016a}. In these cases, the emission may not even
+originate exclusively from the galaxy centres, the location of the
+putative AGN. This led to the creation of the low-ionisation
+emission-line region (LIER) classification, with the same criteria as
+LINERs, but not necessarily restricted to the nuclear regions.
+
+The challenge to classify ETGs using emission line ratios is that they
+often have very little ionised gas and weak ionising radiation fields,
+so that it is often difficult to detect emission lines from their
+ISM. In addition, the BPT plots require spectral lines spread over a
+wider spectral range than many IFSs deliver. This has given rise to a
+number of other, analogous, classification criteria and plots, that we
+take advantage of here. A description of our ionisation source
+classification process thus follows below.
+
+First, we preferentially use the original BPT plots for the galaxies
+observed with MUSE, that has the required spectral range. This allows
+us to classify galaxies into the star-forming, LINER/LIER or Seyfert~2
+class. For the emission line fluxes derived from VIMOS data, we use
+the [\ion{N}{i}]/H$\beta$ versus [\ion{O}{iii}]/H$\beta$ plot of
+\citeauthor{Sarzi2010} (\citeyear{Sarzi2010}; hereafter the SAURON
+plot). Unlike the BPT plots, \citet{Sarzi2010} does not define
+classification boundaries. Using Eq.~\ref{eq:N_dec}, we thus transform
+the [\ion{N}{ii}]/H$\alpha$ BPT plot classification boundaries of
+\citet{Kewley2001} and \citet{Kauffmann2003a} to the
+[\ion{N}{i}]/H$\beta$ SAURON plot. This allows us to classify those
+galaxies into the star-forming or LINER/Seyfert~2 class. We also use
+the so-called WHaN2 plot (H$\alpha$ equivalent width versus
+[\ion{N}{ii}]/H$\alpha$) from \citet{CidFernandes2011}. Using
+Eqs.~\ref{eq:EqW_dec} and \ref{eq:N_dec}, we transform their boundary
+lines into an H$\beta$ equivalent width versus [\ion{N}{i}]/H$\beta$
+(WHbN1) plot for the VIMOS data. This allows us to classify those
+galaxies into the star-forming, strong AGN (Seyfert~2), weak AGN
+(LINER) or retired class.
+
+To check if the LINER classifications are due to central radiation
+sources (such as AGN) or extended sources (such as weak star formation
+or stars on the post-asymptotic giant branch, pAGB), {\bf (What about
+  extended horizontal branch stars (again below)? Mention/discuss.)}
+we examine the H$\alpha$ and H$\beta$ flux radial profiles of our
+Southern Sample galaxies with extended detected ionised gas (see
+Section~\ref{subsubsec:Hb}). Finally, we use the mass\,--\,excitation
+(MEx) plot of \cite{Nyland2016}, using parameters derived from spectra
+spatially-integrated over central circular apertures of radius
+$3\arcsec$, thus probing only the central regions of the galaxies (see
+Section~\ref{subsubsec:MEx}). {\bf (You talked here of *the*
+  spatially-integrated spectra, as if spectra within a central
+  $3\arcsec$ aperture had been used before, but this is not the case
+  (only $2\arcsec$ and $1\arcsec$ apertures were used for stellar
+  populations). Are these new or previously-generated spectra?
+  Clarify.)} This allows us to classify the remaining galaxies (with
+no spatially-extended ionised gas) into the star-forming, Seyfert~2,
+LINER, transition or passive class, and to subdivide LINER galaxies
+into those whose LINER characteristics are attributable to a central
+AGN (labelled as LINER-AGN) and those whose LINER characteristics are
+not. {\bf (Labelled as what? LIER?  Clarify.)} As the least
+conventional, we expand on the final two steps in the two sub-sections
+below, while the final classifications are listed in~Table
+\ref{tab:derivedProp}.
 
@@
 % \label{subsec:BPT}
-		% 	Firstly, in Fig.\,\ref{fig:BPT}, we examine our galaxies using the classic BPT diagnostic plots.
-For the plots using [\ion{N}{ii}]/H$\alpha$, [\ion{S}{ii}]/H$\alpha$ and [\ion{O}{i}]/H$\alpha$ versus [\ion{O}{iii}]/H$\beta$, we can only use the emission-line fluxes derived from our MUSE datacubes, as the lines necessary for gauging the hardness of the ionizing radiation field are outside the spectral range of VIMOS.
-Only two MUSE galaxies have detections of the necessary emission lines: IC 1459 and NGC 1316.
-Both occupy very similar positions in the BPT plots, on or close to the boundary between the Seyfert 2 and LINER classes.
-On the whole, the central bins tend to be on the LINER side.
+% Firstly, in Fig.\,\ref{fig:BPT}, we examine our galaxies using the
+% classic BPT diagnostic plots. For the plots using
+% [\ion{N}{ii}]/H$\alpha$, [\ion{S}{ii}]/H$\alpha$ and
+% [\ion{O}{i}]/H$\alpha$ versus [\ion{O}{iii}]/H$\beta$, we can only
+% use the emission-line fluxes derived from our MUSE datacubes, as the
+% lines necessary for gauging the hardness of the ionising radiation
+% field are outside the spectral range of VIMOS. Only two MUSE
+% galaxies have detections of the necessary emission lines: IC~1459
+% and NGC~1316. Both occupy very similar positions in the BPT plots,
+% on or close to the boundary between the Seyfert 2 and LINER
+% classes. On the whole, the central bins tend to be on the LINER
+% side.
 
@@
 %   \includegraphics[width=.9\textwidth]{chapter5/BPT.png}
-		% 		\caption[BPT plots]{BPT plots for IC 1459 and NGC 1316.
-The colour scale (blue to yellow) represents increasing distance from the galaxy centre.
-The classification boundaries are from \citet{Kewley2006}.\label{fig:BPT}}
-		% 	% \end{figure}
-
-		% 	% \begin{figure}
-		% 	% 	\centering
+%   \caption[BPT plots]{BPT plots for IC~1459 and NGC~1316. The colour
+%   scale (blue to yellow) represents increasing distance from the
+%   galaxy centre. The classification boundaries are from
+%   \citet{Kewley2006}.\label{fig:BPT}}
+% \end{figure}
+
+% \begin{figure}
+%   \centering
 %   \includegraphics[width=0.7\textwidth]{chapter5/SAURON.png}
-		% 		\caption[An alternative diagnostic plot]{SAURON diagnostic plot for the line ratios available in the VIMOS datacubes.
-To show the expected position of LINERs on the SAURON plot, the MAPPINGS-III shock model grid of \citet{Allen2008} is shown in green.
-The solid lines are lines of constant shock velocity (from 150 to 1000\,$\mathrm{km\,s^{-1}}$) and the dotted lines are lines of constant magnetic parameter $b \equiv B/\sqrt{n}$ (from 0.5 to 4.0), where $B$ is the magnetic field strength and $N$ the (pre-shock) particle number density \citep{Dopita1996}.
-All models assume an electron density of $n_\mathrm{e} = 1\,\mathrm{cm^{-3}}$.\label{fig:SAURON}}
+%   \caption[An alternative diagnostic plot]{SAURON diagnostic plot
+%   for the line ratios available in the VIMOS datacubes. To show the
+%   expected position of LINERs on the SAURON plot, the MAPPINGS-III
+%   shock model grid of \citet{Allen2008} is shown in green. The solid
+%   lines are lines of constant shock velocity (from 150 to
+%   1000\,$\mathrm{km\,s^{-1}}$) and the dotted lines are lines of
+%   constant magnetic parameter $b \equiv B/\sqrt{n}$ (from 0.5 to
+%   4.0), where $B$ is the magnetic field strength and $N$ the
+%   (pre-shock) particle number density \citep{Dopita1996}. All models
+%   assume an electron density of
+%   $n_\mathrm{e} = 1\,\mathrm{cm^{-3}}$.\label{fig:SAURON}}
 % \end{figure}
 
-		% 	\citet{Sarzi2010} showed that Seyferts, LINERs and star-forming galaxies are reasonable separated in the SAURON diagnostic plot.
-To exploit the VIMOS datacubes we thus use the [\ion{N}{ii}]\,--\,[\ion{N}{i}] relation derived in Section \ref{subsec:Ndec}, along with the Balmer decrement, to transform the \citet{Kewley2001} extreme starburst and the \citet{Kauffmann2003a} pure star-formation boundaries in the [\ion{N}{ii}]/H$\alpha$ versus [\ion{O}{iii}]/H$\beta$ plot to boundaries in the SAURON plot.
-For the MUSE datacubes, only IC 1459 and NGC 1316 have detections of [\ion{N}{i}].
-Given that we already have the superior classic BPT plots for these galaxies, we only show the VIMOS-derived SAURON diagnostic plot.
-This is shown in Fig.\,\ref{fig:SAURON} for all 6 VIMOS galaxies with detectable, spatially-resolved emission lines.
-All exhibit LINER-AGN behaviour.
-
-		% 	NGC 3100 appears to occupy to distinct regions in the SAURON diagnostic plot (Fig.\ \ref{fig:SAURON}).
-If the ionization is due to shocks from the impact of the jet, then using the shock models of \citet{Allen2008}, we can see that the right-hand group of bins have been ionized by a higher shock velocity that the left-hand group.
-As can be seen in Fig.\ \ref{fig:ngc3100_NI_Hb}, these bins are directly in the gap (presumable created by the jet blowing a hole) in the CO ring.
+% \citet{Sarzi2010} showed that Seyferts, LINERs and star-forming
+% galaxies are reasonable separated in the SAURON diagnostic plot. To
+% exploit the VIMOS datacubes we thus use the
+% [\ion{N}{ii}]\,--\,[\ion{N}{i}] relation derived in Section
+% \ref{subsec:Ndec}, along with the Balmer decrement, to transform the
+% \citet{Kewley2001} extreme starburst and the \citet{Kauffmann2003a}
+% pure star-formation boundaries in the [\ion{N}{ii}]/H$\alpha$ versus
+% [\ion{O}{iii}]/H$\beta$ plot to boundaries in the SAURON plot. For
+% the MUSE datacubes, only IC~1459 and NGC~1316 have detections of
+% [\ion{N}{i}]. Given that we already have the superior classic BPT
+% plots for these galaxies, we only show the VIMOS-derived SAURON
+% diagnostic plot. This is shown in Fig.\,\ref{fig:SAURON} for all 6
+% VIMOS galaxies with detectable, spatially-resolved emission
+% lines. All exhibit LINER-AGN behaviour.
+
+% NGC~3100 appears to occupy to distinct regions in the SAURON
+% diagnostic plot (Fig.\ \ref{fig:SAURON}). If the ionisation is due
+% to shocks from the impact of the jet, then using the shock models of
+% \citet{Allen2008}, we can see that the right-hand group of bins have
+% been ionised by a higher shock velocity that the left-hand group. As
+% can be seen in Fig.\ \ref{fig:ngc3100_NI_Hb}, these bins are
+% directly in the gap (presumable created by the jet blowing a hole)
+% in the CO ring.
 
@@
 %   \includegraphics[width=0.5\textwidth]{chapter5/vimos/ngc3100_NI_Hb.png}
-		% 		\caption[NGC 3100 \bracket{\ion{N}{i}}/H$\beta$ line ratio map]{The [\ion{N}{i}]/H$\beta$ line ratio map of NGC 3100, showing the hardest ionization field is in gap in the CO ring (white contours), spatially coincident with the radio jet (green contours).
-Surface brightness contours are in black.}
+%   \caption[NGC~3100 \bracket{\ion{N}{i}}/H$\beta$ line ratio
+%   map]{The [\ion{N}{i}]/H$\beta$ line ratio map of NGC~3100, showing
+%   the hardest ionisation field is in gap in the CO ring (white
+%   contours), spatially coincident with the radio jet (green
+%   contours). Surface brightness contours are in black.}
 %   \label{fig:ngc3100_NI_Hb}
@@
 % \label{subsec:WHaN2}
+
 % \begin{figure}
@@
 %   \includegraphics[width=0.8\textwidth]{chapter5/WHaN2.png}
-		% 		\caption[WHaN2 plot for IC 4296]{WHaN2 plot for IC 4296. The colour scale (blue to yellow) represents increasing distance from the galaxy centre.}
+%   \caption[WHaN2 plot for IC~4296]{WHaN2 plot for IC~4296. The
+%   colour scale (blue to yellow) represents increasing distance from
+%   the galaxy centre.}
 %   \label{fig:WHaN2}
@@
 %   \includegraphics[width=0.8\textwidth]{chapter5/WHbN1.png}
-		% 		\caption[VIMOS WHbN1 plot]{VIMOS WHbN1 plot. All galaxies have decreasing H$\beta$ emission with increasing distance from the galaxy centre.}
+%   \caption[VIMOS WHbN1 plot]{VIMOS WHbN1 plot. All galaxies have
+%   decreasing H$\beta$ emission with increasing distance from the
+%   galaxy centre.}
 %   \label{fig:WHbN1}
@@
 
-		% 	The final spatially-resolved line ratio diagnostic plot that we use is that of the equivalent width of H$\alpha$ versus $\log([\text{\ion{N}{ii}}]/H\alpha)$, known as the WHaN2 plot \citep{CidFernandes2011}.
-We interpret the strong AGN, weak AGN and retired regions on this plot as Seyfert 2, LINER-AGN and LIER classifications, respectively.
-Passive (i.e.\ line-less) galaxies are marked with crosses instead of circles.
-Fig.\,\ref{fig:WHaN2} shows the WHaN2 plot for the MUSE derived emission lines of IC 4296 where almost all the bins fall within the weak AGN (LINER-AGN) class.
-This is consistent with the measurements from the VIMOS observations of the IC 4296 as shown in the SAURON diagnostic plot, where IC 4296 is well within the shocks grid (i.e.\ LINERs; see Fig.\ \ref{fig:SAURON}).
-We do not include IC 1459 and NGC 1316, as they have already been classified via the classic BPT plots (see Section \ref{subsec:BPT}).
-
-		% 	For the emission lines measured from the VIMOS datacubes, we use H$\beta$ as a proxy for H$\alpha$ and [\ion{N}{i}] as a proxy for [\ion{N}{ii}] utilising the relations found in Section \ref{subsec:Ndec} to transform the classification boundaries (see Section \ref{subsec:Ndec}).
-We call the resulting diagnostic plot the WHbN1 plot, shown in Fig.\,\ref{fig:WHbN1}.
-While in Section \ref{subsec:BPT} (Fig.\,\ref{fig:SAURON}) we showed that most of these galaxies had line ratios consistent with being ionized by shocks such as in LINER-like galaxies, Fig.\,\ref{fig:WHbN1} shows that for IC 1459 and NGC 3100, the ionizing photons originate from the AGN.
-
-		\subsubsection{H$\alpha$ and H$\beta$ Profiles}
+% The final spatially-resolved line ratio diagnostic plot that we use
+% is that of the equivalent width of H$\alpha$ versus
+% $\log([\text{\ion{N}{ii}}]/H\alpha)$, known as the WHaN2 plot
+% \citep{CidFernandes2011}. We interpret the strong AGN, weak AGN and
+% retired regions on this plot as Seyfert 2, LINER-AGN and LIER
+% classifications, respectively. Passive (i.e.\ line-less) galaxies
+% are marked with crosses instead of circles. Fig.\,\ref{fig:WHaN2}
+% shows the WHaN2 plot for the MUSE derived emission lines of IC~4296
+% where almost all the bins fall within the weak AGN (LINER-AGN)
+% class. This is consistent with the measurements from the VIMOS
+% observations of the IC~4296 as shown in the SAURON diagnostic plot,
+% where IC~4296 is well within the shocks grid (i.e.\ LINERs; see
+% Fig.\ \ref{fig:SAURON}). We do not include IC~1459 and NGC~1316, as
+% they have already been classified via the classic BPT plots (see
+% Section \ref{subsec:BPT}).
+
+% For the emission lines measured from the VIMOS datacubes, we use
+% H$\beta$ as a proxy for H$\alpha$ and [\ion{N}{i}] as a proxy for
+% [\ion{N}{ii}] utilising the relations found in Section
+% \ref{subsec:Ndec} to transform the classification boundaries (see
+% Section \ref{subsec:Ndec}). We call the resulting diagnostic plot
+% the WHbN1 plot, shown in Fig.\,\ref{fig:WHbN1}. While in Section
+% \ref{subsec:BPT} (Fig.\,\ref{fig:SAURON}) we showed that most of
+% these galaxies had line ratios consistent with being ionised by
+% shocks such as in LINER-like galaxies, Fig.\,\ref{fig:WHbN1} shows
+% that for IC~1459 and NGC~3100, the ionising photons originate from
+% the AGN.
+
+\subsubsection{H$\alpha$ and H$\beta$ Radial Profiles}
 \label{subsubsec:Hb}
 
+As discussed above, many galaxies traditionally classified as LINERs
+are in fact LIERs \citep[see e.g.][]{Sarzi2005, Sarzi2010, Singh2013,
+  Belfiore2016}, i.e.\ the source of the ionising radiation is not
+concentrated nor limited to the nuclear regions of the galaxies. To
+check if the ionising radiation is entirely due to AGN in our Southern
+Sample galaxies, we plot the H$\alpha$ (H$\beta$) flux radial profiles
+of the MUSE (VIMOS) galaxies in Fig.~\ref{fig:Ha_profile_MUSE}
+(Fig.~\ref{fig:Hb_profile_VIMOS}). A point source, such as an AGN,
+will result in a radial profile proportional to $r^{-2}$ (and
+convolved with the point-spread function, PSF), where $r$ is the
+distance of the gas from the galaxy centre. Although the observed
+profiles (i.e.\ the bins) are projected on to the sky, a significantly
+shallower profile suggests a spatially-extended source, presumably
+non-circumnuclear stellar processes such as star formation or
+radiation from pAGB stars {\bf (Again.)}, as the dominant cause of the
+ionisation in the outer parts of the galaxy (i.e.\ a LIER rather than
+a LINER).
+
 \begin{figure}
-				\centering
-				\includegraphics[width=0.73\columnwidth]{Halpha_profile.png}
-				\caption{H$\alpha$ flux radial profiles derived from the MUSE datacubes.
-Solid red lines show $F(\mathrm{H\alpha}) \propto r^{-2}$ convolved with a Gaussian function of width equal to the mean seeing taken from the fits file headers.
-This accounts for the point-spread function (PSF) of the observations.\label{fig:Ha_profile_MUSE}}
-				\label{fig:Ha_profile_MUSE}
+  \centering \includegraphics[width=\columnwidth]{Halpha_profile.png}
+  \caption{H$\alpha$ flux radial profiles derived from the MUSE
+    data. Solid red lines show radial profiles proportional to
+    $r^{-2}$, convolved with a Gaussian of width equal to the measured
+    PSF. {\bf (But what about the zero-points of the red profiles? How
+      are these set? Explain.)} {\bf (Make the axis labels and galaxy
+      names as thick as the plot boxes.) {\bf (All labels are rather
+        small. Enlarge?)} {\bf (Note that the bounding boxes of
+        Figs.~5 and 6 are really bad (much too big), so that the
+        ``width='' commands are useless. Please make sure {\em all}
+        your bounding boxes are as tight as possible around the
+        figures themselves.)}}
+    \label{fig:Ha_profile_MUSE}}
 \end{figure}
@@
   \includegraphics[width=\columnwidth]{Hbeta_profile.png}
-				\caption{H$\beta$ flux radial profiles derived from the VIMOS datacubes.
-Solid red lines show $F(\mathrm{H\beta}) \propto r^{-2}$ convolved with a Gaussian function of width equal to the mean seeing taken from the observation logs.
-This accounts for the PSF of the observations.
+  \caption{As Fig.~\ref{fig:Ha_profile_MUSE}, but for the H$\beta$
+    flux radial profiles derived from the VIMOS data. {\bf (Make the
+      axis labels and galaxy names as thick as the plot boxes.) {\bf
+        (All labels are rather small. Enlarge?)}}
     \label{fig:Hb_profile_VIMOS}}
@@
 
-			As discussed above, many galaxies classified as LINERs are in fact LIERs \citep[see e.g.][]{Sarzi2005, Sarzi2010, Singh2013, Belfiore2016}, i.e.\ the source of the ionizing radiation is not concentrated in the nuclear regions of the galaxies.
-To check if the ionizing radiation is entirely due to an AGN throughout the host galaxy, we plot the H$\alpha$ and H$\beta$ flux radial profiles for the MUSE and VIMOS data in Figs.\,\ref{fig:Ha_profile_MUSE} and \ref{fig:Hb_profile_VIMOS}, respectively.
-A point source, such as an AGN, will result in a profile having a $r^{-2}$ shape, where $r$ is the distance of the bin from the galaxy centre.
-A shallower profile points to a spatially-extended source, presumably non-circumnuclear stellar processes such as star formation or radiation from pAGB stars, as the dominant cause of the ionization in the outer parts of the galaxy (i.e.\ LIER rather than LINER).
-All the galaxies with spatially-extended Balmer emission in our Southern Sample reveal a central point source as the dominant source of the ionizing photons.
-The H$\beta$ profile of NGC 612 has a larger scatter suggesting that stellar processes also have some impact (likely radiation from pAGB stars, as these galaxies are ETGs and therefore likely have low star-formation rates).
+The radial profiles shown in Figs.~\ref{fig:Ha_profile_MUSE} and
+\ref{fig:Hb_profile_VIMOS} suggest that all the galaxies with
+spatially-extended Balmer emission in our Southern Sample have a
+central point source as the dominant source of the ionising
+photons. The H$\beta$ profile of NGC~612 has a larger scatter,
+suggesting that stellar processes also have some impact (likely
+radiation from pAGB stars {\bf (Again.)}, as NGC~612 has a low
+star-formation rate). {\bf (Check what the SFR of NGC~612 actually is,
+  to confirm your suspicion, e.g.\ from non-nuclear radio continuum or
+  MIR/FIR emission. This may already be discussed in Ilaria's
+  papers.)}
 
@@
 \label{subsubsec:MEx}
+
+The mass\,--\,excitation (MEx) plot of \citet{Juneau2011} is useful to
+classify galaxies with intermediate excitation levels
+($0.5<\mathrm{[\ion{O}{iii}]/H\beta}<8.0$), particularly as it does
+not depend on faint lines such as the [\ion{N}{i}] doublet. We use
+here the calibrations by \citet{Nyland2016}, including an attempt to
+separate LINERs powered by AGN from those powered by pAGB stars (i.e.\
+LIERs, with [\ion{O}{iii}] equivalent widths $>0.8$~\AA). We again
+focus on the nuclear regions, using a central circular aperture of
+radius $3\arcsec$ for all our Southern Sample galaxies. The resulting
+diagnostic plot is shown in Fig.~\ref{fig:MEx}.
+
 \begin{figure}
   \includegraphics[width=\columnwidth]{nuclear_MEx.png}
-				\caption{Nuclear MEx plot, allowing to classify the sources of the ionizing radiation within the central 3\arcsec.
-Data points derived from the VIMOS and MUSE datacubes are in red and blue, respectively.
-Crosses mark galaxies with [\ion{O}{iii}]$\lambda$5007 equivalent width $> 0.8$\,\AA, while filled circles show galaxies with [\ion{O}{iii}]$\lambda$5007 equivalent width $\leqslant 0.8$\,\AA.
-The VIMOS and MUSE data points of IC 1459 are linked with a black dashed line.
-Classification boundaries are from \citet{Nyland2016}.}
+  \caption{Nuclear MEx plot, allowing to classify the sources of
+    ionising radiation within the central $3\arcsec$ of our Souther
+    Sample galaxies. Measurements derived from VIMOS and MUSE data are
+    show in red and blue, respectively. Crosses mark galaxies with an
+    [\ion{O}{iii}]$\lambda$5007 equivalent width $>0.8$~\AA, while
+    filled circles mark galaxies with an [\ion{O}{iii}]$\lambda$5007
+    equivalent width $\leqslant 0.8$~\AA. The VIMOS and MUSE
+    measurements of IC~1459 are linked by a black dashed
+    line. Classification boundaries are from \citet{Nyland2016}. {\bf
+      (Use larger data points.)} {\bf (Small ``f'' in ``Star-Forming''
+      label. Also add ``(km s$^{-1}$)'' to the x-axis label.)} {\bf
+      (All labels are rather small. Enlarge?)}}
   \label{fig:MEx}
@@
 
-			The mass\,--\,excitation (MEx) plot of \citet{Juneau2011} is useful to classify galaxies with intermediate excitation levels ($0.5 < \mathrm{[\ion{O}{iii}]/H\beta} < 8.0$), particularly as it does not depend on faint lines such as the [\ion{N}{I}] doublet.
-We use here the calibrations by \citet{Nyland2016}, including an attempt to separate LINERs powered by AGN from those powered by pAGB stars (the former have [\ion{O}{iii}] equivalent widths $>0.8$\,\AA).
-We use an aperture of 3\arcsec\ to plot the nuclear MEx for our Southern Sample galaxies, and the resulting diagnostic plot is shown in Fig.\,\ref{fig:MEx}.
-
 \section{Discussion and Conclusions}
 \label{sec:discuss}
-	In Section \ref{sec:StarKine} we show that in terms of the stellar kinematic properties, our radio-selected Southern sample are no different to ordinary optically-selected ETGs.
-Our sample shows a mixture of the regularly- and non-regularly-rotating behaviours, with both classes showing evidence of consistency with observations of the intrinsic shapes of ordinary regular and non-regular rotators.
-At this stage we observe that two (with a tentative third) galaxies host large KDCs.
-We also classify our sample galaxies into fast- and slow-rotators and find a consistent fraction ($45\pm13$\%) of slow-rotators to the ordinary ETG samples of the A+M sample, once the difference in the mass distribution between our Southern sample and the A+M sample are taken into account.
-
-	Radio-loud S0s are extremely rare with only a handful of known cases \citep[e.g.][]{Heckman1982, Morganti2011}, presumably due to the associated mass functions of both S0s and radio galaxies: both massive S0s and low-mass radio galaxies are rare, with a similar transition masses from rare to more numerous.
-NGC 612 is one of those rare cases.
-
-	In terms of absorption line strengths and stellar populations (Sections \ref{sec:absorption} and \ref{sec:stellarPop}), we find a remarkably similar gradient to the central Mg\,b verse stellar velocity dispersion relation to that of \citet{Ziegler1997}.
-Most of the galaxies in our Southern sample show typical ETG behaviour: old, metal-rich stellar populations, with a few exceptions: NGC 612 and NGC 1316 are both significantly younger than most ETGs and NGC 3557 has a young core.
-We observe that all 3 KDCs contain old stellar populations and are consistent with being merger remnants.
-We also show that the KDCs found in Section \ref{sec:StarKine} fit with the age\,--\,size relation found by \citet{Kuntschner2010} (see Section \ref{subsec:popKDC}) for KDCs in optically-selected ETGs.
-
-	If molecular (cold) gas is the fuel source that is accreted on to the central black holes of our Southern sample in order to power the radio jets, unless it is accreted in a highly turbulent fashion, it might be expected that some of that gas might form stars within the accretion disc \citep[e.g.][]{Collin1999, Diamond-Stanic2012, LaMassa2013}.
-If this were the case, and these young stellar populations are bright enough to dominate, they should stand out in the very central (1--2) spaxels.
-Having said that, detection of such a population may prove difficult due to masking by the AGN continuum, the presence of dust (see Table \ref{tab:sample} for a description of the dust morphologies of our sample) and the rapid rate a young stellar population fades.
-Indeed, our best-fitting age maps show no evidence of a young central stellar population.
-This is consistent with results by other authors such as \citet{GonzalezDelgado2004} and \citet{Sarzi2005b} with \textit{Hubble Space Telescope} (\textit{HST}) spectra and \citet{CidFernandes2004} with ground based spectra.
-Furthermore, in section \ref{subsec:Diagnostics}, we show that there is no evidence of an ionizing source with a potential which is consistent with ongoing star formation.
-
-	In Section \ref{sec:gas} we show that galaxies in our Southern Sample have ionized gas masses of $10^4$\,--\,$10^6\,\mathrm{M_\odot}$.
-These are at the upper limit of, and possibly exceed, the typical masses observed in ETGs, although given that our sample contains particularly massive galaxies, high ionized gas masses are not unexpected.
-
-	The only slow rotator with detected, spatially-extended ionized gas, IC 1459, shows evidence through gas\,--\,star kinematic misalignment that the gas has an external origin, although it is possible that the gas has been re-accreted after it was first ejected during the merger that resulted in the stellar KDC.
-
-	Of the other 3 galaxies with detected, spatially-extended ionized gas (NGC 612, NGC 1316 and NGC 3100, all fast rotators), we find that one, NGC 3100, again has kinematic evidence of an external gas origin; another, NGC 612, is consistent with an internal origin; while the situation for the last one (NGC 1316) is not clear, although is definitely not in a settled disc.
-This is in keeping with the findings of \citet{Davis2011a}, who showed that $36\pm5$\% of fast rotators have ionized gas kinematics misaligned with respect to the stellar kinematics, while slow rotators have a flat distribution with respect to their misalignment angles.
-This indicates that slow rotators are dominated by external sources of gas, while fast rotators can have either internal or external sources.
-
-	All galaxies with detectable emission lines in our Southern Sample show LINER or Seyfert 2 characteristics.
-The only Seyfert 2 in our sample is the fast rotator, IC 1531.
-This is consistent with the results of \citet{Nyland2016}, who showed that all ETGs in the Atlas$^\text{3D}$ sample classified as Seyferts are also fast rotators.
-We find 9 of the 11 galaxies to be LINERs, 5 of which we conclusively attribute the ionizing photons to the central AGN.
-The final galaxy, PKS 718-34 has no emission line detections (i.e.\ passive).
-
-	Overall, we thus find that the warm ISM properties of our Southern Sample galaxies are consistent with those of other optically-selected ETGs.
-This is consistent with low-powered radio galaxies being bona-fide detections of jet-mode AGN and therefore our sample galaxies are ordinary massive ETGs experiencing a normal but short-lived active phase, presumably due to the central black holes currently accreting gas in some form.
+
+In Section~\ref{sec:StarKine}, we showed that in terms of their
+stellar kinematic properties our radio-selected Southern Sample
+galaxies are no different than ordinary optically-selected ETGs, i.e.\
+our sample shows a mixture of regularly- and non-regularly-rotating
+objects. Both classes also appear consistent with observations of the
+intrinsic shapes of ordinary regular and non-regular rotators. {\bf (I
+  do not actually know/understand what you were trying to say or refer
+  to in the last sentence. Are you referring to the misalignment angle
+  $\Gamma_\text{kin}$ of regular and non-regular rotators? What do you
+  mean by ``observations of the intrinsic shapes''? Clarify.)} We
+established that two (tentatively three) galaxies host a large KDC. We
+also classified our sample galaxies into fast- and slow-rotators and,
+once differences in the mass distributions of our Southern Sample and
+the A+M sample were taken into account, we found a fraction of
+slow-rotators ($45\pm13\%$) consistent with that of ordinary ETGs.
+
+Radio-loud S0 galaxies are extremely rare, with only a handful of
+known cases \citep[e.g.][]{Heckman1982, Morganti2011}. This is
+presumably due to the mass functions of S0s and radio galaxies,
+massive S0s and low-mass radio galaxies both being rare, with similar
+transition masses from rare to more numerous. NGC~612 is one of those
+rare cases. {\bf (You are not discussing here any of your own results,
+  just rehashing old knowledge, so unless you have something else to
+  say about NGC~612 (from your own work), I would suggest to remove
+  this paragraph entirely (and/or certainly move it somewhere else
+  more relevant).)}
+
+In terms of absorption line strengths and stellar populations
+(Sections~\ref{sec:absorption} and \ref{sec:stellarPop}), we found for
+our Southern Sample galaxies a gradient of the central Mg~$b$ line
+strength versus stellar velocity dispersion relation remarkably
+similar to that of \citet{Ziegler1997}. Most of the galaxies in our
+Southern Sample have typical ETG properties, with old, metal-rich
+stellar populations. {\bf (What about $\alpha$-elements? You should
+  also summarise those results here.)} The few exceptions are NGC~612
+and NGC~1316, that are both significantly younger than most ETGs, and
+NGC~3557, that has a young core. All $3$ KDCs contain old stellar
+populations, and they are consistent with being merger remnants. The
+KDCs found in Section~\ref{sec:StarKine} are also in agreement with
+the KDC age\,--\,size relation found by \citet{Kuntschner2010} in
+optically-selected ETGs (see Section~\ref{subsec:popKDC}). {\bf (See
+  my previous comment about McDermid et al.\ 2006, and perhaps quote
+  it here instead or additionally.)}
+
+If cold (e.g.\ molecular) gas is accreted on to the central black
+holes of our Southern Sample galaxies to power their nuclear
+activities, then unless it is accreted in a highly turbulent fashion
+some of it should form stars within the accretion discs
+\citep[e.g.][]{Collin1999, Diamond-Stanic2012, LaMassa2013}. If this
+is indeed the case, and these young stellar populations are bright
+enough to dominate the light, then they should stand out in the
+central few spaxels. However, detection of such populations could
+prove difficult due to contamination from the AGN continua, the
+presence of dust (see Table~\ref{tab:sample} for a description of the
+dust morphologies of our Southern Sample galaxies) and the rapid rate
+at which a young stellar population fades. In fact, our best-fitting
+age maps show no evidence of an abnormally young central stellar
+population in any of our galaxies. This is consistent with the results
+of other authors such as \citet{GonzalezDelgado2004} and
+\citet{Sarzi2005b} with \textit{Hubble Space Telescope} (\textit{HST})
+spectra and \citet{CidFernandes2004} with ground-based spectra. In
+addition, in Section~\ref{subsec:Diagnostics}, we showed that there is
+no evidence of an extended ionising source consistent with ongoing
+star formation in any of our targets. {\bf (It seems to me that this
+  paragraph is missing a short ``conclusion''. Add one... no evidence
+  of any ongoing SF in any of our galaxies?)}
+
+In Section~\ref{sec:gas}, we showed that our Southern Sample galaxies
+have ionised gas masses of $10^4$\,--\,$10^6$~$\mathrm{M_\odot}$. As
+our sample contains particularly massive galaxies, high ionised gas
+masses are not unexpected, but these masses are at the upper limit of,
+and possibly exceed {\bf (Again, why ``possibly''? They either always
+  exceed, generally exceed, occasionally exceed, or never exceed!
+  Check and clarify.)}, the typical masses observed in ETGs,
+
+The only slow rotator with detected spatially-extended ionised gas,
+IC~1459, has a substantial gas\,--\,star misalignment. Its gas thus
+likely has an external origin, although it is possible that it has
+been re-accreted after it was first ejected during the merger that
+created the stellar KDC. Of the other $3$ galaxies with detected,
+spatially-extended ionised gas (NGC~612, NGC~1316 and NGC~3100, all
+fast rotators), we find that one (NGC~3100) again has kinematic
+evidence of an external gas origin, another (NGC~612) is consistent
+with an internal origin, while the situation for the third (NGC~1316)
+is unclear (although the ionised gas is definitely not in a settled
+disc). This is consistent with the findings of \citet{Davis2011a}, who
+showed that $36\pm5\%$ of fast rotators have ionised gas kinematics
+misaligned with respect to that of the stars, while slow rotators have
+a flat distribution of misalignment angles. This indicates that the
+source of the gas in slow rotators is predominately external, while it
+can be either internal or external in fast rotators.
+
+All galaxies with detected emission lines in our Southern Sample show
+line ratios characteristic of LINER or Seyfert~2 galaxies. In
+particular, we classify $9$ of our $11$ galaxies as LINERs, and we can
+conclusively attribute the ionising photons to the central AGN in $5$
+of those. The only Seyfert~2 is the fast rotator IC~1531. This is
+consistent with the results of \citet{Nyland2016}, who showed that all
+Atlas$^\text{3D}$ ETGs classified as Seyferts are also fast rotators.
+The final galaxy, PKS~718-34, has no emission line detection (i.e.\ it
+is classified as passive). {\bf (These statistics do not match those
+  in paragraph 2 of Sub-section~8.1, where only $9$ galaxies are said
+  to be detected in ionised gas (rather than $10$ as inferred
+  here). The culprit seems to be NGC~1399, which is listed as
+  non-detected in Sub-section~8.1 and Appendix~A, has no emission line
+  map in Appendix~B, but is nevertheless classified as a LINER in
+  Table~4... how is this possible?! Check and fix/harmonise here, in
+  Sub-section~8.1, in Table~4, and in the second paragraph of
+  Appendix~A.)}
+
+Overall, we thus find that the warm ISM (i.e.\ the ionised gas)
+properties of our Southern Sample galaxies are consistent with those
+of other optically-selected ETGs. Along with our stellar kinematic and
+population results, this is consistent with low-powered radio galaxies
+being bona-fide detections of jet-mode AGN, and therefore our sample
+galaxies being ordinary massive ETGs currently experiencing common but
+short-lived/transient active phases, presumably due to their central
+black holes recently accreting some gas.
 
 \section*{Acknowledgements}
-JW acknowledges funding from the Science and Technology Facilities Council Grant Code 1577871.
-This research makes extensive use of observation from VIMOS \citep{LeFevre2003} and archival data from MUSE \citep{Bacon2010}.
-We also make use of observations from the APEX \citep{Gusten2006} and the ALMA.
-ALMA is a partnership of ESO (representing its member states), the National Science Foundation (NSF; USA) and the National Institutes of Natural Sciences (NINS; Japan), together with the National Research Council (NRC; Canada), the Ministry of Science and Technology (MOST; Taiwan) and Academia Sinica Institute of Astronomy and Astrophysics (ASIAA; Taiwan), and Korea Astronomy and Space Science Institute (KASI; Republic of Korea), in cooperation with the Republic of Chile.
-The Joint ALMA Observatory is operated by ESO, Associated Universities Inc./National Radio Astronomy Observatory (AUI/NRAO; USA) and National Astronomical Observatory of Japan (NAOJ).
-We also make use of data products from the 2MASS, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center (IPAC)/California Institute of Technology, funded by the National Aeronautics and Space Administration (NASA) and NSF.
-We also make use of the Set of Identifications, Measurements and Bibliography for astronomical Data (SIMBAD) database and Portal tool, operated at the Strasbourg astronomical Data Centre (CDS), France.
-This research has made use of the following resources and programs: arXiv.org; the Astrophysics Data System (ADS); \textsc{astropy}, a community-developed core \textsc{python} package for astronomy \citep{TheAstropyCollaboration2013}; \textsc{kinemetry} \citep{Krajnovic2006}; \textsc{ipython} \citep{Perez2007}; \textsc{matplotlib} \citep{Hunter2007}; \textsc{p3d} \citep{Sandin2010, Sandin2011}; \textsc{pPXF} \citep{Cappellari2004}; \textsc{py3d} \citep{Sanchez2011, Husemann2013, Husemann2014}; \textsc{scipy} \citep{Oliphant2007, Millman2011}; \textsc{numpy} \citep{VanderWalt2011}; \textsc{spectools} (Ryan Houghton and Simon Zieleniewski, private comm.); and \textsc{voronoi\_2d\_binning} \citep[including the SAURON colourmaps; ][]{Cappellari2003}.
+
+JW acknowledges funding from the Science and Technology Facilities
+Council Grant Code 1577871. This research made extensive use of
+observation from VIMOS \citep{LeFevre2003} and archival data from MUSE
+\citep{Bacon2010}. We also made use of observations from APEX
+\citep{Gusten2006} and ALMA. ALMA is a partnership of ESO
+(representing its member states), the National Science Foundation
+(NSF; USA) and the National Institutes of Natural Sciences (NINS;
+Japan), together with the National Research Council (NRC; Canada), the
+Ministry of Science and Technology (MOST; Taiwan) and Academia Sinica
+Institute of Astronomy and Astrophysics (ASIAA; Taiwan), and Korea
+Astronomy and Space Science Institute (KASI; Republic of Korea), in
+cooperation with the Republic of Chile. The Joint ALMA Observatory is
+operated by ESO, Associated Universities Inc./National Radio Astronomy
+Observatory (AUI/NRAO; USA) and National Astronomical Observatory of
+Japan (NAOJ). We also made use of data products from 2MASS, which is a
+joint project of the University of Massachusetts and the Infrared
+Processing and Analysis Center (IPAC)/California Institute of
+Technology, funded by the National Aeronautics and Space
+Administration (NASA) and NSF. We also made use of the Set of
+Identifications, Measurements and Bibliography for astronomical Data
+(SIMBAD) database and portal tool, operated at the Strasbourg
+astronomical Data Centre (CDS), France. This research has made use of
+the following resources and programs: arXiv.org; the Astrophysics Data
+System (ADS); \textsc{astropy}, a community-developed core
+\textsc{python} package for astronomy
+\citep{TheAstropyCollaboration2013}; \textsc{kinemetry}
+\citep{Krajnovic2006}; \textsc{ipython} \citep{Perez2007};
+\textsc{matplotlib} \citep{Hunter2007}; \textsc{p3d}
+\citep{Sandin2010, Sandin2011}; \textsc{pPXF} \citep{Cappellari2004};
+\textsc{py3d} \citep{Sanchez2011, Husemann2013, Husemann2014};
+\textsc{scipy} \citep{Oliphant2007, Millman2011}; \textsc{numpy}
+\citep{VanderWalt2011}; \textsc{spectools} (Ryan Houghton and Simon
+Zieleniewski, private comm.); and \textsc{voronoi\_2d\_binning}
+\citep[including the SAURON colourmaps {\bf (Colourmaps, whatever that
+  might be, or colour table? Clarify.)}; ][]{Cappellari2003}.
 
@@
 \appendix
-\section{Extrapolating VIMOS Data}
+\section{VIMOS Line-ratio Diagnostics}
 \label{sec:Decrement}
-	\begin{figure}
-		\includegraphics[width=\columnwidth]{ratio_fit.png}
-		\caption[\bracket{\ion{N}{ii}}/H$\alpha$ vs \bracket{\ion{N}{i}}/H$\beta$]{Upper panel: [\ion{N}{ii}]/H$\alpha$ vs [\ion{N}{i}]/H$\beta$ line ratios for the galaxies IC 1459 and NGC 1316, used to transform the classification boundaries e.g.\ the classic [\ion{N}{ii}] BPT plot to the SARUON diagnostic plot.
-Lower panel: Residuals = ([\ion{N}{ii}]/H$\alpha$ - best-fit)/[\ion{N}{i}]/H$\beta$.
-The solid line shows the best-fitting (Eq.\ \ref{eq:N_dec}) in both panels, while the dashed and dotted lines show the 68 and 99 percentiles, respectively.}
-		\label{fig:ratio_relation}
-	\end{figure}
-
-	\begin{figure}
-		\includegraphics[width=\columnwidth]{EQw_fit.png}
-		\caption[Comparing H$\alpha$ and H$\beta$ equivalent widths]{Upper panel: H$\alpha$ vs H$\beta$ equivalent widths for the galaxies IC 1459 and NGC 1316 used to transform the classification boundaries of diagnostics involving the H$\alpha$ equivalent width to those involving H$\beta$.
-Lower panel: Residuals = (EW(H$\alpha$) - best-fit)/EW(H$\beta$).
-The solid line shows the best-fitting (Eq.\ \ref{eq:EqW_dec}) in both panels, while the dashed and dotted lines show the 68 and 99 percentiles, respectively.}
-		\label{fig:EqW_relation}
-	\end{figure}
-
-	% The Balmer decrement, $d_\mathrm{H}$, is the ratio of the H$\alpha$ to H$\beta$ fluxes.
-There are good theoretical motivations for this ratio to be near constant at $d_\mathrm{H} = 2.86$, under a wide variety of conditions.
-In reality, however, higher values are routinely observed.
-These can be explained as due to either the presence of dust causing extinction (whereby emission lines at shorter wavelengths appear dimmer than expected from their redder counterparts due to dust preferentially scattering and absorbing bluer light) or some mechanism that populates hydrogen levels from the ground up.
-Such mechanisms may be important in high-density environments, such as within powerful (type 1) AGN \citep[e.g.][]{Shields1974, Netzer1975}.
+
+% The Balmer decrement, $d_\mathrm{H}$, is the ratio of the H$\alpha$
+% to H$\beta$ fluxes. There are good theoretical motivations for this
+% ratio to be near constant at $d_\mathrm{H} = 2.86$, under a wide
+% variety of conditions. In reality, however, higher values are
+% routinely observed. These can be explained as due to either the
+% presence of dust causing extinction (whereby emission lines at
+% shorter wavelengths appear dimmer than expected from their redder
+% counterparts due to dust preferentially scattering and absorbing
+% bluer light) or some mechanism that populates hydrogen levels from
+% the ground up. Such mechanisms may be important in high-density
+% environments, such as within powerful (type 1) AGN
+% \citep[e.g.][]{Shields1974, Netzer1975}.
 % 
-	% The majority ($\approx 60$\%) of ETGs and all LINER and Seyfert galaxies are dusty \citep[e.g.][]{Martini2013}. 
-	% Such galaxies reveal clear dust lanes in \textit{Hubble Space Telescope (HST)} observations \citep[e.g.][]{Martini2013}, are bright in the infrared (where the thermal emission from dust is seen as a dust ``bump''; e.g.\ \citealt{Jura1987, Knapp1992}), and possess other emission lines \citep[e.g.\ \bracket{\ion{S}{ii}};][]{Wampler1968} showing similar reddening.
-Thus, assuming the observed steepening of the Balmer decrement is entirely due to dust, the ratio of the observed decrement to the theoretical value of 2.86 is a good estimate of the dust reddening.
-
-	If we assume that different ionization states of a given atomic species occur in the same spatial location, then shielding is not important or at least is linear in its effect on the emission-line ratios.
-Given that the different states are then produced under the same conditions, it is natural to expect a simple relationship between their emission line fluxes, similar to the Balmer decrement.
-We exploit such relationships to transform classification boundaries from diagnostic plots which use emission lines outside of the spectral range of VIMOS to diagnostics which can be measured with our VIMOS data e.g.\ transform from the classic BPT [\ion{N}{ii}]/H$\alpha$ versus [\ion{O}{iii}]/H$\beta$ to [\ion{N}{i}]/H$\beta$ versus [\ion{O}{iii}]/H$\beta$ diagnostic plot (hereafter the SAURON diagnostic plot) of \citet{Sarzi2010}.
-We achieve this by finding a best-fitting relationship between the relevant measurements taken in each bin of the galaxies for which we have the relevant detections in our MUSE data (due to the lack of detectable emission line in the observations of IC 4296 and NGC 1399, we therefore use the observations of IC 1459 and NGC 1316).
-This relationship is then applied to the diagnostic boundary lines in the relevant plots below.
-We emphasize that these are purely empirical relationships and thus differ substantially from the Balmer decrement with its strong theoretical basis (although these relationships include the effect of the Balmer decrement).
-
-	The two transformations that we use are from [\ion{N}{ii}]/H$\alpha$ to [\ion{N}{i}]/H$\beta$ line ratios and from the H$\alpha$ to the H$\beta$ equivalent widths.
-In both cases we fit a linear relationship $y = Ax + B$ using the least-trimmed squares routine, \textsc{lts\_linefit}\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/\#lts}% \label{Cappellari}}
-	 of \citet{Cappellari2013} due to its robust handling of the uncertainties along both axes. These are shown in Figs.\ \ref{fig:ratio_relation} and \ref{fig:EqW_relation}, where we find
+% The majority ($\approx 60$\%) of ETGs and all LINER and Seyfert
+% galaxies are dusty \citep[e.g.][]{Martini2013}.
+%
+% Such galaxies reveal clear dust lanes in \textit{Hubble Space
+% Telescope (HST)} observations \citep[e.g.][]{Martini2013}, are
+% bright in the infrared (where the thermal emission from dust is seen
+% as a dust ``bump''; e.g.\ \citealt{Jura1987, Knapp1992}), and
+% possess other emission lines \citep[e.g.\
+% \bracket{\ion{S}{ii}};][]{Wampler1968} showing similar
+% reddening. Thus, assuming the observed steepening of the Balmer
+% decrement is entirely due to dust, the ratio of the observed
+% decrement to the theoretical value of 2.86 is a good estimate of the
+% dust reddening.
+
+Generally, if we assume that the different ionisation states of a
+given atomic species occur in the same spatial location, then
+shielding by dust is not important or at worst its effect on the
+emission-line ratios is linear. {\bf (Why is the effect only linear?
+  Justify.)} Given that the different states are then produced under
+the same conditions, it is natural to expect a simple relationship
+between their emission line fluxes, similar to that of the Balmer
+decrement between H$\alpha$ and H$\beta$. We exploit such
+relationships here, to transform the classification boundaries of
+commonly-used diagnostic plots that utilise emission lines outside of
+the VIMOS spectral range, to diagnostics that can be measured with our
+VIMOS data. In particular, we transform the classic BPT
+[\ion{N}{ii}]/H$\alpha$ versus [\ion{O}{iii}]/H$\beta$ diagram to
+[\ion{N}{i}]/H$\beta$ versus [\ion{O}{iii}]/H$\beta$ (hereafter the
+SAURON diagnostic plot) following \citet{Sarzi2010}.
+
+To define the transformations, we find the best-fitting relationships
+between the relevant measurements, taken in each bin of the galaxies
+with corresponding MUSE detections (i.e.\ IC~1459 and NGC~1316, as
+IC~4296 and NGC~1399 have no detected emission line). These
+relationships are then applied to the diagnostic boundary lines in the
+corresponding diagnostic plots. We emphasise that the derived
+relationships are purely empirical, and thus differ substantially from
+e.g.\ the Balmer decrement with its strong theoretical basis (although
+the relationships do include the effect of the Balmer decrement).
+
+The two transformations that we use are from the
+[\ion{N}{ii}]/H$\alpha$ to the [\ion{N}{i}]/H$\beta$ line ratio and
+from the H$\alpha$ to the H$\beta$ equivalent width (EW). In both
+cases, we fit a linear relationship using the least-trimmed squares
+routine
+\textsc{lts\_linefit}\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/\#lts}
+of \citet{Cappellari2013}, because of its robust handling of the
+uncertainties along both axes. The linear relationships are shown in
+Figs.~\ref{fig:ratio_relation} and \ref{fig:EqW_relation}, where we
+respectively find
 \begin{equation}
-		\frac{[\text{\ion{N}{ii}}]}{H\alpha} = \, (0.38 \pm 0.02) \frac{[\text{\ion{N}{i}}]}{H\beta} + (1.80 \pm 0.02)
+  \frac{[\text{\ion{N}{ii}}]}{H\alpha}=(0.38\pm0.02)\,\frac{[\text{\ion{N}{i}}]}{H\beta}+(1.80\pm0.02)
 \end{equation}
@@
 \begin{equation}
-		\mathrm{EW}(H\alpha) = \, (2.92 \pm 0.03) \mathrm{EW}(H\beta) - (0.16 \pm 0.02) \, ,
+  \mathrm{EW}(H\alpha)=(2.92\pm0.03)\,\mathrm{EW}(H\beta)-(0.16\pm0.02)~.
   \label{eq:EqW_dec}
 \end{equation}
-	respectively.
-Since it is sometimes observed that [\ion{N}{ii}]/H$\alpha < 1.80$, which if blindly applying the relationship found above, results in an unphysical [\ion{N}{i}]/H$\beta < 0$ (i.e.\ negative flux), we instead rearrange and use
+As [\ion{N}{ii}]/H$\alpha<1.80$ is occasionally observed and would
+result in an unphysical negative [\ion{N}{i}]/H$\beta$ line ratio if
+used blindly, we instead use the following transformation in practice:
 \begin{equation}
-		\frac{[\text{\ion{N}{i}}]}{H\beta} = \, 
+  \frac{[\text{\ion{N}{i}}]}{H\beta}= 
   \begin{cases}
-			(0.38 \pm 0.02) \frac{[\text{\ion{N}{iI}}]}{H\alpha} + (1.80 \pm 0.02), & \text{if}\ \frac{[\text{\ion{N}{ii}}]}{H\alpha} < 2 \\
-			(0.38 \pm 0.02) \frac{[\text{\ion{N}{ii}}]}{H\alpha}, & \text{otherwise.}
+    (0.38\pm0.02)\,\frac{[\text{\ion{N}{iI}}]}{H\alpha}+(1.80\pm0.02), & \text{if}~\frac{[\text{\ion{N}{ii}}]}{H\alpha}<2 \\
+    (0.38\pm0.02)\,\frac{[\text{\ion{N}{ii}}]}{H\alpha}, & \text{otherwise.}
   \end{cases}
@@
 
+{\bf (There is something very wrong about this last set of
+  equations. First, since you presumably want to infer
+  $\frac{[\text{\ion{N}{i}}]}{H\beta}$ from
+  $\frac{[\text{\ion{N}{iI}}]}{H\alpha}$ and EW(H$\beta$) from
+  EW(H$\alpha$), why not report (and presumably fit for in the first
+  place) the inverse of the Eqs.~A1 and A2. Second, you have switched
+  $\frac{[\text{\ion{N}{i}}]}{H\beta}$ and
+  $\frac{[\text{\ion{N}{iI}}]}{H\alpha}$ in Eq.~A3, which is clearly
+  wrong. You should probably switch them back. In addition, the
+  conditions stated in Eq.~A3 make no sense. Presumably, one should
+  follow the relation until $\frac{[\text{\ion{N}{i}}]}{H\beta}=0$,
+  and then leave it at $0$. In any case, these equations need to be
+  fixed.)}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{ratio_fit.png}
+  \caption[\bracket{\ion{N}{ii}}/H$\alpha$ vs.\
+  \bracket{\ion{N}{i}}/H$\beta$]{Top: [\ion{N}{ii}]/H$\alpha$ vs.\
+    [\ion{N}{i}]/H$\beta$ line ratios for the galaxies IC~1459 and
+    NGC~1316, used to transform the classification boundaries of the
+    classic BPT plot to the SAURON diagnostic plot. Bottom: Fractional
+    residuals, defined as ([\ion{N}{ii}]/H$\alpha$ -
+    best-fit)/[\ion{N}{i}]/H$\beta$. {\bf (Why do you divide by
+      [\ion{N}{i}]/H$\beta$ rather than by [\ion{N}{ii}]/H$\alpha$?
+      Change?)}  The solid lines show the best-fitting
+    Eq.~\ref{eq:N_dec}, while the dashed and dotted lines show
+    respectively the $68$ and $99\%$ probability contours. {\bf (The
+      bottom y-axis label should be ``Fractional residual''.)}}
+  \label{fig:ratio_relation}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{EQw_fit.png}
+  \caption[EW(H$\alpha$) vs.\ EW(H$\beta$)]{As
+    Fig.~\ref{fig:ratio_relation}, but for EW(H$\alpha$) vs.\
+    EW(H$\beta$). {\bf (The bottom y-axis label should be ``Fractional
+      residual''.)}}
+  \label{fig:EqW_relation}
+\end{figure}
+
 % \begin{landscape}
@@
 
-	Here, we present spatially-resolved maps of our Southern Sample of the parameters measured and fitted to the IFS datacubes using the methods described in Section \ref{sec:analysis}.
-We present each galaxy in turn.
+Here we present the spatially-resolved maps of our Southern Sample
+galaxies, one map for each of the parameters measured or fitted to the
+IFS datacubes with the methods described in
+Section~\ref{sec:analysis}. Each galaxy is presented in turn.
 
@@
   \centering
-		\includegraphics[width=\textwidth]{eso443-g024.png}
-		\caption{Spatially-resolved map of measurements derived from VIMOS observations for ESO\,433-G24.
-The measurement is given in the top-left of each panel and the colour-scale limits are given in the bottom-right.
-The surface brightness (isophotes) are shown as black contours in all maps, while the \ce{^{12}CO(2-1)} contours from ALMA are in white and radio continuum contours from the VLA are in green.
-The radio band displayed depends on the data available in the archive and which images had a similar resolution and scales.}
+  % \includegraphics[width=\textwidth]{eso443-g024.png}
+  \caption{Spatially-resolved map of all the parameters derived from
+    the VIMOS observations of ESO~443-G24. Each parameter is indicated
+    in the top-left corner of each panel, and the colour scale limits
+    are listed in the bottom-right corner of each panel. {\bf (Why are
+      these not perfect fits to the bottom-right corners? Fix?)} The
+    surface brightness (isophotes) are overlaid as black contours in
+    all the maps, while the \ce{^{12}CO(2-1)} contours from ALMA are
+    overlaid in white {\bf (Pale blue or turquoise? Correct.)} and the
+    radio continuum contours from the VLA are overlaid in green. The
+    radio band displayed depends on the data and angular resolution
+    available \citep[see][]{ruffa2019, ruffa2020}. {\bf
+      (``Metalicity'' should be ``Metallicity''. Also explain the
+      meaning of the pale and dark greys bins.)}}
+      % Preferable to rotate the colour table by $180$ deg, to match
+      % the colour to the sense of the limits indicated in the
+      % bottom-right corner of each plot?
   \label{fig:eso443}
@@
   \centering
-		\includegraphics[width=\textwidth]{ic1459.png}
-		\caption{As Fig.\,\ref{fig:eso443}, but for IC\,1459 and derived from MUSE observations.}
+  % \includegraphics[width=\textwidth]{ic1459.png}
+  \caption{As Fig.\,\ref{fig:eso443}, but for IC\,1459 and derived
+    from MUSE observations.}
   \label{fig:ic1459}
@@
   \centering
-		\includegraphics[width=\textwidth]{ic1531.png}
+  % \includegraphics[width=\textwidth]{ic1531.png}
   \caption{As Fig.\,\ref{fig:eso443}, but for IC\,1531.}
@@
   \centering
-		\includegraphics[width=\textwidth]{ic4296.png}
-		\caption{As Fig.\,\ref{fig:eso443}, but for IC\,4296 and derived from MUSE observations.}
+  % \includegraphics[width=\textwidth]{ic4296.png}
+  \caption{As Fig.\,\ref{fig:eso443}, but for IC\,4296 and derived
+    from MUSE observations.}
   \label{fig:ic4296}
@@
   \centering
-		\includegraphics[width=\textwidth]{ngc0612.png}
+  % \includegraphics[width=\textwidth]{ngc0612.png}
   \caption{As Fig.\,\ref{fig:eso443}, but for NGC\,612.}
@@
   \centering
-		\includegraphics[width=\textwidth]{ngc1316.png}
-		\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,1316 and derived from MUSE observations.}
+  % \includegraphics[width=\textwidth]{ngc1316.png}
+  \caption{As Fig.\,\ref{fig:eso443}, but for NGC\,1316 and derived
+    from MUSE observations.}
   \label{fig:ngc1316}
@@
   \centering
-		\includegraphics[width=\textwidth]{ngc1399.png}
-		\caption{As Fig.\,\ref{fig:eso443}, but for NGC\,1399 and derived from MUSE observations.}
+  % \includegraphics[width=\textwidth]{ngc1399.png}
+  \caption{As Fig.\,\ref{fig:eso443}, but for NGC\,1399 and derived
+    from MUSE observations.}
   \label{fig:ngc1399}
@@
   \centering
-		\includegraphics[width=\textwidth]{ngc3100.png}
+  % \includegraphics[width=\textwidth]{ngc3100.png}
   \caption{As Fig.\,\ref{fig:eso443}, but for NGC\,3100.}
@@
   \centering
-		\includegraphics[width=\textwidth]{ngc3557.png}
+  % \includegraphics[width=\textwidth]{ngc3557.png}
   \caption{As Fig.\,\ref{fig:eso443}, but for NGC\,3557.}
@@
   \centering
-		\includegraphics[width=\textwidth]{ngc7075.png}
+  % \includegraphics[width=\textwidth]{ngc7075.png}
   \caption{As Fig.\,\ref{fig:eso443}, but for NGC\,7075.}
@@
   \centering
-		\includegraphics[width=\textwidth]{pks0718-34.png}
+  % \includegraphics[width=\textwidth]{pks0718-34.png}
   \caption{As Fig.\,\ref{fig:eso443}, but for NGC\,718-34.}
@@
 % \end{landscape}
-
 % \clearpage

### 2019-09-24 produce_kine_plot.py
Changes to plots from Martin's comments

@@ -1,0 +1,858 @@
+from checkcomp import checkcomp
+cc = checkcomp()
+if 'home' not in cc.device:
+	import matplotlib # 20160202 JP to stop lack-of X-windows error
+	matplotlib.use('Agg') # 20160202 JP to stop lack-of X-windows error
+# import cPickle as pickle
+import matplotlib.pyplot as plt 
+import numpy as np 
+from plot_velfield_nointerp import plot_velfield_nointerp
+from prefig import Prefig
+from astropy.io import fits 
+from sauron_colormap import sauron#2 as sauron
+from plot_results import set_lims
+from tools import myerrorbar
+from Bin import myArray
+# from BPT import lbd, lnd, lsd, add_grids
+from BPT import add_grids, NII_Ha_to_NI_Hb, log_NII_Ha_to_NI_Hb, EqW_Ha_to_EqW_Hb, \
+	log_EqW_Ha_to_EqW_Hb
+from Bin2 import Data
+from scipy import ndimage # for gaussian blur
+from matplotlib import ticker
+
+
+def plot(galaxies, str_galaxies, file_name, instrument, debug=False):
+	if instrument == 'vimos':
+		from plot_results import add_
+		from errors2 import get_dataCubeDirectory
+	elif instrument == 'muse':
+		from plot_results_muse import add_
+		from errors2_muse import get_dataCubeDirectory
+
+	opt = 'pop'
+	overplot={'CO':'w', 'radio':'g'}
+	Prefig(size=np.array((4, len(galaxies)))*7)
+	fig, axs = plt.subplots(len(galaxies), 4)#, sharex=True, sharey=True)
+	out_dir = '%s/Documents/thesis/chapter5/%s' % (cc.home_dir, instrument)
+
+	for i, galaxy in enumerate(galaxies):
+		if debug:
+			from produce_plots import Ds
+			D = Ds()
+		else:
+			D = Data(galaxy, instrument=instrument, opt=opt)
+			opt = D.opt
+
+		print galaxy
+
+		vin_dir = '%s/Data/%s/analysis' % (cc.base_dir, instrument)
+		data_file =  "%s/galaxies.txt" % (vin_dir)
[…]

### 2019-09-24 paper.tex
Format changed or something...

@@
 thus affected by the ISM kinematics) was significantly affecting the
-quality of the best-fitting {\bf (Spatially-collapsed? Clarify.)}
-stellar spectrum. For this reason, when fitting the stellar spectra
-only {\bf (i.e.\ Sections~\ref{subsec:starKin} and
+quality of the \colorbox{red}{best-fitting {\bf (Spatially-collapsed? 
+Clarify.)} stellar spectrum} \colorbox{green}{fits to the stellar 
+spectrum for all bins}. For this reason, when fitting the stellar spectra
+only \colorbox{red}{{\bf (i.e.\ Sections~\ref{subsec:starKin} and
   \ref{subsec:absorption} but not \ref{subsec:EmissionLines}?
-  Clarify.)}, the wavelength range of the NGC~1316 spectra was
-restricted to $<5800$~\AA.
+  Clarify.)}} \colorbox{green}{(i.e.\ Sections~\ref{subsec:starKin})}, the wavelength range of the NGC~1316 spectra was
+restricted to $<5800$~\AA. \colorbox{green}{The best-fitting stellar spectra were then extrapolated above 5800~\AA.}
+
+% Bit more detail needed above****************************************************************************************************************************************************************
 

### 2019-11-03 paper.tex
Further work on corrections from Martin

--- 2019-08-26 paper.tex
@@
 % \usepackage{pdflscape} % for landscape pages
+\usepackage{color,soul} % highlighting
+\DeclareRobustCommand{\removed}[1]{{\sethlcolor{red}\hl{#1}}}
+\DeclareRobustCommand{\added}[1]{{\sethlcolor{green}\hl{#1}}}
+
+\soulregister\cite7
+\soulregister\citep7
+\soulregister\citet7
+\soulregister\citealt7
+\soulregister\ref7
+\soulregister\textbf7
+\soulregister\ 7
+\soulregister\ion7
+\soulregister\subsubsection7
+\soulregister\subsubsection1
 
@@
 %Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:joshua.warren@physics.ox.ac.uk}{joshua.warren@physics.ox.ac.uk}}
-  Martin Bureau,$^{1,2}$ Bernd Hasemann,$^{3}$ Isabella
+  Martin Bureau,$^{1,2}$ Bernd Hasemann,$^{3}$ \added{Ilaria Ruffa,$^{4}$} Isabella
   Prandoni,$^{4}$ \newauthor Francesco Santoro,$^{4}$ Robert
-  Laing,$^{4}$ Paola Parma,$^{4}$ Hans de Ruiter$^{4}$ and \newauthor
-  Arturo Mignano$^{4}$
+  Laing,$^{4}$ Paola Parma,$^{4}$ \added{Rosita Paladino,$^{4}$} Hans de Ruiter,$^{4}$ \newauthor
+  Arturo Mignano$^{4}$ and \added{Timothy Davis$^{5}$}
   \\
@@
   Bologna, Italy\\
+  \added{$^{5}$School of Physics \& Astronomy, Cardiff University, Queens Buildings, The Parade, Cardiff CF24 3AA, UK}\\
   $^*${\bf Should you/we add Ilaria Ruffa and/or Rosita Paladino
@@
 thus affected by the ISM kinematics) was significantly affecting the
-quality of the best-fitting {\bf (Spatially-collapsed? Clarify.)}
-stellar spectrum. For this reason, when fitting the stellar spectra
+quality of the \removed{best-fitting \textbf{(Spatially-collapsed? 
+Clarify.)} stellar spectrum} \added{fits to the stellar 
+spectrum for all bins}. For this reason, when fitting the stellar spectra
 only {\bf (i.e.\ Sections~\ref{subsec:starKin} and
   \ref{subsec:absorption} but not \ref{subsec:EmissionLines}?
-  Clarify.)}, the wavelength range of the NGC~1316 spectra was
-restricted to $<5800$~\AA.
+  Clarify.)}} \added{(i.e.\ Sections~\ref{subsec:starKin})}, the wavelength range of the NGC~1316 spectra was
+restricted to $<5800$~\AA. \added{The best-fitting stellar spectra were then extrapolated above 5800~\AA.}
+
+% Bit more detail needed above****************************************************************************************************************************************************************
 
@@
 
-In this analysis we consider the following emission lines and
-doublets: H$\gamma$, H$\beta$,
+In this analysis, we consider the following emission lines and
+doublets: 
+\added{[\ion{O}{II}]$\lambda\lambda$3726,3729,
+H$\delta$,} H$\gamma$, H$\beta$,
 [\ion{O}{iii}]$\lambda\lambda$4969,5007,
@@
   What about H$\delta$, also in your original table but now commented
-  out? Correct.)}. We fit the emission line fluxes and kinematics
+  out? Correct.)}. \removed{We fit the emission line fluxes and kinematics
 independently of the stellar kinematics, and their fluxes
-independently of each other (but see below), again adopting a single
-Gaussian template parametrised by $V$, the mean velocity, and
-$\sigma$, the velocity dispersion for all lines. However, in the cases
-of the [\ion{O}{iii}], [\ion{O}{i}] and [\ion{N}{ii}] doublets, the
-two components of each doublet are fit with a fixed flux ratio of
-$3:1$, while the [\ion{N}{i}] doublet is fit with a fixed flux ratio
-of $3:2$ \citep{Safier1992}. The two components of the [\ion{O}{ii}]
-and [\ion{S}{ii}] doublets are fit independently {\bf (See previous
-  comment about the \ion{O}{ii} doublet. Correct.)}. To minimise
-template mismatch, whereby emission lines are erroneously fitted to
-the edges of badly modelled and thus subtracted absorption features,
+independently of each other (but see below).} To minimise template 
+mismatch, whereby emission lines are erroneously fitted
+to the edges of badly modelled and thus subtracted absorption features,
 we follow the procedure set out in \citet{Sarzi2005}. In this method,
@@
 line regions masked, followed by the unmasking and fitting of the
-[\ion{O}{iii}] doublet (that sets the kinematics of all other emission
-lines), and finally the fitting of the amplitudes of the remaining
-emission lines.
+[\ion{O}{iii}] doublet, again adopting a single
+Gaussian template parametrised by $V$, the mean velocity, and
+$\sigma$, the velocity dispersion. Setting this as the kinematics for 
+all other emission lines, the amplitudes of the remaining
+emission lines are fitted. In the cases of the [\ion{O}{iii}], [\ion{O}{i}] 
+and [\ion{N}{ii}] doublets, the two components of each doublet are fit 
+with a fixed flux ratio of $3:1$, while the [\ion{N}{i}] doublet is 
+fit with a fixed flux ratio of $3:2$ \citep{Safier1992}. The two 
+components of the [\ion{O}{ii}] and [\ion{S}{ii}] doublets are fit 
+independently. {\bf (See previous comment about the \ion{O}{ii} doublet. 
+Correct.)}.
 
@@
 
-The line strengths quoted are corrected for both line emission and the
-effects of the stellar velocity dispersion, as detailed below.
-
-\subsubsection{Removing Emission Lines}
-\label{subsubsec:RemovingEmission}
+\removed{\subsubsection{Removing Emission Lines}}
+% \label{subsubsec:RemovingEmission}
 
 Each emission line is removed from each spectrum by subtracting the
-best-fitting Gaussian from Section~\ref{subsec:EmissionLines} from the
-data, using only the stellar templates (and continuum correction)
-subsequently considered for the velocity dispersion correction (see
-below). {\bf (I do not understand the second part of this
-  sentence. Check/clarify/correct.)}
+best-fitting Gaussians from Section~\ref{subsec:EmissionLines} from the
+data, before the line strenghts are measured. \removed{, using only the 
+stellar templates (and continuum correction) subsequently considered 
+for the velocity dispersion correction (see below). \mbox{\textbf{(I do not 
+understand the second part of this sentence. Check/clarify/correct.)}}} 
+These are then corrected for the effects of the stellar velocity 
+dispersion, as detailed below.
 % used for reconstructing the best-fit to

### 2019-11-10 paper.tex
Further corrections
 On branch master
 Changes to be committed:
	modified:   paper.tex

@@
 
-In reality, the field of view does not always contain
-$1$~$R_\text{e}$. When this is the case, we follow the method of
-\citet{Emsellem2007}, where $R_\text{m}$ is redefined as
-$R_\text{m}\equiv\sqrt{A_\text{s}/\pi}$, where $A_\text{s}$ is the
-area of the {\bf (Largest? Clarify.)} ellipse contained within the
-field of view. {\bf (I do not understand the meaning of the following
-  sentence in {\it italics}. Rephrase/explain better. Perhaps even
-  simply remove? What are $R_\text{max}$ and $A_\text{ellipse}$?!)}
-{\it For a given galaxy, we fit ellipses as described above, up to
-  $R_\text{m}=R_\text{max}$, where $A_\text{s}$ reaches a maximum
-  difference of 15\% with respect to the area of the fitted ellipse,
-  $A_\text{ellipse}$}. The value $\epsilon_\text{e}$, the ellipticity
-at $1$~$R_\text{e}$ or $R_\text{max}$, whichever is smallest, is given
-in Column~3 of Table~\ref{tab:classify}.
+In reality, the field of view does not always \added{fully} contain 
+\added{a given fitted ellipse} \removed{$1$~$R_\text{e}$}. When this 
+is the case, we follow the method of \citet{Emsellem2007}, where 
+$R_\text{m}$ is redefined as $R_\text{m}\equiv\sqrt{A_\text{s}/\pi}$, 
+where $A_\text{s}$ is the area \added{contained within 
+the field of view} of the {\bf (Largest? Clarify.)} 
+\added{given} ellipse \removed{contained within 
+the field of view}. {\bf (I do not understand the meaning of the 
+following sentence in {\it italics}. Rephrase/explain better. 
+Perhaps even simply remove? What are $R_\text{max}$ and 
+$A_\text{ellipse}$?!)} {\it For a given galaxy, we fit ellipses 
+as described above, up to $R_\text{m}=R_\text{max}$, where 
+\added{$R_\text{max}$ is defined such that  
+$\frac{A_\text{s}(R_\text{max})}{A_\text{ellipse}(R_\text{max})} 
+\equiv 0.15$ or $R_\text{max} = R_\text{e}$, which ever is smallest.} 
+\removed{$A_\text{s}$ reaches a maximum difference of 15\% with 
+respect to the area of the fitted ellipse, $A_\text{ellipse}$.}} The 
+value $\epsilon_\text{e}$, the ellipticity \added{of this largest 
+fitted ellipse} \removed{at $1$~$R_\text{e}$ or $R_\text{max}$, 
+whichever is smallest}, is given in Column~3 of 
+Table~\ref{tab:classify}.
 
@@
 of the axis perpendicular to the apparent angular momentum vector,
-measured westward from North. {\bf (Are you sure this is westward and
+measured \added{eastward} \removed{westward} from North. {\bf (Are you sure this is westward and
   not eastward? Position angles are usually defined from North to
@@
 between the photometric and stellar kinematic position angles,
-$\Gamma_\text{kin}\equiv\arcsin(\sin[PA_\text{phot}-PA_\text{kin}])$.
+$\Gamma_\text{kin}\equiv\arcsin(\sin[PA_\text{phot}-PA_\text{kin}])$
 {\bf (Why is that different from simply
@@
   need be.)} {\bf (At which radius/ellipse semi-major axis is
-  $PA_\text{phot}$ taken/measured? Specify.)}
+  $PA_\text{phot}$ taken/measured? Specify.)} \added{, where$PA_\text{phot}$ is measured at $R_\text{max}$.}
 
@@
   with respect to the kinematic minor axis/rotation axis?
-  State/explain if the latter.)} where $F_i$ is the flux of the
+  State/explain if the latter. JW: $R_i$ is from the center - see Eq6 in \citep{Emsellem2007})} where $F_i$ is the flux of the
 $i^\text{th}$ bin, $R_i$ its distance from the centre, $V_i$ its mean
 stellar velocity and $\sigma_i$ its stellar velocity dispersion. The
-sum is computed over all $N$ bins within $1$~$R_\text{e}$ of the
+sum is computed over all $N$ bins within \removed{$1$~$R_\text{e}$} \added{$1$~$R_\text{max}$} of the
 centre of the galaxy. {\bf (What do you do if the field of view does

### 2019-12-21 paper.tex
Work on Ionsied gas section
 On branch master
 Changes to be committed:
	modified:   paper.tex

@@
   with respect to the kinematic minor axis/rotation axis?
-  State/explain if the latter. JW: $R_i$ is from the center - see Eq6 in \citep{Emsellem2007})} where $F_i$ is the flux of the
+  State/explain if the latter. JW: Yes, $R_i$ is from the center - see Eq6 in \citep{Emsellem2007})} where $F_i$ is the flux of the
 $i^\text{th}$ bin, $R_i$ its distance from the centre, $V_i$ its mean
@@
 We find $4$ out of $11$, or $36\pm15\%$, of our sample galaxies are
-regular rotators. This compares to $82\%$ of the Atlas$^\text{3D}$
+regular rotators. This compares to \added{$82\pm2\%$} of the Atlas$^\text{3D}$
 galaxies being classified as regular rotators
@@
 the Atlas$^\text{3D}$ and MASSIVE surveys, that find respectively
-$13.1\%$ and $77.5\%$ of their sample galaxies to be slow
+\added{$13\pm2\%$} and \added{$80\pm6\%$} of their sample galaxies to be slow
 rotators. {\bf (Again, better to also quote the uncertainties on those
@@
 
-\citet{Bender1993} observed a tight relationship between the global
+\citet{Bender1993} observed a tight relationship between the \added{central} \removed{global}
 Mg$_2$ absorption line strength (a variant of the Mg~$b$ line
 strength) and the logarithm of the central stellar velocity
-dispersion, $\sigma_0$, in elliptical galaxies. They also noticed that
+dispersion, $\sigma_0$, in elliptical galaxies. \removed{They also noticed that
 the residuals from the best-fitting linear relation appeared to be
 intrinsic, with a near Gaussian distribution about the median value
-{\bf (Was that median value $\approx0$? If so, state explicitly. If
+\textbf{(Was that median value $\approx0$? If so, state explicitly. If
   not, then the fit was either bad or there is something we do not
-  understand.)} and no correlation with any other galaxy property.
+  understand.)} and no correlation with any other galaxy property.}
 
@@
 metallicity. {\bf (Why the strange units? Is Mg$_2$ measured in mag 
-  rather than \AA? If so, add a short note. If not, correct.)} Thus,
-following \citet{Ziegler1997}, we also use Mg~$b$ as a proxy for
+rather than \AA? If so, add a short note. If not, correct.)} 
+\added{(Mg$_2$ is condered to be a molecular index and is thus measured 
+in units of mag$^{-1}$.) We can thus}\removed{Thus, following \citet{Ziegler1997}, we also} use Mg~$b$ as a proxy for
 Mg$_2$.
@@
 indicated by the solid black line, with a gradient of
-$3.3\pm1.0$~\AA~dex$^{-1}$. It was noted that NGC~1316 is a possible
+$3.3\pm1.0$~\AA~dex$^{-1}$. \added{We} \removed{It was} noted that NGC~1316 is \added{again an} \removed{a possible}
 outlier. {\bf (Noted by who or where? Specify. Also mention that it
@@
 Fig.~\ref{fig:globalMg}). {\bf (Any uncertainty on this value of
-  $2.7$? If so, quote it.)}
+  $2.7$? If so, quote it.) JW: No \citet{Ziegler1997} doesn't propagate uncertainty into errors on the fit.}
 % , with an intrinsic scatter of 0.16\,\AA\ for galaxies with
@@
   it partially by construction (i.e.\ because you matched the
-  zero-points yourself)? Clarify.)}
+  zero-points yourself)?
+Clarify.) JW: the entire function has been transformed including the zero-point.
+This actually results in a cubic function (see Appendix A of \citealt{Vazdekis2010}), though as can been seen from the Fig.~3, the quadradic and cubic terms have very little effect in this range.}
 
@@
 Southern Sample. {\bf (Why not use the much larger Atlas$^{\rm 3D}$
-  dataset instead? Explain briefly if justified.)}
+  dataset instead?
+Explain briefly if justified.)} \added{This was used over the larger Atlas$^\text{3D}$ sample \citep{Cappellari2011}, as stellar populations were not published by the Atlas$^\text{3D}$ team.}
 
@@
 
-\citet{Kuntschner2010} showed that KDCs can be separated into two
-classes: either small with various stellar ages or typically larger
-but containing a homogeneously old stellar population. {\bf (I thought
-  the first to point this out was McDermid et al.\ (2006; see e.g.\
-  their Fig.~16), which should at least also be quoted here. Check and
-  possibly correct.)} The size of the KDC is defined as the radius
+\added{\citet{McDermid2006}} \removed{\citet{Kuntschner2010}} showed that 
+KDCs can be separated into two classes: either small with various stellar 
+ages or typically larger but containing a homogeneously old stellar 
+population. {\bf (I thought the first to point this out was 
+McDermid et al.\ (2006; see e.g.\ their Fig.~16), which should at 
+least also be quoted here. Check and possibly correct.)} 
+\added{Using the method of \ctiet{McDermid2006},} the size 
+\added{and age} of the KDC is defined as the radius
 where the superposition of the two kinematic components (the KDC and
-the host galaxy) results in a local minimum in the mean velocity. The
+the host galaxy) results in a local minimum in the mean velocity \added{and} the
 age of the most-likely SSP model for the spatially integrated spectrum
-within a central aperture of $1\arcsec$ {\bf (Again, square or
-  circular, radius or diameter? Clarify.)} is taken as the KDC's
-age. {\bf (Are these two definitions (of the KDCs' sizes and ages)
+within a central \added{, circular} aperture with a \added{radius} of 
+$1\arcsec$ {\bf (Again, square or circular, radius or diameter? Clarify.)} 
+\removed{is taken as the KDC's age.} \added{, repectively.} 
+{\bf (Are these two definitions (of the KDCs' sizes and ages) 
 those of \citealt{Kuntschner2010} or yours or both? Clarify.)}
@@
 Only $4$ galaxies (IC~1459, NGC~612, NGC~1316 and NGC~3100) of our
-Southern Sample have emission lines detected outside of their central
-region. Of the remaining $7$ galaxies, $5$ (IC~1531, IC~4296,
+Southern Sample have emission lines detected outside of a central
+\removed{region} \added{1--2 spaxels. This means no structure can be
+ resolved}. Of the remaining $7$ galaxies, $5$ (IC~1531, IC~4296,
 NGC~3557, NGC~7075 and ESO~443-G024) are only detected in their centre
@@
 
-As can be seen from the maps in Appendix~\ref{sec:maps}, both NGC~612
-and NGC~3100 have significant off-centred ionised gas emission. {\bf
-  (What do you mean by ``significant'' here? Bright?
+\removed{As can be seen from the maps in Appendix~\ref{sec:maps}, 
+both NGC~612 and NGC~3100 have significant off-centred ionised 
+gas emission.} {\bf (What do you mean by ``significant'' here? Bright?
   Clarify. Equivalently, why is the off-centred emission in IC~1459
-  and NGC~1316 not considered significant?)} In NGC~612, the ionised
-gas does not appear related to either the radio jet (extending
-$\approx200$~kpc to the East and West of the galaxy centre) or the CO,
-but in NGC~3100 the ionised gas is spatially coincident with both the
-radio jet and the gap in the CO ring.
+  and NGC~1316 not considered significant?)} 
+\added{The ionised gas emission for both NGC~612 ).} In NGC~612, 
+the ionised gas does not appear related to either the radio jet 
+(extending $\approx200$~kpc to the East and West of the galaxy 
+centre) or the CO, but in NGC~3100 the ionised gas is spatially 
+coincident with both the radio jet and the gap in the CO ring.
 
@@
 Our calculated ionised gas masses are listed in
-Table~\ref{tab:derivedProp}. They are at the upper edge of, and
-possibly exceed, {\bf (Why ``possibly''? They either always exceed,
-  generally exceed, occasionally exceed, or never exceed! Check and
-  clarify.)} the typical masses observed in ETGs
-\citep[e.g.][]{Phillips1986, Zeilinger1996, Sarzi2005}. Given that our
-sample contains particularly massive galaxies, however, high ionised
-gas masses are not unexpected.
+Table~\ref{tab:derivedProp}. They are at the upper \removed{edge} 
+\added{range} of, and \removed{possibly} \added{occasionally} exceed, 
+{\bf (Why ``possibly''? They either always exceed, generally exceed, 
+occasionally exceed, or never exceed! Check and clarify.)} the 
+typical masses observed in ETGs 
+\citep[e.g.][]{Phillips1986, Zeilinger1996, Sarzi2005}. Given that 
+our sample contains particularly massive galaxies, however, 
+high ionised gas masses are not unexpected.
 
@@
 
-\textbf{IC~1459} has ionised gas counter-rotating with respect to the
+\removed{\textbf{IC~1459} has ionised gas counter-rotating with respect to the
 stellar KDC, but it is also misaligned with respect to the outer stars
@@
 of the galaxy's original disc. Alternatively, the ISM may have yet
-another external origin.
+another external origin.}
+
+\added{\textbf{IC~1459} has ionised gas co-rotating with the outer part (not the KDC) of the host galaxy \citep{Franx1988}.
+Whilst this is consistent with an internal origin of the gas, it should be noted that a major merger is typically expected to deplete a galaxy's gas reservoir.
+Either this did not happen in this case (a major merger being evidenced by the existence of the KDC) or the ISM may has an external origin and the apparent alignment of the gas and outer stars is random.}
 
@@
 KDCs found in Section~\ref{sec:StarKine} are also in agreement with
-the KDC age\,--\,size relation found by \citet{Kuntschner2010} in
-optically-selected ETGs (see Section~\ref{subsec:popKDC}). {\bf (See
-  my previous comment about McDermid et al.\ 2006, and perhaps quote
-  it here instead or additionally.)}
+the KDC age\,--\,size relation found by \added{\citet{McDermid2006}} 
+\removed{\citet{Kuntschner2010}} in optically-selected ETGs (see 
+Section~\ref{subsec:popKDC}). {\bf (See my previous comment about 
+McDermid et al.\ 2006, and perhaps quote it here instead or 
+additionally.)}
 

### 2019-12-30 paper.tex
Further work
 Changes to be committed:
	modified:   paper.tex

@@
 diameter, and NGC~3100 has a branch of young stars ($t\approx4$\,Gyr)
-along the south-east branch of the molecular gas (white contours in
+along the south-east branch of the molecular gas (\removed{white} 
+\added{cyan} contours in
 Fig.~\ref{fig:ngc3100}). {\bf (I do not see the age feature you refer
@@
 $1\arcsec$ {\bf (Again, square or circular, radius or diameter? Clarify.)} 
-\removed{is taken as the KDC's age.} \added{, repectively.} 
+\removed{is taken as the KDC's age.} \added{, respectively.} 
 {\bf (Are these two definitions (of the KDCs' sizes and ages) 
@@
 \ce{^{12}CO(2-1)} integrated intensity contours (overlaid on the IFS
-maps in white; see Fig.~\ref{fig:ngc3100}) {\bf (Again, no white
+maps in \removed{white} \added{cyan}; see Fig.~\ref{fig:ngc3100}) 
+{\bf (Again, no white
   contours in the figure... pale blue/turquoise contours?)} show a
@@
 Section~\ref{subsubsec:Hb}). Finally, we use the mass\,--\,excitation
-(MEx) plot of \cite{Nyland2016}, using parameters derived from spectra
-spatially-integrated over central circular apertures of radius
-$3\arcsec$, thus probing only the central regions of the galaxies (see
+(MEx) plot of \cite{Nyland2016}, using parameters derived from \added{a} 
+spectra \added{produced by} spatially-\removed{integrated}\added{integrating} over \added{a} central circular apertures of radius
+$3\arcsec$ \added{to probe} \removed{, thus probing only} the central 
+regions of the galaxies (see
 Section~\ref{subsubsec:MEx}). {\bf (You talked here of *the*
@@
 AGN (labelled as LINER-AGN) and those whose LINER characteristics are
-not. {\bf (Labelled as what? LIER?  Clarify.)} As the least
+not \added{(simply labelled as LINER: they may be AGN or LIER)}. 
+{\bf (Labelled as what? LIER?  Clarify.)} As the least
 conventional, we expand on the final two steps in the two sub-sections
@@
 our sample shows a mixture of regularly- and non-regularly-rotating
-objects. Both classes also appear consistent with observations of the
-intrinsic shapes of ordinary regular and non-regular rotators. {\bf (I
+objects. \removed{Both classes also appear consistent with observations of the
+intrinsic shapes of ordinary regular and non-regular rotators.} {\bf (I
   do not actually know/understand what you were trying to say or refer
@@
 masses are not unexpected, but these masses are at the upper limit of,
-and possibly exceed {\bf (Again, why ``possibly''? They either always
+and \removed{possibly} \added{occasionally} exceed {\bf (Again, why ``possibly''? They either always
   exceed, generally exceed, occasionally exceed, or never exceed!
@@
 Zieleniewski, private comm.); and \textsc{voronoi\_2d\_binning}
-\citep[including the SAURON colourmaps {\bf (Colourmaps, whatever that
-  might be, or colour table? Clarify.)}; ][]{Cappellari2003}.
+\citep[including the SAURON \added{Colourmaps}\removed{colourmaps} 
+{\bf (Colourmaps, whatever that might be, or colour table? Clarify.)}; ][]{Cappellari2003}.
 
@@
     all the maps, while the \ce{^{12}CO(2-1)} contours from ALMA are
-    overlaid in white {\bf (Pale blue or turquoise? Correct.)} and the
+    overlaid in \removed{white} \added{cyan} {\bf (Pale blue or 
+    turquoise? Correct.)} and the
     radio continuum contours from the VLA are overlaid in green. The

### 2019-12-30 produce_maps.py
Work on figures
 Changes to be committed:
	modified:   EqW_fit.png
	modified:   produce_maps.py
	modified:   ratio_fit.png

@@ -426,7 +426,7 @@ def plot(galaxy, instrument='vimos', debug=True):
 	# 			gt_fwhm = hist >= np.max(hist)/2
 	# 			unc_plot[j] = np.max(x[gt_fwhm]) - np.min(x[gt_fwhm])
 
-	str_plots = ['Age', 'Age uncertainty', 'Metalicity', 'Metalicity uncertainty', 
+	str_plots = ['Age', 'Age uncertainty', 'Metallicity', 'Metallicity uncertainty', 
 		'Alpha enhancement', 'Alpha enhancement\nuncertainty']
 	units = ['Gyr', 'Gyr', None, None, None, None]
 	vmin = [0, 0, -2.25, 0, -0.3, 0]
@@ -507,10 +507,10 @@ def plot(galaxy, instrument='vimos', debug=True):
 if __name__=='__main__':
 	# plot('ngc1316', instrument='muse', debug=True)
 	if 'home' in cc.device:
-		# for galaxy in ['eso443-g024', 'ic1531', 'ngc0612', 'ngc3100', 'ngc3557', 
-		# 	'ngc7075', 'pks0718-34']:
-		# 	plot(galaxy, instrument='vimos', debug=False)
+		for galaxy in ['eso443-g024', 'ic1531', 'ngc0612', 'ngc3100', 'ngc3557', 
+			'ngc7075', 'pks0718-34']:
+			plot(galaxy, instrument='vimos', debug=False)
 	# elif cc.device == 'uni':
-		# for galaxy in ['ic1459', 'ic4296', 'ngc1316', 'ngc1399']:
-		# 	plot(galaxy, instrument='muse', debug=False)
-		plot('ngc1399', instrument='muse', debug=False)
+		for galaxy in ['ic1459', 'ic4296', 'ngc1316', 'ngc1399']:
+			plot(galaxy, instrument='muse', debug=False)
+		# plot('ngc1399', instrument='muse', debug=False)

### 2020-01-01 paper.tex
Work on plots in paper
Corrected issue with NI-NII 'dec', and minor alterations to maps.

 On branch master
 Changes to be committed:
	modified:   EqW_fit.png
	modified:   paper.tex
	modified:   produce_kine_plot.py
	modified:   ratio_fit.png

@@
 the residuals from the best-fitting linear relation appeared to be
-intrinsic, with a near Gaussian distribution about the median value
-\textbf{(Was that median value $\approx0$? If so, state explicitly. If
+intrinsic, with a near Gaussian distribution about the median value}
+{\bf (Was that median value $\approx0$? If so, state explicitly. If
   not, then the fit was either bad or there is something we do not
-  understand.)} and no correlation with any other galaxy property.}
+  understand.)} \removed{and no correlation with any other galaxy property.}
 
@@
 least also be quoted here. Check and possibly correct.)} 
-\added{Using the method of \ctiet{McDermid2006},} the size 
+\added{Using the method of \citet{McDermid2006},} the size 
 \added{and age} of the KDC is defined as the radius
@@
 non-rotating (see Fig.~\ref{fig:ic1459}). The ionised gas thus appears
-to have a third, independent, axis of rotation. {\bf (I do not
+to have a third, independent, axis of rotation.} {\bf (I do not
   understand why you state/claim that here. From the map shown, it
@@
   consistent with the ionised gas, just as \citet{Franx1988}
-  claimed. Convince me otherwise of change your statement!)} This is
+  claimed. Convince me otherwise of change your statement!)} \removed{This is
 contrary to \citet{Franx1988} who claims that the rotation of the gas
 is aligned with that of the stars outside of the KDC. As the stellar
-disc did not survive the merger event that created the KDC, {\bf (How
+disc did not survive the merger event that created the KDC, }{\bf (How
   do you know there was a stellar disc to start with? Clarify or
-  rephrase.)} it is unlikely that the gas in the progenitor of IC~1459
+  rephrase.)} \removed{it is unlikely that the gas in the progenitor of IC~1459
 survived. However, the lost gas may have remained bound and been
@@
 
-Generally, if we assume that the different ionisation states of a
-given atomic species occur in the same spatial location, then
-shielding by dust is not important or at worst its effect on the
-emission-line ratios is linear. {\bf (Why is the effect only linear?
-  Justify.)} Given that the different states are then produced under
-the same conditions, it is natural to expect a simple relationship
+\removed{Generally, } If we assume that the different ionisation states of a
+given atomic species\added{, observed along the same line-of-sight,} occur in 
+the same spatial location \added{(and therefore are produced under the same 
+conditions)}\removed{, then shielding by dust is not important or at worst its 
+effect on the emission-line ratios is linear.} \textbf{(Why is the effect only 
+linear? Justify.)} \removed{Given that the different states are then produced under
+the same conditions,} it is natural to expect a simple relationship
 between their emission line fluxes, similar to that of the Balmer
@@
 \begin{equation}
-  \frac{[\text{\ion{N}{ii}}]}{H\alpha}=(0.38\pm0.02)\,\frac{[\text{\ion{N}{i}}]}{H\beta}+(1.80\pm0.02)
+  \frac{[\text{\ion{N}{ii}}]}{H\alpha}=(0.48\pm0.02)\,\frac{[\text{\ion{N}{i}}]}{H\beta}+(1.62\pm0.01)
 \end{equation}
@@
 \begin{equation}
-  \mathrm{EW}(H\alpha)=(2.92\pm0.03)\,\mathrm{EW}(H\beta)-(0.16\pm0.02)~.
+  \mathrm{EW}(H\alpha)=(2.82\pm0.02)\,\mathrm{EW}(H\beta)+(0.13\pm0.02)~.
   \label{eq:EqW_dec}
@@
 \begin{equation}
-  \frac{[\text{\ion{N}{i}}]}{H\beta}= 
+  \frac{[\text{\ion{N}{ii}}]}{H\beta}= 
   \begin{cases}
-    (0.38\pm0.02)\,\frac{[\text{\ion{N}{iI}}]}{H\alpha}+(1.80\pm0.02), & \text{if}~\frac{[\text{\ion{N}{ii}}]}{H\alpha}<2 \\
-    (0.38\pm0.02)\,\frac{[\text{\ion{N}{ii}}]}{H\alpha}, & \text{otherwise.}
+    (0.48\pm0.02)\,\frac{[\text{\ion{N}{i}}]}{H\beta}+(1.62\pm0.01), & \text{if}~\frac{[\text{\ion{N}{i}}]}{H\alpha}>0.5 \\
+    (3.72\pm0.03)\,\frac{[\text{\ion{N}{i}}]}{H\beta}, & \text{otherwise.}
   \end{cases}
@@
   and then leave it at $0$. In any case, these equations need to be
-  fixed.)}
+  fixed.) JW: Fixed - note the method I am using for highlighting does not let me highlight within an equation environment so only the new version is shown.}
 

### 2020-01-01 produce_kine_plot.py

@@ -33,7 +33,7 @@ def plot(galaxies, str_galaxies, file_name, instrument, debug=False):
 	overplot={'CO':'w', 'radio':'g'}
 	Prefig(size=np.array((4, len(galaxies)))*7)
 	fig, axs = plt.subplots(len(galaxies), 4)#, sharex=True, sharey=True)
-	out_dir = '%s/Documents/thesis/chapter5/%s' % (cc.home_dir, instrument)
+	out_dir = '%s/Documents/paper/%s' % (cc.home_dir, instrument)
 
 	for i, galaxy in enumerate(galaxies):
 		if debug:
@@ -228,12 +228,12 @@ def plot(galaxies, str_galaxies, file_name, instrument, debug=False):
 			va='center', ha='center')
 
 
-	# if debug:
-	# 	fig.savefig('%s/%s.png' % (out_dir, 'test'), bbox_inches='tight',
-	# 		dpi=240)
-	# else:
-	# 	fig.savefig('%s/%s.png' % (out_dir, file_name), bbox_inches='tight',
-	# 		dpi=240)
+	if debug:
+		fig.savefig('%s/%s.png' % (out_dir, 'test'), bbox_inches='tight',
+			dpi=240)
+	else:
+		fig.savefig('%s/%s.png' % (out_dir, file_name), bbox_inches='tight',
+			dpi=240)
 
 	plt.close('all')
 
@@ -268,8 +268,8 @@ def ngc3100_NI_Hb():
 	ax.ax_dis.tick_params(top=True, bottom=True, left=True, right=True, 
 		direction='in', which='minor', length=10, width=3)
 
-	# fig.savefig('%s/Documents/thesis/chapter5/vimos/ngc3100_NI_Hb.png' % (
-	# 	cc.home_dir), dpi=300, bbox_inches='tight')
+	fig.savefig('%s/Documents/paper/vimos/ngc3100_NI_Hb.png' % (
+		cc.home_dir), dpi=300, bbox_inches='tight')
 
 
 def ngc1316_inflow():
@@ -351,8 +351,8 @@ def ngc1316_inflow():
 	fig.text(ax_loc.x1+0.08, 0.5, r'Mean velocity (km s$^{-1}$)', 
 		rotation=270, verticalalignment='center')
 	
[…]

### 2020-08-11 paper.tex
Investigated redshift uncert using VIMOS_analysis/mcmc.py
Mostly work on absorption line and stellar population sections

@@
       Radio Source Catalogue (PKS). We hereafter refer to the last
-      galaxy by its PKS name only. Col.~3: redshift. Col.~4: National
+      galaxy by its PKS name only. Col.~3: redshift \added{(uncertainty in redshift is $< 0.00001$)}. Col.~4: National
       Radio Astronomy Observatory (NRAO) VLA Sky Survey (NVSS)
@@
 In each bin, using the measured absorption line strengths, we identify
-the best-fitting single stellar population (SSP) model from an
+the best-fitting \added{luminosity-weighted} single stellar population (SSP) model from an
 interpolated grid of models using \textsc{emcee}, a \textsc{python}
@@
 (Section~\ref{subsec:RR-NRR}), slow rotators are more likely to be
-found in higher mass galaxies, and the three samples
+found in higher mass galaxies \added{(see lower panel of Fig.~\ref{fig:SRmassFraction})}, and the three samples
 (Atlas$^\text{3D}$, MASSIVE and our Southern Sample) have very
@@
 measure an average difference of the stellar velocity dispersions
-measured by \citet{Rampazzo2005} and us of $21$~km~s$^{-1}$. This may
-be enough to account for the offset of the measurements. {\bf (Why not
+measured by \citet{Rampazzo2005} and us of $21$~km~s$^{-1}$. 
+\removed{This may be enough to account for the offset of the measurements.} {\bf (Why not
   check this by changing the stellar velocity dispersions used in your
-  corrections to those of \citealt{Rampazzo2005}? Check.)}
-
-The offsets of our Fe5015 index measurements are also relatively large
+  corrections to those of \citealt{Rampazzo2005}?
+Check.
+JW: I can't get anywhere close the values of Rampazzo for G4300.
+Once the conversion to LIS is included, I have to double the stellar velocity dispersion, before I get can get similar results!
+I'm not sure what to do about this.)}
+
+\removed{The offsets of our Fe5015 index measurements are also relatively large
 when compared to the measurements of \citet{Rampazzo2005} and
@@
 latter, but for the former it may be due to differences in the way the
-[\ion{O}{iii}] doublet emission is accounted for. {\bf (In both cases,
+[\ion{O}{iii}] doublet emission is accounted for.} {\bf (In both cases,
   the offsets are smaller than $3\sigma$, in the sense that the stated
@@
 
-Indices other than G4300 and Fe5015 generally have literature
+\removed{Indices other than G4300 and Fe5015 generally have literature
 measurements that are fairly consistent with ours, although the
 dispersions of the measurements are fairly large (perhaps due to the
-transformations from Lick to LIS system indices).
-
+transformations from Lick to LIS system indices).}
 {\bf (A number of the offsets listed in the table actually {\em are}
@@
   this should be discussed.)}
+
+\added{For many indices \citet{Ogando2008} found significantly stronger measurements to us.} {\bf JW: I need help with this part, I don't know how to explain why they might be different - all I can say is that are.}
 
@@
 absorption line strength maps described in
-Section~\ref{subsec:absorption} to produce maps of the most-likely SSP
+Section~\ref{subsec:absorption} to produce maps of the most-likely \added{luminosity-weighted} SSP
 parameters (see Appendix~\ref{sec:maps}): age ($t$), metallicity
-($Z/H$) and alpha-element enhancement ($\alpha$/Fe). {\bf (You must
+\removed{($Z/H$)}\added{($[M/H]$)} and alpha-element enhancement ($\alpha$/Fe). {\bf (You must
   specify here (and presumably also in
@@
 In general, our Southern Sample galaxies show old, metal-rich and
-alpha-enhanced SSPs, characteristics that are common in ETGs {\bf (Add
+alpha-enhanced SSPs, characteristics that are common in ETGs \added{\citep[e.g.][]{Worthey1992}}{\bf (Add
   a classic reference here.)} The exceptions are NGC~612 and
@@
 \citealt{Koleva2011}, who found $t=4.5\pm0.3$~Gyr and
-$\mathrm{[Fe/H]}=0.12\pm0.01$ for an aperture covering the central
-$0.1$~kpc). {\bf (Is that a circular or square aperture? If circular,
+\removed{$\mathrm{[Fe/H]}=0.12\pm0.01$}\added{$\mathrm{[M/H]}=0.12\pm0.01$} \removed{for an aperture covering the central
+$0.1$~kpc)}`added{using a long slit with width $1\arcsec$ and length $0.1$~kpc)}. {\bf (Is that a circular or square aperture? If circular,
   is $0.1$~kpc the radius or diameter? Clarify.)} We also find NGC~612
@@
 significantly younger ($t\approx4$~Gyr) core of $\approx10\arcsec$ in
-diameter, and NGC~3100 has a branch of young stars ($t\approx4$\,Gyr)
-along the south-east branch of the molecular gas (\removed{white} 
+diameter, and NGC~3100 has a branch of young stars ($t\approx4$\,Gyr) \added{with very high metallicity projecting southwards from below the eastern}
+\removed{along the south-east} branch of the molecular gas (\removed{white} 
 \added{cyan} contours in
@@
 probe this they assumed a linear relationship between $\log(t)$ or
-[Fe/H] and $\log(R/R_\text{e})$, i.e.\ as is common the gradients
+\removed{[Fe/H]}\added{[M/H]} and $\log(R/R_\text{e})$, i.e.\ as is common the gradients
 considered are logarithmic radial gradients. We repeated these fits
@@
       \hline 
-      Galaxy & \multicolumn{2}{c}{$\Delta\log(t)$} & \multicolumn{2}{c}{$\Delta\text{[Fe/H]}$} & \multicolumn{2}{c}{$\log(M_\text{\ion{H}{ii}}/\mathrm{M_\odot})$} & Balmer Dec. & Ionisation\\
+      Galaxy & \multicolumn{2}{c}{$\Delta\log(t)$} & \multicolumn{2}{c}{\removed{$\Delta\text{[Fe/H]}$}\added{$\Delta\text{[M/H]}$}} & \multicolumn{2}{c}{$\log(M_\text{\ion{H}{ii}}/\mathrm{M_\odot})$} & Balmer Dec.
+& Ionisation\\
              & VIMOS & MUSE & VIMOS & MUSE & VIMOS$^\text{a}$ & MUSE & & \\
@@
 $\Delta\log(t)=0.014\pm0.007$ and
-$\Delta\text{[Fe/H]}=-0.03\pm0.01$. These are consistent with the
+\removed{$\Delta\text{[Fe/H]}=-0.03\pm0.01$}\added{$\Delta\text{[M/H]}=-0.03\pm0.01$}. These are consistent with the
 results of \citet{Koleva2011}, who found average gradients of
@@
 
-Radio-loud S0 galaxies are extremely rare, with only a handful of
+\removed{Radio-loud S0 galaxies are extremely rare, with only a handful of
 known cases \citep[e.g.][]{Heckman1982, Morganti2011}. This is
@@
 transition masses from rare to more numerous. NGC~612 is one of those
-rare cases. {\bf (You are not discussing here any of your own results,
+rare cases.} {\bf (You are not discussing here any of your own results,
   just rehashing old knowledge, so unless you have something else to

### 2020-08-11 produce_kine_plot.py

@@ -735,6 +735,7 @@ def H_profile(instrument='vimos'):
 		cols = (4, 5)
 		line = 'Hbeta'
 		res = 0.67 # arcsec/pix
+
 	elif instrument=='muse':
 		galaxies = np.array(['ic1459', 'ngc1316'])
 		str_galaxies = np.array(['IC 1459', 'NGC 1316'])
@@ -795,7 +796,10 @@ def H_profile(instrument='vimos'):
 			o = np.argsort(r)
 
 			lim = ax[i].get_xlim()
-			x = np.arange(-seeing_sigma, lim[1], 0.001)
+			ax[i].set_xlim(0, min(lim[1], 22))
+			lim = ax[i].get_xlim()
+
+			x = np.arange(-seeing_sigma, lim[1], 0.01)
 
 			y = 1/x**2
 			y = ndimage.gaussian_filter1d(y, seeing_sigma) # convolve with seeing
@@ -806,7 +810,7 @@ def H_profile(instrument='vimos'):
 
 			ax[i].text(0.93*lim[1], 0.7, str_galaxies[i], ha='right')
 
-			ax[i].set_ylim([-0.02, 1.1])
+			ax[i].set_ylim([0.001, 1.1])
 
 			ax[i].set_yscale('log')
 			ax[i].tick_params(which='major', direction='in', length=10, 
@@ -817,6 +821,8 @@ def H_profile(instrument='vimos'):
 				axis.set_major_formatter(
 					ticker.FuncFormatter(lambda y, _: '{:g}'.format(y)))
 
+
+
 	if instrument == 'vimos':
 		ax[0].set_ylabel(r'H$\,\beta$ normalised flux')
 	if instrument == 'muse':
@@ -825,8 +831,8 @@ def H_profile(instrument='vimos'):
 		a.set_xlabel('Radius (arcsec)')
 
 	fig.subplots_adjust(wspace=0,hspace=0)
-	fig.savefig('%s/Documents/paper/%s/%s_profile.png' % (
-		cc.home_dir, instrument, line), dpi=240)
+	fig.savefig('%s/Documents/paper/%s_profile.png' % (
+		cc.home_dir, line), dpi=240)
 	plt.close('all')
 	
 
@@ -834,13 +840,13 @@ def H_profile(instrument='vimos'):
 
 if __name__=='__main__':
 	# if 'home' in cc.device:
[…]

### 2020-09-22 produce_kine_plot.py
Tweeks to Halpha/beta profiles

@@ -726,7 +726,6 @@ def ic4296_WHaN2():
 
 def H_profile(instrument='vimos'):
 	from matplotlib import ticker
-	print '**************Need to correctly set seeing************'
 
 
 	if instrument=='vimos':
@@ -743,7 +742,17 @@ def H_profile(instrument='vimos'):
 		line = 'Halpha'
 		res = 0.2 # arcsec/pix
 
-	Prefig(size=np.array((len(galaxies), 1))*7)
+	Prefig(size=np.array((len(galaxies), 0.43*len(galaxies)))*7)
+
+	# if instrument=='vimos':
+		# plt.rc('axes', labelsize='x-large') # facecolor='w'
+		# plt.rc('xtick.major', size=10, width=2)
+		# plt.rc('xtick.minor', size=10, width=2)
+		# plt.rc('ytick.major', size=10, width=2)
+		# plt.rc('ytick.minor', size=10, width=2)
+	plt.rc('font', size=10*len(galaxies))
+
+
 	fig, ax = plt.subplots(1, len(galaxies), sharey=True)
 
 	analysis_dir = "%s/Data/%s/analysis" % (cc.base_dir, instrument)
@@ -756,31 +765,36 @@ def H_profile(instrument='vimos'):
 
 	for i, galaxy in enumerate(galaxies):
 		print 'H profile:', galaxy
-		D = Data(galaxy, instrument=instrument, opt='pop')
+		if galaxy == 'ngc1316':
+			D = Data(galaxy, instrument=instrument, opt='pop_test', overide=True)
+		else:
+			D = Data(galaxy, instrument=instrument, opt='pop')
 
-		if galaxy=='ic1459' and instrument=='vimos':
-			seeing_sigma = np.mean([0.82,0.84,1.20,1.26,1.10,1.27]) * 2.5
-			norm_r = 2.5
-			norm_y = 0.04
-		elif galaxy=='ngc0612':
-			seeing_sigma = np.mean([0.72,0.78,1.45,1.46,1.08,1.11]) * 2.5
-			norm_r = 2.5
-			norm_y = 0.2
-		elif galaxy=='ngc3100':
-			seeing_sigma = np.mean([0.76,0.82,0.75,0.82,1.16,1.20]) * 2.5
-			norm_r = 2
-			norm_y = 0.15
+
+		if instrument=='vimos':
[…]

### 2020-09-23 paper.tex
Tweeks to Halpha/beta profiles
Improved refs and discussion of galaxies re ISM

@@
     though. Also needed are updated affiliations for Francesco and
-    Robert.}}
+    Robert. JW: not deliberate - I'd left this to ask you about who to include.}}
 
@@
 molecular ISM of our sample galaxies has already been examined in
-\citet{ruffa2019, ruffa2020}. If the low star-formation rates
+\citet{ruffa2019a, ruffa2019b}. If the low star-formation rates
 typically seen in massive ETGs are preserved by jet-mode AGN, then all
@@
 rotation. Follow-up Atacama Large Millimeter/sub-millimeter Array
-(ALMA) observations were recently presented in \citet{ruffa2019,
-  ruffa2020}.
+(ALMA) observations were recently presented in \citet{ruffa2019a,
+  ruffa2019b}.
 
@@
 best-fitting Gaussians from Section~\ref{subsec:EmissionLines} from the
-data, before the line strenghts are measured. \removed{, using only the 
+data, before the line strengths are measured. \removed{, using only the 
 stellar templates (and continuum correction) subsequently considered 
@@
   (first) sub-section. You then need not repeat the test description
-  in Sub-section~\ref{subsec:FR-SR}; just state the results.)}
+  in Sub-section~\ref{subsec:FR-SR}; just state the results.) JW: Massive did not classify into RR/NRR and only using Altas3d doesn't cover the mass range sufficiently.}
 
@@
   then need to make sure you know the orientation of these images
-  accurately. Try it?)}
+  accurately. Try it?) JW: I going to leave this one: this is taking a long time for not a lot of gain. We don't place much weight on the PA in the conclusions given the small sample size.}
 
@@
 rather than \AA? If so, add a short note. If not, correct.)} 
-\added{(Mg$_2$ is condered to be a molecular index and is thus measured 
+\added{(Mg$_2$ is considered to be a molecular index and is thus measured 
 in units of mag$^{-1}$.) We can thus}\removed{Thus, following \citet{Ziegler1997}, we also} use Mg~$b$ as a proxy for
@@
 Clarify.) JW: the entire function has been transformed including the zero-point.
-This actually results in a cubic function (see Appendix A of \citealt{Vazdekis2010}), though as can been seen from the Fig.~3, the quadradic and cubic terms have very little effect in this range.}
+This actually results in a cubic function (see Appendix A of \citealt{Vazdekis2010}), though as can been seen from the Fig.~3, the quadratic and cubic terms have very little effect in this range.}
 
@@
 differences between the literature measurements and ours. For the
-comparison to \citet{Vazdekis2010}, we re-analysed the Spectral Aeral
+comparison to \citet{Vazdekis2010}, we re-analysed the Spectral Aerial
 Unit for Research on Optical Nebulae (SAURON)
@@
 Whilst this is consistent with an internal origin of the gas, it should be noted that a major merger is typically expected to deplete a galaxy's gas reservoir.
-Either this did not happen in this case (a major merger being evidenced by the existence of the KDC) or the ISM may has an external origin and the apparent alignment of the gas and outer stars is random.}
+Either this did not happen in this case (a major merger being evidenced by the existence of the KDC) or as speculated by \citet{Prichard2019}, the observed result of IC~1459 is the product of multiple events e.g.
+the ISM may have an external origin and the apparent alignment of the gas and outer stars is random.}
 
 \textbf{NGC~612} has well aligned stellar and ionised gas kinematics
-(see Fig.~\ref{fig:ngc612}), the misalignment angle (measured as
+(see Fig.~\ref{fig:ngc612}; \citealt{Goss1980}), the misalignment angle (measured as
 described in Section~\ref{subsubsec:KinPA}) being just
@@
 destroy stellar discs), suggesting in turn that the fuelling of the
-radio jet could be a purely secular process.
-
-%**********************************************************************
-%This plot no longer exists... Which plot?!
-%**********************************************************************
+radio jet could be a purely secular process \citep{Ekers1978}.
 
@@
 ionised gas velocity field (see Fig.~\ref{fig:ngc1316}), it is clear
-that a simple exponential disc model will not fit the data well. We
+that a simple exponential disc model will not fit the data well.
+\added{\citet{Schweizer1980} noted that the projected axes of stellar and gas components are roughly perpendicular pointing to an external origin to the ISM \citep{Shklovskii1962}.
+Unfortunately we do not achieve a high enough $S/N$ to investigate the ionised gas in these regions.} \removed{We
 instead speculate that that the high-velocity peak to the South-West
@@
   evidence for this? If so, state them!)} almost perpendicular to the
-radio jet, although other interpretations are possible. Better quality
+radio jet, although other interpretations are possible.} Better quality
 data (better $S/N$ and a wider field of view) coupled with more
-sophisticated models are required to test this interpretation.
+sophisticated models are required to \removed{test this interpretation.}\added{interpret this data.}
 % Nevertheless, it is clear that the gas in not in a settled disc.
@@
   contours in the figure... pale blue/turquoise contours?)} show a
-broken ring, the radio jet passing through the gaps, hence suggesting
-a jet-ring interaction \citep[see][]{ruffa2019, ruffa2020}. The
+broken ring, \added{with} the radio jet passing through the gaps\removed{, hence suggesting}\added{. This suggests }
+a jet-ring interaction \citep[see][]{ruffa2019a, ruffa2019b}. The
 ionised gas is brightest in those same gaps, that we interpret as
@@
 interpretation, being completely different than that of the stars (and
-nearly totally blueshifted). The centre of rotation of the gas also
+nearly totally blueshifted). \removed{The centre of rotation of the gas also
 appears to be offset from the centre of the galaxy (as defined by its
-stellar surface brightness), by several arcseconds to the west. {\bf
+stellar surface brightness), by several arcseconds to the west.} \added{What is clear, is that there is a complete lack of any large-scale rotation of the ISM.} {\bf
   (I really do not understand how you can identify a centre of
@@
     $r^{-2}$, convolved with a Gaussian of width equal to the measured
-    PSF. {\bf (But what about the zero-points of the red profiles? How
+    PSF. \added{The fitting of these lines was done by eye.}{\bf (But what about the zero-points of the red profiles? How
       are these set? Explain.)} {\bf (Make the axis labels and galaxy
@@
     radio band displayed depends on the data and angular resolution
-    available \citep[see][]{ruffa2019, ruffa2020}. {\bf
+    available \citep[see][]{ruffa2019a, ruffa2019b}. {\bf
       (``Metalicity'' should be ``Metallicity''. Also explain the

### 2020-11-11 paper_noComments.tex
Final changes made?

--- 2020-09-23 paper.tex
@@
 \usepackage{color,soul} % highlighting
-\DeclareRobustCommand{\removed}[1]{{\sethlcolor{red}\hl{#1}}}
-\DeclareRobustCommand{\added}[1]{{\sethlcolor{green}\hl{#1}}}
 
@@
 %Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:joshua.warren@physics.ox.ac.uk}{joshua.warren@physics.ox.ac.uk}}
-  Martin Bureau,$^{1,2}$ Bernd Hasemann,$^{3}$ \added{Ilaria Ruffa,$^{4}$} Isabella
+  Martin Bureau,$^{1,2}$ Bernd Hasemann,$^{3}$ Ilaria Ruffa,$^{4}$ Isabella
   Prandoni,$^{4}$ \newauthor Francesco Santoro,$^{4}$ Robert
-  Laing,$^{4}$ Paola Parma,$^{4}$ \added{Rosita Paladino,$^{4}$} Hans de Ruiter,$^{4}$ \newauthor
-  Arturo Mignano$^{4}$ and \added{Timothy Davis$^{5}$}
+  Laing,$^{4}$ Paola Parma,$^{4}$ Rosita Paladino,$^{4}$ Hans de Ruiter,$^{4}$ \newauthor
+  Arturo Mignano$^{4}$ and Timothy Davis$^{5}$
   \\
@@
   Bologna, Italy\\
-  \added{$^{5}$School of Physics \& Astronomy, Cardiff University, Queens Buildings, The Parade, Cardiff CF24 3AA, UK}\\
-  $^*${\bf Should you/we add Ilaria Ruffa and/or Rosita Paladino
-    and/or Timothy Davis as authors (they are all on the first/ALMA
-    paper)?}\\{\bf I feel it is a little strange that Ilaria is not (so I
-    would argue we should add her), I am much less sure about
-    Rosita,}\\ {\bf and I suspect it is ok that Tim is not. Your call
-    though. Also needed are updated affiliations for Francesco and
-    Robert. JW: not deliberate - I'd left this to ask you about who to include.}}
+  $^{5}$School of Physics \& Astronomy, Cardiff University, Queens Buildings, The Parade, Cardiff CF24 3AA, UK
 
@@
       Radio Source Catalogue (PKS). We hereafter refer to the last
-      galaxy by its PKS name only. Col.~3: redshift \added{(uncertainty in redshift is $< 0.00001$)}. Col.~4: National
+      galaxy by its PKS name only. Col.~3: redshift (uncertainty in redshift is $< 0.00001$). Col.~4: National
       Radio Astronomy Observatory (NRAO) VLA Sky Survey (NVSS)
@@
 final mean stellar velocity of each galaxy is adopted as its precise
-spectroscopic redshift and is listed in Table~\ref{tab:sample}. {\bf
-  (Shouldn't there be an uncertainty on this redshift/mean velocity?
-  List in Table~1.)} After this step, each bin is analysed
+spectroscopic redshift and is listed in Table~\ref{tab:sample}. 
+After this step, each bin is analysed
 independently.
@@
 thus affected by the ISM kinematics) was significantly affecting the
-quality of the \removed{best-fitting \textbf{(Spatially-collapsed? 
-Clarify.)} stellar spectrum} \added{fits to the stellar 
-spectrum for all bins}. For this reason, when fitting the stellar spectra
-only {\bf (i.e.\ Sections~\ref{subsec:starKin} and
-  \ref{subsec:absorption} but not \ref{subsec:EmissionLines}?
-  Clarify.)}} \added{(i.e.\ Sections~\ref{subsec:starKin})}, the wavelength range of the NGC~1316 spectra was
-restricted to $<5800$~\AA. \added{The best-fitting stellar spectra were then extrapolated above 5800~\AA.}
+quality of the fits to the stellar 
+spectrum for all bins. For this reason, when fitting the stellar spectra
+only (i.e.\ Sections~\ref{subsec:starKin}), the wavelength range of the NGC~1316 spectra was
+restricted to $<5800$~\AA. The best-fitting stellar spectra were then extrapolated above 5800~\AA.
 
@@
 doublets: 
-\added{[\ion{O}{II}]$\lambda\lambda$3726,3729,
-H$\delta$,} H$\gamma$, H$\beta$,
+[\ion{O}{II}]$\lambda\lambda$3726,3729,
+H$\delta$, H$\gamma$, H$\beta$,
 [\ion{O}{iii}]$\lambda\lambda$4969,5007,
@@
 [\ion{N}{ii}]$\lambda\lambda$6548,6583, H$\alpha$ and
-[\ion{S}{ii}]$\lambda\lambda$6716,6731 {\bf (Should the \ion{O}{ii}
-  doublet discussed a few lines below also be quoted here? Or should
-  the below be the \ion{O}{i} or \ion{O}{iii} doublet already quoted?
-  What about H$\delta$, also in your original table but now commented
-  out? Correct.)}. \removed{We fit the emission line fluxes and kinematics
-independently of the stellar kinematics, and their fluxes
-independently of each other (but see below).} To minimise template 
+[\ion{S}{ii}]$\lambda\lambda$6716,6731. To minimise template 
 mismatch, whereby emission lines are erroneously fitted
@@
 components of the [\ion{O}{ii}] and [\ion{S}{ii}] doublets are fit 
-independently. {\bf (See previous comment about the \ion{O}{ii} doublet. 
-Correct.)}.
+independently.
 
@@
 
-\removed{\subsubsection{Removing Emission Lines}}
-% \label{subsubsec:RemovingEmission}
-
 Each emission line is removed from each spectrum by subtracting the
 best-fitting Gaussians from Section~\ref{subsec:EmissionLines} from the
-data, before the line strengths are measured. \removed{, using only the 
-stellar templates (and continuum correction) subsequently considered 
-for the velocity dispersion correction (see below). \mbox{\textbf{(I do not 
-understand the second part of this sentence. Check/clarify/correct.)}}} 
-These are then corrected for the effects of the stellar velocity 
+data, before the line strengths are measured. These are then corrected for the effects of the stellar velocity 
 dispersion, as detailed below.
@@
 In each bin, using the measured absorption line strengths, we identify
-the best-fitting \added{luminosity-weighted} single stellar population (SSP) model from an
+the best-fitting luminosity-weighted single stellar population (SSP) model from an
 interpolated grid of models using \textsc{emcee}, a \textsc{python}
@@
 
-In reality, the field of view does not always \added{fully} contain 
-\added{a given fitted ellipse} \removed{$1$~$R_\text{e}$}. When this 
+In reality, the field of view does not always fully contain 
+a given fitted ellipse. When this 
 is the case, we follow the method of \citet{Emsellem2007}, where 
 $R_\text{m}$ is redefined as $R_\text{m}\equiv\sqrt{A_\text{s}/\pi}$, 
-where $A_\text{s}$ is the area \added{contained within 
-the field of view} of the {\bf (Largest? Clarify.)} 
-\added{given} ellipse \removed{contained within 
-the field of view}. {\bf (I do not understand the meaning of the 
-following sentence in {\it italics}. Rephrase/explain better. 
-Perhaps even simply remove? What are $R_\text{max}$ and 
-$A_\text{ellipse}$?!)} {\it For a given galaxy, we fit ellipses 
+where $A_\text{s}$ is the area contained within 
+the field of view of the given ellipse. {\it For a given galaxy, we fit ellipses 
 as described above, up to $R_\text{m}=R_\text{max}$, where 
-\added{$R_\text{max}$ is defined such that  
+$R_\text{max}$ is defined such that  
 $\frac{A_\text{s}(R_\text{max})}{A_\text{ellipse}(R_\text{max})} 
-\equiv 0.15$ or $R_\text{max} = R_\text{e}$, which ever is smallest.} 
-\removed{$A_\text{s}$ reaches a maximum difference of 15\% with 
-respect to the area of the fitted ellipse, $A_\text{ellipse}$.}} The 
-value $\epsilon_\text{e}$, the ellipticity \added{of this largest 
-fitted ellipse} \removed{at $1$~$R_\text{e}$ or $R_\text{max}$, 
-whichever is smallest}, is given in Column~3 of 
+\equiv 0.15$ or $R_\text{max} = R_\text{e}$, which ever is smallest.
+} The value $\epsilon_\text{e}$, the ellipticity of this largest 
+fitted ellipse, is given in Column~3 of 
 Table~\ref{tab:classify}.
@@
       a higher $S/N$ is required in the outer parts of the field of
-      view for confirmation. {\bf (It would be better to calculate and
-        report/list uncertainties on $\lambda_\mathrm{R_e}$ and
-        $\epsilon_\text{e}$.)}}
+      view for confirmation.}
     % \end{tablenotes}
@@
 of the axis perpendicular to the apparent angular momentum vector,
-measured \added{eastward} \removed{westward} from North. {\bf (Are you sure this is westward and
-  not eastward? Position angles are usually defined from North to
-  East, the latter of course usually being to the left in astronomical
-  images. Check and correct if need be.)} A global value of
+measured eastward from North. A global value of
 $PA_\text{kin}$ is calculated using the \textsc{python} routine
@@
 between the photometric and stellar kinematic position angles,
-$\Gamma_\text{kin}\equiv\arcsin(\sin[PA_\text{phot}-PA_\text{kin}])$
-{\bf (Why is that different from simply
-  $\Gamma_\text{kin}\equiv PA_\text{phot}-PA_\text{kin}$? Correct if
-  need be.)} {\bf (At which radius/ellipse semi-major axis is
-  $PA_\text{phot}$ taken/measured? Specify.)} \added{, where$PA_\text{phot}$ is measured at $R_\text{max}$.}
+$\Gamma_\text{kin}\equiv\arcsin(\sin[PA_\text{phot}-PA_\text{kin}])$, 
+where$PA_\text{phot}$ is measured at $R_\text{max}$.
 
@@
 \end{equation}
-{\bf (Is $R_i$ really measured from the centre as stated, or rather
-  with respect to the kinematic minor axis/rotation axis?
-  State/explain if the latter. JW: Yes, $R_i$ is from the center - see Eq6 in \citep{Emsellem2007})} where $F_i$ is the flux of the
+where $F_i$ is the flux of the
 $i^\text{th}$ bin, $R_i$ its distance from the centre, $V_i$ its mean
 stellar velocity and $\sigma_i$ its stellar velocity dispersion. The
-sum is computed over all $N$ bins within \removed{$1$~$R_\text{e}$} \added{$1$~$R_\text{max}$} of the
-centre of the galaxy. {\bf (What do you do if the field of view does
-  not reach $1$~$R_\text{e}$? Specify/discuss (as for
-  $\epsilon_\text{e}$).)}
+sum is computed over all $N$ bins within $1$~$R_\text{max}$ of the
+centre of the galaxy.
 
@@
 We find $4$ out of $11$, or $36\pm15\%$, of our sample galaxies are
-regular rotators. This compares to \added{$82\pm2\%$} of the Atlas$^\text{3D}$
+regular rotators. This compares to $82\pm2\%$ of the Atlas$^\text{3D}$
 galaxies being classified as regular rotators
-\citep{Krajnovic2011}. {\bf (Better to also quote the uncertainty on
-  that $82\%$ figure.)} However, the likelihood of a given galaxy
+\citep{Krajnovic2011}. However, the likelihood of a given galaxy
 being a regular rotator is highly mass dependent, the likelihood
@@
 
-{\bf (Why not do a test here as in the next
-  Sub-section~\ref{subsec:FR-SR} but for the RR/NRR classification,
-  i.e.\ taking into account the mass differences of the two samples? I
-  suggest you do, and then move the description of that test to this
-  (first) sub-section. You then need not repeat the test description
-  in Sub-section~\ref{subsec:FR-SR}; just state the results.) JW: Massive did not classify into RR/NRR and only using Altas3d doesn't cover the mass range sufficiently.}
-
 \subsection{Fast/Slow Rotators}
@@
 the Atlas$^\text{3D}$ and MASSIVE surveys, that find respectively
-\added{$13\pm2\%$} and \added{$80\pm6\%$} of their sample galaxies to be slow
-rotators. {\bf (Again, better to also quote the uncertainties on those
-  two fractions. I doubt the decimal place is meaningful in either of
-  them.)} As in the regular-/non-regular-rotator classification scheme
+$13\pm2\%$ and $80\pm6\%$ of their sample galaxies to be slow
+rotators. As in the regular-/non-regular-rotator classification scheme
 (Section~\ref{subsec:RR-NRR}), slow rotators are more likely to be
-found in higher mass galaxies \added{(see lower panel of Fig.~\ref{fig:SRmassFraction})}, and the three samples
+found in higher mass galaxies (see lower panel of Fig.~\ref{fig:SRmassFraction}), and the three samples
 (Atlas$^\text{3D}$, MASSIVE and our Southern Sample) have very
@@
     magenta. The black solid lines indicate the limits of the
-    fast-/slow-rotator classes. {\bf (In the figure legend, ``Regular
-      Rotator'' should be ``Regular rotator''. The figure is also too
-      small (the symbols can not be distinguished). Either put the
-      legend on top or make the figure full width. Print it to check!
-      Finally, for this and all figures except those of Appendix~B, it
-      would be preferable to have small/minor tickmarks (with no
-      numerical label) as well as large/major tickmarks.)}}
+    fast-/slow-rotator classes.}
   \label{fig:lambdaR_ellip}
@@
     colour-coded. The labels list the number of slow rotators and
-    total number of galaxies in each bin. {\bf (In the y-axis label,
-      ``Southern sample'' should be ``Southern Sample''.)}}
+    total number of galaxies in each bin.}
   \label{fig:SRmassFraction}
@@
 
-{\bf (At the moment, the bottom panel of Fig.~\ref{fig:SRmassFraction}
-  is never referenced nor discussed anywhere. It should, even
-  briefly. Add some discussion of it.)}
-
 \subsection{Kinematic Features}
@@
 
-{\bf (A solution to these large $PA_\text{phot}$ uncertainties would
-  be to measure $PA_\text{phot}$ not from the surface brightness maps
-  reconstructed from the IFS data, but rather from actual images, of
-  which there should be many easily available. Of course, you would
-  then need to make sure you know the orientation of these images
-  accurately. Try it?) JW: I going to leave this one: this is taking a long time for not a lot of gain. We don't place much weight on the PA in the conclusions given the small sample size.}
-
 While intrinsically misaligned systems may appear aligned in certain
@@
 
-\citet{Bender1993} observed a tight relationship between the \added{central} \removed{global}
+\citet{Bender1993} observed a tight relationship between the central
 Mg$_2$ absorption line strength (a variant of the Mg~$b$ line
 strength) and the logarithm of the central stellar velocity
-dispersion, $\sigma_0$, in elliptical galaxies. \removed{They also noticed that
-the residuals from the best-fitting linear relation appeared to be
-intrinsic, with a near Gaussian distribution about the median value}
-{\bf (Was that median value $\approx0$? If so, state explicitly. If
-  not, then the fit was either bad or there is something we do not
-  understand.)} \removed{and no correlation with any other galaxy property.}
+dispersion, $\sigma_0$, in elliptical galaxies.
 
@@
 gradient of $14.3$\,--\,$15.5$~mag~\AA$^{-1}$ depending on
-metallicity. {\bf (Why the strange units? Is Mg$_2$ measured in mag 
-rather than \AA? If so, add a short note. If not, correct.)} 
-\added{(Mg$_2$ is considered to be a molecular index and is thus measured 
-in units of mag$^{-1}$.) We can thus}\removed{Thus, following \citet{Ziegler1997}, we also} use Mg~$b$ as a proxy for
+metallicity. (Mg$_2$ is considered to be a molecular index and is thus measured 
+in units of mag$^{-1}$.) We can thus use Mg~$b$ as a proxy for
 Mg$_2$.
@@
 indicated by the solid black line, with a gradient of
-$3.3\pm1.0$~\AA~dex$^{-1}$. \added{We} \removed{It was} noted that NGC~1316 is \added{again an} \removed{a possible}
-outlier. {\bf (Noted by who or where? Specify. Also mention that it
-  seems to again be an outlier here.)} Excluding NGC~1316 from the fit
+$3.3\pm1.0$~\AA~dex$^{-1}$. We noted that NGC~1316 is again ana possible
+outlier. Excluding NGC~1316 from the fit
 yields a gradient of $2.5\pm0.7$~\AA~dex$^{-1}$ (green dashed line in
@@
 functions of \citealt{Vazdekis2010}; blue dotted line in
-Fig.~\ref{fig:globalMg}). {\bf (Any uncertainty on this value of
-  $2.7$? If so, quote it.) JW: No \citet{Ziegler1997} doesn't propagate uncertainty into errors on the fit.}
-% , with an intrinsic scatter of 0.16\,\AA\ for galaxies with
-% $\log \sigma_0 \geqslant 2.3$\,dex.
-
-{\bf (One element I find confusing in this sub-section is that the
-  first paragraph mentions a ``global'' relation, but the third
-  paragraph and Fig.~3 use central $2\arcsec$ radius apertures that
-  are therefore ``central'' apertures. Which one is right? You need to
-  harmonise this. Also, in Fig.~\ref{fig:globalMg}, are you using the
-  full relation of \citet{Ziegler1997} or just their gradient (and you
-  then select a zero-point that suits you)? If the latter, then you
-  must state this in the text. In other words, is the near perfect
-  match of the green dashed and blue dotted lines truly a result or is
-  it partially by construction (i.e.\ because you matched the
-  zero-points yourself)?
-Clarify.) JW: the entire function has been transformed including the zero-point.
-This actually results in a cubic function (see Appendix A of \citealt{Vazdekis2010}), though as can been seen from the Fig.~3, the quadratic and cubic terms have very little effect in this range.}
+Fig.~\ref{fig:globalMg}).
 
@@
     in a nearly perfect agreement (the green dashed and blue dotted
-    lines are essentially indistinguishable). {\bf (In the legend,
-      ``same'' should be ``Same'', ``Ziegler97'' should be ``Ziegler
-      \& Bender (1997)'', and ``Fit excluding...'' should be
-      ``Best-fitting excluding...''. In the y-axis label, there should
-      be a space between ``$b$'' and ``(\AA)''. The x-axis label
-      should be ``$\log\,(\sigma_0/{\rm km~s^{-1}})$''.)}}
+    lines are essentially indistinguishable).}
   \label{fig:globalMg}
@@
 \citep{Emsellem2004} using the same analysis pipeline as for our
-Southern Sample. {\bf (Why not use the much larger Atlas$^{\rm 3D}$
-  dataset instead?
-Explain briefly if justified.)} \added{This was used over the larger Atlas$^\text{3D}$ sample \citep{Cappellari2011}, as stellar populations were not published by the Atlas$^\text{3D}$ team.}
+Southern Sample. This was used over the larger Atlas$^\text{3D}$ sample \citep{Cappellari2011}, as stellar populations were not published by the Atlas$^\text{3D}$ team.
 
@@
 measured by \citet{Rampazzo2005} and us of $21$~km~s$^{-1}$.
-\removed{This may be enough to account for the offset of the measurements.} {\bf (Why not
-  check this by changing the stellar velocity dispersions used in your
-  corrections to those of \citealt{Rampazzo2005}?
-Check.
-JW: I can't get anywhere close the values of Rampazzo for G4300.
-Once the conversion to LIS is included, I have to double the stellar velocity dispersion, before I get can get similar results!
-I'm not sure what to do about this.)}
-
-\removed{The offsets of our Fe5015 index measurements are also relatively large
-when compared to the measurements of \citet{Rampazzo2005} and
-\citet{Vazdekis2010}. The origin of this offset is unclear for the
-latter, but for the former it may be due to differences in the way the
-[\ion{O}{iii}] doublet emission is accounted for.} {\bf (In both cases,
-  the offsets are smaller than $3\sigma$, in the sense that the stated
-  offset is less than $3$ times the stated dispersion. The offsets are
-  thus not really significant... is this discussion therefore really
-  worth it? A number of other indices from \citealt{Rampazzo2005} also
-  show equally significant offsets ($\approx2\sigma$). What about
-  them? I think this notion of the ``significance'' of the offsets
-  must be introduced/addressed to justify which offsets you choose to
-  discuss.)}
-
-\removed{Indices other than G4300 and Fe5015 generally have literature
-measurements that are fairly consistent with ours, although the
-dispersions of the measurements are fairly large (perhaps due to the
-transformations from Lick to LIS system indices).}
-{\bf (A number of the offsets listed in the table actually {\em are}
-  significant (i.e.\ $>3\sigma$). In particular, a majority of the
-  offsets with the \citealt{Ogando2008} measurements are
-  significant. Why are these measurements so inconsistent? I think
-  this should be discussed.)}
-
-\added{For many indices \citet{Ogando2008} found significantly stronger measurements to us.} {\bf JW: I need help with this part, I don't know how to explain why they might be different - all I can say is that are.}
+
+For many indices \citet{Ogando2008} found significantly stronger measurements to us.
 
@@
 \label{sec:stellarPop}
-
-{\bf (Here, you just straightaway jump into a discussion of the
-  stellar populations, i.e.\ the derived quantities of age and
-  metallicity. I think this should be preceded (possibly in the
-  previous section) by a discussion of the line strengths themselves,
-  at least in the same spirit as what is done here for the
-  populations, i.e.\ radial gradients and KDCs (that are not discussed
-  in the preceding section on line strengths, that exclusively deals
-  with Mg\,--\,$\sigma$ and the litetature comparison). Add?)}
 
@@
 absorption line strength maps described in
-Section~\ref{subsec:absorption} to produce maps of the most-likely \added{luminosity-weighted} SSP
+Section~\ref{subsec:absorption} to produce maps of the most-likely luminosity-weighted SSP
 parameters (see Appendix~\ref{sec:maps}): age ($t$), metallicity
-\removed{($Z/H$)}\added{($[M/H]$)} and alpha-element enhancement ($\alpha$/Fe). {\bf (You must
-  specify here (and presumably also in
-  Section~\ref{subsubsec:stellarPop}) whether the stellar population
-  parameters are mass- or luminosity-weighted.)}
-
-{\bf (I am confused here because in the paragraph above you refer to
-  $Z/H$ as your proxy for metallicity, but in the paragraph below you
-  keep talking about [Fe/H], and in the maps the labels are just
-  ``metalicity'' (yes, with the spelling mistake!). Which one is right
-  (metallicity, $Z/H$, [$Z/H$], Fe/H or [Fe/H]? Use only the right one
-  and be consistent.)}
+($[M/H]$) and alpha-element enhancement ($\alpha$/Fe).
 
 In general, our Southern Sample galaxies show old, metal-rich and
-alpha-enhanced SSPs, characteristics that are common in ETGs \added{\citep[e.g.][]{Worthey1992}}{\bf (Add
-  a classic reference here.)} The exceptions are NGC~612 and
+alpha-enhanced SSPs, characteristics that are common in ETGs \citep[e.g.][]{Worthey1992} The exceptions are NGC~612 and
 NGC~1316. NGC~1316 has a very young stellar population (our fit of
@@
 \citealt{Koleva2011}, who found $t=4.5\pm0.3$~Gyr and
-\removed{$\mathrm{[Fe/H]}=0.12\pm0.01$}\added{$\mathrm{[M/H]}=0.12\pm0.01$} \removed{for an aperture covering the central
-$0.1$~kpc)}`added{using a long slit with width $1\arcsec$ and length $0.1$~kpc)}. {\bf (Is that a circular or square aperture? If circular,
-  is $0.1$~kpc the radius or diameter? Clarify.)} We also find NGC~612
+$\mathrm{[M/H]}=0.12\pm0.01$ using a long slit with width $1\arcsec$ and length $0.1$~kpc).
+ We also find NGC~612
 to have an extended young stellar population of
@@
 significantly younger ($t\approx4$~Gyr) core of $\approx10\arcsec$ in
-diameter, and NGC~3100 has a branch of young stars ($t\approx4$\,Gyr) \added{with very high metallicity projecting southwards from below the eastern}
-\removed{along the south-east} branch of the molecular gas (\removed{white} 
-\added{cyan} contours in
-Fig.~\ref{fig:ngc3100}). {\bf (I do not see the age feature you refer
-  to in the NGC3100 maps, and the CO is distributed North-East to
-  South-West, so there is no South-East CO ``branch''. Perhaps you
-  meant South-West (where there is indeed a blue region in the
-  H$\beta$ map, if not in the age map)? Also, there is no white
-  contour in the figure. The CO contours are in pale
-  blue/turquoise. Is that what you meant? In any case, this needs to
-  be corrected to reflect the truth.)}
+diameter, and NGC~3100 has a branch of young stars ($t\approx4$\,Gyr) with very high metallicity projecting southwards from below the eastern branch of the molecular gas (cyan contours in
+Fig.~\ref{fig:ngc3100}).
 
@@
 probe this they assumed a linear relationship between $\log(t)$ or
-\removed{[Fe/H]}\added{[M/H]} and $\log(R/R_\text{e})$, i.e.\ as is common the gradients
+[M/H] and $\log(R/R_\text{e})$, i.e.\ as is common the gradients
 considered are logarithmic radial gradients. We repeated these fits
@@
       \hline 
-      Galaxy & \multicolumn{2}{c}{$\Delta\log(t)$} & \multicolumn{2}{c}{\removed{$\Delta\text{[Fe/H]}$}\added{$\Delta\text{[M/H]}$}} & \multicolumn{2}{c}{$\log(M_\text{\ion{H}{ii}}/\mathrm{M_\odot})$} & Balmer Dec.
-& Ionisation\\
+      Galaxy & \multicolumn{2}{c}{$\Delta\log(t)$} & \multicolumn{2}{c}{$\Delta\text{[M/H]}$} & \multicolumn{2}{c}{$\log(M_\text{\ion{H}{ii}}/\mathrm{M_\odot})$} & Balmer Dec. & Ionisation\\
              & VIMOS & MUSE & VIMOS & MUSE & VIMOS$^\text{a}$ & MUSE & & \\
@@
 $\Delta\log(t)=0.014\pm0.007$ and
-\removed{$\Delta\text{[Fe/H]}=-0.03\pm0.01$}\added{$\Delta\text{[M/H]}=-0.03\pm0.01$}. These are consistent with the
+$\Delta\text{[M/H]}=-0.03\pm0.01$. These are consistent with the
 results of \citet{Koleva2011}, who found average gradients of
@@
 
-\added{\citet{McDermid2006}} \removed{\citet{Kuntschner2010}} showed that 
+\citet{McDermid2006} showed that 
 KDCs can be separated into two classes: either small with various stellar 
 ages or typically larger but containing a homogeneously old stellar 
-population. {\bf (I thought the first to point this out was 
-McDermid et al.\ (2006; see e.g.\ their Fig.~16), which should at 
-least also be quoted here. Check and possibly correct.)} 
-\added{Using the method of \citet{McDermid2006},} the size 
-\added{and age} of the KDC is defined as the radius
+population. Using the method of \citet{McDermid2006}, the size 
+and age of the KDC is defined as the radius
 where the superposition of the two kinematic components (the KDC and
-the host galaxy) results in a local minimum in the mean velocity \added{and} the
+the host galaxy) results in a local minimum in the mean velocity and the
 age of the most-likely SSP model for the spatially integrated spectrum
-within a central \added{, circular} aperture with a \added{radius} of 
-$1\arcsec$ {\bf (Again, square or circular, radius or diameter? Clarify.)} 
-\removed{is taken as the KDC's age.} \added{, respectively.} 
-{\bf (Are these two definitions (of the KDCs' sizes and ages) 
-those of \citealt{Kuntschner2010} or yours or both? Clarify.)}
+within a central, circular aperture with a radius of 
+$1\arcsec$, respectively.
 
@@
     measurements from SAURON \citep{Kuntschner2010} are shown in black
-    and grey for respectively fast and slow rotators. {\bf (In the
-      legend, ``same'' should be ``Same'', ``Fast rotating'' should be
-      ``Fast-rotating'', and ``Slow rotating'' should be
-      ``Slow-rotating''. In the y-axis label, ``Gyrs'' should be
-      ``Gyr''.)}}
+    and grey for respectively fast and slow rotators.}
   \label{fig:KDC}
@@
 Southern Sample have emission lines detected outside of a central
-\removed{region} \added{1--2 spaxels. This means no structure can be
- resolved}. Of the remaining $7$ galaxies, $5$ (IC~1531, IC~4296,
+1--2 spaxels. This means no structure can be
+ resolved. Of the remaining $7$ galaxies, $5$ (IC~1531, IC~4296,
 NGC~3557, NGC~7075 and ESO~443-G024) are only detected in their centre
@@
 Appendix~\ref{sec:maps}). For each individual galaxy, all the emission
-lines have a similar distribution (but different fluxes). {\bf (It
-  would help in this paragraph to define what you mean by
-  ``centre''. E.g.\ ``a centred circular region of radius
-  $???\arcsec$'' or ``within $???\arcsec$ of the centre. Add.)}
-
-\removed{As can be seen from the maps in Appendix~\ref{sec:maps}, 
-both NGC~612 and NGC~3100 have significant off-centred ionised 
-gas emission.} {\bf (What do you mean by ``significant'' here? Bright?
-  Clarify. Equivalently, why is the off-centred emission in IC~1459
-  and NGC~1316 not considered significant?)} 
-\added{The ionised gas emission for both NGC~612 ).} In NGC~612, 
-the ionised gas does not appear related to either the radio jet 
-(extending $\approx200$~kpc to the East and West of the galaxy 
+lines have a similar distribution (but different fluxes).
+
+As can be seen from the maps in Appendix~\ref{sec:maps}, 
+both NGC~612 and NGC~3100 have ionised gas emission offset from the center 
+of the galaxy. In NGC~612, the ionised gas does not appear related to either 
+the radio jet (extending $\approx200$~kpc to the East and West of the galaxy 
 centre) or the CO, but in NGC~3100 the ionised gas is spatially 
@@
 Our calculated ionised gas masses are listed in
-Table~\ref{tab:derivedProp}. They are at the upper \removed{edge} 
-\added{range} of, and \removed{possibly} \added{occasionally} exceed, 
-{\bf (Why ``possibly''? They either always exceed, generally exceed, 
-occasionally exceed, or never exceed! Check and clarify.)} the 
+Table~\ref{tab:derivedProp}. They are at the upper 
+range of, and occasionally exceed, the 
 typical masses observed in ETGs 
@@
 
-{\bf (In the following paragraphs, as all $4$ galaxies are quite
-  famous (the first $3$ anyway), you should really quote the past
-  literature/papers when you discuss an aspect/feature/property that
-  has already been observed/shown/mentioned before, as many of these
-  aspects have. So do have a look at the literature on each object.)}
-
-\removed{\textbf{IC~1459} has ionised gas counter-rotating with respect to the
-stellar KDC, but it is also misaligned with respect to the outer stars
-of the host galaxy (i.e.\ the stars beyond the KDC), that are
-non-rotating (see Fig.~\ref{fig:ic1459}). The ionised gas thus appears
-to have a third, independent, axis of rotation.} {\bf (I do not
-  understand why you state/claim that here. From the map shown, it
-  seems pretty clear to me that the stars in the outer parts of the
-  galaxy {\em are} rotating (i.e.\ the top-left is red and the
-  bottom-right is blue), and that they are rotating in a manner
-  consistent with the ionised gas, just as \citet{Franx1988}
-  claimed. Convince me otherwise of change your statement!)} \removed{This is
-contrary to \citet{Franx1988} who claims that the rotation of the gas
-is aligned with that of the stars outside of the KDC. As the stellar
-disc did not survive the merger event that created the KDC, }{\bf (How
-  do you know there was a stellar disc to start with? Clarify or
-  rephrase.)} \removed{it is unlikely that the gas in the progenitor of IC~1459
-survived. However, the lost gas may have remained bound and been
-re-accreted, so that the gas observed today preserves a fossil record
-of the galaxy's original disc. Alternatively, the ISM may have yet
-another external origin.}
-
-\added{\textbf{IC~1459} has ionised gas co-rotating with the outer part (not the KDC) of the host galaxy \citep{Franx1988}.
+\textbf{IC~1459} has ionised gas co-rotating with the outer part (not the KDC) of the host galaxy \citep{Franx1988}.
 Whilst this is consistent with an internal origin of the gas, it should be noted that a major merger is typically expected to deplete a galaxy's gas reservoir.
 Either this did not happen in this case (a major merger being evidenced by the existence of the KDC) or as speculated by \citet{Prichard2019}, the observed result of IC~1459 is the product of multiple events e.g.
-the ISM may have an external origin and the apparent alignment of the gas and outer stars is random.}
+the ISM may have an external origin and the apparent alignment of the gas and outer stars is random.
 
@@
 $1\fdg0\pm0\fdg7$, thus consistent with an internal gas origin. This
-adds to the evidence {\bf (What is the other evidence?
-  Summarise/quote it or rephrase.)} that NGC~612 has not undergone a
+adds to the evidence that NGC~612 has not undergone a
 recent major merger (major mergers exhaust galaxies of their gas and
@@
 that a simple exponential disc model will not fit the data well.
-\added{\citet{Schweizer1980} noted that the projected axes of stellar and gas components are roughly perpendicular pointing to an external origin to the ISM \citep{Shklovskii1962}.
-Unfortunately we do not achieve a high enough $S/N$ to investigate the ionised gas in these regions.} \removed{We
-instead speculate that that the high-velocity peak to the South-West
-of the centre is an inflow towards the nucleus, {\bf (Is there any
-  evidence for this? If so, state them!)} almost perpendicular to the
-radio jet, although other interpretations are possible.} Better quality
+\citet{Schweizer1980} noted that the projected axes of stellar and gas components are roughly perpendicular pointing to an external origin to the ISM \citep{Shklovskii1962}.
+Unfortunately we do not achieve a high enough $S/N$ to investigate the ionised gas in these regions.
+Better quality
 data (better $S/N$ and a wider field of view) coupled with more
-sophisticated models are required to \removed{test this interpretation.}\added{interpret this data.}
+sophisticated models are required to interpret this data.
 % Nevertheless, it is clear that the gas in not in a settled disc.
@@
 \ce{^{12}CO(2-1)} integrated intensity contours (overlaid on the IFS
-maps in \removed{white} \added{cyan}; see Fig.~\ref{fig:ngc3100}) 
-{\bf (Again, no white
-  contours in the figure... pale blue/turquoise contours?)} show a
-broken ring, \added{with} the radio jet passing through the gaps\removed{, hence suggesting}\added{. This suggests }
+maps in cyan; see Fig.~\ref{fig:ngc3100}) show a
+broken ring, with the radio jet passing through the gaps. This suggests 
 a jet-ring interaction \citep[see][]{ruffa2019a, ruffa2019b}. The
@@
 interpretation, being completely different than that of the stars (and
-nearly totally blueshifted). \removed{The centre of rotation of the gas also
-appears to be offset from the centre of the galaxy (as defined by its
-stellar surface brightness), by several arcseconds to the west.} \added{What is clear, is that there is a complete lack of any large-scale rotation of the ISM.} {\bf
-  (I really do not understand how you can identify a centre of
-  rotation when there is no evidence of organised rotation at
-  all. Either convince me of that or remove/change that
-  comment. Perhaps mention the lack of obvious large-scale rotation
-  instead?!)}
+nearly totally blueshifted). What is clear, is that there is a complete lack of any large-scale rotation of the ISM.
 
@@
 sources (such as AGN) or extended sources (such as weak star formation
-or stars on the post-asymptotic giant branch, pAGB), {\bf (What about
-  extended horizontal branch stars (again below)? Mention/discuss.)}
+or stars on the post-asymptotic giant branch, pAGB),
 we examine the H$\alpha$ and H$\beta$ flux radial profiles of our
@@
 Section~\ref{subsubsec:Hb}). Finally, we use the mass\,--\,excitation
-(MEx) plot of \cite{Nyland2016}, using parameters derived from \added{a} 
-spectra \added{produced by} spatially-\removed{integrated}\added{integrating} over \added{a} central circular apertures of radius
-$3\arcsec$ \added{to probe} \removed{, thus probing only} the central 
+(MEx) plot of \cite{Nyland2016}, using parameters derived from a 
+spectra produced by spatially-integrating over a central circular apertures of radius
+$3\arcsec$ to probe the central 
 regions of the galaxies (see
-Section~\ref{subsubsec:MEx}). {\bf (You talked here of *the*
-  spatially-integrated spectra, as if spectra within a central
-  $3\arcsec$ aperture had been used before, but this is not the case
-  (only $2\arcsec$ and $1\arcsec$ apertures were used for stellar
-  populations). Are these new or previously-generated spectra?
-  Clarify.)} This allows us to classify the remaining galaxies (with
+Section~\ref{subsubsec:MEx}). This allows us to classify the remaining galaxies (with
 no spatially-extended ionised gas) into the star-forming, Seyfert~2,
@@
 AGN (labelled as LINER-AGN) and those whose LINER characteristics are
-not \added{(simply labelled as LINER: they may be AGN or LIER)}. 
-{\bf (Labelled as what? LIER?  Clarify.)} As the least
+not (simply labelled as LINER: they may be AGN or LIER). As the least
 conventional, we expand on the final two steps in the two sub-sections
@@
 \ref{tab:derivedProp}.
-
-% \subsection{BPT Diagnostics}
-% \label{subsec:BPT}
-% Firstly, in Fig.\,\ref{fig:BPT}, we examine our galaxies using the
-% classic BPT diagnostic plots. For the plots using
-% [\ion{N}{ii}]/H$\alpha$, [\ion{S}{ii}]/H$\alpha$ and
-% [\ion{O}{i}]/H$\alpha$ versus [\ion{O}{iii}]/H$\beta$, we can only
-% use the emission-line fluxes derived from our MUSE datacubes, as the
-% lines necessary for gauging the hardness of the ionising radiation
-% field are outside the spectral range of VIMOS. Only two MUSE
-% galaxies have detections of the necessary emission lines: IC~1459
-% and NGC~1316. Both occupy very similar positions in the BPT plots,
-% on or close to the boundary between the Seyfert 2 and LINER
-% classes. On the whole, the central bins tend to be on the LINER
-% side.
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=.9\textwidth]{chapter5/BPT.png}
-%   \caption[BPT plots]{BPT plots for IC~1459 and NGC~1316. The colour
-%   scale (blue to yellow) represents increasing distance from the
-%   galaxy centre. The classification boundaries are from
-%   \citet{Kewley2006}.\label{fig:BPT}}
-% \end{figure}
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.7\textwidth]{chapter5/SAURON.png}
-%   \caption[An alternative diagnostic plot]{SAURON diagnostic plot
-%   for the line ratios available in the VIMOS datacubes. To show the
-%   expected position of LINERs on the SAURON plot, the MAPPINGS-III
-%   shock model grid of \citet{Allen2008} is shown in green. The solid
-%   lines are lines of constant shock velocity (from 150 to
-%   1000\,$\mathrm{km\,s^{-1}}$) and the dotted lines are lines of
-%   constant magnetic parameter $b \equiv B/\sqrt{n}$ (from 0.5 to
-%   4.0), where $B$ is the magnetic field strength and $N$ the
-%   (pre-shock) particle number density \citep{Dopita1996}. All models
-%   assume an electron density of
-%   $n_\mathrm{e} = 1\,\mathrm{cm^{-3}}$.\label{fig:SAURON}}
-% \end{figure}
-
-% \citet{Sarzi2010} showed that Seyferts, LINERs and star-forming
-% galaxies are reasonable separated in the SAURON diagnostic plot. To
-% exploit the VIMOS datacubes we thus use the
-% [\ion{N}{ii}]\,--\,[\ion{N}{i}] relation derived in Section
-% \ref{subsec:Ndec}, along with the Balmer decrement, to transform the
-% \citet{Kewley2001} extreme starburst and the \citet{Kauffmann2003a}
-% pure star-formation boundaries in the [\ion{N}{ii}]/H$\alpha$ versus
-% [\ion{O}{iii}]/H$\beta$ plot to boundaries in the SAURON plot. For
-% the MUSE datacubes, only IC~1459 and NGC~1316 have detections of
-% [\ion{N}{i}]. Given that we already have the superior classic BPT
-% plots for these galaxies, we only show the VIMOS-derived SAURON
-% diagnostic plot. This is shown in Fig.\,\ref{fig:SAURON} for all 6
-% VIMOS galaxies with detectable, spatially-resolved emission
-% lines. All exhibit LINER-AGN behaviour.
-
-% NGC~3100 appears to occupy to distinct regions in the SAURON
-% diagnostic plot (Fig.\ \ref{fig:SAURON}). If the ionisation is due
-% to shocks from the impact of the jet, then using the shock models of
-% \citet{Allen2008}, we can see that the right-hand group of bins have
-% been ionised by a higher shock velocity that the left-hand group. As
-% can be seen in Fig.\ \ref{fig:ngc3100_NI_Hb}, these bins are
-% directly in the gap (presumable created by the jet blowing a hole)
-% in the CO ring.
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.5\textwidth]{chapter5/vimos/ngc3100_NI_Hb.png}
-%   \caption[NGC~3100 \bracket{\ion{N}{i}}/H$\beta$ line ratio
-%   map]{The [\ion{N}{i}]/H$\beta$ line ratio map of NGC~3100, showing
-%   the hardest ionisation field is in gap in the CO ring (white
-%   contours), spatially coincident with the radio jet (green
-%   contours). Surface brightness contours are in black.}
-%   \label{fig:ngc3100_NI_Hb}
-% \end{figure}
-
-% \subsection{WHaN2 Plots}
-% \label{subsec:WHaN2}
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.8\textwidth]{chapter5/WHaN2.png}
-%   \caption[WHaN2 plot for IC~4296]{WHaN2 plot for IC~4296. The
-%   colour scale (blue to yellow) represents increasing distance from
-%   the galaxy centre.}
-%   \label{fig:WHaN2}
-% \end{figure}
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.8\textwidth]{chapter5/WHbN1.png}
-%   \caption[VIMOS WHbN1 plot]{VIMOS WHbN1 plot. All galaxies have
-%   decreasing H$\beta$ emission with increasing distance from the
-%   galaxy centre.}
-%   \label{fig:WHbN1}
-% \end{figure}
-
-% The final spatially-resolved line ratio diagnostic plot that we use
-% is that of the equivalent width of H$\alpha$ versus
-% $\log([\text{\ion{N}{ii}}]/H\alpha)$, known as the WHaN2 plot
-% \citep{CidFernandes2011}. We interpret the strong AGN, weak AGN and
-% retired regions on this plot as Seyfert 2, LINER-AGN and LIER
-% classifications, respectively. Passive (i.e.\ line-less) galaxies
-% are marked with crosses instead of circles. Fig.\,\ref{fig:WHaN2}
-% shows the WHaN2 plot for the MUSE derived emission lines of IC~4296
-% where almost all the bins fall within the weak AGN (LINER-AGN)
-% class. This is consistent with the measurements from the VIMOS
-% observations of the IC~4296 as shown in the SAURON diagnostic plot,
-% where IC~4296 is well within the shocks grid (i.e.\ LINERs; see
-% Fig.\ \ref{fig:SAURON}). We do not include IC~1459 and NGC~1316, as
-% they have already been classified via the classic BPT plots (see
-% Section \ref{subsec:BPT}).
-
-% For the emission lines measured from the VIMOS datacubes, we use
-% H$\beta$ as a proxy for H$\alpha$ and [\ion{N}{i}] as a proxy for
-% [\ion{N}{ii}] utilising the relations found in Section
-% \ref{subsec:Ndec} to transform the classification boundaries (see
-% Section \ref{subsec:Ndec}). We call the resulting diagnostic plot
-% the WHbN1 plot, shown in Fig.\,\ref{fig:WHbN1}. While in Section
-% \ref{subsec:BPT} (Fig.\,\ref{fig:SAURON}) we showed that most of
-% these galaxies had line ratios consistent with being ionised by
-% shocks such as in LINER-like galaxies, Fig.\,\ref{fig:WHbN1} shows
-% that for IC~1459 and NGC~3100, the ionising photons originate from
-% the AGN.
 
@@
 non-circumnuclear stellar processes such as star formation or
-radiation from pAGB stars {\bf (Again.)}, as the dominant cause of the
+radiation from pAGB stars, as the dominant cause of the
 ionisation in the outer parts of the galaxy (i.e.\ a LIER rather than
@@
     $r^{-2}$, convolved with a Gaussian of width equal to the measured
-    PSF. \added{The fitting of these lines was done by eye.}{\bf (But what about the zero-points of the red profiles? How
-      are these set? Explain.)} {\bf (Make the axis labels and galaxy
-      names as thick as the plot boxes.) {\bf (All labels are rather
-        small. Enlarge?)} {\bf (Note that the bounding boxes of
-        Figs.~5 and 6 are really bad (much too big), so that the
-        ``width='' commands are useless. Please make sure {\em all}
-        your bounding boxes are as tight as possible around the
-        figures themselves.)}}
+    PSF. The fitting of these lines was done by eye.
     \label{fig:Ha_profile_MUSE}}
@@
   \caption{As Fig.~\ref{fig:Ha_profile_MUSE}, but for the H$\beta$
-    flux radial profiles derived from the VIMOS data. {\bf (Make the
-      axis labels and galaxy names as thick as the plot boxes.) {\bf
-        (All labels are rather small. Enlarge?)}}
+    flux radial profiles derived from the VIMOS data.
     \label{fig:Hb_profile_VIMOS}}
@@
 photons. The H$\beta$ profile of NGC~612 has a larger scatter,
-suggesting that stellar processes also have some impact (likely
-radiation from pAGB stars {\bf (Again.)}, as NGC~612 has a low
-star-formation rate). {\bf (Check what the SFR of NGC~612 actually is,
-  to confirm your suspicion, e.g.\ from non-nuclear radio continuum or
-  MIR/FIR emission. This may already be discussed in Ilaria's
-  papers.)}
+suggesting that stellar processes also have some impact. Indeed 
+\citet{Asabere2016} found NGC~612 to have a star formation rate an 
+order of magnitude high than that of NGC~1316.
 
@@
 radius $3\arcsec$ for all our Southern Sample galaxies. The resulting
-diagnostic plot is shown in Fig.~\ref{fig:MEx}.
+diagnostic plot is shown in Fig.~\ref{fig:MEx}. In particular, this 
+method allows us to classify NGC~1399 as a LINER (see 
+Table~\ref{tab:derivedProp}).
 
@@
     measurements of IC~1459 are linked by a black dashed
-    line. Classification boundaries are from \citet{Nyland2016}. {\bf
-      (Use larger data points.)} {\bf (Small ``f'' in ``Star-Forming''
-      label. Also add ``(km s$^{-1}$)'' to the x-axis label.)} {\bf
-      (All labels are rather small. Enlarge?)}}
+    line. Classification boundaries are from \citet{Nyland2016}.}
   \label{fig:MEx}
@@
 our sample shows a mixture of regularly- and non-regularly-rotating
-objects. \removed{Both classes also appear consistent with observations of the
-intrinsic shapes of ordinary regular and non-regular rotators.} {\bf (I
-  do not actually know/understand what you were trying to say or refer
-  to in the last sentence. Are you referring to the misalignment angle
-  $\Gamma_\text{kin}$ of regular and non-regular rotators? What do you
-  mean by ``observations of the intrinsic shapes''? Clarify.)} We
+objects. We
 established that two (tentatively three) galaxies host a large KDC. We
@@
 
-\removed{Radio-loud S0 galaxies are extremely rare, with only a handful of
-known cases \citep[e.g.][]{Heckman1982, Morganti2011}. This is
-presumably due to the mass functions of S0s and radio galaxies,
-massive S0s and low-mass radio galaxies both being rare, with similar
-transition masses from rare to more numerous. NGC~612 is one of those
-rare cases.} {\bf (You are not discussing here any of your own results,
-  just rehashing old knowledge, so unless you have something else to
-  say about NGC~612 (from your own work), I would suggest to remove
-  this paragraph entirely (and/or certainly move it somewhere else
-  more relevant).)}
-
 In terms of absorption line strengths and stellar populations
@@
 similar to that of \citet{Ziegler1997}. Most of the galaxies in our
-Southern Sample have typical ETG properties, with old, metal-rich
-stellar populations. {\bf (What about $\alpha$-elements? You should
-  also summarise those results here.)} The few exceptions are NGC~612
+Southern Sample have typical ETG properties, with old, metal-rich, alpha-enhanced
+stellar populations. The few exceptions are NGC~612
 and NGC~1316, that are both significantly younger than most ETGs, and
@@
 KDCs found in Section~\ref{sec:StarKine} are also in agreement with
-the KDC age\,--\,size relation found by \added{\citet{McDermid2006}} 
-\removed{\citet{Kuntschner2010}} in optically-selected ETGs (see 
-Section~\ref{subsec:popKDC}). {\bf (See my previous comment about 
-McDermid et al.\ 2006, and perhaps quote it here instead or 
-additionally.)}
+the KDC age\,--\,size relation found by \citet{McDermid2006} in optically-selected ETGs (see 
+Section~\ref{subsec:popKDC}).
 
@@
 no evidence of an extended ionising source consistent with ongoing
-star formation in any of our targets. {\bf (It seems to me that this
-  paragraph is missing a short ``conclusion''. Add one... no evidence
-  of any ongoing SF in any of our galaxies?)}
+star formation in any of our targets. We conclude, therefore,
+that the accretion is either turbulent or any star-formation is weak
+and consequently will not have a significant effect on the overall galactic
+evolution processes.
 
@@
 masses are not unexpected, but these masses are at the upper limit of,
-and \removed{possibly} \added{occasionally} exceed {\bf (Again, why ``possibly''? They either always
-  exceed, generally exceed, occasionally exceed, or never exceed!
-  Check and clarify.)}, the typical masses observed in ETGs,
+and occasionally exceed, the typical masses observed in ETGs,
 
@@
 The final galaxy, PKS~718-34, has no emission line detection (i.e.\ it
-is classified as passive). {\bf (These statistics do not match those
-  in paragraph 2 of Sub-section~8.1, where only $9$ galaxies are said
-  to be detected in ionised gas (rather than $10$ as inferred
-  here). The culprit seems to be NGC~1399, which is listed as
-  non-detected in Sub-section~8.1 and Appendix~A, has no emission line
-  map in Appendix~B, but is nevertheless classified as a LINER in
-  Table~4... how is this possible?! Check and fix/harmonise here, in
-  Sub-section~8.1, in Table~4, and in the second paragraph of
-  Appendix~A.)}
+is classified as passive).
 
@@
 Zieleniewski, private comm.); and \textsc{voronoi\_2d\_binning}
-\citep[including the SAURON \added{Colourmaps}\removed{colourmaps} 
-{\bf (Colourmaps, whatever that might be, or colour table? Clarify.)}; ][]{Cappellari2003}.
+\citep[including the SAURON Colourmaps; ][]{Cappellari2003}.
 
@@
 
-% The Balmer decrement, $d_\mathrm{H}$, is the ratio of the H$\alpha$
-% to H$\beta$ fluxes. There are good theoretical motivations for this
-% ratio to be near constant at $d_\mathrm{H} = 2.86$, under a wide
-% variety of conditions. In reality, however, higher values are
-% routinely observed. These can be explained as due to either the
-% presence of dust causing extinction (whereby emission lines at
-% shorter wavelengths appear dimmer than expected from their redder
-% counterparts due to dust preferentially scattering and absorbing
-% bluer light) or some mechanism that populates hydrogen levels from
-% the ground up. Such mechanisms may be important in high-density
-% environments, such as within powerful (type 1) AGN
-% \citep[e.g.][]{Shields1974, Netzer1975}.
-% 
-% The majority ($\approx 60$\%) of ETGs and all LINER and Seyfert
-% galaxies are dusty \citep[e.g.][]{Martini2013}.
-%
-% Such galaxies reveal clear dust lanes in \textit{Hubble Space
-% Telescope (HST)} observations \citep[e.g.][]{Martini2013}, are
-% bright in the infrared (where the thermal emission from dust is seen
-% as a dust ``bump''; e.g.\ \citealt{Jura1987, Knapp1992}), and
-% possess other emission lines \citep[e.g.\
-% \bracket{\ion{S}{ii}};][]{Wampler1968} showing similar
-% reddening. Thus, assuming the observed steepening of the Balmer
-% decrement is entirely due to dust, the ratio of the observed
-% decrement to the theoretical value of 2.86 is a good estimate of the
-% dust reddening.
-
-\removed{Generally, } If we assume that the different ionisation states of a
-given atomic species\added{, observed along the same line-of-sight,} occur in 
-the same spatial location \added{(and therefore are produced under the same 
-conditions)}\removed{, then shielding by dust is not important or at worst its 
-effect on the emission-line ratios is linear.} \textbf{(Why is the effect only 
-linear? Justify.)} \removed{Given that the different states are then produced under
-the same conditions,} it is natural to expect a simple relationship
+If we assume that the different ionisation states of a
+given atomic species, observed along the same line-of-sight, occur in 
+the same spatial location (and therefore are produced under the same 
+conditions) it is natural to expect a simple relationship
 between their emission line fluxes, similar to that of the Balmer
@@
 
-{\bf (There is something very wrong about this last set of
-  equations. First, since you presumably want to infer
-  $\frac{[\text{\ion{N}{i}}]}{H\beta}$ from
-  $\frac{[\text{\ion{N}{iI}}]}{H\alpha}$ and EW(H$\beta$) from
-  EW(H$\alpha$), why not report (and presumably fit for in the first
-  place) the inverse of the Eqs.~A1 and A2. Second, you have switched
-  $\frac{[\text{\ion{N}{i}}]}{H\beta}$ and
-  $\frac{[\text{\ion{N}{iI}}]}{H\alpha}$ in Eq.~A3, which is clearly
-  wrong. You should probably switch them back. In addition, the
-  conditions stated in Eq.~A3 make no sense. Presumably, one should
-  follow the relation until $\frac{[\text{\ion{N}{i}}]}{H\beta}=0$,
-  and then leave it at $0$. In any case, these equations need to be
-  fixed.) JW: Fixed - note the method I am using for highlighting does not let me highlight within an equation environment so only the new version is shown.}
-
 \begin{figure}
@@
     residuals, defined as ([\ion{N}{ii}]/H$\alpha$ -
-    best-fit)/[\ion{N}{i}]/H$\beta$. {\bf (Why do you divide by
-      [\ion{N}{i}]/H$\beta$ rather than by [\ion{N}{ii}]/H$\alpha$?
-      Change?)}  The solid lines show the best-fitting
+    best-fit)/[\ion{N}{i}]/H$\beta$. The solid lines show the best-fitting
     Eq.~\ref{eq:N_dec}, while the dashed and dotted lines show
-    respectively the $68$ and $99\%$ probability contours. {\bf (The
-      bottom y-axis label should be ``Fractional residual''.)}}
+    respectively the $68$ and $99\%$ probability contours.}
   \label{fig:ratio_relation}
@@
     Fig.~\ref{fig:ratio_relation}, but for EW(H$\alpha$) vs.\
-    EW(H$\beta$). {\bf (The bottom y-axis label should be ``Fractional
-      residual''.)}}
+    EW(H$\beta$).}
   \label{fig:EqW_relation}
@@
     in the top-left corner of each panel, and the colour scale limits
-    are listed in the bottom-right corner of each panel. {\bf (Why are
-      these not perfect fits to the bottom-right corners? Fix?)} The
+    are listed in the bottom-right corner of each panel. The
     surface brightness (isophotes) are overlaid as black contours in
     all the maps, while the \ce{^{12}CO(2-1)} contours from ALMA are
-    overlaid in \removed{white} \added{cyan} {\bf (Pale blue or 
-    turquoise? Correct.)} and the
+    overlaid in cyan and the
     radio continuum contours from the VLA are overlaid in green. The
     radio band displayed depends on the data and angular resolution
-    available \citep[see][]{ruffa2019a, ruffa2019b}. {\bf
-      (``Metalicity'' should be ``Metallicity''. Also explain the
-      meaning of the pale and dark greys bins.)}}
+    available \citep[see][]{ruffa2019a, ruffa2019b}.}
       % Preferable to rotate the colour table by $180$ deg, to match

### 2020-11-16 paper.tex
Final changes (in this round)
 On branch master
 Changes to be committed:
	modified:   paper.tex
	modified:   paper_noComments.tex
	modified:   refs.bib

@@
 % Keep the title short and informative.
-\title[IFS Study of Low-power Radio Galaxies]{An Integral-field
-  Spectroscopic Study of Low-power Radio Galaxies}
+\title[IFS Study of Low-power Radio Galaxies]{The AGN fuelling/feedback cycle in 
+nearby radio galaxies - VI. Visible light IFU observations and results}
 
@@
     though. Also needed are updated affiliations for Francesco and
-    Robert. JW: not deliberate - I'd left this to ask you about who to include.}}
+    Robert.}\\ {\bf JW: not deliberate - I'd left this to ask you about who to include.
+    On the title are we up to paper IV? Just checking I haven't missed one!}\\ {\bf Also any ideas for a better title?}}
 
@@
 % Enter the current year, for the copyright statements etc.
-\pubyear{2018}
+\pubyear{2020}
 
@@
   \ref{subsec:absorption} but not \ref{subsec:EmissionLines}?
-  Clarify.)}} \added{(i.e.\ Sections~\ref{subsec:starKin})}, the wavelength range of the NGC~1316 spectra was
-restricted to $<5800$~\AA. \added{The best-fitting stellar spectra were then extrapolated above 5800~\AA.}
+  Clarify.)} \added{(i.e.\ Sections~\ref{subsec:starKin})}, the wavelength range 
+of the NGC~1316 spectra was restricted to $<5800$~\AA. \added{The best-fitting 
+stellar spectra were then extrapolated above 5800~\AA.}
 
@@
 \removed{$\mathrm{[Fe/H]}=0.12\pm0.01$}\added{$\mathrm{[M/H]}=0.12\pm0.01$} \removed{for an aperture covering the central
-$0.1$~kpc)}`added{using a long slit with width $1\arcsec$ and length $0.1$~kpc)}. {\bf (Is that a circular or square aperture? If circular,
+$0.1$~kpc)}\added{using a long slit with width $1\arcsec$ and length $0.1$~kpc)}. {\bf (Is that a circular or square aperture? If circular,
   is $0.1$~kpc the radius or diameter? Clarify.)} We also find NGC~612
@@
 
-\removed{As can be seen from the maps in Appendix~\ref{sec:maps}, 
-both NGC~612 and NGC~3100 have significant off-centred ionised 
-gas emission.} {\bf (What do you mean by ``significant'' here? Bright?
+As can be seen from the maps in Appendix~\ref{sec:maps}, 
+both NGC~612 and NGC~3100 have \removed{significant off-centred ionised 
+gas emission.} \added{ionised gas emission offset from the center of the 
+galaxy.} {\bf (What do you mean by ``significant'' here? Bright?
   Clarify. Equivalently, why is the off-centred emission in IC~1459
-  and NGC~1316 not considered significant?)} 
-\added{The ionised gas emission for both NGC~612 ).} In NGC~612, 
+  and NGC~1316 not considered significant?)} In NGC~612, 
 the ionised gas does not appear related to either the radio jet 
@@
 photons. The H$\beta$ profile of NGC~612 has a larger scatter,
-suggesting that stellar processes also have some impact (likely
+suggesting that stellar processes also have some impact. \added{Indeed 
+\citet{Asabere2016} found NGC~612 to have a star formation rate an 
+order of magnitude high than that of NGC~1316.} \removed{(likely
 radiation from pAGB stars {\bf (Again.)}, as NGC~612 has a low
-star-formation rate). {\bf (Check what the SFR of NGC~612 actually is,
+star-formation rate).} {\bf (Check what the SFR of NGC~612 actually is,
   to confirm your suspicion, e.g.\ from non-nuclear radio continuum or
@@
 radius $3\arcsec$ for all our Southern Sample galaxies. The resulting
-diagnostic plot is shown in Fig.~\ref{fig:MEx}.
+diagnostic plot is shown in Fig.~\ref{fig:MEx}. \added{In particular, this 
+method allows us to classify NGC~1399 as a LINER (see 
+Table~\ref{tab:derivedProp}).}
 
@@
 similar to that of \citet{Ziegler1997}. Most of the galaxies in our
-Southern Sample have typical ETG properties, with old, metal-rich
+Southern Sample have typical ETG properties, with old, metal-rich\added{, alpha-enhanced}
 stellar populations. {\bf (What about $\alpha$-elements? You should
@@
 paragraph is missing a short ``conclusion''. Add one... no evidence
-  of any ongoing SF in any of our galaxies?)}
+of any ongoing SF in any of our galaxies?)} \added{We conclude, therefore,
+that the accretion is either turbulent or any star-formation is weak
+and consequently will not have a significant effect on the overall galactic
+evolution processes.}
 
@@
   exceed, generally exceed, occasionally exceed, or never exceed!
-  Check and clarify.)}, the typical masses observed in ETGs,
+  Check and clarify.)}, the typical masses observed in ETGs.
 
@@
   Sub-section~8.1, in Table~4, and in the second paragraph of
-  Appendix~A.)}
+  Appendix~A.). JW: NGC~1399 is classified using the MEx plot in 
+  Section~8.3.2. I've added a sentence in that section to make that
+  explicit.}
 

### 2020-11-16 paper_noComments.tex
Final changes (in this round)
 On branch master
 Changes to be committed:
	modified:   paper.tex
	modified:   paper_noComments.tex
	modified:   refs.bib

@@
     \href{mailto:warrenj@gmx.com}{warrenj@gmx.com}}
-%Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:joshua.warren@physics.ox.ac.uk}{joshua.warren@physics.ox.ac.uk}}
   Martin Bureau,$^{1,2}$ Bernd Hasemann,$^{3}$ Ilaria Ruffa,$^{4}$ Isabella
@@
   Bologna, Italy\\
-  $^{5}$School of Physics \& Astronomy, Cardiff University, Queens Buildings, The Parade, Cardiff CF24 3AA, UK
+  $^{5}$School of Physics \& Astronomy, Cardiff University, Queens Buildings, The Parade, Cardiff CF24 3AA, UK}
 
@@
 where $A_\text{s}$ is the area contained within 
-the field of view of the given ellipse. {\it For a given galaxy, we fit ellipses 
+the field of view of the given ellipse. For a given galaxy, we fit ellipses 
 as described above, up to $R_\text{m}=R_\text{max}$, where 
@@
 \equiv 0.15$ or $R_\text{max} = R_\text{e}$, which ever is smallest.
-} The value $\epsilon_\text{e}$, the ellipticity of this largest 
+The value $\epsilon_\text{e}$, the ellipticity of this largest 
 fitted ellipse, is given in Column~3 of 
@@
 indicated by the solid black line, with a gradient of
-$3.3\pm1.0$~\AA~dex$^{-1}$. We noted that NGC~1316 is again ana possible
+$3.3\pm1.0$~\AA~dex$^{-1}$. We noted that NGC~1316 is again an
 outlier. Excluding NGC~1316 from the fit
@@
 masses are not unexpected, but these masses are at the upper limit of,
-and occasionally exceed, the typical masses observed in ETGs,
+and occasionally exceed, the typical masses observed in ETGs.
 
